### 2022-05-15 paper.tex
Updated paper.tex

\documentclass{article}

%Neurips Template Comments:
	% if you need to pass options to natbib, use, e.g.:
	%     \PassOptionsToPackage{numbers, compress}{natbib}
	% before loading neurips_2022

	% ready for submission
	% \usepackage{neurips_2022}

	% to compile a preprint version, e.g., for submission to arXiv, add add the
	% [preprint] option:
			% \usepackage[preprint]{neurips_2022}

	% to compile a camera-ready version, add the [final] option, e.g.:
	\usepackage[final]{neurips_2022}

	% to avoid loading the natbib package, add option nonatbib:
	%    \usepackage[nonatbib]{neurips_2022}

%Neurips Template Packages
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors

%Ryan Packages
\usepackage{graphicx}       % images
\graphicspath{ {./images/} }

\title{TRITON: Texture Recovering Image Translation Network [[TODO Make catchier]]}

\author{%
	Ryan Burgert \\
	Department of Computer Science\\
	Stony Brook University\\
	Stony Brook, NY 11794 \\
	\texttt{rburgert@cs.stonybrook.edu} \\
	% \And
	% Michael Ryoo \\
	% Department of Computer Science\\
	% Stony Brook University\\
	% Stony Brook, NY 11794 \\
	% \texttt{mryoo@cs.stonybrook.edu} \\
}

\begin{document}

\maketitle

\begin{abstract}
	Image translation has been succesful in improving benchmarks in robotic reinforcement learning.
	Current unpaired sim to real image translation algorithms are not globally temporally consistent. 
	These techniques do not leverage the latent 3d geometry that creates the input images.
	Much of the content in photographs can be approximated as albedo maps on the surfaces of 3d objects.
	In this paper, we combine differentiable rendering with image translation to recover the textures of 3d objects.
	This algorithm takes advantage of the input geometry by projecting learnable textures onto their surfaces, before feeding it into an image translation algorithm.
	With the addition of certain losses, we achieve temporal consistency without using temporal queues (such as optical flow etc...reword this sentence?).
	Previous algorithms that have tried to perform unpaired image translation using neural textures have been limited to camera movements.
	In contrast, this algorithm can handle the movements of objects in the scene, which is useful for downstream tasks such as robotic manipulation.
	Our experiments show that in addition to achieving higher temporal consistency, the accuracy of the translations with respect to ground truth photographs is improved by this approach.
\end{abstract}

\section{Submission of papers to NeurIPS 2022}

Please read the instructions below carefully and follow them faithfully.

\subsection{Style}

Papers to be submitted to NeurIPS 2022 must be prepared according to the
instructions presented here. Papers may only be up to {\bf nine} pages long,
including figures. Additional pages \emph{containing only acknowledgments and
	references} are allowed. Papers that exceed the page limit will not be
reviewed, or in any other way considered for presentation at the conference.

The margins in 2022 are the same as those in 2007, which allow for $\sim$$15\%$
more words in the paper compared to earlier years.

Authors are required to use the NeurIPS \LaTeX{} style files obtainable at the
NeurIPS website as indicated below. Please make sure you use the current files
and not previous versions. Tweaking the style files may be grounds for
rejection.

\subsection{Retrieval of style files}

The style files for NeurIPS and other conference information are available on
the World Wide Web at
\begin{center}
	\url{http://www.neurips.cc/}
\end{center}
The file \verb+neurips_2022.pdf+ contains these instructions and illustrates the
various formatting requirements your NeurIPS paper must satisfy.

The only supported style file for NeurIPS 2022 is \verb+neurips_2022.sty+,
rewritten for \LaTeXe{}.  \textbf{Previous style files for \LaTeX{} 2.09,
	Microsoft Word, and RTF are no longer supported!}

The \LaTeX{} style file contains three optional arguments: \verb+final+, which
creates a camera-ready copy, \verb+preprint+, which creates a preprint for
submission to, e.g., arXiv, and \verb+nonatbib+, which will not load the
\verb+natbib+ package for you in case of package clash.

\paragraph{Preprint option}
If you wish to post a preprint of your work online, e.g., on arXiv, using the
NeurIPS style, please use the \verb+preprint+ option. This will create a
nonanonymized version of your work with the text ``Preprint. Work in progress.''
in the footer. This version may be distributed as you see fit. Please \textbf{do
	not} use the \verb+final+ option, which should \textbf{only} be used for
papers accepted to NeurIPS.

At submission time, please omit the \verb+final+ and \verb+preprint+
options. This will anonymize your submission and add line numbers to aid
review. Please do \emph{not} refer to these line numbers in your paper as they
will be removed during generation of camera-ready copies.

The file \verb+neurips_2022.tex+ may be used as a ``shell'' for writing your
paper. All you have to do is replace the author, title, abstract, and text of
the paper with your own.

The formatting instructions contained in these style files are summarized in
Sections \ref{gen_inst}, \ref{headings}, and \ref{others} below.

\section{General formatting instructions}
\label{gen_inst}

The text must be confined within a rectangle 5.5~inches (33~picas) wide and
9~inches (54~picas) long. The left margin is 1.5~inch (9~picas).  Use 10~point
type with a vertical spacing (leading) of 11~points.  Times New Roman is the
preferred typeface throughout, and will be selected for you by default.
Paragraphs are separated by \nicefrac{1}{2}~line space (5.5 points), with no
indentation.

The paper title should be 17~point, initial caps/lower case, bold, centered
between two horizontal rules. The top rule should be 4~points thick and the
bottom rule should be 1~point thick. Allow \nicefrac{1}{4}~inch space above and
below the title to rules. All pages should start at 1~inch (6~picas) from the
top of the page.

For the final version, authors' names are set in boldface, and each name is
centered above the corresponding address. The lead author's name is to be listed
first (left-most), and the co-authors' names (if different address) are set to
follow. If there is only one co-author, list both author and co-author side by
side.

Please pay special attention to the instructions in Section \ref{others}
regarding figures, tables, acknowledgments, and references.

\section{Headings: first level}
\label{headings}

All headings should be lower case (except for first word and proper nouns),
flush left, and bold.

First-level headings should be in 12-point type.

\subsection{Headings: second level}

Second-level headings should be in 10-point type.

\subsubsection{Headings: third level}

Third-level headings should be in 10-point type.

\paragraph{Paragraphs}

There is also a \verb+\paragraph+ command available, which sets the heading in
bold, flush left, and inline with the text, with the heading followed by 1\,em
of space.

\section{Citations, figures, tables, references}
\label{others}

These instructions apply to everyone.

\subsection{Citations within the text}

The \verb+natbib+ package will be loaded for you by default.  Citations may be
author/year or numeric, as long as you maintain internal consistency.  As to the
format of the references themselves, any style is acceptable as long as it is
used consistently.

The documentation for \verb+natbib+ may be found at
\begin{center}
	\url{http://mirrors.ctan.org/macros/latex/contrib/natbib/natnotes.pdf}
\end{center}
Of note is the command \verb+\citet+, which produces citations appropriate for
use in inline text.  For example,
\begin{verbatim}
	 \citet{hasselmo} investigated\dots
\end{verbatim}
produces
\begin{quote}
	Hasselmo, et al.\ (1995) investigated\dots
\end{quote}

If you wish to load the \verb+natbib+ package with options, you may add the
following before loading the \verb+neurips_2022+ package:
\begin{verbatim}
	 \PassOptionsToPackage{options}{natbib}
\end{verbatim}

If \verb+natbib+ clashes with another package you load, you can add the optional
argument \verb+nonatbib+ when loading the style file:
\begin{verbatim}
	 \usepackage[nonatbib]{neurips_2022}
\end{verbatim}

As submission is double blind, refer to your own published work in the third
person. That is, use ``In the previous work of Jones et al.\ [4],'' not ``In our
previous work [4].'' If you cite your other papers that are not widely available
(e.g., a journal paper under review), use anonymous author names in the
citation, e.g., an author of the form ``A.\ Anonymous.''

\subsection{Footnotes}

Footnotes should be used sparingly.  If you do require a footnote, indicate
footnotes with a number\footnote{Sample of the first footnote.} in the
text. Place the footnotes at the bottom of the page on which they appear.
Precede the footnote with a horizontal rule of 2~inches (12~picas).

Note that footnotes are properly typeset \emph{after} punctuation
marks.\footnote{As in this example.}

\subsection{Figures}

\begin{figure}
	\centering
	\fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
	\caption{Sample figure caption.}
\end{figure}

All artwork must be neat, clean, and legible. Lines should be dark enough for
purposes of reproduction. The figure number and caption always appear after the
figure. Place one line space before the figure caption and one line space after
the figure. The figure caption should be lower case (except for first word and
proper nouns); figures are numbered consecutively.

You may use color figures.  However, it is best for the figure captions and the
paper body to be legible if the paper is printed in either black/white or in
color.

\subsection{Tables}

All tables must be centered, neat, clean and legible.  The table number and
title always appear before the table.  See Table~\ref{sample-table}.

Place one line space before the table title, one line space after the
table title, and one line space after the table. The table title must
be lower case (except for first word and proper nouns); tables are
numbered consecutively.

Note that publication-quality tables \emph{do not contain vertical rules.} We
strongly suggest the use of the \verb+booktabs+ package, which allows for
typesetting high-quality, professional tables:
\begin{center}
	\url{https://www.ctan.org/pkg/booktabs}
\end{center}
This package was used to typeset Table~\ref{sample-table}.

\begin{table}
	\caption{Sample table title}
	\label{sample-table}
	\centering
	\begin{tabular}{lll}
		\toprule
		\multicolumn{2}{c}{Part}                   \\
		\cmidrule(r){1-2}
		Name     & Description     & Size ($\mu$m) \\
		\midrule
		Dendrite & Input terminal  & $\sim$100     \\
		Axon     & Output terminal & $\sim$10      \\
		Soma     & Cell body       & up to $10^6$  \\
		\bottomrule
	\end{tabular}
\end{table}

\section{Final instructions}

Do not change any aspects of the formatting parameters in the style files.  In
particular, do not modify the width or length of the rectangle the text should
fit into, and do not change font sizes (except perhaps in the
\textbf{References} section; see below). Please note that pages should be
numbered.

\section{Preparing PDF files}

Please prepare submission files with paper size ``US Letter,'' and not, for
example, ``A4.''

Fonts were the main cause of problems in the past years. Your PDF file must only
contain Type 1 or Embedded TrueType fonts. Here are a few instructions to
achieve this.

\begin{itemize}

\item You should directly generate PDF files using \verb+pdflatex+.

\item You can check which fonts a PDF files uses.  In Acrobat Reader, select the
	menu Files$>$Document Properties$>$Fonts and select Show All Fonts. You can
	also use the program \verb+pdffonts+ which comes with \verb+xpdf+ and is
	available out-of-the-box on most Linux machines.

\item The IEEE has recommendations for generating PDF files whose fonts are also
	acceptable for NeurIPS. Please see
	\url{http://www.emfield.org/icuwb2010/downloads/IEEE-PDF-SpecV32.pdf}

\item \verb+xfig+ "patterned" shapes are implemented with bitmap fonts.  Use
	"solid" shapes instead.

\item The \verb+\bbold+ package almost always uses bitmap fonts.  You should use
	the equivalent AMS Fonts:
\begin{verbatim}
	 \usepackage{amsfonts}
\end{verbatim}
followed by, e.g., \verb+\mathbb{R}+, \verb+\mathbb{N}+, or \verb+\mathbb{C}+
for $\mathbb{R}$, $\mathbb{N}$ or $\mathbb{C}$.  You can also use the following
workaround for reals, natural and complex:
\begin{verbatim}
	 \newcommand{\RR}{I\!\!R} %real numbers
	 \newcommand{\Nat}{I\!\!N} %natural numbers
	 \newcommand{\CC}{I\!\!\!\!C} %complex numbers
\end{verbatim}
Note that \verb+amsfonts+ is automatically loaded by the \verb+amssymb+ package.

\end{itemize}

If your file contains type 3 fonts or non embedded TrueType fonts, we will ask
you to fix it.

\subsection{Margins in \LaTeX{}}

Most of the margin problems come from figures positioned by hand using
\verb+\special+ or other commands. We suggest using the command
\verb+\includegraphics+ from the \verb+graphicx+ package. Always specify the
figure width as a multiple of the line width as in the example below:
\begin{verbatim}
	 \usepackage[pdftex]{graphicx} ...
	 \includegraphics[width=0.8\linewidth]{myfile.pdf}
\end{verbatim}
See Section 4.4 in the graphics bundle documentation
(\url{http://mirrors.ctan.org/macros/latex/required/graphics/grfguide.pdf})

A number of width problems arise when \LaTeX{} cannot properly hyphenate a
line. Please give LaTeX hyphenation hints using the \verb+\-+ command when
necessary.

\begin{ack}
Use unnumbered first level headings for the acknowledgments. All acknowledgments
go at the end of the paper before the list of references. Moreover, you are required to declare
funding (financial activities supporting the submitted work) and competing interests (related financial activities outside the submitted work).
More information about this disclosure can be found at: \url{https://neurips.cc/Conferences/2022/PaperInformation/FundingDisclosure}.

Do {\bf not} include this section in the anonymized submission, only in the final paper. You can use the \texttt{ack} environment provided in the style file to autmoatically hide this section in the anonymized submission.
\end{ack}

\section*{References}

References follow the acknowledgments. Use unnumbered first-level heading for
the references. Any choice of citation style is acceptable as long as you are
consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
when listing the references.
Note that the Reference section does not count towards the page limit.
\medskip

{
\small

[1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms for
connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and T.K.\ Leen
(eds.), {\it Advances in Neural Information Processing Systems 7},
pp.\ 609--616. Cambridge, MA: MIT Press.

[2] Bower, J.M.\ \& Beeman, D.\ (1995) {\it The Book of GENESIS: Exploring
	Realistic Neural Models with the GEneral NEural SImulation System.}  New York:
TELOS/Springer--Verlag.

[3] Hasselmo, M.E., Schnell, E.\ \& Barkai, E.\ (1995) Dynamics of learning and
recall at excitatory recurrent synapses and cholinergic modulation in rat
hippocampal region CA3. {\it Journal of Neuroscience} {\bf 15}(7):5249-5262.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Checklist}

%%% BEGIN INSTRUCTIONS %%%
The checklist follows the references.  Please
read the checklist guidelines carefully for information on how to answer these
questions.  For each question, change the default \answerTODO{} to \answerYes{},
\answerNo{}, or \answerNA{}.  You are strongly encouraged to include a {\bf
justification to your answer}, either by referencing the appropriate section of
your paper or providing a brief inline description.  For example:
\begin{itemize}
	\item Did you include the license to the code and datasets? \answerYes{See Section~\ref{gen_inst}.}
	\item Did you include the license to the code and datasets? \answerNo{The code and the data are proprietary.}
	\item Did you include the license to the code and datasets? \answerNA{}
\end{itemize}
Please do not modify the questions and only use the provided macros for your
answers.  Note that the Checklist section does not count towards the page
limit.  In your paper, please delete this instructions block and only keep the
Checklist section heading above along with the questions/answers below.
%%% END INSTRUCTIONS %%%

\begin{enumerate}

\item For all authors...
\begin{enumerate}
	\item Do the main claims made in the abstract and introduction accurately reflect the paper's contributions and scope?
	      \answerTODO{}
	\item Did you describe the limitations of your work?
	      \answerTODO{}
	\item Did you discuss any potential negative societal impacts of your work?
	      \answerTODO{}
	\item Have you read the ethics review guidelines and ensured that your paper conforms to them?
	      \answerTODO{}
\end{enumerate}

\item If you are including theoretical results...
\begin{enumerate}
	\item Did you state the full set of assumptions of all theoretical results?
	      \answerTODO{}
	\item Did you include complete proofs of all theoretical results?
	      \answerTODO{}
\end{enumerate}

\item If you ran experiments...
\begin{enumerate}
	\item Did you include the code, data, and instructions needed to reproduce the main experimental results (either in the supplemental material or as a URL)?
		\answerTODO{}
	\item Did you specify all the training details (e.g., data splits, hyperparameters, how they were chosen)?
		\answerTODO{}
				\item Did you report error bars (e.g., with respect to the random seed after running experiments multiple times)?
		\answerTODO{}
				\item Did you include the total amount of compute and the type of resources used (e.g., type of GPUs, internal cluster, or cloud provider)?
		\answerTODO{}
\end{enumerate}

\item If you are using existing assets (e.g., code, data, models) or curating/releasing new assets...
\begin{enumerate}
	\item If your work uses existing assets, did you cite the creators?
	      \answerTODO{}
	\item Did you mention the license of the assets?
	      \answerTODO{}
	\item Did you include any new assets either in the supplemental material or as a URL?
	      \answerTODO{}
	\item Did you discuss whether and how consent was obtained from people whose data you're using/curating?
	      \answerTODO{}
	\item Did you discuss whether the data you are using/curating contains personally identifiable information or offensive content?
	      \answerTODO{}
\end{enumerate}

\item If you used crowdsourcing or conducted research with human subjects...
\begin{enumerate}
	\item Did you include the full text of instructions given to participants and screenshots, if applicable?
	      \answerTODO{}
	\item Did you describe any potential participant risks, with links to Institutional Review Board (IRB) approvals, if applicable?
	      \answerTODO{}
	\item Did you include the estimated hourly wage paid to participants and the total amount spent on participant compensation?
	      \answerTODO{}
\end{enumerate}

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendix

\section{Appendix}

Optionally include extra information (complete proofs, additional experiments and plots) in the appendix.
This section will often be part of the supplemental material.

\end{document}

### 2022-05-16 paper.tex
Added new abstract

@@
 \begin{abstract}
-	Image translation has been succesful in improving benchmarks in robotic reinforcement learning.
-	Current unpaired sim to real image translation algorithms are not globally temporally consistent. 
-	These techniques do not leverage the latent 3d geometry that creates the input images.
-	Much of the content in photographs can be approximated as albedo maps on the surfaces of 3d objects.
-	In this paper, we combine differentiable rendering with image translation to recover the textures of 3d objects.
-	This algorithm takes advantage of the input geometry by projecting learnable textures onto their surfaces, before feeding it into an image translation algorithm.
-	With the addition of certain losses, we achieve temporal consistency without using temporal queues (such as optical flow etc...reword this sentence?).
-	Previous algorithms that have tried to perform unpaired image translation using neural textures have been limited to camera movements.
-	In contrast, this algorithm can handle the movements of objects in the scene, which is useful for downstream tasks such as robotic manipulation.
-	Our experiments show that in addition to achieving higher temporal consistency, the accuracy of the translations with respect to ground truth photographs is improved by this approach.
+	Unpaired image translation algorithms can be used for sim-to-real tasks, but they often fail to generate temporally consistent results.
+	Because of this, the details or even identity of a particular object might change as it moves across a scene.
+	We present a new approach that combines differential rendering with image translation to achieve temporal consistency over indefinite timescales.
+	We call this algorithm TRITON (Texture Recovering Image Translation Network): an unsupervised, end-to-end, stateless sim-to-real algorithm.
+	Unlike previous techniques, TRITON leverages the underlying 3d geometry of input scenes by generating realistic-looking learnable neural textures.
+	These textures are projected onto the surfaces of input scenes, which are then fed through an image translation network to obtain the final outputs.
+	By settling on a particular albedo for the objects in a scene, we ensure consistency between frames statelessly [[ie. no need for optical flow]].
+	Unlike previous algorithms, TRITON is not limited to camera movements - it can handle the movement of objects as well, making it useful for downstream tasks such as robotic manipulation.
+	Our experiments show that in addition to achieving higher temporal consistency, the translations are closer to ground truth photographs than previous techniques.
 \end{abstract}

### 2022-05-16 paper.tex
Added new abstract

@@
 	We present a new approach that combines differential rendering with image translation to achieve temporal consistency over indefinite timescales.
-	We call this algorithm TRITON (Texture Recovering Image Translation Network): an unsupervised, end-to-end, stateless sim-to-real algorithm.
+	We call this algorithm TRITON (Texture Recovering Image Translation Network): an unsupervised, end-to-end, stateless sim-to-real algorithm. [[Too many adjectives?]]
 	Unlike previous techniques, TRITON leverages the underlying 3d geometry of input scenes by generating realistic-looking learnable neural textures.
 	These textures are projected onto the surfaces of input scenes, which are then fed through an image translation network to obtain the final outputs.
-	By settling on a particular albedo for the objects in a scene, we ensure consistency between frames statelessly [[ie. no need for optical flow]].
+	By settling on particular albedos for scene objects, we ensure consistency between frames statelessly. [[ie. no need for optical flow]]
+	In addition, we introduce a translation consistency loss that further improves the consistency of the results.
+[[I called this “view consistency loss” in the code and to you, but translation consistency loss might be a better name?
+What do you think?]]
 	Unlike previous algorithms, TRITON is not limited to camera movements - it can handle the movement of objects as well, making it useful for downstream tasks such as robotic manipulation.

### 2022-05-16 paper.tex
Added Emmy!

--- 2022-05-16 paper.tex
@@
 
-\title{TRITON: Texture Recovering Image Translation Network [[TODO Make catchier]]}
+\title{TRITON: Learning to Recover Textures through Image Translation}
 
@@
 	% \texttt{mryoo@cs.stonybrook.edu} \\
+	\And
+	Emma Burgert \\
+	Ryan Burgert's Dog\\
 }
@@
 \begin{abstract}
-	Unpaired image translation algorithms can be used for sim-to-real tasks, but they often fail to generate temporally consistent results.
+	Unpaired image translation algorithms can be used for sim-to-real tasks, but most fail to generate temporally consistent results.
 	Because of this, the details or even identity of a particular object might change as it moves across a scene.

### 2022-05-29 paper.tex
Changed the paper title
paper.tex: Removed [[a thing like this]] from abstract

@@
 
-\title{TRITON: Learning to Recover Textures through Image Translation}
+\title{TRITON: Torwards Globally Consistent Sim-to-Real Transfer}
 
@@
 	These textures are projected onto the surfaces of input scenes, which are then fed through an image translation network to obtain the final outputs.
-	By settling on a particular albedo for the objects in a scene, we ensure consistency between frames statelessly [[ie. no need for optical flow]].
+	By settling on a particular albedo for the objects in a scene, we ensure consistency between frames statelessly.
 	Unlike previous algorithms, TRITON is not limited to camera movements - it can handle the movement of objects as well, making it useful for downstream tasks such as robotic manipulation.

### 2022-06-02 UnprojectPseudoCode.py
Added UnprojectPseudoCode.py

@@ -1,0 +1,30 @@
+UVL: CHW (UVL)
+I: CHW (RGB)
+OUT: LC,OH,OW
+
+
+# IH, IW = (input height, input width)
+# OH, OW = (output height, output width)
+# NL = (number of labels aka number of textures)
+
+#Assume the image's values and UVL values range between 0 and 1.
+IH,IW=256,256 #During training, the algorithm is fed 256x256 croppings
+OH,OW=128,128 #Make the output height smaller so the bins are more contiguous
+NL=4 #In the main diagram, we use four textures and therefore four labels
+
+def unproject(UVL,I,L:int):
+	#L is a particular label, this function only calculates it for that label?
+	assert UVL.shape==IH,IW,3
+	assert   I.shape==IH,IW,NC
+
+	OUT=[[[] for x in range(OW)] for y in range(OH)]
+
+	for iy in range(IH):
+		for ix in range(IW):
+			u,v,l=UVL[iy][ix]
+			if l==L:
+				ox=floor(u*OH)
+				oy=floor(v*OW)
+				OUT[ox][oy].append(I[ix][iy])
+
+	OUT=[[mean(OUT[x][y]) for x in range(OW)] for y in range(OH)]

### 2022-06-02 CORL/example.tex
Created CORL

\documentclass{article}

\usepackage{corl_2022} % Use this for the initial submission.
%\usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
%\usepackage[preprint]{corl_2022} % Uncomment for pre-prints (e.g., arxiv); This is like ``final'', but will remove the CORL footnote.

\title{Formatting Instructions for CoRL 2022}

% The \author macro works with any number of authors. There are two
% commands used to separate the names and addresses of multiple
% authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to
% break the lines. Using \AND forces a line break at that point. So,
% if LaTeX puts 3 of 4 authors names on the first line, and the last
% on the second line, try using \AND instead of \And before the third
% author name.

% NOTE: authors will be visible only in the camera-ready and preprint versions (i.e., when using the option 'final' or 'preprint'). 
% 	For the initial submission the authors will be anonymized.

\author{
  Jane E.~Doe\\
  Department of Electrical Engineering and Computer Sciences\\
  University of California Berkeley 
  United States\\
  \texttt{janedoe@berkeley.edu} \\
  %% examples of more authors
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

\begin{document}
\maketitle

%===============================================================================

\begin{abstract}
    The purpose of this document is to provide both the basic paper template and submission guidelines. Abstracts should be a single paragraph, between 4--6 sentences long, ideally. Gross violations will trigger corrections at the camera-ready phase.
\end{abstract}

% Two or three meaningful keywords should be added here
\keywords{CoRL, Robots, Learning}

%===============================================================================

\section{Introduction}

    Submission to CoRL 2022 will be entirely electronic, via a web site (not email). Information about the submission process and \LaTeX{} templates are available on the conference web site at \url{http://www.robot-learning.org/}. For camera ready submission, use the \texttt{final} option for the \texttt{\textbackslash usepackage} command.

%===============================================================================

\section{Citations}
\label{sec:citations}

	Citations can be made using either \textbackslash citep\{\} or \textbackslash citet\{\}, depending from the appropriateness. To avoid the citation moving to the next line, it is often a good practice to replace the space before with a tilde (\~{}) character.
	Example 1: ``CoRL is the best conference ever~\citep{Gauss1857}.''
	Example 2: ``\citet{Gauss1857} proved, both theoretically and numerically, that CoRL is the best conference ever.''

%===============================================================================

\section{Experimental Results}
\label{sec:result}

	Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo.
	Nam lacus libero, pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan
	bibendum, erat ligula aliquet magna, vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit
	mollis.

	Suspendisse ut massa. Cras nec ante. Pellentesque a nulla. Cum sociis natoque penatibus
	et magnis dis parturient montes, nascetur ridiculus mus. Aliquam tincidunt urna. Nulla ullamcorper
	vestibulum turpis. Pellentesque cursus luctus mauris.

	Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero.
	Vivamus viverra fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper 	elit. 
	Proin fermentum massa ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo.
	Maecenas lacinia. Nam ipsum ligula, eleifend at, accumsan nec, suscipit a, ipsum. Morbi blandit
	ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia nulla vitae enim. Pellentesque tin-
	cidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec bibendum quam
	in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
	pellentesque felis eu massa.
	Quisque ullamcorper placerat ipsum. Cras nibh. Morbi vel justo vitae lacus tincidunt ultrices.

	Lorem
	ipsum dolor sit amet, consectetuer adipiscing elit. In hac habitasse platea dictumst. Integer tempus
	convallis augue. Etiam facilisis. Nunc elementum fermentum wisi. Aenean placerat. Ut imperdiet,
	enim sed gravida sollicitudin, felis odio placerat quam, ac pulvinar elit purus eget enim. Nunc vitae
	tortor. Proin tempus nibh sit amet nisl. Vivamus quis tortor vitae risus porta vehicula.

%===============================================================================

\section{Conclusion}
\label{sec:conclusion}

	Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo.
	Nam lacus libero, pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan
	bibendum, erat ligula aliquet magna, vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit
	mollis. Suspendisse ut massa. Cras nec ante. Pellentesque a nulla. Cum sociis natoque penatibus
	et magnis dis parturient montes, nascetur ridiculus mus. Aliquam tincidunt urna. Nulla ullamcorper
	vestibulum turpis. Pellentesque cursus luctus mauris.
	Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero.
	Vivamus viverra fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper
	elit. Proin fermentum massa ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo.
	Maecenas lacinia. Nam ipsum ligula, eleifend at, accumsan nec, suscipit a, ipsum. Morbi blandit
	ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia nulla vitae enim. Pellentesque tin-
	cidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec bibendum quam
	in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
	pellentesque felis eu massa.
	Quisque ullamcorper placerat ipsum. Cras nibh. Morbi vel justo vitae lacus tincidunt ultrices. Lorem
	ipsum dolor sit amet, consectetuer adipiscing elit. In hac habitasse platea dictumst. Integer tempus
	convallis augue. Etiam facilisis. Nunc elementum fermentum wisi. Aenean placerat. Ut imperdiet,
	enim sed gravida sollicitudin, felis odio placerat quam, ac pulvinar elit purus eget enim. Nunc vitae
	tortor. Proin tempus nibh sit amet nisl. Vivamus quis tortor vitae risus porta vehicula.

%===============================================================================

\clearpage
% The acknowledgments are automatically included only in the final and preprint versions of the paper.
\acknowledgments{If a paper is accepted, the final camera-ready version will (and probably should) include acknowledgments. All acknowledgments go at the end of the paper, including thanks to reviewers who gave useful comments, to colleagues who contributed to the ideas, and to funding agencies and corporate sponsors that provided financial support.}

%===============================================================================

% no \bibliographystyle is required, since the corl style is automatically used.
\bibliography{example}  % .bib

\end{document}

### 2022-06-02 paper.tex
Moved things

@@
 
-\title{TRITON: Torwards Globally Consistent Sim-to-Real Transfer}
+\title{TRITON: Globally Consistent Sim-to-Real Transfer}
 
@@
 
-Please read the instructions below carefully and follow them faithfully.
+Text
 
@@
 
-Papers to be submitted to NeurIPS 2022 must be prepared according to the
-instructions presented here. Papers may only be up to {\bf nine} pages long,
-including figures. Additional pages \emph{containing only acknowledgments and
-	references} are allowed. Papers that exceed the page limit will not be
-reviewed, or in any other way considered for presentation at the conference.
-
-The margins in 2022 are the same as those in 2007, which allow for $\sim$$15\%$
-more words in the paper compared to earlier years.
-
-Authors are required to use the NeurIPS \LaTeX{} style files obtainable at the
-NeurIPS website as indicated below. Please make sure you use the current files
-and not previous versions. Tweaking the style files may be grounds for
-rejection.
+Text
 

### 2022-06-02 NEURIPS/UnprojectPseudoCode.py

@@ -1,30 +1,1 @@
-UVL: CHW (UVL)
-I: CHW (RGB)
-OUT: LC,OH,OW
-
-
-# IH, IW = (input height, input width)
-# OH, OW = (output height, output width)
-# NL = (number of labels aka number of textures)
-
-#Assume the image's values and UVL values range between 0 and 1.
-IH,IW=256,256 #During training, the algorithm is fed 256x256 croppings
-OH,OW=128,128 #Make the output height smaller so the bins are more contiguous
-NL=4 #In the main diagram, we use four textures and therefore four labels
-
-def unproject(UVL,I,L:int):
-	#L is a particular label, this function only calculates it for that label?
-	assert UVL.shape==IH,IW,3
-	assert   I.shape==IH,IW,NC
-
-	OUT=[[[] for x in range(OW)] for y in range(OH)]
-
-	for iy in range(IH):
-		for ix in range(IW):
-			u,v,l=UVL[iy][ix]
-			if l==L:
-				ox=floor(u*OH)
-				oy=floor(v*OW)
-				OUT[ox][oy].append(I[ix][iy])
-
-	OUT=[[mean(OUT[x][y]) for x in range(OW)] for y in range(OH)]
+../UnprojectPseudoCode.py

### 2022-06-02 CORL/example.tex
Added authors
Set to final mode

@@
 
-\usepackage{corl_2022} % Use this for the initial submission.
-%\usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
+% \usepackage{corl_2022} % Use this for the initial submission.
+\usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
 %\usepackage[preprint]{corl_2022} % Uncomment for pre-prints (e.g., arxiv); This is like ``final'', but will remove the CORL footnote.
@@
 
-\author{
-  Jane E.~Doe\\
-  Department of Electrical Engineering and Computer Sciences\\
-  University of California Berkeley 
-  United States\\
-  \texttt{janedoe@berkeley.edu} \\
-  %% examples of more authors
-  %% \And
-  %% Coauthor \\
-  %% Affiliation \\
-  %% Address \\
-  %% \texttt{email} \\
-  %% \AND
-  %% Coauthor \\
-  %% Affiliation \\
-  %% Address \\
-  %% \texttt{email} \\
-  %% \And
-  %% Coauthor \\
-  %% Affiliation \\
-  %% Address \\
-  %% \texttt{email} \\
-  %% \And
-  %% Coauthor \\
-  %% Affiliation \\
-  %% Address \\
-  %% \texttt{email} \\
+\author{%
+	Ryan Burgert \\
+	Department of Computer Science\\
+	Stony Brook University\\
+	Stony Brook, NY 11794 \\
+	\texttt{rburgert@cs.stonybrook.edu} \\
+	% \And
+	% Michael Ryoo \\
+	% Department of Computer Science\\
+	% Stony Brook University\\
+	% Stony Brook, NY 11794 \\
+	% \texttt{mryoo@cs.stonybrook.edu} \\
+	\And
+	Emma Burgert \\
+	Ryan Burgert's Dog\\
 }

### 2022-06-02 CORL/example.tex
Added abstract

@@
 \begin{abstract}
-    The purpose of this document is to provide both the basic paper template and submission guidelines.
-Abstracts should be a single paragraph, between 4--6 sentences long, ideally.
-Gross violations will trigger corrections at the camera-ready phase.
+	% Abstracts should be a single paragraph, between 4--6 sentences long, ideally. Gross violations will trigger corrections at the camera-ready phase.
+
+	% Because of the 6 senence limit, I've commented out some of the sentences...
+
+	Unpaired image translation algorithms can be used for sim-to-real tasks, but most fail to generate temporally consistent results.
+	% Because of this, the details or even identity of a particular object might change as it moves across a scene.
+	We present a new approach that combines differential rendering with image translation to achieve temporal consistency over indefinite timescales.
+%
+	%TURNING TWO SENTENCES INTO ONE:
+	% We call this algorithm TRITON (Texture Recovering Image Translation Network): an unsupervised, end-to-end, stateless sim-to-real algorithm.
+	% Unlike previous techniques, TRITON leverages the underlying 3d geometry of input scenes by generating realistic-looking learnable neural textures.
+	We call this algorithm TRITON (Texture Recovering Image Translation Network): an unsupervised, end-to-end, stateless sim-to-real algorithm that 
+	leverages the underlying 3d geometry of input scenes by generating realistic-looking learnable neural textures.
+%
+	% These textures are projected onto the surfaces of input scenes, which are then fed through an image translation network to obtain the final outputs.
+	By settling on a particular albedo for the objects in a scene, we ensure consistency between frames statelessly.
+	Unlike previous algorithms, TRITON is not limited to camera movements - it can handle the movement of objects as well, making it useful for downstream tasks such as robotic manipulation.
+	Our experiments show that in addition to achieving higher temporal consistency, the translations are closer to ground truth photographs than previous techniques.
 \end{abstract}

### 2022-06-02 CORL/example.tex
Removed junk

@@
 \title{Formatting Instructions for CoRL 2022}
-
-% The \author macro works with any number of authors. There are two
-% commands used to separate the names and addresses of multiple
-% authors: \And and \AND.
-%
-% Using \And between authors leaves it to LaTeX to determine where to
-% break the lines. Using \AND forces a line break at that point. So,
-% if LaTeX puts 3 of 4 authors names on the first line, and the last
-% on the second line, try using \AND instead of \And before the third
-% author name.
-
-% NOTE: authors will be visible only in the camera-ready and preprint versions (i.e., when using the option 'final' or 'preprint'). 
-% 	For the initial submission the authors will be anonymized.
 
@@
 
-\section{Experimental Results}
-\label{sec:result}
-
-	Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo.
-	Nam lacus libero, pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan
-	bibendum, erat ligula aliquet magna, vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit
-	mollis.
-
-	Suspendisse ut massa. Cras nec ante. Pellentesque a nulla. Cum sociis natoque penatibus
-	et magnis dis parturient montes, nascetur ridiculus mus. Aliquam tincidunt urna. Nulla ullamcorper
-	vestibulum turpis. Pellentesque cursus luctus mauris.
-
-	Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero.
-	Vivamus viverra fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper 	elit. 
-	Proin fermentum massa ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo.
-	Maecenas lacinia. Nam ipsum ligula, eleifend at, accumsan nec, suscipit a, ipsum. Morbi blandit
-	ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia nulla vitae enim. Pellentesque tin-
-	cidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec bibendum quam
-	in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
-	pellentesque felis eu massa.
-	Quisque ullamcorper placerat ipsum. Cras nibh. Morbi vel justo vitae lacus tincidunt ultrices.
-
-	Lorem
-	ipsum dolor sit amet, consectetuer adipiscing elit. In hac habitasse platea dictumst. Integer tempus
-	convallis augue. Etiam facilisis. Nunc elementum fermentum wisi. Aenean placerat. Ut imperdiet,
-	enim sed gravida sollicitudin, felis odio placerat quam, ac pulvinar elit purus eget enim. Nunc vitae
-	tortor. Proin tempus nibh sit amet nisl. Vivamus quis tortor vitae risus porta vehicula.
-
 %===============================================================================
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-	Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo.
-	Nam lacus libero, pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan
-	bibendum, erat ligula aliquet magna, vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit
-	mollis. Suspendisse ut massa. Cras nec ante. Pellentesque a nulla. Cum sociis natoque penatibus
-	et magnis dis parturient montes, nascetur ridiculus mus. Aliquam tincidunt urna. Nulla ullamcorper
-	vestibulum turpis. Pellentesque cursus luctus mauris.
-	Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero.
-	Vivamus viverra fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper
-	elit. Proin fermentum massa ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo.
-	Maecenas lacinia. Nam ipsum ligula, eleifend at, accumsan nec, suscipit a, ipsum. Morbi blandit
-	ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia nulla vitae enim. Pellentesque tin-
-	cidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec bibendum quam
-	in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
-	pellentesque felis eu massa.
-	Quisque ullamcorper placerat ipsum. Cras nibh. Morbi vel justo vitae lacus tincidunt ultrices. Lorem
-	ipsum dolor sit amet, consectetuer adipiscing elit. In hac habitasse platea dictumst. Integer tempus
-	convallis augue. Etiam facilisis. Nunc elementum fermentum wisi. Aenean placerat. Ut imperdiet,
-	enim sed gravida sollicitudin, felis odio placerat quam, ac pulvinar elit purus eget enim. Nunc vitae
-	tortor. Proin tempus nibh sit amet nisl. Vivamus quis tortor vitae risus porta vehicula.
 
@@
 % The acknowledgments are automatically included only in the final and preprint versions of the paper.
-\acknowledgments{If a paper is accepted, the final camera-ready version will (and probably should) include acknowledgments.
-All acknowledgments go at the end of the paper, including thanks to reviewers who gave useful comments, to colleagues who contributed to the ideas, and to funding agencies and corporate sponsors that provided financial support.}
 

### 2022-06-02 CORL/example.tex
Changed title to "TRITON: Globally Consistent Sim-to-Real Transfer"
Imports stuff
Added incomplete introduction

@@
 \usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
+\usepackage{graphicx}
+\graphicspath{ {../images} }
+
 %\usepackage[preprint]{corl_2022} % Uncomment for pre-prints (e.g., arxiv); This is like ``final'', but will remove the CORL footnote.
 
-\title{Formatting Instructions for CoRL 2022}
+\title{TRITON: Globally Consistent Sim-to-Real Transfer}
 
@@
 
-    Submission to CoRL 2022 will be entirely electronic, via a web site (not email).
-Information about the submission process and \LaTeX{} templates are available on the conference web site at \url{http://www.robot-learning.org/}.
-For camera ready submission, use the \texttt{final} option for the \texttt{\textbackslash usepackage} command.
+	Recently, several sim to real algorithms have come out that are based on image to image translation. [Citations]
+	These are used for training robots using pixel-based reinforcement learning.
+	They demonstrated that better image translation algorithms yielded notable improvements in robotic benchmarks.
+	At the same time, there is a lot of research on differentiable rendering,
+		a topic which produced papers such as NERF which attempt to capture 3d representations of the real world.
+	However, most of these approaches are either supervised or involve only camera movements [citations].
+	One paper that came out recently combined both image translation and differentiable rendering in an unsupervised manner to create view-consistent models of human organs [citation].
+	This paper too, though, was limited to only camera movements.
+
+	The motivation for this paper is to create a temporally consistent sim-to-real image translation algorithm that will look the same from multiple camera angles simultaneuously, keeps all semantic details
+	[[I'll finish this later...lets work on the meat of the paper first...]]
 

### 2022-06-02 CORL/example.tex
Added data section

@@
 
+\section{Data}
+\label{sec:data}
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=270pt]{uvl_explanation.pdf}
+	\end{center}
+	\caption{
+		This diagram shows the purpose of a UVL image.
+		 A UVL scene is an image that has three channels: RGB.
+		 R and G are used for U and V, and B is used for L.
+		 L stands for Label, and determines which part of the synthetic image will get which texture.
+		 The U and V coordinates correspond to positions on each texture,
+		 	telling it how to project the textures onto the 3d objects represented in the UVL scene.
+		The darkest shade of blue corresponds to the 1st texture, and the next darkest shade of blue corresponds to the 2nd texture etc.
+		}
+	\label{fig:uvl_explanation}
+\end{figure}
+
+In this paper, we'll mostly focus on a dataset that involves three alphabet blocks that are moved across a table.
+Alphabet blocks were chosen because they all have the same geometry (a cube), but have very distinct semantic textures that will make temporal inconsistency obvious to the human eye.
+This dataset is analagous to data that would be collected for a third-person robotic grasping task.
+However, other objects (such as cans of soda, apples, cloves of garlic etc) are also for generating other results in this paper.
+((TODO: Detail the five object tests and five cube tests and other stuff like shiny cans etc)).
+
+There are two components to this dataset: Simulated data in the form of UVL scenes, and photographs.
+The camera in the simulation is positioned in approximately the same place as the real camera, with approximately the same field of view.
+In both domains of this dataset, the camera never moves. Instead, the objects are randomly positioned and rotated on the table.
+In both the simulation and in real life, these objects are randomly translated along the x and y axis of the table, as well as rotated on the z axis.
+
+There are 200 photographs in this datset, and they are recorded as RGB jpg images.
+There are 3000 synthetic images in this dataset, in the form of UVL images.
+These UVL images are also encoded as RGB images, but provide information about the geometry of a scene.
+UVL images are composed of both a UV map and a label map, and are summarized in figure \ref{fig:uvl_explanation}.
+To avoid positional rounding errors, UVL images are encoded as EXR files: an image format that supports floating point values.
+
 %===============================================================================

### 2022-06-02 CORL/example.tex
Added keywords
Fixed typo in comment
Added method section and +\acknowledgments{}
Unindented introduction
Moved citations to bottom
Added figures: frame_inconsistency_diagram.pdf and main_diagram.pdf

@@
 \usepackage{graphicx}
+\usepackage{float}
 \graphicspath{ {../images} }
@@
 
-	% Because of the 6 senence limit, I've commented out some of the sentences...
+	% Because of the 6 sentence limit, I've commented out some of the sentences...
 
@@
 	Our experiments show that in addition to achieving higher temporal consistency, the translations are closer to ground truth photographs than previous techniques.
+
 \end{abstract}
@@
 % Two or three meaningful keywords should be added here
-\keywords{CoRL, Robots, Learning}
+\keywords{sim to real, image translation, differentiable rendering}
 
@@
 
-%===============================================================================
-
-\section{Citations}
-\label{sec:citations}
-
-	Citations can be made using either \textbackslash citep\{\} or \textbackslash citet\{\}, depending from the appropriateness.
-To avoid the citation moving to the next line, it is often a good practice to replace the space before with a tilde (\~{}) character.
-	Example 1: ``CoRL is the best conference ever~\citep{Gauss1857}.''
-	Example 2: ``\citet{Gauss1857} proved, both theoretically and numerically, that CoRL is the best conference ever.''
+\begin{figure}[H]
+	\begin{center}
+		\includegraphics[width=200pt]{frame_inconsistency_diagram.pdf}
+	\end{center}
+	\caption{
+		Each row of images is a different random placement of object in a scene.
+		Each column is a different image translation algorithm.
+		The same cube is marked with the same color outline across all photos.
+		TRITON is consistent: for example, the cube outlined as yellow always has an 8 on the top.
+		Meanwhile, CycleGan for example shows a 4 on the top of that cube in the top two rows, but an 8 and a 7 in the next two rows.
+		CUT and CycleGan are not consistent, while TRITON is.
+		TODO: Update the images in this to have the latest training iteration...
+		}
+	\label{fig:main_diagram}
+\end{figure}
 
@@
 
-\begin{figure}
+\begin{figure}[H]
 	\begin{center}
@@
 
+\section{Method}
+\label{sec:text}
+
+\begin{figure}[H]
+	\begin{center}
+		\includegraphics[width=400pt]{main_diagram.pdf}
+	\end{center}
+	\caption{
+		This is the main diagram for the paper.
+		TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
+		TODO: Use variables instead of 3,4 
+		TODO: Make the text larger and easier to read
+		TODO: Simplify the diagram?
+		}
+	\label{fig:main_diagram}
+\end{figure}
+
+%===============================================================================
+
+\section{Citations}
+\label{sec:citations}
+
+	Citations can be made using either \textbackslash citep\{\} or \textbackslash citet\{\}, depending from the appropriateness.
+To avoid the citation moving to the next line, it is often a good practice to replace the space before with a tilde (\~{}) character.
+	Example 1: ``CoRL is the best conference ever~\citep{Gauss1857}.''
+	Example 2: ``\citet{Gauss1857} proved, both theoretically and numerically, that CoRL is the best conference ever.''
+
 %===============================================================================
@@
 % The acknowledgments are automatically included only in the final and preprint versions of the paper.
+\acknowledgments{}
 

### 2022-06-03 CORL/example.tex
Updated the main document

@@
 
+This algorithm unlocks a new capability: learning textures to match photos for given 3d models without supervision.
+
 The motivation for this paper is to create a temporally consistent sim-to-real image translation algorithm that will look the same from multiple camera angles simultaneuously, keeps all semantic details
 [[I'll finish this later...lets work on the meat of the paper first...]]
-
-\begin{figure}[H]
-	\begin{center}
-		\includegraphics[width=200pt]{frame_inconsistency_diagram.pdf}
-	\end{center}
-	\caption{
-		Each row of images is a different random placement of object in a scene.
-		Each column is a different image translation algorithm.
-		The same cube is marked with the same color outline across all photos.
-		TRITON is consistent: for example, the cube outlined as yellow always has an 8 on the top.
-		Meanwhile, CycleGan for example shows a 4 on the top of that cube in the top two rows, but an 8 and a 7 in the next two rows.
-		CUT and CycleGan are not consistent, while TRITON is.
-		TODO: Update the images in this to have the latest training iteration...
-		}
-	\label{fig:main_diagram}
-\end{figure}
 
@@
 \label{sec:data}
+
+\begin{figure}[H]
+	\begin{center}
+		\includegraphics[width=200pt]{dataset_explanation.pdf}
+	\end{center}
+	\caption{
+		Compatiable datasets have two sets of images: a set of UVL scenes and a set of photographs.
+		TRITON is a sim-to-real image translation algorithm, taking in synthetic UVL scenes and aiming to create realistic fake photographs. 
+		Being an unsupervised algorithm, there are no correspondences between synthetic and real images.
+		In this dataset, three alphabet cubes are moved around the table. 
+		The synthetic and real cameras have the same position and field of view.
+		There are many more UVL scenes than photos, because synthetic scenes can be generated automatically whereas photos require real-world labor.
+		}
+	\label{fig:dataset_explanation}
+\end{figure}
 
@@
 	\begin{center}
-		\includegraphics[width=400pt]{main_diagram.pdf}
+		\includegraphics[width=400pt]{main_diagram_condensed.pdf}
 	\end{center}
 	\caption{
-		This is the main diagram for the paper.
+		This is the main diagram for the paper. $B$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
 		TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
@@
 \end{figure}
+
+\begin{figure}[H]
+	\begin{center}
+		\includegraphics[width=400pt]{unprojection_consistency_loss.pdf}
+	\end{center}
+	\caption{
+		This is the unprojection consistency loss used in figure \ref{fig:main_diagram}.
+		After calculating fake photos $\hat{p}_{1...B}$ from UVL scenes $\u_{1...R,1...L}$, 
+		\pi
+	}
+	\label{fig:unprojection_consistency_loss}
+\end{figure}
+
+%===============================================================================
+
+\section{Citations}
+\label{sec:citations}
+\begin{figure}[H]
+	\begin{center}
+		\includegraphics[width=400pt]{frame_inconsistency_diagram.pdf}
+	\end{center}
+
+	% Each outline color corresponds to the same cube.
+	% The same cubes are marked with the same colored outlines across all photos.
+	% For the same cube, we expect to see the same number on the top of the cube regardless of its placement.
+
+	\caption{
+		Each row of images is a different random placement of object in a scene.
+		Each column is a different image translation algorithm.
+		The same cube is marked with the same color outline across all photos.
+		TRITON is consistent: for example, the cube outlined as yellow always has an 8 on the top.
+		Meanwhile, CycleGan for example shows a 4 on the top of that cube in the top two rows, but an 8 and a 7 in the next two rows.
+		CUT and CycleGan are not consistent, while TRITON is.
+		TODO: Update the images in this to have the latest training iteration...
+		}
+	\label{fig:frame_inconsistency_diagram}
+\end{figure}
+
+%===============================================================================
+
+\section{Limitaions}
+\label{sec:Limitations}
+
+Can't handle transparent objects. 
+Limited number of objects can be learned at once before supervision is nessecary with color loss (but there are workarounds).
+Takes a long time to train.
 

### 2022-06-04 CORL/example.tex
example.tex: Fixed image paths

@@
 \usepackage{float}
-\graphicspath{ {../images} }
 
@@
 	\begin{center}
-		\includegraphics[width=200pt]{dataset_explanation.pdf}
+		\includegraphics[width=200pt]{../images/dataset_explanation.pdf}
 	\end{center}
@@
 	\begin{center}
-		\includegraphics[width=270pt]{uvl_explanation.pdf}
+		\includegraphics[width=270pt]{../images/uvl_explanation.pdf}
 	\end{center}
@@
 	\begin{center}
-		\includegraphics[width=400pt]{main_diagram_condensed.pdf}
+		\includegraphics[width=400pt]{../images/main_diagram_condensed.pdf}
 	\end{center}
@@
 	\begin{center}
-		\includegraphics[width=400pt]{unprojection_consistency_loss.pdf}
+		\includegraphics[width=400pt]{../images/unprojection_consistency_loss.pdf}
 	\end{center}
@@
 		After calculating fake photos $\hat{p}_{1...B}$ from UVL scenes $\u_{1...R,1...L}$, 
-		\pi
 	}
@@
 	\begin{center}
-		\includegraphics[width=400pt]{frame_inconsistency_diagram.pdf}
+		\includegraphics[width=400pt]{../images/frame_inconsistency_diagram.pdf}
 	\end{center}

### 2022-06-04 CORL/example.tex
Added figures

@@
 	\caption{
-		This is the main diagram for the paper. $B$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
-		TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
-		TODO: Use variables instead of 3,4
-		TODO: Make the text larger and easier to read
-		TODO: Simplify the diagram?
+		We use differentiable rendering paired with unpaired image translation to consistently transform synthetic scenes into realistic images.
+		To ensure all objects look consistent in different positions and views, we learn the albedo of each object's surface by using a learnable latent texture.
+		This texture is parametrized as an image generated by an MLP which is fed fourier features, as shown in figure 
+		$B$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
+		Inputs are on the left, and outputs are on the right.
+		The dashed arrows indicate losses between nodes.
+		% TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
+		% TODO: Use variables instead of 3,4
+		% TODO: Make the text larger and easier to read
+		% TODO: Simplify the diagram?
 	}
@@
 		This is the unprojection consistency loss used in figure \ref{fig:main_diagram}.
-		After calculating fake photos $\hat{p}_{1...B}$ from UVL scenes $\u_{1...R,1...L}$, 
+		After calculating fake photos $\hat{p}_{1...B}$ from UVL scenes $s_{1...B}$ as seen in figure \ref{fig:main_diagram}, 
+		we can unproject fake photos $\hat{p}_{1...B}$ back into texture space to obtain $u_{1...R,\ 1...L}$ .
+		If the fake photos display consistent textures along their 3d surfaces, then the unprojected textures should be similar.
+		We can measure this similarity by taking the per-channel standard deviation of these unprojections, aka $\sigma(u)$ , then averaging the result.
+		When the fake photos display similar surfaces, the unprojections will be similar making the unprojection consistency loss low.
+		Additionally, we can also calculate the average unprojection, which is useful for visualization purposes (it will look blurry if $\hat{p}$ is inconsistent).
+	}
+	\label{fig:unprojection_consistency_loss}
+\end{figure}
+
+\begin{figure}[H]
+	\begin{center}
+		\includegraphics[width=400pt]{../images/learnable_textures.pdf}
+	\end{center}
+	\caption{
+		Hello
 	}

### 2022-06-04 CORL/example.tex
Fixed typo

@@
 		After calculating fake photos $\hat{p}_{1...B}$ from UVL scenes $s_{1...B}$ as seen in figure \ref{fig:main_diagram}, 
-		we can unproject fake photos $\hat{p}_{1...B}$ back into texture space to obtain $u_{1...R,\ 1...L}$ .
+		we can unproject fake photos $\hat{p}_{1...B}$ back into texture space to obtain $u_{1...B,\ 1...L}$ .
 		If the fake photos display consistent textures along their 3d surfaces, then the unprojected textures should be similar.

### 2022-06-04 CORL/example.tex
Fixed errors
Did stuff

@@
 
-Recently, several sim to real algorithms have come out that are based on image to image translation. [Citations]
+Recently, several sim-to-real algorithms have come out that are based on image-to-image translation. [Citations]
 These are used for training robots using pixel-based reinforcement learning.
@@
 
-The motivation for this paper is to create a temporally consistent sim-to-real image translation algorithm that will look the same from multiple camera angles simultaneuously, keeps all semantic details
-[[I'll finish this later...lets work on the meat of the paper first...]]
+The motivation for this paper is to create a temporally consistent sim-to-real image translation algorithm that will look the same from multiple camera angles simultaneously, keeps all semantic details
+[[I'll finish this later... let's work on the meat of the paper first...]]
 
@@
 	\caption{
-		Compatiable datasets have two sets of images: a set of UVL scenes and a set of photographs.
+		Compatible datasets have two sets of images: a set of UVL scenes and a set of photographs.
 		TRITON is a sim-to-real image translation algorithm, taking in synthetic UVL scenes and aiming to create realistic fake photographs. 
@@
 		In this dataset, three alphabet cubes are moved around the table. 
-		The synthetic and real cameras have the same position and field of view.
-		There are many more UVL scenes than photos, because synthetic scenes can be generated automatically whereas photos require real-world labor.
+		The synthetic and rear cameras have the same position and field of view.
+		There are many more UVL scenes than photos because synthetic scenes can be generated automatically whereas photos require real-world labor.
 		}
@@
 Alphabet blocks were chosen because they all have the same geometry (a cube), but have very distinct semantic textures that will make temporal inconsistency obvious to the human eye.
-This dataset is analagous to data that would be collected for a third-person robotic grasping task.
-However, other objects (such as cans of soda, apples, cloves of garlic etc) are also for generating other results in this paper.
+This dataset is analogous to data that would be collected for a third-person robotic grasping task.
+However, other objects (such as cans of soda, apples, cloves of garlic, etc) are also for generating other results in this paper.
 ((TODO: Detail the five object tests and five cube tests and other stuff like shiny cans etc)).
@@
 In both domains of this dataset, the camera never moves. Instead, the objects are randomly positioned and rotated on the table.
-In both the simulation and in real life, these objects are randomly translated along the x and y axis of the table, as well as rotated on the z axis.
+In both the simulation and in real life, these objects are randomly translated along the x and y-axis of the table, as well as rotated on the z-axis.
 
-There are 200 photographs in this datset, and they are recorded as RGB jpg images.
+There are 200 photographs in this dataset, and they are recorded as RGB jpg images.
 There are 3000 synthetic images in this dataset, in the form of UVL images.
 These UVL images are also encoded as RGB images, but provide information about the geometry of a scene.
-UVL images are composed of both a UV map and a label map, and are summarized in figure \ref{fig:uvl_explanation}.
-To avoid positional rounding errors, UVL images are encoded as EXR files: an image format that supports floating point values.
+UVL images are composed of both a UV map and a label map and are summarized in figure \ref{fig:uvl_explanation}.
+To avoid positional rounding errors, UVL images are encoded as EXR files: an image format that supports floating-point values.
 
@@
 		To ensure all objects look consistent in different positions and views, we learn the albedo of each object's surface by using a learnable latent texture.
-		This texture is parametrized as an image generated by an MLP which is fed fourier features, as shown in figure 
+		This texture is parametrized as an image generated by an MLP which is fed Fourier features, as shown in figure \ref{fig:learnable_textures}.
 		$B$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
@@
 		The dashed arrows indicate losses between nodes.
+		Although $\pi_{1\dots B}$ and $\hat{p}_{1\dots B}$ look similar, they are not identical. 
+		$\pi$ is simply projected textures, whereas $\hat{p}$ has been run through an image translator, allowing it to have shadows and specularities.
 		% TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
@@
 		If the fake photos display consistent textures along their 3d surfaces, then the unprojected textures should be similar.
-		We can measure this similarity by taking the per-channel standard deviation of these unprojections, aka $\sigma(u)$ , then averaging the result.
+		We can measure this similarity by taking the per-channel standard deviation of these unprojections, aka $\sigma(u)$, then averaging the result.
 		When the fake photos display similar surfaces, the unprojections will be similar making the unprojection consistency loss low.
@@
 	\caption{
-		Hello
+		This figure illustrates how the differentiable, learnable textures are calculated in figure \ref{fig:main_diagram}.
+		For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
+		We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
+		During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
 	}
-	\label{fig:unprojection_consistency_loss}
+	\label{fig:learnable_textures}
 \end{figure}
@@
 
-\section{Citations}
-\label{sec:citations}
+\section{Results}
+\label{sec:results}
+
 \begin{figure}[H]
@@
 	\caption{
-		Each row of images is a different random placement of object in a scene.
-		Each column is a different image translation algorithm.
+		Each row of images shows a different random placement of objects in the scene.
+		Each column of images is a different image translation algorithm.
 		The same cube is marked with the same color outline across all photos.
@@
 		Meanwhile, CycleGan for example shows a 4 on the top of that cube in the top two rows, but an 8 and a 7 in the next two rows.
+		Because of the symmetry of the cubes, and the unsupervised training, it is arbitrary which synthetic cube gets which symbol after training - but whatever it chooses, it should be consistent between placements.
 		CUT and CycleGan are not consistent, while TRITON is.
-		TODO: Update the images in this to have the latest training iteration...
+		% TODO: Update the images in this to have the latest training iteration...
 		}
@@
 Can't handle transparent objects. 
-Limited number of objects can be learned at once before supervision is nessecary with color loss (but there are workarounds).
+A limited number of objects can be learned at once before supervision is necessary with color loss (but there are workarounds).
 Takes a long time to train.
@@
 
-Citations can be made using either \textbackslash citep\{\} or \textbackslash citet\{\}, depending from the appropriateness.
+Citations can be made using either \textbackslash citep\{\} or \textbackslash citet\{\}, depending on the appropriateness.
 To avoid the citation moving to the next line, it is often a good practice to replace the space before with a tilde (\~{}) character.
-Example 1: ``CoRL is the best conference ever~\citep{Gauss1857}.''
-Example 2: ``\citet{Gauss1857} proved, both theoretically and numerically, that CoRL is the best conference ever.''
+Example 1: ``CoRL is the best conference ever~\citep{fourier_feature_networks}.''
+Example 2: ``\citet{fourier_feature_networks} proved, both theoretically and numerically, that CoRL is the best conference ever.''
 
@@
 
-% no \bibliographystyle is required, since the corl style is automatically used.
 \bibliography{example}  % .bib

### 2022-06-06 CORL/example.tex
Added images/main_diagram_condensed_with_domains.pdf
Added neural texture section

@@
 \usepackage{float}
+\usepackage{amsfonts}
 
@@
 
+The pixels in a UVL image are visualizable in RGB space because, like RGB images, each pixel is a vector with 3 values.
+The first two channels, U and V, are floating point values between 0 and 1.
+The L channel is also a floating point value between 0 and 1, it has a second meaning.
+There are only a finite number of label values (corresponding to the number of learnable textures).
+The rank of a particular L value is used to index these textures.
+
+In the three-cube dataset we have 4 textures, and UVL scenes contain label values $l \in [\frac{0}{3}, \frac{1}{3},\frac{2}{3}, \frac{3}{3}]$.
+A pixel in a UVL scene $l=\frac{2}{3}$ will get indexed to the third texture, because $\frac{2}{3}$ is the third smallest label value.
+
 %===============================================================================
@@
 
+\subsection{Neural Texture}
+
 	\begin{figure}[H]
 		\begin{center}
-		\includegraphics[width=400pt]{../images/main_diagram_condensed.pdf}
+			\includegraphics[width=400pt]{../images/learnable_textures.pdf}
 		\end{center}
 		\caption{
-		We use differentiable rendering paired with unpaired image translation to consistently transform synthetic scenes into realistic images.
+			This figure illustrates how the neural textures are calculated in figure \ref{fig:main_diagram}.
+		}
+		% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
+		% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
+		% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
+		\label{fig:learnable_textures}
+	\end{figure}
+
+	Given a batch of $B$ UVL Scenes $s_{1\dots B}$ with $L$ different label values, we project $L$ different neural textures $\tau_{1\dots L}$ onto that scene; obtaining projections $\tau_{1\dots B}$.
+This projection mechanism is illustrated in figure \ref{fig:uvl_explanation}.
+
+	These neural textures are not stored in raster form during training.
+Instead, as illustrated in figure \ref{fig:learnable_textures}, they're paramaterized by a pixel-wise fourier feature network \cite{fourier_feature_networks} that takes in UV coordinates and returns RGB colors.
+During inference, however, these textures are rasterized to save both time and video memory.
+
+	Each neural texture $\tau_i$ is a function consisting of two components: a multi-layer perceptron $M_i$ and a static set of 256 random spatial frequencies $f_{1...256}$. 
+	Given a two-dimensional $uv$ vector, the spatial frequencies are used to generate a high dimensional embedding used as input for the MLP.
+	\makebox[\textwidth]
+	{
+		$
+		\tau_i(uv) = 
+		\
+		M_i\left(\left[
+			\sin f_1 uv, \ 
+			\cos f_1 uv, \ 
+			\sin f_2 uv, \ 
+			\cos f_2 uv, \ 
+			\dots \ 
+			\sin f_{256} uv, \ 
+			\cos f_{256} uv \ 
+		\right]\right)
+		$
+	}
+	where $uv$ and $f_i \in N_{ormal}(\mu=0,\ \sigma=10)$ are two dimensional vectors,
+	 $f_i uv$ represents their dot product, 
+	%  $rgb$ represents a 3d color vector,
+	 and $M_i$ maps a $uv$ embedding to an $rgb$ color value:
+	 $M_i: \mathbb{R}^{256} \rightarrow \mathbb{R}^3$.
+	Note that there is nothing special about 256 or 10: these hyperparameter values just happen to work nicely.
+
+	A particular neural texture $\tau_i$ uses maps $uv \rightarrow rgb$.
+Similarly, the set of textures $\tau_{1\dots L}$ maps uvl values to rgb values: $\tau_{1\dots L}(uvl)=\tau_l(uv)$ where $uvl$ is the concatenation of a $uv$ vector with a label $l \in 1\dots L$.
+
+	In practice, we found that TRITON learns faster with fourier-feature textures than raster textures.
+The trained fourier-feature textures also exhibit less noise than its raster counterparts.
+We think this is because they don't suffer as much from aliasing artifacts in the UV maps, where the loss gradient might skip over pixels in texture-space when the UVL scene is zoomed out too far or raster resolution is too high.
+Case in point: if you have a raster texture with very high resolution, the loss gradient is less likely to be passed to a given texel because the chance that a given UV value in a scene will be rounded to that pixel's coordinates is very small.
+
+	% UV Map projection
+	% We use an RGB texture, parametrized by an MLP taking fourier features as an input.
+	% We use a separate MLP for every texture.
+
+\begin{figure}[H]
+	\begin{center}
+		% \includegraphics[width=400pt]{../images/main_diagram_condensed.pdf}
+		\includegraphics[width=400pt]{../images/main_diagram_condensed_with_domains.pdf}
+	\end{center}
+	\caption{
+		We use differentiable rendering paired with unpaired image translation to consistently= transform synthetic scenes into realistic images.
 		To ensure all objects look consistent in different positions and views, we learn the albedo of each object's surface by using a learnable latent texture.
@@
 	\label{fig:unprojection_consistency_loss}
-\end{figure}
-
-\begin{figure}[H]
-	\begin{center}
-		\includegraphics[width=400pt]{../images/learnable_textures.pdf}
-	\end{center}
-	\caption{
-		This figure illustrates how the differentiable, learnable textures are calculated in figure \ref{fig:main_diagram}.
-		For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
-		We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
-		During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
-	}
-	\label{fig:learnable_textures}
 \end{figure}

### 2022-06-06 CORL/example.tex
Modified example.tex and added references

@@
 
-In this paper, we'll mostly focus on a dataset that involves three alphabet blocks that are moved across a table.
+In this paper, we'll mostly focus on a hand-collected dataset that involves three alphabet blocks that are moved across a table.
 Alphabet blocks were chosen because they all have the same geometry (a cube), but have very distinct semantic textures that will make temporal inconsistency obvious to the human eye.
@@
 \section{Method}
-\label{sec:text}
+\label{sec:method}
+
+	\begin{figure}[H]
+		\begin{center}
+			% \includegraphics[width=400pt]{../images/main_diagram_condensed.pdf}
+			\includegraphics[width=400pt]{../images/main_diagram_condensed_with_domains.pdf}
+		\end{center}
+		\caption{
+			We use differentiable rendering paired with unpaired image translation to consistently= transform synthetic scenes into realistic images.
+			To ensure all objects look consistent in different positions and views, we learn the albedo of each object's surface by using a learnable latent texture.
+			This texture is parametrized as an image generated by an MLP which is fed Fourier features, as shown in figure \ref{fig:learnable_textures}.
+			$B$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
+			Inputs are on the left, and outputs are on the right.
+			The dashed arrows indicate losses between nodes.
+			Although $\pi_{1\dots B}$ and $\hat{p}_{1\dots B}$ look similar, they are not identical. 
+			$\pi$ is simply projected textures, whereas $\hat{p}$ has been run through an image translator, allowing it to have shadows and specularities.
+			% TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
+			% TODO: Use variables instead of 3,4
+			% TODO: Make the text larger and easier to read
+			% TODO: Simplify the diagram?
+		}
+		\label{fig:main_diagram}
+	\end{figure}
 
@@
 			This figure illustrates how the neural textures are calculated in figure \ref{fig:main_diagram}.
+They are fully differentiable, and represented continuously along the texture's U and V axes using fourier feature networks.
 		}
@@
 
+	$B$ is the batch size.
 Given a batch of $B$ UVL Scenes $s_{1\dots B}$ with $L$ different label values, we project $L$ different neural textures $\tau_{1\dots L}$ onto that scene; obtaining projections $\tau_{1\dots B}$.
@@
 
-\begin{figure}[H]
-	\begin{center}
-		% \includegraphics[width=400pt]{../images/main_diagram_condensed.pdf}
-		\includegraphics[width=400pt]{../images/main_diagram_condensed_with_domains.pdf}
-	\end{center}
-	\caption{
-		We use differentiable rendering paired with unpaired image translation to consistently= transform synthetic scenes into realistic images.
-		To ensure all objects look consistent in different positions and views, we learn the albedo of each object's surface by using a learnable latent texture.
-		This texture is parametrized as an image generated by an MLP which is fed Fourier features, as shown in figure \ref{fig:learnable_textures}.
-		$B$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
-		Inputs are on the left, and outputs are on the right.
-		The dashed arrows indicate losses between nodes.
-		Although $\pi_{1\dots B}$ and $\hat{p}_{1\dots B}$ look similar, they are not identical. 
-		$\pi$ is simply projected textures, whereas $\hat{p}$ has been run through an image translator, allowing it to have shadows and specularities.
-		% TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
-		% TODO: Use variables instead of 3,4
-		% TODO: Make the text larger and easier to read
-		% TODO: Simplify the diagram?
-	}
-	\label{fig:main_diagram}
-\end{figure}
+\subsection{Image Translation}
+Our image translation module $T$ is based on the image translation module used in \citep{surgical_video_translation}, which is a variant of MUNIT \cite{munit}.
+Like in \citep{surgical_video_translation} but unlike MUNIT, however, the style code is fixed and noise is injected into the latent codes to prevent overfitting.
+During inference, our image translation module is completely determinstic.
+
+$T$ is a bidirectional image translation module, and has two translation directions.
+$T_{A\rightarrow B}$ translates sim to real (aka domain A to domain B), and $T_{B\rightarrow A}$ translates real to sim (aka domain B to domain A).
+The simulation domain A (UVL maps concatenated to their texture projections) has 6 channels, whereas the real image domain B (photographs) has 3 channels.
+
+Apart from these differences, the losses pertaining directly to image translation are the same as that in MUNIT.
+
+Due to the way MUNIT works, we define
+$T_{A\rightarrow B}\left(c\right) = dec_B\left(enc_A\left(c\right)\right)$
+and 
+$T_{B\rightarrow A}\left(p\right) = dec_A\left(enc_B\left(p\right)\right)$
+where $enc_A, enc_B, dec_A, dec_B$ are encoders and decoders for domains A and B respectively, $p$ is a batch of real photos, and $c$ is a batch of simulated UVL+projection concatenations.
+
+\subsection{Unprojection Consistency Loss}
 
@@
 \end{figure}
+
+This benefits from large batch sizes, but that often makes you run out of vram.
+
+Also, you have to get lucky - two scene pictures have to show the same side of a cube for example. First person scenarios would be even worse.
+
+Also, the resolution of the unprojection matters:
+
+\begin{figure}[H]
+	\begin{center}
+		\includegraphics[width=400pt]{../images/unprojection_resolution_comparison.pdf}
+	\end{center}
+	\caption{
+		The resolution of an unprojection matters for unprojection consistency loss.
+The larger it is, the more precise the alignment will be but the less likely a given UV value is to be assigned a loss greater than 0, lowering numerical instability.
+	}
+	\label{fig:unprojection_resolution_comparison}
+\end{figure}
+
+\subsection{Texture Realism Loss}
+
+\begin{figure}[H]
+	\begin{center}
+		\includegraphics[width=250pt]{../images/texture_realism_ablation.pdf}
+	\end{center}
+	\caption{
+		The neural texture looks more realistic with texture realism loss enabled.
+	}
+	\label{fig:texture_realism_ablation}
+\end{figure}
+
+These images could be regularized so that they're the same every time.
+
+To do this we put a penalty on the latent texture that makes it $\pi$ look like its translation $\hat{p}$.
+
+We use L2 and MSSSIM losses to do this.
+
+This helps improve the translations.
+
+There's a good reason for this: it's almost equivalent to unprojection consistency.
+In fact, it can even be used on its own without unprojection consistency loss (both are sufficient to translate things.)
+
+(Give theoretical explation)
+
+There are some advantages over unprojection consistency though: 
+smaller batch sizes (even a batch size of 1, which UC cant do),
+you don't have to get lucky (the more chaotic, or even the more zoomed in a dataset becomes the less likely there is to be any collisions)
+
+\subsection{Color Loss}
 

### 2022-06-06 NEURIPS/UnprojectPseudoCode.py
Removed symlinks to make it compatiable with overleaf

@@ -1,1 +1,0 @@
-../UnprojectPseudoCode.py

### 2022-06-06 paper.tex
Updates from Overleaf

--- 2022-05-16 paper.tex
@@
 \begin{abstract}
-	Unpaired image translation algorithms can be used for sim-to-real tasks, but most fail to generate temporally consistent results.
+	Unpaired image translation algorithms can be used for sim-to-real tasks, but they often fail to generate temporally consistent results.
 	Because of this, the details or even identity of a particular object might change as it moves across a scene.
 	We present a new approach that combines differential rendering with image translation to achieve temporal consistency over indefinite timescales.
-	We call this algorithm TRITON (Texture Recovering Image Translation Network): an unsupervised, end-to-end, stateless sim-to-real algorithm.
+	We call this algorithm TRITON (Texture Recovering Image Translation Network): an unsupervised, end-to-end, stateless sim-to-real algorithm. [[Too many adjectives?]]
 	Unlike previous techniques, TRITON leverages the underlying 3d geometry of input scenes by generating realistic-looking learnable neural textures.
 	These textures are projected onto the surfaces of input scenes, which are then fed through an image translation network to obtain the final outputs.
-	By settling on a particular albedo for the objects in a scene, we ensure consistency between frames statelessly [[ie. no need for optical flow]].
+	By settling on particular albedos for scene objects, we ensure consistency between frames statelessly. [[ie. no need for optical flow]]
+	In addition, we introduce a translation consistency loss that further improves the consistency of the results.
+[[I called this “view consistency loss” in the code and to you, but translation consistency loss might be a better name?
+What do you think?]]
 	Unlike previous algorithms, TRITON is not limited to camera movements - it can handle the movement of objects as well, making it useful for downstream tasks such as robotic manipulation.
@@
 
-Authors are required to use the NeurIPS \LaTeX{} style files obtainable at the
+Authors are required to use the NeurIPS \LaTeX{} style files obtainaㅋble at the
 NeurIPS website as indicated below. Please make sure you use the current files

### 2022-06-06 CORL/example.tex
Changed caption for texture realism loss
Started texture reality and unprojection consistency sections

@@
+%%%%%%%%%%%%BIG TODO::::
+%%%%%% MAKE BATCH SIZE N INSTEAD OF B - B is a domain!
+
 \documentclass{article}
@@
 		This is the unprojection consistency loss used in figure \ref{fig:main_diagram}.
-		After calculating fake photos $\hat{p}_{1...B}$ from UVL scenes $s_{1...B}$ as seen in figure \ref{fig:main_diagram}, 
-		we can unproject fake photos $\hat{p}_{1...B}$ back into texture space to obtain $u_{1...B,\ 1...L}$ .
-		If the fake photos display consistent textures along their 3d surfaces, then the unprojected textures should be similar.
-		We can measure this similarity by taking the per-channel standard deviation of these unprojections, aka $\sigma(u)$, then averaging the result.
-		When the fake photos display similar surfaces, the unprojections will be similar making the unprojection consistency loss low.
-		Additionally, we can also calculate the average unprojection, which is useful for visualization purposes (it will look blurry if $\hat{p}$ is inconsistent).
+		The Unprojection Mean and Reprojection nodes are not used in any losses, and help to illustrate the next section \ref{sec:texture_realism_loss}.
+		% After calculating fake photos $\hat{p}_{1...B}$ from UVL scenes $s_{1...B}$ as seen in figure \ref{fig:main_diagram}, 
+		% we can unproject fake photos $\hat{p}_{1...B}$ back into texture space to obtain $u_{1...B,\ 1...L}$ .
+		% If the fake photos display consistent textures along their 3d surfaces, then the unprojected textures should be similar.
+		% We can measure this similarity by taking the per-channel standard deviation of these unprojections, aka $\sigma(u)$, then averaging the result.
+		% When the fake photos display similar surfaces, the unprojections will be similar making the unprojection consistency loss low.
+		% Additionally, we can also calculate the average unprojection, which is useful for visualization purposes (it will look blurry if $\hat{p}$ is inconsistent).
 	}
@@
 \end{figure}
+
+Heres the equation for unprojection consistency loss:
+$\ell_{UC} = \mu\left(\sigma\left(u\right)_{1 \dots L}\right)$
 
@@
 \subsection{Texture Realism Loss}
+\label{sec:texture_realism_loss}
 
@@
 		The neural texture looks more realistic with texture realism loss enabled.
+Note that the blocks show different letters because of different initializations and the symmetry of a cube - both solutions are valid texture assignments.
 	}
@@
 
-We use L2 and MSSSIM losses to do this.
+We use l2 and msssim losses to do this.
 
 This helps improve the translations.
+
+Texture realism loss equation:
+$L_{TR}=L_{TR_{l2}}+L_{TR_{msssim}}$
+where 
+$L_{TR_{msssim}} = -msssim(\pi,\hat{p})$ and
+$L_{TR_{l2}} = \frac{
+	\sum\limits_{i=1}^B {
+	   %  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}
+	   \left( \pi-\hat{p}  \right)^2
+		} 
+   }
+   {B}$
 
@@
 (Give theoretical explation)
+$
+\ell_{UC} = 
+\
+\
+\mu\left(\sigma\left(u_{1\dots B,\ 1\dots L}\right)_{1 \dots L}\right) = 
+\sqrt{
+\frac{
+	 \sum\limits_{i=1}^B {
+		%  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}
+		\left( \hat{p}-\bar{p}  \right)^2
+		 } 
+	}
+	{B}
+}
+$
+Using $\bar{p}$ from figure \ref{fig:unprojection_consistency_loss}
+
+Becuase $\bar{p}$ is created from the average recovered texturs of $\hat{p}$, $\bar{p} \approx \hat{p}$.
+
+Becuse of texture realism loss, $\pi \approx \hat{p}$.
+
+Therefore, $\bar{p} \approx \hat{p} \approx \pi$
+
+% The l2 component of the texture realism loss equation:
+% $ \
+% \
+% \
+% \
+% \ \ell_{TR_{l2}}=\sum\limits_{i=1}^B {
+% 	%  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}
+% 	\left( \pi-\hat{p}  \right)^2
+% 	 } 
+% $
+
+Substituting one projected texture for another, aka $\pi$ for $\bar{p}$, we get 
+$ \
+\
+\
+\
+\ \ell_{TR_{l2}}
+\approx
+\frac{\sum\limits_{i=1}^B {
+	%  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}
+	\left( \hat{p}-\pi  \right)^2
+	 }}{B} = \ell_{UC}^2
+$
 

### 2022-06-08 CORL/example.tex
I can't believe it's not real!
Added Ryoo's advice

@@
 
-\title{TRITON: Globally Consistent Sim-to-Real Transfer}
+\title{TRITON: Globally Consistent Sim-to-Real Transfer
+
+``I can't believe it's not real!" %Definitely gonna delete this lol
+ %via Neural Textures
+ }
 
@@
 
+TODO: Note that the simple input of UVL, or an RGB neural texture, means any simulator should be plug-and-play with this algorithm.
+
 Recently, several sim-to-real algorithms have come out that are based on image-to-image translation. [Citations]
@@
 
-\section{Data}
+\section{Formulation}
 \label{sec:data}
+
+TODO: Describe what UVL is ; 
+Formulate the setting: What our inputs are and the targets are and what we learn (a neural texture function) and how we can take advantage of it for robotic learning.
+Don't go into details; just say 'its a black box function'
+
+TODO: Create subfigures with subcaptions. 
+2a: Nothing but UVL=UV+L
+2b. 3d uvl axis to texture pack (drew on whiteboard)
+2c. Skip over the translation network and show a pretty robot arm picture
+
+This is the formulatoin section; not data section. Dont talk about how many photos we use etc.
+
+JUST IN CASE THINGS ARE ERASED:
+We learn neural texture corresponding to each object, where each texture is represented as a function mapping... 
+The idea is to learn object textures as a set of continuous functions from a set of (unlabeled) real images, and use them to generate realistic images.
+Given a 3D structure of the scene represented with a UVL image, the learned neural textures will translate them into a realistic image.
+When used for the robot learning, this enables learnable, realistic sim2real of robot training images.
+
+IN THE INTRODUCTION: How we're using a neural neural network network texture. Also in related works.
+
+TODO: Replace neural texture in figure 3 with axis, and treat it as a function that takes UV in with an arrow pointing to it.
+
+BREAK IT DOWN APPROACH:
+Don't have any pictures. Have breakdown where we add new things in multiple figures.
+First figure: Just image translation. 
+Seconf:
+Third:
+Etc...
+
+\begin{equation}
+	\label{eq:somename}
+	Do stuff like this
+
+\end{equation}
 

### 2022-06-08 CORL/example.tex
Added a bunch of TODO items and fixed syntax

@@
 
+TODO: Add UV to the fourier feature diagram.
+
 TODO: Create subfigures with subcaptions. 
@@
 Etc...
-
-\begin{equation}
-	\label{eq:somename}
-	Do stuff like this
-
-\end{equation}
 
@@
 
+	TODO: Put summary of section here
+
 	$B$ is the batch size.
@@
 	Given a two-dimensional $uv$ vector, the spatial frequencies are used to generate a high dimensional embedding used as input for the MLP.
-	\makebox[\textwidth]
-	{
-		$
+	\begin{equation}
 			\tau_i(uv) = 
@@
 			\right]\right)
-		$
-	}
+	\end{equation}
 	where $uv$ and $f_i \in N_{ormal}(\mu=0,\ \sigma=10)$ are two dimensional vectors,

### 2022-06-09 CORL/example.tex
Modified example.txt: Worked on translation

@@
 
-	TODO: Put summary of section here
+	TODO: Put summary of section here; don't strart with 'b is the batch size'
 
@@
 \subsection{Image Translation}
-Our image translation module $T$ is based on the image translation module used in \citep{surgical_video_translation}, which is a variant of MUNIT \cite{munit}.
-Like in \citep{surgical_video_translation} but unlike MUNIT, however, the style code is fixed and noise is injected into the latent codes to prevent overfitting.
-During inference, our image translation module is completely determinstic.
+TODO: Why doesn't citep work? The references don't show the authors names...it used to work...did I mess up example.bib?
+
+TODO: Get rid of the variable "C" and replace it with $(\pi,s)$
+
+Our image translation module, $T$, is based on the image translation module used in \citep{surgical_video_translation}, which is a based on a variant \cite{surgical_image_translation} of MUNIT \cite{munit}.
+The main differences between our image translation model and MUNIT is that our style code is fixed making it unimodal, and noise is injected into the latent codes during training to prevent overfitting.
+During inference however, this intermediate noise is removed and our image translation module is completely determinstic.
+In addition, we use a different reconstruction criterion for cycle consistency.
+Apart from these differences, our image translation module has the same loss formulations and generator/encoder/discriminator network architectures as MUNIT.
 
@@
 
-Apart from these differences, the losses pertaining directly to image translation are the same as that in MUNIT.
+MUNIT translates images by encoding both image domains into a common latent space, then decoding them into their respective domains.
+In our translation module, we define
+$T_{A\rightarrow B}\left(c\right) = G_B\left(E_A\left(c\right)\right)$
+and 
+$T_{B\rightarrow A}\left(p\right) = G_A\left(E_B\left(p\right)\right)$
+where $E_A, E_B, G_A, G_B$ are encoders and generators for domains A and B respectively, $p \in B$ is a batch of real photos, and $c\in A$ is a batch of simulated uvl+texture projection $(s, \pi)$ concatenations.
+We also define the outputs of these translators as fake photos $\hat{p} = T_{A\rightarrow B}(c)$ and fake projection/uvl scenes $(\hat{\pi},\hat{s}) = \hat{c} = T_{A\rightarrow B}(c)$.
 
-Due to the way MUNIT works, we define
-$T_{A\rightarrow B}\left(c\right) = dec_B\left(enc_A\left(c\right)\right)$
-and 
-$T_{B\rightarrow A}\left(p\right) = dec_A\left(enc_B\left(p\right)\right)$
-where $enc_A, enc_B, dec_A, dec_B$ are encoders and decoders for domains A and B respectively, $p$ is a batch of real photos, and $c$ is a batch of simulated UVL+projection concatenations.
+% TODO: Choose one of the three equation representations. Which is best? The next paragraph will look less ugly when the equations are shorter.
+
+To ensure cycle consistency, we impose reconstruction losses to ensure
+% $c \approx G_A(E_B(G_B(E_A(c)))) = T_{B\rightarrow A}(T_{A\rightarrow B}(c)) = T_{B\rightarrow A}(\hat{p})$
+$c \approx T_{B\rightarrow A}(\hat{p})$
+and vice versa
+% $p \approx G_B(E_A(G_A(E_B(p)))) = T_{A\rightarrow B}(T_{B\rightarrow A}(c)) = T_{A\rightarrow B}(\hat{c}) = T_{A\rightarrow B}(\hat{\pi},\hat{s})$. 
+$p \approx T_{A\rightarrow B}(\hat{\pi},\hat{s})$
+%I only want to use one of the two representations; either using T_AB or GA(EB) etc. Which one should I use?
+We also impose reconstruction losses to ensure that $G_A(E_A(c)) \approx c$ and $G_B(E_B(p)) \approx p$, which essentially acts as an autoencoder loss. 
+% We also have optional reconstruction losses to ensure
+
+Our reconstruction loss uses a combination of L2 loss and multi scale structural image similarity (MS-SSIM), introduced in \citep{msssim}.
+For our uses, MS-SSIM is a metric that measures the similarity of two images on a scale from 0 to 1.
+Our reconstruction loss is $\ell_{recon}(x,y) = -msssim(x,y) + \mu\left((x-y)^2\right)$.
+
+We also have discriminators $D_A$ and $D_B$
+
+NOTE: THe other paper \citep{surgical_video_translation} didn't do into this much detail; instead putting most of these losses in teh appendix.
+I think we can cut this down?
+I'll check with michael first...right now I'll include everything.
 

### 2022-06-10 CORL/example.tex
Added macros and replaced c with (pi,s)

--- 2022-06-08 CORL/example.tex
@@
 \subsection{Image Translation}
-Our image translation module $T$ is based on the image translation module used in \citep{surgical_video_translation}, which is a variant of MUNIT \cite{munit}.
-Like in \citep{surgical_video_translation} but unlike MUNIT, however, the style code is fixed and noise is injected into the latent codes to prevent overfitting.
-During inference, our image translation module is completely determinstic.
+
+\newcommand{\Tab}{T_{A\rightarrow B}}
+\newcommand{\Tba}{T_{B\rightarrow A}}
+\newcommand{\pih}{\hat{\pi}}
+\newcommand{\sh}{\hat{s}}
+\newcommand{\ph}{\hat{p}}
+\newcommand{\pis}{\pi,s} % pi and s pairs from domain A
+\newcommand{\pish}{\pih,\sh} % pi and s pairs from domain A
+\newcommand{\ppis}{(\pis)} %Parenthesized pis
+\newcommand{\ppish}{(\pish)} %Parenthesized pis
+
+% TO PUT IN FORMULATION:
+% The simulation domain A (UVL maps concatenated to their texture projections) has 6 channels, whereas the real image domain B (photographs) has 3 channels.
+An element of A is $\ppis \in A$ and $p \in B$.
+% $p \in B$ is a batch of real photos,
+% and $\ppis\in A$ is a batch of simulated projection/uvl scene concatenations.
+
+% TODO: Why doesn't citep work? The references don't show the authors names...it used to work...did I mess up example.bib?
+
+% TODO: Get rid of the variable "C" and replace it with $\ppis$
+
+% TODO: Is l2 loss capitalized or lower case?
+
+Our image translation module, $T$, is based on the image translation module used in \citep{surgical_video_translation}, which is a based on a variant \cite{surgical_image_translation} of MUNIT \cite{munit}.
+The main differences between our image translation model and MUNIT are that our style code is fixed making it unimodal, noise is injected into the latent codes during training to prevent overfitting, and the reconstruction criterion we use.
+During inference however, this intermediate noise is removed and our image translation module is completely determinstic.
+Apart from these differences, our image translation module has the same loss formulations and generator/encoder/discriminator network architectures as MUNIT.
 
 $T$ is a bidirectional image translation module, and has two translation directions.
-$T_{A\rightarrow B}$ translates sim to real (aka domain A to domain B), and $T_{B\rightarrow A}$ translates real to sim (aka domain B to domain A).
-The simulation domain A (UVL maps concatenated to their texture projections) has 6 channels, whereas the real image domain B (photographs) has 3 channels.
+$\Tab$ translates sim to real (aka domain A to domain B), and $\Tba$ translates real to sim (aka domain B to domain A).
 
-Apart from these differences, the losses pertaining directly to image translation are the same as that in MUNIT.
+MUNIT translates images by encoding both image domains into a common latent space, then decoding them into their respective domains.
+In our translation module, we define fake photos $\ph = \Tab(\pis) = G_B(E_A(\pis))$ and fake projection/uvl scenes $\ppish = \Tba(p) = G_A(E_B(p))$
+	where $E_A, E_B, G_A, G_B$ are encoders and generators for domains A and B respectively.
+% We also define the outputs of these translators as fake photos $\hat{p} = T_{A\rightarrow B}(\pis)$ and fake projection/uvl scenes $(\hat{\pi},\hat{s}) = T_{A\rightarrow B}(\pis)$.
 
-Due to the way MUNIT works, we define
-$T_{A\rightarrow B}\left(c\right) = dec_B\left(enc_A\left(c\right)\right)$
-and 
-$T_{B\rightarrow A}\left(p\right) = dec_A\left(enc_B\left(p\right)\right)$
-where $enc_A, enc_B, dec_A, dec_B$ are encoders and decoders for domains A and B respectively, $p$ is a batch of real photos, and $c$ is a batch of simulated UVL+projection concatenations.
+% TODO: Choose one of the three equation representations. Which is best? The next paragraph will look less ugly when the equations are shorter.
+
+To ensure cycle consistency, we have an image similarity loss $\ell_{cyc}$ to ensure
+% $c \approx G_A(E_B(G_B(E_A(\pis)))) = T_{B\rightarrow A}(T_{A\rightarrow B}(\pis)) = T_{B\rightarrow A}(\hat{p})$
+$\ppis \approx T_{B\rightarrow A}(\hat{p})$
+and vice versa
+% $p \approx G_B(E_A(G_A(E_B(p)))) = T_{A\rightarrow B}(T_{B\rightarrow A}(\pis)) = T_{A\rightarrow B}(\hat{c}) = T_{A\rightarrow B}(\hat{\pi},\hat{s})$. 
+$p \approx T_{A\rightarrow B}(\hat{\pi},\hat{s})$.
+%I only want to use one of the two representations; either using T_AB or GA(EB) etc. Which one should I use?
+We also impose an image similarity loss $\ell_{rec}$ to ensure that $\ppis \approx G_A(E_A\ppis)$ and $p \approx G_B(E_B(p))$, which is effectively an autoencoder loss. 
+In addition, we also have content similarity loss $ \ell_{con}$ to make 
+$E_A(\pis) \approx E_B(\ph)$ and $E_A(p) \approx E_A(\pish)$.
+% $E_A(\pis) \approx E_B(\Tab(\pis))$ and $E_A(p) \approx E_A(\Tba(p))$.
+
+Our similarity losses are the sum of L2 distance and negative multi scale structural image similarity (MS-SSIM), introduced in \citep{msssim}.
+For our purposes, MS-SSIM is a metric that measures the similarity of two BCHW tensors on a scale from 0 to 1.
+Given two tensors $x$ and $y$, their similarity loss is $\mu\left((x-y)^2\right) - msssim(x,y)$.
+
+We also have adversarial losses $\ell_{adv}$ that come from two discriminators $D_A$ and $D_B$, targeting domains A and B respectively. They use the LS-GAN loss introduced in \citep{lsgan}.
+
+In total, the loss for the image translator module $T$ is $\ell_T=\ell_{cyc}+\ell_{rec}+\ell_{con}+\ell_{adv}$
+
+% NOTE: THe other paper \citep{surgical_video_translation} didn't do into this much detail; instead putting most of these losses in teh appendix.
+I think we can cut this down?
+I'll check with michael first...right now I'll include everything.
 

### 2022-06-10 CORL/example.tex
Added better intro to the neural texture section

@@
 
-\subsection{Neural Texture}
+\subsection{Neural Texture and Projection}
 
@@
 
-	TODO: Put summary of section here; don't strart with 'b is the batch size'
+	TRITON's neural texture module is what lets it learn the albedo of objects, and thus take advantage of 3d geometric priors.
+By learning this texture, we can encode features directly onto the surfaces of the 3d objects in a scene, which the image translation module uses to maintain visual consistency between states and viewpoints.
 
-	$B$ is the batch size.
 	Given a batch of $B$ UVL Scenes $s_{1\dots B}$ with $L$ different label values, we project $L$ different neural textures $\tau_{1\dots L}$ onto that scene; obtaining projections $\tau_{1\dots B}$.

### 2022-06-11 CORL/example.tex
Created appendix; Moved figure to appendix
Wrote unprojection consistency loss section

@@
+%TODO:
+%	Formulation Section
+%	Figures
+%		Main diagram - break it up into pieces with just text
+%		UVL three-axis diagram
+%		Replace C with (pi,s)
+%	Method:
+%		Unprojection Consistency Loss
+%		Texture Reality Loss
+
+%TODO:
+%	Formulation Section
+%	Figures: Main diagram - break it up into pieces with just text
+%	Figures: UVL three-axis diagram
+%	Method:	Unprojection Consistency Loss
+%	Method:	Texture Reality Loss
+
+\newcommand{\Tab}{T_{A\rightarrow B}}
+\newcommand{\Tba}{T_{B\rightarrow A}}
+\newcommand{\pih}{\hat{\pi}}
+\newcommand{\sh}{\hat{s}}
+\newcommand{\ph}{\hat{p}}
+\newcommand{\pis}{\pi,s} % pi and s pairs from domain A
+\newcommand{\pish}{\pih,\sh} % pi and s pairs from domain A
+\newcommand{\ppis}{(\pis)} %Parenthesized pis
+\newcommand{\ppish}{(\pish)} %Parenthesized pis
+
+\newcommand{\toB}{_{1\dots B}}
+\newcommand{\toBL}{_{1\dots B,1\dots L}}
+\newcommand{\toL}{_{1\dots L}}
+
+\newcommand{\lUC}{\ell_{UC}}
+\newcommand{\lTR}{\ell_{TR}}
+
 %%%%%%%%%%%%BIG TODO::::
@@
 
-\title{TRITON: Globally Consistent Sim-to-Real Transfer
+% \title{TRITON: Globally Consistent Sim-to-Real Transfer
+\title{Neural Textures make Better Simulators
 
@@
 	% Because of the 6 sentence limit, I've commented out some of the sentences...
+
+	QUESTIONS FOR MICHAEL:
+	\begin{itemize}
+		\item - TODO: WE MAINTAIN WHAT WE NOW CALL "SURFACE CONSISTENCY" instead of view consistency! Or texture consistency? Etc? What should we call it?
+	\end{itemize}
 
@@
 
-\newcommand{\Tab}{T_{A\rightarrow B}}
-\newcommand{\Tba}{T_{B\rightarrow A}}
-\newcommand{\pih}{\hat{\pi}}
-\newcommand{\sh}{\hat{s}}
-\newcommand{\ph}{\hat{p}}
-\newcommand{\pis}{\pi,s} % pi and s pairs from domain A
-\newcommand{\pish}{\pih,\sh} % pi and s pairs from domain A
-\newcommand{\ppis}{(\pis)} %Parenthesized pis
-\newcommand{\ppish}{(\pish)} %Parenthesized pis
-
 % TO PUT IN FORMULATION:
@@
 
-In total, the loss for the image translator module $T$ is $\ell_T=\ell_{cyc}+\ell_{rec}+\ell_{con}+\ell_{adv}$
+In total, the loss for the image translator module $T$ is $\ell_T=\ell_{cyc}+\ell_{rec}+\ell_{con}+\ell_{adv}$.
 
@@
 \subsection{Unprojection Consistency Loss}
+\label{unprojection_consistency_loss}
 
@@
 
-Heres the equation for unprojection consistency loss:
-$\ell_{UC} = \mu\left(\sigma\left(u\right)_{1 \dots L}\right)$
+To maintain surface consistency, we sample a random batch of UVL scenes $S\toB$, and translate them into $\ph\toB$.
+Using geometric knowledge of the scene encoded in $S\toB$, we individually unproject each $\ph_i \in \ph\toB$ back into texture space, to obtain $B$ sets of $L$ unprojected textures $u\toBL$.
+We then use the per-pixel, batch-wise standard deviation of the unprojections as unprojection consistency loss $\lUC = \sigma(u\toBL)\toL$.
+This loss observes how badly these unprojections differ from one another, and thus how different the object surfaces appear between translations.
 
-This benefits from large batch sizes, but that often makes you run out of vram.
+Intuitively, if $\lUC$ were $0$, it would mean the object surfaces in translations $\ph$ appear exactly the same in every scene.
 
-Also, you have to get lucky - two scene pictures have to show the same side of a cube for example. First person scenarios would be even worse.
+This loss is a fairly intuitive and effective way to maintain surface consistency. There are some caveats to this loss, however.
+In order to produce a standard deviation greater than $0$, we must have a batch size greater than $1$.
+In fact, $\lUC$ is most useful with large batch sizes because observing the same surface in multiple elements of a batch becomes more likely as the batch size increases.
+There is a limited number of elements we can fit into video memory, so environments that rarely show a particular region of a surface will rarely have $\lUC$ applied to that region.
+In first-person environments, this might be more of a problem - particularly when exploring multiple rooms (a task we haven't done though - should I mention this?)
 
-Also, the resolution of the unprojection matters:
+To michael: Should we mention these caveats in this section, or mention them in the texture realism loss section? That section addresses all of these issues...
 
-\begin{figure}[H]
-	\begin{center}
-		\includegraphics[width=400pt]{../images/unprojection_resolution_comparison.pdf}
-	\end{center}
-	\caption{
-		The resolution of an unprojection matters for unprojection consistency loss.
-The larger it is, the more precise the alignment will be but the less likely a given UV value is to be assigned a loss greater than 0, lowering numerical instability.
-	}
-	\label{fig:unprojection_resolution_comparison}
-\end{figure}
+% Also, you have to get lucky - two scene pictures have to show the same side of a cube for example. First person scenarios would be even worse.
 
@@
 
+\section{Appendix} 
+Also, the resolution of the unprojection matters:
+
+\begin{figure}[H]
+	\begin{center}
+		\includegraphics[width=400pt]{../images/unprojection_resolution_comparison.pdf}
+	\end{center}
+	\caption{
+		The resolution of an unprojection matters for unprojection consistency loss.
+The larger it is, the more precise the alignment will be but the less likely a given UV value is to be assigned a loss greater than 0, lowering numerical instability.
+	}
+	\label{fig:unprojection_resolution_comparison}
+\end{figure}
+
 \end{document}

### 2022-06-11 CORL/example.tex
Added some texture realism text

@@
 \subsection{Image Translation}
+\label{sec:image_translation}
 
@@
 \subsection{Unprojection Consistency Loss}
-\label{unprojection_consistency_loss}
+\label{sec:unprojection_consistency_loss}
 
@@
 We then use the per-pixel, batch-wise standard deviation of the unprojections as unprojection consistency loss $\lUC = \sigma(u\toBL)\toL$.
-This loss observes how badly these unprojections differ from one another, and thus how different the object surfaces appear between translations.
+This loss observes how different these unprojections are from one another, and thus how different the object surfaces appear between translations.
 
@@
 
-This loss is a fairly intuitive and effective way to maintain surface consistency. There are some caveats to this loss, however.
+This loss is a fairly intuitive and effective way to maintain surface consistency. There are some caveats, however.
 In order to produce a standard deviation greater than $0$, we must have a batch size greater than $1$.
-In fact, $\lUC$ is most useful with large batch sizes because observing the same surface in multiple elements of a batch becomes more likely as the batch size increases.
-There is a limited number of elements we can fit into video memory, so environments that rarely show a particular region of a surface will rarely have $\lUC$ applied to that region.
-In first-person environments, this might be more of a problem - particularly when exploring multiple rooms (a task we haven't done though - should I mention this?)
+Furthermore, environments that rarely show a particular region of a surface will rarely have $\lUC$ applied to that region because they're unlikely to show up twice in the same batch.
+For this reason, $\lUC$ is most useful with large batch sizes.% because observing the same surface in multiple elements of a batch becomes more likely as the batch size increases.
+But because video memory limits our batch sizes, first-person environments might be more of a challenge for $\lUC$ - particularly when exploring multiple rooms (a task we haven't done though - should I mention this?)
 
@@
 \end{figure}
+
+We can improve the translation results by forcing the neural texture to look realistic, instead of allowing it to have arbitrary colors.
+
+So far, we've taken an image translator $T$ and added neural textures $\tau$ and a surface consistency constraint $\lUC$. 
+If we wanted to, could stop here - those formulations are sufficient to produce consistent sim-to-real translations.
+However, we can improve this further.
+
+Up until now we have not put any constraints on this neural texture. With only the above constraints, $\tau$ might look wildly different each time you train it.
+As seen in the top row of figure \ref{fig:texture_realism_ablation}, the neural texture might not look anything like the translation results.
+
+We introduce a new loss, called texture realism loss. $\lTR$ image similarity loss that encourages $\pi \approx \ph$.
+In other words, $\lTR$ makes the neural texture more realistic by making the neural texture projections more realistic.
+This loss forces the neural texture to approximate the albedo of the surfaces in a scene.
+This image similarity loss is calculated the same way image similarity losses are calculated in section \ref{sec:image_translation}: L2 loss minus MSSSIM.
 

### 2022-06-11 CORL/example.tex
Moved texture realism theory to appendix

@@
 We can improve the translation results by forcing the neural texture to look realistic, instead of allowing it to have arbitrary colors.
+To do this we add an image similarity loss that makes $\pi$ look like its translation $\hat{p}$.
 
@@
 This helps improve the translations.
-
-Texture realism loss equation:
-$L_{TR}=L_{TR_{l2}}+L_{TR_{msssim}}$
-where 
-$L_{TR_{msssim}} = -msssim(\pi,\hat{p})$ and
-$L_{TR_{l2}} = \frac{
-	\sum\limits_{i=1}^B {
-	   %  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}
-	   \left( \pi-\hat{p}  \right)^2
-		} 
-   }
-   {B}$
-
-There's a good reason for this: it's almost equivalent to unprojection consistency.
-In fact, it can even be used on its own without unprojection consistency loss (both are sufficient to translate things.)
-
-(Give theoretical explation)
-$
-\ell_{UC} = 
-\
-\
-\mu\left(\sigma\left(u_{1\dots B,\ 1\dots L}\right)_{1 \dots L}\right) = 
-\sqrt{
-\frac{
-	 \sum\limits_{i=1}^B {
-		%  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}
-		\left( \hat{p}-\bar{p}  \right)^2
-		 } 
-	}
-	{B}
-}
-$
-Using $\bar{p}$ from figure \ref{fig:unprojection_consistency_loss}
-
-Becuase $\bar{p}$ is created from the average recovered texturs of $\hat{p}$, $\bar{p} \approx \hat{p}$.
-
-Becuse of texture realism loss, $\pi \approx \hat{p}$.
-
-Therefore, $\bar{p} \approx \hat{p} \approx \pi$
-
-% The l2 component of the texture realism loss equation:
-% $ \
-% \
-% \
-% \
-% \ \ell_{TR_{l2}}=\sum\limits_{i=1}^B {
-% 	%  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}
-% 	\left( \pi-\hat{p}  \right)^2
-% 	 } 
-% $
-
-Substituting one projected texture for another, aka $\pi$ for $\bar{p}$, we get 
-$ \
-\
-\
-\
-\ \ell_{TR_{l2}}
-\approx
-\frac{\sum\limits_{i=1}^B {
-	%  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}
-	\left( \hat{p}-\pi  \right)^2
-	 }}{B} = \ell_{UC}^2
-$
 
@@
 \section{Appendix} 
+\label{sec:appendix}
+
+	\subsection*{Unprojection Recovery Resolution Effect}
+
 		Also, the resolution of the unprojection matters:
@@
 
+	\subsection*{Texture Realism Theory}
+		\label{sec:texture_realism_theory}
+		Texture realism loss equation:
+		$L_{TR}=L_{TR_{l2}}+L_{TR_{msssim}}$
+		where 
+		$L_{TR_{msssim}} = -msssim(\pi,\hat{p})$ and
+		$L_{TR_{l2}} = \frac{
+			\sum\limits_{i=1}^B {
+			%  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}
+			\left( \pi-\hat{p}  \right)^2
+				} 
+		}
+		{B}$
+
+		There's a good reason for this: it's almost equivalent to unprojection consistency.
+		In fact, it can even be used on its own without unprojection consistency loss (both are sufficient to translate things.)
+
+		(Give theoretical explation)
+		$
+		\ell_{UC} = 
+		\
+		\
+		\mu\left(\sigma\left(u_{1\dots B,\ 1\dots L}\right)_{1 \dots L}\right) = 
+		\sqrt{
+		\frac{
+			\sum\limits_{i=1}^B {
+				%  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}
+				\left( \hat{p}-\bar{p}  \right)^2
+				} 
+			}
+			{B}
+		}
+		$
+		Using $\bar{p}$ from figure \ref{fig:unprojection_consistency_loss}
+
+		Becuase $\bar{p}$ is created from the average recovered texturs of $\hat{p}$, $\bar{p} \approx \hat{p}$.
+
+		Becuse of texture realism loss, $\pi \approx \hat{p}$.
+
+		Therefore, $\bar{p} \approx \hat{p} \approx \pi$
+
+		% The l2 component of the texture realism loss equation:
+		% $ \
+		% \
+		% \
+		% \
+		% \ \ell_{TR_{l2}}=\sum\limits_{i=1}^B {
+		% 	%  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}
+		% 	\left( \pi-\hat{p}  \right)^2
+		% 	 } 
+		% $
+
+		Substituting one projected texture for another, aka $\pi$ for $\bar{p}$, we get 
+		$ \
+		\
+		\
+		\
+		\ \ell_{TR_{l2}}
+		\approx
+		\frac{\sum\limits_{i=1}^B {
+			%  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}
+			\left( \hat{p}-\pi  \right)^2
+			}}{B} = \ell_{UC}^2
+		$
+
 \end{document}

### 2022-06-11 CORL/example.tex
Tidied up texture reality section

--- 2022-06-11 CORL/example.tex
@@
 We can improve the translation results by forcing the neural texture to look realistic, instead of allowing it to have arbitrary colors.
+To do this, we add a texture realism loss $\lTR$.
+$\lTR$ is an image similarity loss that makes $\pi$ look like its translation $\hat{p}$.
+In other words, $\lTR$ makes the neural texture more realistic by making the neural texture projections more realistic.
 
@@
 
-Up until now we have not put any constraints on this neural texture. With only the above constraints, $\tau$ might look wildly different each time you train it.
-As seen in the top row of figure \ref{fig:texture_realism_ablation}, the neural texture might not look anything like the translation results.
+% Up until now we have not put any constraints on this neural texture. 
+Without $\lTR$, $\tau$ can look wildly different each time you train it.
+As seen in the top row of figure \ref{fig:texture_realism_ablation}, the neural texture looks very unrealistic - the colors are completely arbitrary.
+After adding $\lTR$ though, $\pih \approx \ph$, and $\tau$ to represents the albedo of the surfaces in the scene.
+The image similarity loss used in $\lTR$ is calculated the same way image similarity losses are calculated in section \ref{sec:image_translation}: L2 loss minus MSSSIM.
 
-We introduce a new loss, called texture realism loss. $\lTR$ image similarity loss that encourages $\pi \approx \ph$.
-In other words, $\lTR$ makes the neural texture more realistic by making the neural texture projections more realistic.
-This loss forces the neural texture to approximate the albedo of the surfaces in a scene.
-This image similarity loss is calculated the same way image similarity losses are calculated in section \ref{sec:image_translation}: L2 loss minus MSSSIM.
+As it turns out, $\lTR$ is sufficient to ensure surface consistency without $\lUC$, though using both yields better results than either one alone. 
+For an explanation of why this is the case, see the appendix \ref{sec:texture_realism_theory}.
+There are some advantages to using $\lTR$ alone though: when just using $\lTR$ you can use batch sizes as small as $B=1$, allowing you to save video memory. 
+Using $\lTR$ is also more numerically stable, as you no longer have to worry about whether the same surfaces are seen across multiple scenes in a batch.
 
-These images could be regularized so that they're the same every time.
+% We introduce a new loss, called texture realism loss that fixes this: $\lTR$ is an image similarity loss that encourages $\pi \approx \ph$.
+% This loss forces the neural texture to approximate the albedo of the surfaces in a scene.
 
-To do this we put a penalty on the latent texture that makes it $\pi$ look like its translation $\hat{p}$.
+% These images could be regularized so that they're the same every time.
+% 
+% To do this we put a penalty on the latent texture that makes it $\pi$ look like its translation $\hat{p}$. 
+% 
+% We use l2 and msssim losses to do this.
+% 
+% This helps improve the translations.
+% 
+% There are some advantages over unprojection consistency though: 
+% smaller batch sizes (even a batch size of 1, which UC cant do),
+% you don't have to get lucky (the more chaotic, or even the more zoomed in a dataset becomes the less likely there is to be any collisions)
 
-We use l2 and msssim losses to do this.
+\subsection{Color Loss}
+ASK MICHAEL: I'd rather not mention this and run out the page limit...it's not very important, and not used in the robot experiments.
+It's only used in the experiment with the five items including the apple.
+Can we add it to the appendix instead?
 
-This helps improve the translations.
+%===============================================================================
+
+\section{Results}
+\label{sec:results}
+
+\begin{figure}[H]
+	\begin{center}
+		\includegraphics[width=400pt]{../images/frame_inconsistency_diagram.pdf}
+	\end{center}
+
+	% Each outline color corresponds to the same cube.
+	% The same cubes are marked with the same colored outlines across all photos.
+	% For the same cube, we expect to see the same number on the top of the cube regardless of its placement.
+
+	\caption{
+		Each row of images shows a different random placement of objects in the scene.
+		Each column of images is a different image translation algorithm.
+		The same cube is marked with the same color outline across all photos.
+		TRITON is consistent: for example, the cube outlined as yellow always has an 8 on the top.
+		Meanwhile, CycleGan for example shows a 4 on the top of that cube in the top two rows, but an 8 and a 7 in the next two rows.
+		Because of the symmetry of the cubes, and the unsupervised training, it is arbitrary which synthetic cube gets which symbol after training - but whatever it chooses, it should be consistent between placements.
+		CUT and CycleGan are not consistent, while TRITON is.
+		% TODO: Update the images in this to have the latest training iteration...
+		}
+	\label{fig:frame_inconsistency_diagram}
+\end{figure}
+
+%===============================================================================
+
+\section{Limitaions}
+\label{sec:Limitations}
+
+Can't handle transparent objects. 
+A limited number of objects can be learned at once before supervision is necessary with color loss (but there are workarounds).
+Takes a long time to train.
+
+%===============================================================================
+
+\section{Citations} 
+\label{sec:citations}
+
+Citations can be made using either \textbackslash citep\{\} or \textbackslash citet\{\}, depending on the appropriateness.
+To avoid the citation moving to the next line, it is often a good practice to replace the space before with a tilde (\~{}) character.
+Example 1: ``CoRL is the best conference ever~\citep{fourier_feature_networks}.''
+Example 2: ``\citet{fourier_feature_networks} proved, both theoretically and numerically, that CoRL is the best conference ever.''
+
+%===============================================================================
+
+\clearpage
+% The acknowledgments are automatically included only in the final and preprint versions of the paper.
+\acknowledgments{}
+
+%===============================================================================
+
+\bibliography{example}  % .bib
+
+\clearpage
+
+\section{Appendix} 
+\label{sec:appendix}
+
+	\subsection*{Unprojection Recovery Resolution Effect}
+
+		Also, the resolution of the unprojection matters:
+
+		\begin{figure}[H]
+			\begin{center}
+				\includegraphics[width=400pt]{../images/unprojection_resolution_comparison.pdf}
+			\end{center}
+			\caption{
+				The resolution of an unprojection matters for unprojection consistency loss.
+The larger it is, the more precise the alignment will be but the less likely a given UV value is to be assigned a loss greater than 0, lowering numerical instability.
+			}
+			\label{fig:unprojection_resolution_comparison}
+		\end{figure}
+
+	\subsection*{Texture Realism Theory}
+		\label{sec:texture_realism_theory}
+
+		THIS SECTION IS UNPOLISHED, BUT CONTAINS  THE NESSECARY CONTENT.
+		I'll delete this section if you don't think its important enough to keep.
 
@@
 
-There are some advantages over unprojection consistency though: 
-smaller batch sizes (even a batch size of 1, which UC cant do),
-you don't have to get lucky (the more chaotic, or even the more zoomed in a dataset becomes the less likely there is to be any collisions)
-
-\subsection{Color Loss}
-
-%===============================================================================
-
-\section{Results}
-\label{sec:results}
-
-\begin{figure}[H]
-	\begin{center}
-		\includegraphics[width=400pt]{../images/frame_inconsistency_diagram.pdf}
-	\end{center}
-
-	% Each outline color corresponds to the same cube.
-	% The same cubes are marked with the same colored outlines across all photos.
-	% For the same cube, we expect to see the same number on the top of the cube regardless of its placement.
-
-	\caption{
-		Each row of images shows a different random placement of objects in the scene.
-		Each column of images is a different image translation algorithm.
-		The same cube is marked with the same color outline across all photos.
-		TRITON is consistent: for example, the cube outlined as yellow always has an 8 on the top.
-		Meanwhile, CycleGan for example shows a 4 on the top of that cube in the top two rows, but an 8 and a 7 in the next two rows.
-		Because of the symmetry of the cubes, and the unsupervised training, it is arbitrary which synthetic cube gets which symbol after training - but whatever it chooses, it should be consistent between placements.
-		CUT and CycleGan are not consistent, while TRITON is.
-		% TODO: Update the images in this to have the latest training iteration...
-		}
-	\label{fig:frame_inconsistency_diagram}
-\end{figure}
-
-%===============================================================================
-
-\section{Limitaions}
-\label{sec:Limitations}
-
-Can't handle transparent objects. 
-A limited number of objects can be learned at once before supervision is necessary with color loss (but there are workarounds).
-Takes a long time to train.
-
-%===============================================================================
-
-\section{Citations} 
-\label{sec:citations}
-
-Citations can be made using either \textbackslash citep\{\} or \textbackslash citet\{\}, depending on the appropriateness.
-To avoid the citation moving to the next line, it is often a good practice to replace the space before with a tilde (\~{}) character.
-Example 1: ``CoRL is the best conference ever~\citep{fourier_feature_networks}.''
-Example 2: ``\citet{fourier_feature_networks} proved, both theoretically and numerically, that CoRL is the best conference ever.''
-
-%===============================================================================
-
-\clearpage
-% The acknowledgments are automatically included only in the final and preprint versions of the paper.
-\acknowledgments{}
-
-%===============================================================================
-
-\bibliography{example}  % .bib
-
-\section{Appendix} 
-Also, the resolution of the unprojection matters:
-
-\begin{figure}[H]
-	\begin{center}
-		\includegraphics[width=400pt]{../images/unprojection_resolution_comparison.pdf}
-	\end{center}
-	\caption{
-		The resolution of an unprojection matters for unprojection consistency loss.
-The larger it is, the more precise the alignment will be but the less likely a given UV value is to be assigned a loss greater than 0, lowering numerical instability.
-	}
-	\label{fig:unprojection_resolution_comparison}
-\end{figure}
-
 \end{document}

### 2022-06-12 CORL/example.tex
Minor edits + added color loss

@@
 
-	TRITON's neural texture module is what lets it learn the albedo of objects, and thus take advantage of 3d geometric priors.
+	TRITON's neural texture module lets it  of objects, and thus take advantage of 3d geometric priors.
 By learning this texture, we can encode features directly onto the surfaces of the 3d objects in a scene, which the image translation module uses to maintain visual consistency between states and viewpoints.
@@
 	These neural textures are not stored in raster form during training.
-Instead, as illustrated in figure \ref{fig:learnable_textures}, they're paramaterized by a pixel-wise fourier feature network \cite{fourier_feature_networks} that takes in UV coordinates and returns RGB colors.
+Instead, as illustrated in figure \ref{fig:learnable_textures}, they're paramaterized by pixel-wise fourier feature networks \cite{fourier_feature_networks} that take in UV coordinates and returns RGB colors.
 During inference, however, these textures are rasterized to save both time and video memory.
@@
 The trained fourier-feature textures also exhibit less noise than its raster counterparts.
-We think this is because they don't suffer as much from aliasing artifacts in the UV maps, where the loss gradient might skip over pixels in texture-space when the UVL scene is zoomed out too far or raster resolution is too high.
+We think this is because they don't suffer as muchIt cfrom aliasing artifacts in the UV maps, where the loss gradient might skip over pixels in texture-space when the UVL scene is zoomed out too far or raster resolution is too high.
 Case in point: if you have a raster texture with very high resolution, the loss gradient is less likely to be passed to a given texel because the chance that a given UV value in a scene will be rounded to that pixel's coordinates is very small.
@@
 Our image translation module, $T$, is based on the image translation module used in \citep{surgical_video_translation}, which is a based on a variant \cite{surgical_image_translation} of MUNIT \cite{munit}.
-The main differences between our image translation model and MUNIT are that our style code is fixed making it unimodal, noise is injected into the latent codes during training to prevent overfitting, and the reconstruction criterion we use.
+The main differences between our image translation model and MUNIT are that our style code is fixed making it unimodal, noise is injected into the latent codes during training to prevent overfitting, and we use a different image similarity metric.
 During inference however, this intermediate noise is removed and our image translation module is completely determinstic.
@@
 \subsection{Color Loss}
-ASK MICHAEL: I'd rather not mention this and run out the page limit...it's not very important, and not used in the robot experiments.
+
+TRITON is very robust to geomtric imperfections. However, sometimes it takes this a bit too far - it can overfit textures onto the wrong objects and still maintain consistency.
+In one example, it manages to map an apple texture onto a cube.
+
+To help TRITON correctly match textures to objects, we introduce a small amount of supervision by adding a color loss.
+I'm going to stop writing this because I don't know if I even want to keep this in the paper...you can achieve the same result by running the algorithm multiple times, and so its not strictly nessecary.
+
+ASK MICHAEL: I'd rather not mention this entire section and run out the page limit...it's not very important, and not used in the robot experiments.
 It's only used in the experiment with the five items including the apple.

### 2022-06-12 CORL/example.tex
Added method overview

@@
 \newcommand{\toB}{_{1\dots B}}
-\newcommand{\toBL}{_{1\dots B,1\dots L}}
+% \newcommand{\toBL}{_{1\dots B,\text{ } 1\dots L}}
+\newcommand{\toBL}{_{1\dots B, 1\dots L}}
 \newcommand{\toL}{_{1\dots L}}
@@
 \usepackage{amsfonts}
+\usepackage{amsmath}
 
@@
 
+Domain A and B
+p hat
+s hat
+
 \section{Method}
@@
 	\caption{
-			We use differentiable rendering paired with unpaired image translation to consistently= transform synthetic scenes into realistic images.
-			To ensure all objects look consistent in different positions and views, we learn the albedo of each object's surface by using a learnable latent texture.
-			This texture is parametrized as an image generated by an MLP which is fed Fourier features, as shown in figure \ref{fig:learnable_textures}.
-			$B$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
+		% We use differentiable rendering paired with unpaired image translation to consistently= transform synthetic scenes into realistic images.
+		% To ensure all objects look consistent in different positions and views, we learn the albedo of each object's surface by using a learnable latent texture.
+		% This texture is parametrized as an image generated by an MLP which is fed Fourier features, as shown in figure \ref{fig:learnable_textures}.
+		% $B$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
+		This figure is an overview of how TRITON works, showing all submodules and losses.
 		Inputs are on the left, and outputs are on the right.
 		The dashed arrows indicate losses between nodes.
-			Although $\pi_{1\dots B}$ and $\hat{p}_{1\dots B}$ look similar, they are not identical. 
-			$\pi$ is simply projected textures, whereas $\hat{p}$ has been run through an image translator, allowing it to have shadows and specularities.
+		Although $\pi\toB$ and $\ph\toB$ look similar, they are not identical - $\lTR$ encourages them to look as similar as possible.
+		% $\pi$ is simply projected textures, whereas $\hat{p}$ has been run through an image translator, allowing it to have shadows and specularities.
 		% TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
@@
 \end{figure}
+
+	In this section, we describe how TRITON works to translate images from domain A (simulation) to domain B (photos) while maintaining surface consistency. 
+	TRITON has four main components: a neural texture, an image translator, and two surface consistency losses.
+	\begin{enumerate}
+		\item{
+			Neural Textures $\tau\toL$: Given an input scene $s$ depicting 3d objects with labels $1\dots L$, we project learnable RGB textures $\tau\toL$ to their surfaces to obtain projection $\pi$. 
+			These neural textures are represented implicitly by a neural network that maps UV values to RGB values, and are learned jointly with the image translator.
+			\begin{equation}
+				\pi=\tau\toL(s)
+			\end{equation}
+			We then concatenate the scenes with the projections channelwise to obtain images from domain A: $\ppis \in A$.
+		}
+		\item{
+			Bidirectional Image Translator $T$: $\Tab$ translates images from domain A to domain B, and $\Tba$ translates images from domain B to domain A.
+			\begin{equation}
+				\ph=\Tab(\pis)\ \ \ \text{ and }\ \ \ \ppish=\Tba(p)
+			\end{equation}
+			$T$ is a variation of MUNIT, and inherits adversarial losses $\ell_{adv}$, as well cycle consistency losses $\ell_{cyc}$ and reconstruction losses $\ell_{rec}$.
+		}
+		\item {
+			Unprojection Consistency Loss $\lUC$: To keep the object surfaces consistent between a batch of $B$ scenes, we impose a pixel-wise similarity loss between these surfaces by warping them back into a common texture space using the UV and label values contained in the original scene.
+			\begin{equation}
+				u\toBL=\text{unproject}(\ph\toB,s\toB)\ \ \ \text{ and } \ \ \ \lTR \Rightarrow u_1 \approx u_2 \dots \approx u_B
+			\end{equation}
+		}
+		\item{
+			Texture Realism Loss $\lTR$: To encourage the neural textures to look as realistic as possible, we try to make the projections look like the final output. 
+			\begin{equation}
+				\lTR \Rightarrow \pi \approx \ph
+			\end{equation}
+			As it turns out, $\lTR$ is sufficiently powerful loss to generate surface-consistent translations even without $\lUC$, although the results are better when both losses are used.
+		}
+
+	\end{enumerate}
 
@@
 For our purposes, MS-SSIM is a metric that measures the similarity of two BCHW tensors on a scale from 0 to 1.
-Given two tensors $x$ and $y$, their similarity loss is $\mu\left((x-y)^2\right) - msssim(x,y)$.
+Given two tensors $x$ and $y$, their similarity loss is $\mu\left((x-y)^2\right) - \text{msssim}(x,y)$.
 

### 2022-06-12 CORL/example.tex
Updates from Overleaf

--- 2022-06-11 CORL/example.tex
@@
-%TODO:
-%	Formulation Section
-%	Figures
-%		Main diagram - break it up into pieces with just text
-%		UVL three-axis diagram
-%		Replace C with (pi,s)
-%	Method:
-%		Unprojection Consistency Loss
-%		Texture Reality Loss
-
-%TODO:
-%	Formulation Section
-%	Figures: Main diagram - break it up into pieces with just text
-%	Figures: UVL three-axis diagram
-%	Method:	Unprojection Consistency Loss
-%	Method:	Texture Reality Loss
-
-\newcommand{\Tab}{T_{A\rightarrow B}}
-\newcommand{\Tba}{T_{B\rightarrow A}}
-\newcommand{\pih}{\hat{\pi}}
-\newcommand{\sh}{\hat{s}}
-\newcommand{\ph}{\hat{p}}
-\newcommand{\pis}{\pi,s} % pi and s pairs from domain A
-\newcommand{\pish}{\pih,\sh} % pi and s pairs from domain A
-\newcommand{\ppis}{(\pis)} %Parenthesized pis
-\newcommand{\ppish}{(\pish)} %Parenthesized pis
-
-\newcommand{\toB}{_{1\dots B}}
-\newcommand{\toBL}{_{1\dots B,1\dots L}}
-\newcommand{\toL}{_{1\dots L}}
-
-\newcommand{\lUC}{\ell_{UC}}
-\newcommand{\lTR}{\ell_{TR}}
-
-%%%%%%%%%%%%BIG TODO::::
-%%%%%% MAKE BATCH SIZE N INSTEAD OF B - B is a domain!
-
 \documentclass{article}
 
-% \usepackage{corl_2022} % Use this for the initial submission.
-\usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
+\usepackage{corl_2022} % Use this for the initial submission.
+% \usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
 \usepackage{graphicx}
@@
 
-% \title{TRITON: Globally Consistent Sim-to-Real Transfer
-\title{Neural Textures make Better Simulators
-
-``I can't believe it's not real!" %Definitely gonna delete this lol
- %via Neural Textures
- }
+\title{TRITON: Globally Consistent Sim-to-Real Transfer}
 
@@
 
-	QUESTIONS FOR MICHAEL:
-	\begin{itemize}
-		\item - TODO: WE MAINTAIN WHAT WE NOW CALL "SURFACE CONSISTENCY" instead of view consistency! Or texture consistency? Etc? What should we call it?
-	\end{itemize}
-
 	Unpaired image translation algorithms can be used for sim-to-real tasks, but most fail to generate temporally consistent results.
@@
 
-TODO: Note that the simple input of UVL, or an RGB neural texture, means any simulator should be plug-and-play with this algorithm.
-
 Recently, several sim-to-real algorithms have come out that are based on image-to-image translation. [Citations]
@@
 
-\section{Formulation}
+\section{Data}
 \label{sec:data}
-
-TODO: Describe what UVL is ; 
-Formulate the setting: What our inputs are and the targets are and what we learn (a neural texture function) and how we can take advantage of it for robotic learning.
-Don't go into details; just say 'its a black box function'
-
-TODO: Add UV to the fourier feature diagram.
-
-TODO: Create subfigures with subcaptions. 
-2a: Nothing but UVL=UV+L
-2b. 3d uvl axis to texture pack (drew on whiteboard)
-2c. Skip over the translation network and show a pretty robot arm picture
-
-This is the formulatoin section; not data section. Dont talk about how many photos we use etc.
-
-JUST IN CASE THINGS ARE ERASED:
-We learn neural texture corresponding to each object, where each texture is represented as a function mapping... 
-The idea is to learn object textures as a set of continuous functions from a set of (unlabeled) real images, and use them to generate realistic images.
-Given a 3D structure of the scene represented with a UVL image, the learned neural textures will translate them into a realistic image.
-When used for the robot learning, this enables learnable, realistic sim2real of robot training images.
-
-IN THE INTRODUCTION: How we're using a neural neural network network texture. Also in related works.
-
-TODO: Replace neural texture in figure 3 with axis, and treat it as a function that takes UV in with an arrow pointing to it.
-
-BREAK IT DOWN APPROACH:
-Don't have any pictures. Have breakdown where we add new things in multiple figures.
-First figure: Just image translation. 
-Seconf:
-Third:
-Etc...
 
@@
 
+    \textbf{We need some general method description like below:}
+    We learn neural texture corresponding to each object, where each texture is represented as a function mapping... 
+    The idea is to learn object textures as a set of continuous functions from a set of (unlabeled) real images, and use them to generate realistic images.
+    Given a 3D structure of the scene represented with a UVL image, the learned neural textures will translate them into a realistic image.
+    When used for the robot learning, this enables learnable, realistic sim2real of robot training images.
+
 	\begin{figure}[H]
@@
 
-\subsection{Neural Texture and Projection}
+\subsection{Neural Texture}
 
@@
 
-	TRITON's neural texture module is what lets it learn the albedo of objects, and thus take advantage of 3d geometric priors.
-By learning this texture, we can encode features directly onto the surfaces of the 3d objects in a scene, which the image translation module uses to maintain visual consistency between states and viewpoints.
+    The neural texture is a neural function not pixel grid.
 
+	$B$ is the batch size.
 Given a batch of $B$ UVL Scenes $s_{1\dots B}$ with $L$ different label values, we project $L$ different neural textures $\tau_{1\dots L}$ onto that scene; obtaining projections $\tau_{1\dots B}$.
@@
 	Given a two-dimensional $uv$ vector, the spatial frequencies are used to generate a high dimensional embedding used as input for the MLP.
-	\begin{equation}
+	\makebox[\textwidth]
+	{
+		$
 		\tau_i(uv) = 
@@
 		\right]\right)
-	\end{equation}
+		$
+	}
 	where $uv$ and $f_i \in N_{ormal}(\mu=0,\ \sigma=10)$ are two dimensional vectors,
@@
 \subsection{Image Translation}
-\label{sec:image_translation}
-
-% TO PUT IN FORMULATION:
-% The simulation domain A (UVL maps concatenated to their texture projections) has 6 channels, whereas the real image domain B (photographs) has 3 channels.
-An element of A is $\ppis \in A$ and $p \in B$.
-% $p \in B$ is a batch of real photos,
-% and $\ppis\in A$ is a batch of simulated projection/uvl scene concatenations.
-
-% TODO: Why doesn't citep work? The references don't show the authors names...it used to work...did I mess up example.bib?
-
-% TODO: Get rid of the variable "C" and replace it with $\ppis$
-
-% TODO: Is l2 loss capitalized or lower case?
-
-Our image translation module, $T$, is based on the image translation module used in \citep{surgical_video_translation}, which is a based on a variant \cite{surgical_image_translation} of MUNIT \cite{munit}.
-The main differences between our image translation model and MUNIT are that our style code is fixed making it unimodal, noise is injected into the latent codes during training to prevent overfitting, and the reconstruction criterion we use.
-During inference however, this intermediate noise is removed and our image translation module is completely determinstic.
-Apart from these differences, our image translation module has the same loss formulations and generator/encoder/discriminator network architectures as MUNIT.
+Our image translation module $T$ is based on the image translation module used in \citep{surgical_video_translation}, which is a variant of MUNIT \cite{munit}.
+Like in \citep{surgical_video_translation} but unlike MUNIT, however, the style code is fixed and noise is injected into the latent codes to prevent overfitting.
+During inference, our image translation module is completely determinstic.
 
 $T$ is a bidirectional image translation module, and has two translation directions.
-$\Tab$ translates sim to real (aka domain A to domain B), and $\Tba$ translates real to sim (aka domain B to domain A).
+$T_{A\rightarrow B}$ translates sim to real (aka domain A to domain B), and $T_{B\rightarrow A}$ translates real to sim (aka domain B to domain A).
+The simulation domain A (UVL maps concatenated to their texture projections) has 6 channels, whereas the real image domain B (photographs) has 3 channels.
 
-MUNIT translates images by encoding both image domains into a common latent space, then decoding them into their respective domains.
-In our translation module, we define fake photos $\ph = \Tab(\pis) = G_B(E_A(\pis))$ and fake projection/uvl scenes $\ppish = \Tba(p) = G_A(E_B(p))$
-	where $E_A, E_B, G_A, G_B$ are encoders and generators for domains A and B respectively.
-% We also define the outputs of these translators as fake photos $\hat{p} = T_{A\rightarrow B}(\pis)$ and fake projection/uvl scenes $(\hat{\pi},\hat{s}) = T_{A\rightarrow B}(\pis)$.
+Apart from these differences, the losses pertaining directly to image translation are the same as that in MUNIT.
 
-% TODO: Choose one of the three equation representations. Which is best? The next paragraph will look less ugly when the equations are shorter.
-
-To ensure cycle consistency, we have an image similarity loss $\ell_{cyc}$ to ensure
-% $c \approx G_A(E_B(G_B(E_A(\pis)))) = T_{B\rightarrow A}(T_{A\rightarrow B}(\pis)) = T_{B\rightarrow A}(\hat{p})$
-$\ppis \approx T_{B\rightarrow A}(\hat{p})$
-and vice versa
-% $p \approx G_B(E_A(G_A(E_B(p)))) = T_{A\rightarrow B}(T_{B\rightarrow A}(\pis)) = T_{A\rightarrow B}(\hat{c}) = T_{A\rightarrow B}(\hat{\pi},\hat{s})$. 
-$p \approx T_{A\rightarrow B}(\hat{\pi},\hat{s})$.
-%I only want to use one of the two representations; either using T_AB or GA(EB) etc. Which one should I use?
-We also impose an image similarity loss $\ell_{rec}$ to ensure that $\ppis \approx G_A(E_A\ppis)$ and $p \approx G_B(E_B(p))$, which is effectively an autoencoder loss. 
-In addition, we also have content similarity loss $ \ell_{con}$ to make 
-$E_A(\pis) \approx E_B(\ph)$ and $E_A(p) \approx E_A(\pish)$.
-% $E_A(\pis) \approx E_B(\Tab(\pis))$ and $E_A(p) \approx E_A(\Tba(p))$.
-
-Our similarity losses are the sum of L2 distance and negative multi scale structural image similarity (MS-SSIM), introduced in \citep{msssim}.
-For our purposes, MS-SSIM is a metric that measures the similarity of two BCHW tensors on a scale from 0 to 1.
-Given two tensors $x$ and $y$, their similarity loss is $\mu\left((x-y)^2\right) - msssim(x,y)$.
-
-We also have adversarial losses $\ell_{adv}$ that come from two discriminators $D_A$ and $D_B$, targeting domains A and B respectively. They use the LS-GAN loss introduced in \citep{lsgan}.
-
-In total, the loss for the image translator module $T$ is $\ell_T=\ell_{cyc}+\ell_{rec}+\ell_{con}+\ell_{adv}$.
-
-% NOTE: THe other paper \citep{surgical_video_translation} didn't do into this much detail; instead putting most of these losses in teh appendix.
-I think we can cut this down?
-I'll check with michael first...right now I'll include everything.
+Due to the way MUNIT works, we define
+$T_{A\rightarrow B}\left(c\right) = dec_B\left(enc_A\left(c\right)\right)$
+and 
+$T_{B\rightarrow A}\left(p\right) = dec_A\left(enc_B\left(p\right)\right)$
+where $enc_A, enc_B, dec_A, dec_B$ are encoders and decoders for domains A and B respectively, $p$ is a batch of real photos, and $c$ is a batch of simulated UVL+projection concatenations.
 
 \subsection{Unprojection Consistency Loss}
-\label{sec:unprojection_consistency_loss}
 
@@
 		This is the unprojection consistency loss used in figure \ref{fig:main_diagram}.
-		The Unprojection Mean and Reprojection nodes are not used in any losses, and help to illustrate the next section \ref{sec:texture_realism_loss}.
-		% After calculating fake photos $\hat{p}_{1...B}$ from UVL scenes $s_{1...B}$ as seen in figure \ref{fig:main_diagram}, 
-		% we can unproject fake photos $\hat{p}_{1...B}$ back into texture space to obtain $u_{1...B,\ 1...L}$ .
-		% If the fake photos display consistent textures along their 3d surfaces, then the unprojected textures should be similar.
-		% We can measure this similarity by taking the per-channel standard deviation of these unprojections, aka $\sigma(u)$, then averaging the result.
-		% When the fake photos display similar surfaces, the unprojections will be similar making the unprojection consistency loss low.
-		% Additionally, we can also calculate the average unprojection, which is useful for visualization purposes (it will look blurry if $\hat{p}$ is inconsistent).
+		After calculating fake photos $\hat{p}_{1...B}$ from UVL scenes $s_{1...B}$ as seen in figure \ref{fig:main_diagram}, 
+		we can unproject fake photos $\hat{p}_{1...B}$ back into texture space to obtain $u_{1...B,\ 1...L}$ .
+		If the fake photos display consistent textures along their 3d surfaces, then the unprojected textures should be similar.
+		We can measure this similarity by taking the per-channel standard deviation of these unprojections, aka $\sigma(u)$, then averaging the result.
+		When the fake photos display similar surfaces, the unprojections will be similar making the unprojection consistency loss low.
+		Additionally, we can also calculate the average unprojection, which is useful for visualization purposes (it will look blurry if $\hat{p}$ is inconsistent).
 	}
@@
 
-To maintain surface consistency, we sample a random batch of UVL scenes $S\toB$, and translate them into $\ph\toB$.
-Using geometric knowledge of the scene encoded in $S\toB$, we individually unproject each $\ph_i \in \ph\toB$ back into texture space, to obtain $B$ sets of $L$ unprojected textures $u\toBL$.
-We then use the per-pixel, batch-wise standard deviation of the unprojections as unprojection consistency loss $\lUC = \sigma(u\toBL)\toL$.
-This loss observes how different these unprojections are from one another, and thus how different the object surfaces appear between translations.
+This benefits from large batch sizes, but that often makes you run out of vram.
 
-Intuitively, if $\lUC$ were $0$, it would mean the object surfaces in translations $\ph$ appear exactly the same in every scene.
+Also, you have to get lucky - two scene pictures have to show the same side of a cube for example. First person scenarios would be even worse.
 
-This loss is a fairly intuitive and effective way to maintain surface consistency. There are some caveats, however.
-In order to produce a standard deviation greater than $0$, we must have a batch size greater than $1$.
-Furthermore, environments that rarely show a particular region of a surface will rarely have $\lUC$ applied to that region because they're unlikely to show up twice in the same batch.
-For this reason, $\lUC$ is most useful with large batch sizes.% because observing the same surface in multiple elements of a batch becomes more likely as the batch size increases.
-But because video memory limits our batch sizes, first-person environments might be more of a challenge for $\lUC$ - particularly when exploring multiple rooms (a task we haven't done though - should I mention this?)
+Also, the resolution of the unprojection matters:
 
-To michael: Should we mention these caveats in this section, or mention them in the texture realism loss section? That section addresses all of these issues...
-
-% Also, you have to get lucky - two scene pictures have to show the same side of a cube for example. First person scenarios would be even worse.
+\begin{figure}[H]
+	\begin{center}
+		\includegraphics[width=400pt]{../images/unprojection_resolution_comparison.pdf}
+	\end{center}
+	\caption{
+		The resolution of an unprojection matters for unprojection consistency loss.
+The larger it is, the more precise the alignment will be but the less likely a given UV value is to be assigned a loss greater than 0, lowering numerical instability.
+	}
+	\label{fig:unprojection_resolution_comparison}
+\end{figure}
 
 \subsection{Texture Realism Loss}
-\label{sec:texture_realism_loss}
 
@@
 		The neural texture looks more realistic with texture realism loss enabled.
-Note that the blocks show different letters because of different initializations and the symmetry of a cube - both solutions are valid texture assignments.
 	}
@@
 
-We can improve the translation results by forcing the neural texture to look realistic, instead of allowing it to have arbitrary colors.
-To do this, we add a texture realism loss $\lTR$.
-$\lTR$ is an image similarity loss that makes $\pi$ look like its translation $\hat{p}$.
-In other words, $\lTR$ makes the neural texture more realistic by making the neural texture projections more realistic.
+These images could be regularized so that they're the same every time.
 
-So far, we've taken an image translator $T$ and added neural textures $\tau$ and a surface consistency constraint $\lUC$. 
-If we wanted to, could stop here - those formulations are sufficient to produce consistent sim-to-real translations.
-However, we can improve this further.
+To do this we put a penalty on the latent texture that makes it $\pi$ look like its translation $\hat{p}$.
 
-% Up until now we have not put any constraints on this neural texture. 
-Without $\lTR$, $\tau$ can look wildly different each time you train it.
-As seen in the top row of figure \ref{fig:texture_realism_ablation}, the neural texture looks very unrealistic - the colors are completely arbitrary.
-After adding $\lTR$ though, $\pih \approx \ph$, and $\tau$ to represents the albedo of the surfaces in the scene.
-The image similarity loss used in $\lTR$ is calculated the same way image similarity losses are calculated in section \ref{sec:image_translation}: L2 loss minus MSSSIM.
+We use L2 and MSSSIM losses to do this.
 
-As it turns out, $\lTR$ is sufficient to ensure surface consistency without $\lUC$, though using both yields better results than either one alone. 
-For an explanation of why this is the case, see the appendix \ref{sec:texture_realism_theory}.
-There are some advantages to using $\lTR$ alone though: when just using $\lTR$ you can use batch sizes as small as $B=1$, allowing you to save video memory. 
-Using $\lTR$ is also more numerically stable, as you no longer have to worry about whether the same surfaces are seen across multiple scenes in a batch.
+This helps improve the translations.
 
-% We introduce a new loss, called texture realism loss that fixes this: $\lTR$ is an image similarity loss that encourages $\pi \approx \ph$.
-% This loss forces the neural texture to approximate the albedo of the surfaces in a scene.
+There's a good reason for this: it's almost equivalent to unprojection consistency.
+In fact, it can even be used on its own without unprojection consistency loss (both are sufficient to translate things.)
 
-% These images could be regularized so that they're the same every time.
-% 
-% To do this we put a penalty on the latent texture that makes it $\pi$ look like its translation $\hat{p}$. 
-% 
-% We use l2 and msssim losses to do this.
-% 
-% This helps improve the translations.
-% 
-% There are some advantages over unprojection consistency though: 
-% smaller batch sizes (even a batch size of 1, which UC cant do),
-% you don't have to get lucky (the more chaotic, or even the more zoomed in a dataset becomes the less likely there is to be any collisions)
+(Give theoretical explation)
+
+There are some advantages over unprojection consistency though: 
+smaller batch sizes (even a batch size of 1, which UC cant do),
+you don't have to get lucky (the more chaotic, or even the more zoomed in a dataset becomes the less likely there is to be any collisions)
 
 \subsection{Color Loss}
-ASK MICHAEL: I'd rather not mention this and run out the page limit...it's not very important, and not used in the robot experiments.
-It's only used in the experiment with the five items including the apple.
-Can we add it to the appendix instead?
 
@@
 
-\clearpage
-
-\section{Appendix} 
-\label{sec:appendix}
-
-	\subsection*{Unprojection Recovery Resolution Effect}
-
-		Also, the resolution of the unprojection matters:
-
-		\begin{figure}[H]
-			\begin{center}
-				\includegraphics[width=400pt]{../images/unprojection_resolution_comparison.pdf}
-			\end{center}
-			\caption{
-				The resolution of an unprojection matters for unprojection consistency loss.
-The larger it is, the more precise the alignment will be but the less likely a given UV value is to be assigned a loss greater than 0, lowering numerical instability.
-			}
-			\label{fig:unprojection_resolution_comparison}
-		\end{figure}
-
-	\subsection*{Texture Realism Theory}
-		\label{sec:texture_realism_theory}
-
-		THIS SECTION IS UNPOLISHED, BUT CONTAINS  THE NESSECARY CONTENT.
-		I'll delete this section if you don't think its important enough to keep.
-
-		Texture realism loss equation:
-		$L_{TR}=L_{TR_{l2}}+L_{TR_{msssim}}$
-		where 
-		$L_{TR_{msssim}} = -msssim(\pi,\hat{p})$ and
-		$L_{TR_{l2}} = \frac{
-			\sum\limits_{i=1}^B {
-			%  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}
-			\left( \pi-\hat{p}  \right)^2
-				} 
-		}
-		{B}$
-
-		There's a good reason for this: it's almost equivalent to unprojection consistency.
-		In fact, it can even be used on its own without unprojection consistency loss (both are sufficient to translate things.)
-
-		(Give theoretical explation)
-		$
-		\ell_{UC} = 
-		\
-		\
-		\mu\left(\sigma\left(u_{1\dots B,\ 1\dots L}\right)_{1 \dots L}\right) = 
-		\sqrt{
-		\frac{
-			\sum\limits_{i=1}^B {
-				%  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}
-				\left( \hat{p}-\bar{p}  \right)^2
-				} 
-			}
-			{B}
-		}
-		$
-		Using $\bar{p}$ from figure \ref{fig:unprojection_consistency_loss}
-
-		Becuase $\bar{p}$ is created from the average recovered texturs of $\hat{p}$, $\bar{p} \approx \hat{p}$.
-
-		Becuse of texture realism loss, $\pi \approx \hat{p}$.
-
-		Therefore, $\bar{p} \approx \hat{p} \approx \pi$
-
-		% The l2 component of the texture realism loss equation:
-		% $ \
-		% \
-		% \
-		% \
-		% \ \ell_{TR_{l2}}=\sum\limits_{i=1}^B {
-		% 	%  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}
-		% 	\left( \pi-\hat{p}  \right)^2
-		% 	 } 
-		% $
-
-		Substituting one projected texture for another, aka $\pi$ for $\bar{p}$, we get 
-		$ \
-		\
-		\
-		\
-		\ \ell_{TR_{l2}}
-		\approx
-		\frac{\sum\limits_{i=1}^B {
-			%  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}
-			\left( \hat{p}-\pi  \right)^2
-			}}{B} = \ell_{UC}^2
-		$
-
 \end{document}

### 2022-06-12 CORL/example.tex
Created graveyard section and moved dataset_explanation figure into it
Added data subsection of results

--- 2022-06-12 CORL/example.tex
@@
 
-TODO: Describe what UVL is ; 
-Formulate the setting: What our inputs are and the targets are and what we learn (a neural texture function) and how we can take advantage of it for robotic learning.
-Don't go into details; just say 'its a black box function'
+% TODO: Describe what UVL is ; 
+% Formulate the setting: What our inputs are and the targets are and what we learn (a neural texture function) and how we can take advantage of it for robotic learning.
+% Don't go into details; just say 'its a black box function'
 
-TODO: Add UV to the fourier feature diagram.
+% TODO: Add UV to the fourier feature diagram.
 
-TODO: Create subfigures with subcaptions. 
-2a: Nothing but UVL=UV+L
-2b. 3d uvl axis to texture pack (drew on whiteboard)
-2c. Skip over the translation network and show a pretty robot arm picture
+% TODO: Create subfigures with subcaptions. 
+% 2a: Nothing but UVL=UV+L
+% 2b. 3d uvl axis to texture pack (drew on whiteboard)
+% 2c. Skip over the translation network and show a pretty robot arm picture
 
-This is the formulatoin section; not data section. Dont talk about how many photos we use etc.
+% This is the formulatoin section; not data section. Dont talk about how many photos we use etc.
 
-JUST IN CASE THINGS ARE ERASED:
-We learn neural texture corresponding to each object, where each texture is represented as a function mapping... 
-The idea is to learn object textures as a set of continuous functions from a set of (unlabeled) real images, and use them to generate realistic images.
-Given a 3D structure of the scene represented with a UVL image, the learned neural textures will translate them into a realistic image.
-When used for the robot learning, this enables learnable, realistic sim2real of robot training images.
+% JUST IN CASE THINGS ARE ERASED:
+% We learn neural texture corresponding to each object, where each texture is represented as a function mapping... 
+% The idea is to learn object textures as a set of continuous functions from a set of (unlabeled) real images, and use them to generate realistic images.
+% Given a 3D structure of the scene represented with a UVL image, the learned neural textures will translate them into a realistic image.
+% When used for the robot learning, this enables learnable, realistic sim2real of robot training images.
 
-IN THE INTRODUCTION: How we're using a neural neural network network texture. Also in related works.
+% IN THE INTRODUCTION: How we're using a neural neural network network texture. Also in related works.
 
-TODO: Replace neural texture in figure 3 with axis, and treat it as a function that takes UV in with an arrow pointing to it.
+% TODO: Replace neural texture in figure 3 with axis, and treat it as a function that takes UV in with an arrow pointing to it.
 
-BREAK IT DOWN APPROACH:
-Don't have any pictures. Have breakdown where we add new things in multiple figures.
-First figure: Just image translation. 
-Seconf:
-Third:
-Etc...
+% BREAK IT DOWN APPROACH:
+% Don't have any pictures. Have breakdown where we add new things in multiple figures.
+% First figure: Just image translation. 
+% Seconf:
+% Third:
+% Etc...
 
@@
 	\begin{center}
-		\includegraphics[width=200pt]{../images/dataset_explanation.pdf}
+		\includegraphics[width=270pt]{../images/uvl_explanation_minimal.pdf}
 	\end{center}
 	\caption{
-		Compatible datasets have two sets of images: a set of UVL scenes and a set of photographs.
-		TRITON is a sim-to-real image translation algorithm, taking in synthetic UVL scenes and aiming to create realistic fake photographs. 
-		Being an unsupervised algorithm, there are no correspondences between synthetic and real images.
-		In this dataset, three alphabet cubes are moved around the table. 
-		The synthetic and rear cameras have the same position and field of view.
-		There are many more UVL scenes than photos because synthetic scenes can be generated automatically whereas photos require real-world labor.
-		}
-	\label{fig:dataset_explanation}
-\end{figure}
-
-\begin{figure}[H]
-	\begin{center}
-		\includegraphics[width=270pt]{../images/uvl_explanation.pdf}
-	\end{center}
-	\caption{
-		This diagram shows the purpose of a UVL image.
+		% This diagram shows the purpose of a UVL image.
 		A UVL scene is an image that has three channels: RGB.
@@
 
-In this paper, we'll mostly focus on a hand-collected dataset that involves three alphabet blocks that are moved across a table.
-Alphabet blocks were chosen because they all have the same geometry (a cube), but have very distinct semantic textures that will make temporal inconsistency obvious to the human eye.
-This dataset is analogous to data that would be collected for a third-person robotic grasping task.
-However, other objects (such as cans of soda, apples, cloves of garlic, etc) are also for generating other results in this paper.
+% In this paper, we'll mostly focus on a hand-collected dataset that involves three alphabet blocks that are moved across a table.
+% Alphabet blocks were chosen because they all have the same geometry (a cube), but have very distinct semantic textures that will make temporal inconsistency obvious to the human eye.
+% This dataset is analogous to data that would be collected for a third-person robotic grasping task.
+% However, other objects (such as cans of soda, apples, cloves of garlic, etc) are also for generating other results in this paper.
 ((TODO: Detail the five object tests and five cube tests and other stuff like shiny cans etc)).
 
-There are two components to this dataset: Simulated data in the form of UVL scenes, and photographs.
-The camera in the simulation is positioned in approximately the same place as the real camera, with approximately the same field of view.
-In both domains of this dataset, the camera never moves. Instead, the objects are randomly positioned and rotated on the table.
-In both the simulation and in real life, these objects are randomly translated along the x and y-axis of the table, as well as rotated on the z-axis.
+% There are two components to this dataset: Simulated data in the form of UVL scenes, and photographs.
+% The camera in the simulation is positioned in approximately the same place as the real camera, with approximately the same field of view.
+% In both domains of this dataset, the camera never moves. Instead, the objects are randomly positioned and rotated on the table.
+% In both the simulation and in real life, these objects are randomly translated along the x and y-axis of the table, as well as rotated on the z-axis.
 
-There are 200 photographs in this dataset, and they are recorded as RGB jpg images.
-There are 3000 synthetic images in this dataset, in the form of UVL images.
-These UVL images are also encoded as RGB images, but provide information about the geometry of a scene.
-UVL images are composed of both a UV map and a label map and are summarized in figure \ref{fig:uvl_explanation}.
-To avoid positional rounding errors, UVL images are encoded as EXR files: an image format that supports floating-point values.
+% There are 200 photographs in this dataset, and they are recorded as RGB jpg images.
+% There are 3000 synthetic images in this dataset, in the form of UVL images.
+% These UVL images are also encoded as RGB images, but provide information about the geometry of a scene.
+% UVL images are composed of both a UV map and a label map and are summarized in figure \ref{fig:uvl_explanation}.
+% To avoid positional rounding errors, UVL images are encoded as EXR files: an image format that supports floating-point values.
 
-The pixels in a UVL image are visualizable in RGB space because, like RGB images, each pixel is a vector with 3 values.
+% The pixels in a UVL image are visualizable in RGB space because, like RGB images, each pixel is a vector with 3 values.
 The first two channels, U and V, are floating point values between 0 and 1.
@@
 
-In the three-cube dataset we have 4 textures, and UVL scenes contain label values $l \in [\frac{0}{3}, \frac{1}{3},\frac{2}{3}, \frac{3}{3}]$.
+% In the three-cube dataset we have 4 textures, and UVL scenes contain label values $l \in [\frac{0}{3}, \frac{1}{3},\frac{2}{3}, \frac{3}{3}]$.
 A pixel in a UVL scene $l=\frac{2}{3}$ will get indexed to the third texture, because $\frac{2}{3}$ is the third smallest label value.
 
-%===============================================================================
+% %===============================================================================
 
-Domain A and B
-p hat
-s hat
+% Domain A and B
+% p hat
+% s hat
 
@@
 	\end{figure}
+	s
 
@@
 \section{Results}
+
+\subsection*{Data}
+
+Here I detail the datasets used in the results section. 
+Every dataset has two sets of images: UVL scenes and photographs. They are all unpaired, and have RGB values ranging from 0 to 1.
+
+The first dataset to mention is the three-block dataset.  
+It has 300 photos and 2000 UVL scenes.
+It features a table with three alphabet blocks on a table, which are randomly translated along the X and Y axes and rotated randomly along the Z axis.
+Each photograph features these three cubes with a random position and rotation.
+
+[[Insert photographs and UVL maps here; a digram showing each dataset we describe here and 1 or two samples of each domain in each dataset]]
+
+% In this paper, we'll mostly focus on a hand-collected dataset that involves three alphabet blocks that are moved across a table.
+% Alphabet blocks were chosen because they all have the same geometry (a cube), but have very distinct semantic textures that will make temporal inconsistency obvious to the human eye.
+% This dataset is analogous to data that would be collected for a third-person robotic grasping task.
+% However, other objects (such as cans of soda, apples, cloves of garlic, etc) are also for generating other results in this paper.
+((TODO: Detail the five object tests and five cube tests and other stuff like shiny cans etc)).
+
+% There are two components to this dataset: Simulated data in the form of UVL scenes, and photographs.
+% The camera in the simulation is positioned in approximately the same place as the real camera, with approximately the same field of view.
+% In both domains of this dataset, the camera never moves. Instead, the objects are randomly positioned and rotated on the table.
+% In both the simulation and in real life, these objects are randomly translated along the x and y-axis of the table, as well as rotated on the z-axis.
+
+% There are 200 photographs in this dataset, and they are recorded as RGB jpg images.
+% There are 3000 synthetic images in this dataset, in the form of UVL images.
+% These UVL images are also encoded as RGB images, but provide information about the geometry of a scene.
+% UVL images are composed of both a UV map and a label map and are summarized in figure \ref{fig:uvl_explanation}.
+% To avoid positional rounding errors, UVL images are encoded as EXR files: an image format that supports floating-point values.
+
+% The pixels in a UVL image are visualizable in RGB space because, like RGB images, each pixel is a vector with 3 values.
+The first two channels, U and V, are floating point values between 0 and 1.
+The L channel is also a floating point value between 0 and 1, it has a second meaning.
+There are only a finite number of label values (corresponding to the number of learnable textures).
+The rank of a particular L value is used to index these textures.
+
+% In the three-cube dataset we have 4 textures, and UVL scenes contain label values $l \in [\frac{0}{3}, \frac{1}{3},\frac{2}{3}, \frac{3}{3}]$.
+A pixel in a UVL scene $l=\frac{2}{3}$ will get indexed to the third texture, because $\frac{2}{3}$ is the third smallest label value.
+
+% %===============================================================================
+
+% Domain A and B
+% p hat
+% s hat
+
 \label{sec:results}
@@
 
+\section*{Graveyard}
+
+Here I put things I won't include in the paper or appendix, but want to keep for reference until submission
+
+\begin{figure}[H]
+	\begin{center}
+		\includegraphics[width=200pt]{../images/dataset_explanation.pdf}
+	\end{center}
+	\caption{
+		Compatible datasets have two sets of images: a set of UVL scenes and a set of photographs.
+		TRITON is a sim-to-real image translation algorithm, taking in synthetic UVL scenes and aiming to create realistic fake photographs. 
+		Being an unsupervised algorithm, there are no correspondences between synthetic and real images.
+		In this dataset, three alphabet cubes are moved around the table. 
+		The synthetic and rear cameras have the same position and field of view.
+		There are many more UVL scenes than photos because synthetic scenes can be generated automatically whereas photos require real-world labor.
+		}
+	\label{fig:dataset_explanation}
+\end{figure}
+
 \end{document}

### 2022-06-12 CORL/example.tex
Commented out incomplete introduction

@@
 
-TODO: Note that the simple input of UVL, or an RGB neural texture, means any simulator should be plug-and-play with this algorithm.
+I introduce you to TRITON. The rest of the introduction text goes here; I've commented out my old incomplete introduction.
 
-Recently, several sim-to-real algorithms have come out that are based on image-to-image translation. [Citations]
-These are used for training robots using pixel-based reinforcement learning.
-They demonstrated that better image translation algorithms yielded notable improvements in robotic benchmarks.
-At the same time, there is a lot of research on differentiable rendering,
-a topic which produced papers such as NERF which attempt to capture 3d representations of the real world.
-However, most of these approaches are either supervised or involve only camera movements [citations].
-One paper that came out recently combined both image translation and differentiable rendering in an unsupervised manner to create view-consistent models of human organs [citation].
-This paper too, though, was limited to only camera movements.
+% TODO: Note that the simple input of UVL, or an RGB neural texture, means any simulator should be plug-and-play with this algorithm.
 
-This algorithm unlocks a new capability: learning textures to match photos for given 3d models without supervision.
+% Recently, several sim-to-real algorithms have come out that are based on image-to-image translation. [Citations]
+% These are used for training robots using pixel-based reinforcement learning.
+% They demonstrated that better image translation algorithms yielded notable improvements in robotic benchmarks.
+% At the same time, there is a lot of research on differentiable rendering,
+% a topic which produced papers such as NERF which attempt to capture 3d representations of the real world.
+% However, most of these approaches are either supervised or involve only camera movements [citations].
+% One paper that came out recently combined both image translation and differentiable rendering in an unsupervised manner to create view-consistent models of human organs [citation].
+% This paper too, though, was limited to only camera movements.
 
-The motivation for this paper is to create a temporally consistent sim-to-real image translation algorithm that will look the same from multiple camera angles simultaneously, keeps all semantic details
-[[I'll finish this later... let's work on the meat of the paper first...]]
+% This algorithm unlocks a new capability: learning textures to match photos for given 3d models without supervision.
+
+% The motivation for this paper is to create a temporally consistent sim-to-real image translation algorithm that will look the same from multiple camera angles simultaneously, keeps all semantic details
+% [[I'll finish this later... let's work on the meat of the paper first...]]
 
@@
 	\begin{center}
-		\includegraphics[width=270pt]{../images/uvl_explanation_minimal.pdf}
+		\includegraphics[width=400pt]{../images/uvl_explanation_minimal.pdf}
 	\end{center}
@@
 
-\subsection*{Data}
+\subsection{Data}
 

### 2022-06-12 CORL/example.tex
example.tex: Added module_translator.pdf into the latex doc
Commented out the citations section; which we don't need anymore.

@@
 	\end{figure}
-	s
 
@@
 \label{sec:image_translation}
+
+\begin{figure}[H]
+	\begin{center}
+		\includegraphics[width=200pt]{../images/module_translator.pdf}
+	\end{center}
+	\caption{
+		A subset of figure \ref{fig:main_diagram} focusing on the image translation module $T$.
+	}
+	% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
+	% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
+	% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
+	\label{fig:learnable_textures}
+\end{figure}
 
@@
 Can't handle transparent objects.
+
 A limited number of objects can be learned at once before supervision is necessary with color loss (but there are workarounds).
+
 Takes a long time to train.
@@
 
-\section{Citations} 
-\label{sec:citations}
+% \section{Citations} 
+% \label{sec:citations}
 
-Citations can be made using either \textbackslash citep\{\} or \textbackslash citet\{\}, depending on the appropriateness.
+% Citations can be made using either \textbackslash citep\{\} or \textbackslash citet\{\}, depending on the appropriateness.
 To avoid the citation moving to the next line, it is often a good practice to replace the space before with a tilde (\~{}) character.
-Example 1: ``CoRL is the best conference ever~\citep{fourier_feature_networks}.''
-Example 2: ``\citet{fourier_feature_networks} proved, both theoretically and numerically, that CoRL is the best conference ever.''
+% Example 1: ``CoRL is the best conference ever~\citep{fourier_feature_networks}.''
+% Example 2: ``\citet{fourier_feature_networks} proved, both theoretically and numerically, that CoRL is the best conference ever.''
 

### 2022-06-12 CORL/example.tex
Added basic table
example.tex: Added results table, first_diagram.pdf, resized learnable_textures.pdf to 300pt

@@
 \usepackage{amsmath}
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage{array, booktabs, ragged2e}
 
@@
 	% Because of the 6 sentence limit, I've commented out some of the sentences...
-
-	QUESTIONS FOR MICHAEL:
-	\begin{itemize}
-		\item - TODO: WE MAINTAIN WHAT WE NOW CALL "SURFACE CONSISTENCY" instead of view consistency! Or texture consistency? Etc? What should we call it?
-	\end{itemize}
 
@@
 % Etc...
+
+\begin{figure}[H]
+	\begin{center}
+		\includegraphics[width=400pt]{../images/first_diagram.pdf}
+	\end{center}
+	\caption{
+		This is an overview of what TRITON accomplishes.
+		TRITON learns the textures of 3d objects to help translate simulated images into photographs. It does this with unpaired data. Each row is a different dataset.
+		}
+	\label{fig:uvl_explanation}
+\end{figure}
 
@@
 		\begin{center}
-			\includegraphics[width=400pt]{../images/learnable_textures.pdf}
+			\includegraphics[width=300pt]{../images/learnable_textures.pdf}
 		\end{center}
@@
 
+\subsection{Qualitative Differences}
 \begin{figure}[H]
@@
 	\end{figure}
+
+	\begin{figure}[H]
+		\begin{center}
+			\includegraphics[width=400pt]{../images/blurry_recovery.pdf}
+		\end{center}
+		\caption{
+			The recovered texture is more crisp when we have surface consistency losses $\lUC$ and $\lTR$ enabled.
+			[[Michael, should I include CycleGAN and other algos here?]]
+		}
+		\label{fig:unprojection_consistency_loss}
+	\end{figure}
+	% 	Alphabet Three							
+	% 	Masked				Unmasked			
+	% 	LPIPS		L2		LPIPS		L2	
+	% 	Sync	Unsync	Sync	Unsync	Sync	Unsync	Sync	Unsync
+	% Pure MUNIT	0.0437	0.0373	0.00500	0.00490	0.434	0.402	0.0425	0.0392
+	% Texture Only	0.0442	0.0386	0.00586	0.00589	0.285	0.255	0.0364	0.0310
+	% Texture Reality	0.0286	0.0267	0.00479	0.00478	0.117	0.1157	0.0123	0.0122
+	% CycleGAN			TODO: Sync with respect to L2, so sync is always ≥ unsync					
+	% CUT				TODO: Google Synthetic Dataset
+
+	\subsection{Ground Truth Comaprison}
+\begin{table}[H]
+	\begin{tabular}{l|llllllll}
+		& \multicolumn{8}{c}{Three Block Dataset}                                                                                                                                                                                              \\
+		& \multicolumn{4}{c|}{Masked}                                                                                       & \multicolumn{4}{c}{Unmasked}                                                                                     \\
+		& \multicolumn{2}{c|}{L2}                                 & \multicolumn{2}{c|}{LPIPS}                              & \multicolumn{2}{c|}{L2}                                 & \multicolumn{2}{c}{LPIPS}                              \\
+		Algorithm                              & \multicolumn{1}{c|}{Sync} & \multicolumn{1}{c|}{Unsync} & \multicolumn{1}{c|}{Sync} & \multicolumn{1}{c|}{Unsync} & \multicolumn{1}{c|}{Sync} & \multicolumn{1}{c|}{Unsync} & \multicolumn{1}{c|}{Sync} & \multicolumn{1}{c}{Unsync} \\ \hline
+		\textbf{TRITON w/o $\tau, \lUC, \lTR$} & 0.0437                    & 0.0373                      & 0.00500                   & 0.00490                     & 0.434                     & 0.402                       & 0.0425                    & 0.0392                     \\
+		\textbf{TRITON w/o $\lUC, \lTR$}       & 0.0442                    & 0.0386                      & 0.00586                   & 0.00589                     & 0.285                     & 0.255                       & 0.0364                    & 0.0310                     \\
+		\textbf{TRITON}                        & 0.0286                    & 0.0267                      & 0.00479                   & 0.00478                     & 0.117                     & 0.1157                      & 0.0123                    & 0.0122                     \\
+		\textbf{CycleGAN}                      &                           &                             &                           &                             &                           &                             &                           &                            \\
+		\textbf{CUT}                           &                           &                             &                           &                             &                           &                             &                           &
+	\end{tabular}
+\end{table}
+
+[[Figures: Show these results and explain why we have a mask on some of them]]
+
+TODO: Explain what sync and unsync mean, retrieve the results for CycleGAN and CUT
 
@@
 
+\section*{Things to Ask Michael}
+
+QUESTIONS FOR MICHAEL:
+\begin{itemize}
+	\item - TODO: WE MAINTAIN WHAT WE NOW CALL "SURFACE CONSISTENCY" instead of view consistency! Or texture consistency? Etc? What should we call it?
+\end{itemize}
+
 \end{document}

### 2022-06-12 CORL/example.tex
Added comment containing https://www.tablesgenerator.com/#
example.tex: Replaced unprojection_consistency_loss with unprojection_consistency_loss_without_reprojection
Meeting with Michael: June 12

@@
 
-% \usepackage{corl_2022} % Use this for the initial submission.
-\usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
+\usepackage{corl_2022} % Use this for the initial submission.
+% \usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
 \usepackage{graphicx}
@@
 % \title{TRITON: Globally Consistent Sim-to-Real Transfer
-\title{Neural Textures make Better Simulators
+\title{Neural Neural Textures Make Better Simulators
 
-``I can't believe it's not real!" %Definitely gonna delete this lol
+``I Can't Believe It's Not Real!''%Definitely gonna delete this lol
  %via Neural Textures
@@
 		% $B$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
-		This figure is an overview of how TRITON works, showing all submodules and losses.
+		%
+		%JUNE 12:
+		%Don't say 4 main components; say 2 components and 2 losses
+		%TODO: Try to use right-angled arrows
+		%TODO: Use tau as a function
+		%Copy paste the figure multiple times, deleting things
+		%Mention "Neural Neural Texture": Its a function mapping UV to RGB
+		%Formulation doesnt mentino texture; just uvl inputs and final outputs
+		%Always use function notation tau(u,v) instead of just tau (in figure as well) 
+		%The arrow should be running through tau. It's not a variable its a function...
+		%Rename 'B' to "N" for batch size
+		%Figure 8: Align consistent with inconsistent and use all 5 green ones
+		%
+		This figure is an overview TRITON.
 		Inputs are on the left, and outputs are on the right.
-		The dashed arrows indicate losses between nodes.
+		The dashed arrows indicate losses.
 		Although $\pi\toB$ and $\ph\toB$ look similar, they are not identical - $\lTR$ encourages them to look as similar as possible.
@@
 	In this section, we describe how TRITON works to translate images from domain A (simulation) to domain B (photos) while maintaining surface consistency. 
-	TRITON has four main components: a neural texture, an image translator, and two surface consistency losses.
+	TRITON has four main components: a neural texture, an image translator, and two surface consistency losses. [[One or two sentences summarizing the flow - nothing more than that]].
+
+	%JUNE 12:
+	%TODO: MIgrate all four of these teasers into their respective subsections to save space.
+
 	\begin{enumerate}
 		\item{
-			Neural Textures $\tau\toL$: Given an input scene $s$ depicting 3d objects with labels $1\dots L$, we project learnable RGB textures $\tau\toL$ to their surfaces to obtain projection $\pi$. 
+			Neural Neural Textures $\tau\toL: (u,v) \rightarrow (R,G,B)$:
+
+			%What is it...then how do we use it...
+
+			(as the 1st sentence) Define Neural Neural Texture as a function taking....
+
+			(as the 2nd sentence)
+			Given a 3D scene $s$, we apply $\tau\toL$ to each UV to obtain RGB surface values...
+
+			project learnable RGB textures $\tau\toL$ to their surfaces to obtain projection $\pi$.
+
+% 			Neural Neural Textures $\tau\toL(u,v)$: Given an input scene $s$ depicting 3d objects with labels $1\dots L$, we apply a function on their surface's UV values with neural textures $\tau\toL$ to obtain projection $\pi$.
+
 			These neural textures are represented implicitly by a neural network that maps UV values to RGB values, and are learned jointly with the image translator.
@@
 			\end{equation}
-			$T$ is a variation of MUNIT, and inherits adversarial losses $\ell_{adv}$, as well cycle consistency losses $\ell_{cyc}$ and reconstruction losses $\ell_{rec}$.
+			$T$ is a variation of MUNIT~\cite{munit}, and inherits adversarial losses $\ell_{adv}$, as well cycle consistency losses $\ell_{cyc}$ and reconstruction losses $\ell_{rec}$.
 		}
@@
 
-\subsection{Neural Texture and Projection}
+\subsection{Neural Neural Texture and Projection}
 
@@
 
-	TRITON's neural texture module lets it  of objects, and thus take advantage of 3d geometric priors.
-By learning this texture, we can encode features directly onto the surfaces of the 3d objects in a scene, which the image translation module uses to maintain visual consistency between states and viewpoints.
+    %JUNE 12:
+    %Defining what it is and how it's used.
+    %
+    %Justify why we're calling it neural neural texture.
+Unlike previous papers [citations], we learn a neural network instead of a grid of pixels.
+To be explicit we call it neural neural texture.
+%%%%%% Previous papers were more like latent textures but ours is different: it is a funciton.
+Previous works were called "Neural Textures" but we're going to call ours "Neural Neural Textures" - a subtype of neural textures.
 
-	Given a batch of $B$ UVL Scenes $s_{1\dots B}$ with $L$ different label values, we project $L$ different neural textures $\tau_{1\dots L}$ onto that scene; obtaining projections $\tau_{1\dots B}$.
+% 	TRITON's neural neural texture module lets it create features on the surfaces of objects, and thus take advantage of 3d geometric priors. 
+	Using neural neural textures, we can encode features directly onto the surfaces of the 3d objects in a scene, which the image translation module uses to maintain visual consistency between states and viewpoints.
+
+%THIS WILL BE REPLACED BY SUMMARY SECTION
+% 	Given a batch of $B$ UVL Scenes $s_{1\dots B}$ with $L$ different label values, we project $L$ different neural textures $\tau_{1\dots L}$ onto that scene; obtaining projections $\pi_{1\dots B}$.
 This projection mechanism is illustrated in figure \ref{fig:uvl_explanation}.
-
-	These neural textures are not stored in raster form during training.
-Instead, as illustrated in figure \ref{fig:learnable_textures}, they're paramaterized by pixel-wise fourier feature networks \cite{fourier_feature_networks} that take in UV coordinates and returns RGB colors.
-During inference, however, these textures are rasterized to save both time and video memory.
 
@@
 
+	%Squeeze this down - we don't need explanations for why, that can go in the appendix.
 	In practice, we found that TRITON learns faster with fourier-feature textures than raster textures.
 The trained fourier-feature textures also exhibit less noise than its raster counterparts.
-We think this is because they don't suffer as muchIt cfrom aliasing artifacts in the UV maps, where the loss gradient might skip over pixels in texture-space when the UVL scene is zoomed out too far or raster resolution is too high.
+We think this is because they do not suffer as much.
+It cfrom aliasing artifacts in the UV maps, where the loss gradient might skip over pixels in texture-space when the UVL scene is zoomed out too far or raster resolution is too high.
 Case in point: if you have a raster texture with very high resolution, the loss gradient is less likely to be passed to a given texel because the chance that a given UV value in a scene will be rounded to that pixel's coordinates is very small.
@@
 	\begin{center}
-		\includegraphics[width=400pt]{../images/unprojection_consistency_loss.pdf}
+		\includegraphics[width=400pt]{../images/unprojection_consistency_loss_without_reprojection.pdf}
 	\end{center}
@@
 	\begin{center}
-		\includegraphics[width=250pt]{../images/texture_realism_ablation.pdf}
+		\includegraphics[width=25x0pt]{../images/texture_realism_ablation.pdf}
 	\end{center}
@@
 	\subsection{Ground Truth Comaprison}
+
+	%CREATED WITH https://www.tablesgenerator.com/# -- this website is wonderful!!
 \begin{table}[H]
@@
 \label{sec:appendix}
+
+    \subsection{Unsorted}
+     	These neural textures are not stored in raster form during training.
+Instead, as illustrated in figure \ref{fig:learnable_textures}, they're paramaterized by pixel-wise fourier feature networks \cite{fourier_feature_networks} that take in UV coordinates and returns RGB colors.
+During inference, however, these textures are rasterized to save both time and video memory.
 

### 2022-06-13 CORL/example.tex
Added main_diagram_beautiful.pdf
Fixed errors
Moved summaries into their subsections

@@
 		}
-	\label{fig:uvl_explanation}
+	\label{fig:first_diagram}
 \end{figure}
@@
 		% \includegraphics[width=400pt]{../images/main_diagram_condensed.pdf}
-		\includegraphics[width=400pt]{../images/main_diagram_condensed_with_domains.pdf}
+		% \includegraphics[width=400pt]{../images/main_diagram_condensed_with_domains.pdf}
+		\includegraphics[width=400pt]{../images/main_diagram_beautiful.pdf}
 	\end{center}
@@
 
-	\begin{enumerate}
-		\item{
-			Neural Neural Textures $\tau\toL: (u,v) \rightarrow (R,G,B)$:
-
-			%What is it...then how do we use it...
-
-			(as the 1st sentence) Define Neural Neural Texture as a function taking....
-
-			(as the 2nd sentence)
-			Given a 3D scene $s$, we apply $\tau\toL$ to each UV to obtain RGB surface values...
-
-			project learnable RGB textures $\tau\toL$ to their surfaces to obtain projection $\pi$.
-
-% 			Neural Neural Textures $\tau\toL(u,v)$: Given an input scene $s$ depicting 3d objects with labels $1\dots L$, we apply a function on their surface's UV values with neural textures $\tau\toL$ to obtain projection $\pi$.
-
-			These neural textures are represented implicitly by a neural network that maps UV values to RGB values, and are learned jointly with the image translator.
-			\begin{equation}
-				\pi=\tau\toL(s)
-			\end{equation}
-			We then concatenate the scenes with the projections channelwise to obtain images from domain A: $\ppis \in A$.
-		}
-		\item{
-			Bidirectional Image Translator $T$: $\Tab$ translates images from domain A to domain B, and $\Tba$ translates images from domain B to domain A.
-			\begin{equation}
-				\ph=\Tab(\pis)\ \ \ \text{ and }\ \ \ \ppish=\Tba(p)
-			\end{equation}
-			$T$ is a variation of MUNIT~\cite{munit}, and inherits adversarial losses $\ell_{adv}$, as well cycle consistency losses $\ell_{cyc}$ and reconstruction losses $\ell_{rec}$.
-		}
-		\item {
-			Unprojection Consistency Loss $\lUC$: To keep the object surfaces consistent between a batch of $B$ scenes, we impose a pixel-wise similarity loss between these surfaces by warping them back into a common texture space using the UV and label values contained in the original scene.
-			\begin{equation}
-				u\toBL=\text{unproject}(\ph\toB,s\toB)\ \ \ \text{ and } \ \ \ \lTR \Rightarrow u_1 \approx u_2 \dots \approx u_B
-			\end{equation}
-		}
-		\item{
-			Texture Realism Loss $\lTR$: To encourage the neural textures to look as realistic as possible, we try to make the projections look like the final output. 
-			\begin{equation}
-				\lTR \Rightarrow \pi \approx \ph
-			\end{equation}
-			As it turns out, $\lTR$ is sufficiently powerful loss to generate surface-consistent translations even without $\lUC$, although the results are better when both losses are used.
-		}
-
-	\end{enumerate}
-
 \subsection{Neural Neural Texture and Projection}
@@
 Previous works were called "Neural Textures" but we're going to call ours "Neural Neural Textures" - a subtype of neural textures.
+
+	Neural Neural Textures $\tau\toL: (u,v) \rightarrow (R,G,B)$:
+
+	%What is it...then how do we use it...
+
+	(as the 1st sentence) Define Neural Neural Texture as a function taking....
+
+	(as the 2nd sentence)
+	Given a 3D scene $s$, we apply $\tau\toL$ to each UV to obtain RGB surface values...
+
+	project learnable RGB textures $\tau\toL$ to their surfaces to obtain projection $\pi$.
+
+% 			Neural Neural Textures $\tau\toL(u,v)$: Given an input scene $s$ depicting 3d objects with labels $1\dots L$, we apply a function on their surface's UV values with neural textures $\tau\toL$ to obtain projection $\pi$.
+
+	These neural textures are represented implicitly by a neural network that maps UV values to RGB values, and are learned jointly with the image translator.
+	\begin{equation}
+		\pi=\tau\toL(s)
+	\end{equation}
+	We then concatenate the scenes with the projections channelwise to obtain images from domain A: $\ppis \in A$.
 
@@
 		% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
-	\label{fig:learnable_textures}
+		\label{fig:module_translator}
 	\end{figure}
@@
 	% TODO: Is l2 loss capitalized or lower case?
+
+	Bidirectional Image Translator $T$: $\Tab$ translates images from domain A to domain B, and $\Tba$ translates images from domain B to domain A.
+	\begin{equation}
+		\ph=\Tab(\pis)\ \ \ \text{ and }\ \ \ \ppish=\Tba(p)
+	\end{equation}
+	$T$ is a variation of MUNIT~\cite{munit}, and inherits adversarial losses $\ell_{adv}$, as well cycle consistency losses $\ell_{cyc}$ and reconstruction losses $\ell_{rec}$.
 
@@
 
+	Unprojection Consistency Loss $\lUC$: To keep the object surfaces consistent between a batch of $B$ scenes, we impose a pixel-wise similarity loss between these surfaces by warping them back into a common texture space using the UV and label values contained in the original scene.
+	\begin{equation}
+		u\toBL=\text{unproject}(\ph\toB,s\toB)\ \ \ \text{ and } \ \ \ \lTR \Rightarrow u_1 \approx u_2 \dots \approx u_B
+	\end{equation}
+
 	To maintain surface consistency, we sample a random batch of UVL scenes $S\toB$, and translate them into $\ph\toB$.
@@
 		\begin{center}
-		\includegraphics[width=25x0pt]{../images/texture_realism_ablation.pdf}
+			\includegraphics[width=250pt]{../images/texture_realism_ablation.pdf}
 		\end{center}
@@
 	\end{figure}
+
+	Texture Realism Loss $\lTR$: To encourage the neural textures to look as realistic as possible, we try to make the projections look like the final output. 
+	\begin{equation}
+		\lTR \Rightarrow \pi \approx \ph
+	\end{equation}
+	As it turns out, $\lTR$ is sufficiently powerful loss to generate surface-consistent translations even without $\lUC$, although the results are better when both losses are used.
 
@@
 		}
-		\label{fig:unprojection_consistency_loss}
+		\label{fig:blurry_recovery}
 	\end{figure}

### 2022-06-13 CORL/example.tex
Replaced batch size 'B' with batch size 'N'

@@
 
-\newcommand{\toB}{_{1\dots B}}
-% \newcommand{\toBL}{_{1\dots B,\text{ } 1\dots L}}
-\newcommand{\toBL}{_{1\dots B, 1\dots L}}
+\newcommand{\toN}{_{1\dots N}}
+% \newcommand{\toNL}{_{1\dots B,\text{ } 1\dots L}}
+\newcommand{\toNL}{_{1\dots N, 1\dots L}}
 \newcommand{\toL}{_{1\dots L}}
@@
 		% This texture is parametrized as an image generated by an MLP which is fed Fourier features, as shown in figure \ref{fig:learnable_textures}.
-		% $B$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
+		% $N$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
 		%
@@
 		The dashed arrows indicate losses.
-		Although $\pi\toB$ and $\ph\toB$ look similar, they are not identical - $\lTR$ encourages them to look as similar as possible.
+		Although $\pi\toN$ and $\ph\toN$ look similar, they are not identical - $\lTR$ encourages them to look as similar as possible.
 		% $\pi$ is simply projected textures, whereas $\hat{p}$ has been run through an image translator, allowing it to have shadows and specularities.
@@
 %THIS WILL BE REPLACED BY SUMMARY SECTION
-% 	Given a batch of $B$ UVL Scenes $s_{1\dots B}$ with $L$ different label values, we project $L$ different neural textures $\tau_{1\dots L}$ onto that scene; obtaining projections $\pi_{1\dots B}$.
+% 	Given a batch of $N$ UVL Scenes $s_{1\dots B}$ with $L$ different label values, we project $L$ different neural textures $\tau_{1\dots L}$ onto that scene; obtaining projections $\pi_{1\dots B}$.
 This projection mechanism is illustrated in figure \ref{fig:uvl_explanation}.
@@
 
-	Unprojection Consistency Loss $\lUC$: To keep the object surfaces consistent between a batch of $B$ scenes, we impose a pixel-wise similarity loss between these surfaces by warping them back into a common texture space using the UV and label values contained in the original scene.
+	Unprojection Consistency Loss $\lUC$: To keep the object surfaces consistent between a batch of $N$ scenes, we impose a pixel-wise similarity loss between these surfaces by warping them back into a common texture space using the UV and label values contained in the original scene.
 	\begin{equation}
-		u\toBL=\text{unproject}(\ph\toB,s\toB)\ \ \ \text{ and } \ \ \ \lTR \Rightarrow u_1 \approx u_2 \dots \approx u_B
+		u\toNL=\text{unproject}(\ph\toN,s\toN)\ \ \ \text{ and } \ \ \ \lTR \Rightarrow u_1 \approx u_2 \dots \approx u_N
 	\end{equation}
 
-	To maintain surface consistency, we sample a random batch of UVL scenes $S\toB$, and translate them into $\ph\toB$.
-	Using geometric knowledge of the scene encoded in $S\toB$, we individually unproject each $\ph_i \in \ph\toB$ back into texture space, to obtain $B$ sets of $L$ unprojected textures $u\toBL$.
-	We then use the per-pixel, batch-wise standard deviation of the unprojections as unprojection consistency loss $\lUC = \sigma(u\toBL)\toL$.
+	To maintain surface consistency, we sample a random batch of UVL scenes $S\toN$, and translate them into $\ph\toN$.
+	Using geometric knowledge of the scene encoded in $S\toN$, we individually unproject each $\ph_i \in \ph\toN$ back into texture space, to obtain $N$ sets of $L$ unprojected textures $u\toNL$.
+	We then use the per-pixel, batch-wise standard deviation of the unprojections as unprojection consistency loss $\lUC = \sigma(u\toNL)\toL$.
 	This loss observes how different these unprojections are from one another, and thus how different the object surfaces appear between translations.
@@
 	For an explanation of why this is the case, see the appendix \ref{sec:texture_realism_theory}.
-	There are some advantages to using $\lTR$ alone though: when just using $\lTR$ you can use batch sizes as small as $B=1$, allowing you to save video memory. 
+	There are some advantages to using $\lTR$ alone though: when just using $\lTR$ you can use batch sizes as small as $N=1$, allowing you to save video memory. 
 	Using $\lTR$ is also more numerically stable, as you no longer have to worry about whether the same surfaces are seen across multiple scenes in a batch.

### 2022-06-13 CORL/example.tex
Cruched down the neural neural texture section

@@
+%TODO: Revise method section
+%TODO: Create formulation section
+%TODO: Create results section
+
 %TODO:
@@
 \newcommand{\lTR}{\ell_{TR}}
+\newcommand{\eqand}{\ \ \ \text{ and }\ \ \ }
+\newcommand{\real}{\mathbb{R}}
 
@@
 
-	Neural Neural Textures $\tau\toL: (u,v) \rightarrow (R,G,B)$:
+	% Using neural neural textures, we can encode features directly onto the surfaces of the 3d objects in a scene, which the image translation module uses to maintain visual consistency between states and viewpoints.
+	Instead of feeding input scenes $s$ directly into the image translator $\Tab$, we first apply learnable textures $\tau$ to their surfaces as shown in figure \ref{fig:main_diagram}.
+	Previous works called these learnable textures ``neural textures'', and were parametrized as a discrete grid of differentiable texels. 
+	% In contrast, we call our learnable textures ``neural nerual textures'', becuase our textures are a type of neural texture that is parametrized continuously over UV space using a neural fourier feature network.
+	In contrast, we call our learnable textures ``neural nerual textures'', becuase our textures are parametrized continuously over UV space using a neural network.
+	Like previous works, our neural textures $\tau\toL$ are learned jointly with our image translator $T$.
 
+	These neural textures are represented implicitly by a neural network that maps UV values to RGB values.%, and are used to obtain projections $\pi$ from 3d scenes $s$.
+	\begin{equation}
+		\qquad \tau: (u,v) \in\real^2 \rightarrow (r,g,b) \in\real^3 % \eqand 
+	\end{equation}
+
+	Given a 3d UVL scene $s$, we obtain texture projection $\pi=\tau\toL(s)$ by applying $\tau\toL$ to every pixel $(u,v,l) \in s$ individually.
+	Each pixel in the resulting projection $(r,g,b)\in\pi$ is the result of selecting a texture index $i$ based on the label value $l$, then applying $\tau_i$ to the $u,v$ values.
+	\begin{equation}
+		\pi=\tau\toL(s) \eqand (r,g,b) \in \pi = \tau_i(u,v)
+	\end{equation}
+
+	%DISCARDED TEXT:
+	% A particular neural texture $\tau_i$ uses maps $uv \rightarrow rgb$.
+Similarly, the set of textures $\tau_{1\dots L}$ maps uvl values to rgb values: $\tau_{1\dots L}(uvl)=\tau_l(uv)$ where $uvl$ is the concatenation of a $uv$ vector with a label $l \in 1\dots L$.
+	% TRITON's neural neural texture module lets it create features on the surfaces of objects, and thus take advantage of 3d geometric priors.
+
+			% The neural texture applied to a particular scene pixel $(u,v,l) \in s$ is multiplexed by $l$, and the respective output pixel $(r,g,b) \in \pi = \tau_l(u,v)$. 
+			% Texture projections $\pi$ are obatined by applying a set of $L$ different neural neural textures $\tau\toL$ to a UVL scene $s$ pixelwise.
+			% [[IMPORTANT: THIS IS TECHNICALLY INCORRECT AS l IS A VALUE BETWEEN 0 and 1]]
+
+			% where $i\in[1,L]\cap\mathbb{Z}$ is the rank of $l$
+			% When applied to a UVL scene, it is applied to each $(u,v,l) \in s$ pixel individually where every pixel $(r,g,b) \in \pi = \tau$ 
 			%What is it...then how do we use it...
-
-	(as the 1st sentence) Define Neural Neural Texture as a function taking....
-
-	(as the 2nd sentence)
-	Given a 3D scene $s$, we apply $\tau\toL$ to each UV to obtain RGB surface values...
-
-	project learnable RGB textures $\tau\toL$ to their surfaces to obtain projection $\pi$.
-
+			% (as the 2nd sentence)
+			% Given a 3D scene $s$, we apply $\tau\toL$ to each UV to obtain RGB surface values...
+			% project learnable RGB textures $\tau\toL$ to their surfaces to obtain projection $\pi$. 
 			% 			Neural Neural Textures $\tau\toL(u,v)$: Given an input scene $s$ depicting 3d objects with labels $1\dots L$, we apply a function on their surface's UV values with neural textures $\tau\toL$ to obtain projection $\pi$.
 
-	These neural textures are represented implicitly by a neural network that maps UV values to RGB values, and are learned jointly with the image translator.
-	\begin{equation}
-		\pi=\tau\toL(s)
-	\end{equation}
-	We then concatenate the scenes with the projections channelwise to obtain images from domain A: $\ppis \in A$.
-
-% 	TRITON's neural neural texture module lets it create features on the surfaces of objects, and thus take advantage of 3d geometric priors. 
-	Using neural neural textures, we can encode features directly onto the surfaces of the 3d objects in a scene, which the image translation module uses to maintain visual consistency between states and viewpoints.
+			% \begin{equation}
+				% \pi=\tau\toL(s)
+			% \end{equation}
+			%
 
@@
 	 and $M_i$ maps a $uv$ embedding to an $rgb$ color value:
-	 $M_i: \mathbb{R}^{256} \rightarrow \mathbb{R}^3$.
+	 $M_i: \real^{256} \rightarrow \real^3$.
 	Note that there is nothing special about 256 or 10: these hyperparameter values just happen to work nicely.
 
-	A particular neural texture $\tau_i$ uses maps $uv \rightarrow rgb$.
-Similarly, the set of textures $\tau_{1\dots L}$ maps uvl values to rgb values: $\tau_{1\dots L}(uvl)=\tau_l(uv)$ where $uvl$ is the concatenation of a $uv$ vector with a label $l \in 1\dots L$.
-
 	%Squeeze this down - we don't need explanations for why, that can go in the appendix.
-	In practice, we found that TRITON learns faster with fourier-feature textures than raster textures.
-The trained fourier-feature textures also exhibit less noise than its raster counterparts.
-We think this is because they do not suffer as much.
-It cfrom aliasing artifacts in the UV maps, where the loss gradient might skip over pixels in texture-space when the UVL scene is zoomed out too far or raster resolution is too high.
-Case in point: if you have a raster texture with very high resolution, the loss gradient is less likely to be passed to a given texel because the chance that a given UV value in a scene will be rounded to that pixel's coordinates is very small.
+	In practice, we found that TRITON learns faster with fourier-feature textures than raster textures, as well as being smoother and less noisy. 
+	% The trained fourier-feature textures also exhibit less noise than its raster counterparts. 
+	% We think this is because they do not suffer as much. 
+	% It cfrom aliasing artifacts in the UV maps, where the loss gradient might skip over pixels in texture-space when the UVL scene is zoomed out too far or raster resolution is too high. 
+	% Case in point: if you have a raster texture with very high resolution, the loss gradient is less likely to be passed to a given texel because the chance that a given UV value in a scene will be rounded to that pixel's coordinates is very small.
 
@@
 	\begin{equation}
-		\ph=\Tab(\pis)\ \ \ \text{ and }\ \ \ \ppish=\Tba(p)
+		\ph=\Tab(\pis)\eqand\ppish=\Tba(p)
 	\end{equation}

### 2022-06-13 CORL/example.tex
Added commented equation to use parenthesized UV values
Turned (u,v) into uv and (r,g,b) into rgb. Also made neural neural texture and image translation sections good

@@
 		%Formulation doesnt mentino texture; just uvl inputs and final outputs
-		%Always use function notation tau(u,v) instead of just tau (in figure as well) 
+		%Always use function notation tauuv instead of just tau (in figure as well) 
 		%The arrow should be running through tau. It's not a variable its a function...
@@
 	\begin{equation}
-		\qquad \tau: (u,v) \in\real^2 \rightarrow (r,g,b) \in\real^3 % \eqand 
+		\qquad \tau: uv \in\real^2 \rightarrow rgb \in\real^3 % \eqand 
 	\end{equation}
 
-	Given a 3d UVL scene $s$, we obtain texture projection $\pi=\tau\toL(s)$ by applying $\tau\toL$ to every pixel $(u,v,l) \in s$ individually.
-	Each pixel in the resulting projection $(r,g,b)\in\pi$ is the result of selecting a texture index $i$ based on the label value $l$, then applying $\tau_i$ to the $u,v$ values.
+	Given a 3d UVL scene $s$, we obtain texture projection $\pi=\tau\toL(s)$ by applying $\tau\toL$ to every scene pixel $uvl \in s$ individually.
+	Each pixel in the resulting projection $rgb\in\pi$ is the result of selecting a texture index $i$ based on the rank of label value $l$, then applying $\tau_i$ to the $u,v$ values.
 	\begin{equation}
-		\pi=\tau\toL(s) \eqand (r,g,b) \in \pi = \tau_i(u,v)
+		\pi=\tau\toL(s) \eqand rgb \in \pi = \tau_i(uv)
 	\end{equation}
@@
 
-			% The neural texture applied to a particular scene pixel $(u,v,l) \in s$ is multiplexed by $l$, and the respective output pixel $(r,g,b) \in \pi = \tau_l(u,v)$. 
+			% The neural texture applied to a particular scene pixel $uvl \in s$ is multiplexed by $l$, and the respective output pixel $rgb \in \pi = \tau_luv$. 
 			% Texture projections $\pi$ are obatined by applying a set of $L$ different neural neural textures $\tau\toL$ to a UVL scene $s$ pixelwise.
@@
 			% where $i\in[1,L]\cap\mathbb{Z}$ is the rank of $l$
-			% When applied to a UVL scene, it is applied to each $(u,v,l) \in s$ pixel individually where every pixel $(r,g,b) \in \pi = \tau$ 
+			% When applied to a UVL scene, it is applied to each $uvl \in s$ pixel individually where every pixel $rgb \in \pi = \tau$ 
 			%What is it...then how do we use it...
@@
 			% project learnable RGB textures $\tau\toL$ to their surfaces to obtain projection $\pi$. 
-			% 			Neural Neural Textures $\tau\toL(u,v)$: Given an input scene $s$ depicting 3d objects with labels $1\dots L$, we apply a function on their surface's UV values with neural textures $\tau\toL$ to obtain projection $\pi$.
+			% 			Neural Neural Textures $\tau\toLuv$: Given an input scene $s$ depicting 3d objects with labels $1\dots L$, we apply a function on their surface's UV values with neural textures $\tau\toL$ to obtain projection $\pi$.
 
@@
 
-	Each neural texture $\tau_i$ is a function consisting of two components: a multi-layer perceptron $M_i$ and a static set of 256 random spatial frequencies $f_{1...256}$. 
+	% Each neural texture $\tau_i$ is a function consisting of two components: a multi-layer perceptron $M_i$ and a static set of 256 random spatial frequencies $f_{1...256}$. 
+	% Given a two-dimensional $uv$ vector, the spatial frequencies are used to generate a high dimensional embedding used as input for the MLP.
+	% \begin{equation}
+	% 		\tau_i(uv) = 
+	% 		\
+	% 		M_i\left(\left[
+	% 			\sin \left( f_1     \cdot \left(u,v\right) \right) , \ 
+	% 			\cos \left( f_1     \cdot \left(u,v\right) \right) , \ 
+	% 			% \sin \left( f_2     \cdot \left(u,v\right) \right) , \ 
+	% 			% \cos \left( f_2     \cdot \left(u,v\right) \right) , \ 
+	% 			\dots \ 
+	% 			\sin \left( f_{256} \cdot \left(u,v\right) \right) , \ 
+	% 			\cos \left( f_{256} \cdot \left(u,v\right) \right)  \ 
+	% 		\right]\right)
+	% \end{equation}
+	% where $uv$ and $f_i \in N_{ormal}(\mu=0,\ \sigma=10)$ are two dimensional vectors,
+	%  $f_i uv$ represents their dot product, 
+	% %  $rgb$ represents a 3d color vector,
+	%  and $M_i$ maps a $uv$ embedding to an $rgb$ color value:
+	%  $M_i: \real^{256} \rightarrow \real^3$.
+	% Note that there is nothing special about 256 or 10: these hyperparameter values just happen to work nicely.
+
+	Each neural neural texture $\tau_i$ is a function consisting of two components: a multi-layer perceptron $M_i$ and a static set of 256 random spatial frequencies $f_{1...256}$. 
 	Given a two-dimensional $uv$ vector, the spatial frequencies are used to generate a high dimensional embedding used as input for the MLP.
@@
 			\
-			M_i\left(\left[
-				\sin f_1 uv, \ 
-				\cos f_1 uv, \ 
-				\sin f_2 uv, \ 
-				\cos f_2 uv, \ 
+			M_i(
+				\sin( f_1     uv  ) , \ 
+				\cos( f_1     uv  ) , \ 
+				\sin( f_2     uv  ) , \ 
+				\cos( f_2     uv  ) , \ 
 				\dots \ 
-				\sin f_{256} uv, \ 
-				\cos f_{256} uv \ 
-			\right]\right)
+				\sin( f_{256} uv  ) , \ 
+				\cos( f_{256} uv  )  \ 
+			)
 	\end{equation}
@@
 	%Squeeze this down - we don't need explanations for why, that can go in the appendix.
-	In practice, we found that TRITON learns faster with fourier-feature textures than raster textures, as well as being smoother and less noisy. 
+	In practice, we found that TRITON learns faster with neural neural textures than raster neural textures. The generated textures are also smoother and less noisy. 
 	% The trained fourier-feature textures also exhibit less noise than its raster counterparts. 
@@
 
-	Bidirectional Image Translator $T$: $\Tab$ translates images from domain A to domain B, and $\Tba$ translates images from domain B to domain A.
+	% Our image translation module $T$ is bidirectional: $\Tab$ translates images from domain A to domain B, and $\Tba$ translates images from domain B to domain A.
+	Our image translation module $T$ is a bidirectional: $\Tab$ translates sim to real (aka domain A to domain B), and $\Tba$ translates real to sim (aka domain B to domain A).
 	\begin{equation}
-		\ph=\Tab(\pis)\eqand\ppish=\Tba(p)
+		\ph=\Tab(\pis)  \eqand  \ppish=\Tba(p)
 	\end{equation}
-	$T$ is a variation of MUNIT~\cite{munit}, and inherits adversarial losses $\ell_{adv}$, as well cycle consistency losses $\ell_{cyc}$ and reconstruction losses $\ell_{rec}$.
 
-	Our image translation module, $T$, is based on the image translation module used in \citep{surgical_video_translation}, which is a based on a variant \cite{surgical_image_translation} of MUNIT \cite{munit}.
+	$T$, is based on the image translation module used in \citep{surgical_video_translation}, which is a based on a variant \cite{surgical_image_translation} of MUNIT \cite{munit}. 
+	$T$ uses the same network architectures as MUNIT, and also inherits its adversarial losses $\ell_{adv}$, cycle consistency losses $\ell_{cyc}$ and reconstruction losses $\ell_{rec}$.
 	The main differences between our image translation model and MUNIT are that our style code is fixed making it unimodal, noise is injected into the latent codes during training to prevent overfitting, and we use a different image similarity metric.
 	During inference however, this intermediate noise is removed and our image translation module is completely determinstic. 
-Apart from these differences, our image translation module has the same loss formulations and generator/encoder/discriminator network architectures as MUNIT.
-
-	$T$ is a bidirectional image translation module, and has two translation directions.
-$\Tab$ translates sim to real (aka domain A to domain B), and $\Tba$ translates real to sim (aka domain B to domain A).
+	% Apart from these differences, our image translation module has the same loss formulations and generator/encoder/discriminator network architectures as MUNIT.
 

### 2022-06-14 CORL/example.tex
Changed

@@
 
-\subsection{Neural Neural Texture and Projection}
+\subsection{Neural Neural Texture Projection}
 
@@
 
-	$T$, is based on the image translation module used in \citep{surgical_video_translation}, which is a based on a variant \cite{surgical_image_translation} of MUNIT \cite{munit}. 
+	$T$ is based on the image translation module used in \citep{surgical_video_translation}, which is a based on a variant \cite{surgical_image_translation} of MUNIT \cite{munit}. 
 	$T$ uses the same network architectures as MUNIT, and also inherits its adversarial losses $\ell_{adv}$, cycle consistency losses $\ell_{cyc}$ and reconstruction losses $\ell_{rec}$.
@@
 
-	Unprojection Consistency Loss $\lUC$: To keep the object surfaces consistent between a batch of $N$ scenes, we impose a pixel-wise similarity loss between these surfaces by warping them back into a common texture space using the UV and label values contained in the original scene.
+	To keep the object surfaces consistent between a batch of $N$ outputs, we impose a pixel-wise ``unprojection consistency loss'' between these surfaces by unprojecting them back into a common texture space.
 	\begin{equation}
@@
 
-	To maintain surface consistency, we sample a random batch of UVL scenes $S\toN$, and translate them into $\ph\toN$.
+	We sample a random batch of UVL scenes $S\toN$, and translate them into $\ph\toN$.
 	Using geometric knowledge of the scene encoded in $S\toN$, we individually unproject each $\ph_i \in \ph\toN$ back into texture space, to obtain $N$ sets of $L$ unprojected textures $u\toNL$.
@@
 
-	Texture Realism Loss $\lTR$: To encourage the neural textures to look as realistic as possible, we try to make the projections look like the final output. 
+	To encourage the neural textures to look as realistic as possible, we try to make the projections look like the final output by introducing a ``texture realism'' loss $\lTR$. 
+	$\lTR$ is an image similarity loss that makes $\pi$ look like its translation $\hat{p}$.
 	\begin{equation}
@@
 	\end{equation}
-	As it turns out, $\lTR$ is sufficiently powerful loss to generate surface-consistent translations even without $\lUC$, although the results are better when both losses are used.
+	% As it turns out, $\lTR$ is sufficiently powerful loss to generate surface-consistent translations even without $\lUC$, although the results are better when both losses are used.
 
-	We can improve the translation results by forcing the neural texture to look realistic, instead of allowing it to have arbitrary colors.
-	To do this, we add a texture realism loss $\lTR$.
-	$\lTR$ is an image similarity loss that makes $\pi$ look like its translation $\hat{p}$.
-	In other words, $\lTR$ makes the neural texture more realistic by making the neural texture projections more realistic.
+	This loss forces the neural textures to look realistic, instead of allowing them to have arbitrary colors.
+	In other words, $\lTR$ makes the neural textures more realistic by making their projections look more realistic, like the final outputs.
 
-	So far, we've taken an image translator $T$ and added neural textures $\tau$ and a surface consistency constraint $\lUC$. 
-	If we wanted to, could stop here - those formulations are sufficient to produce consistent sim-to-real translations.
-	However, we can improve this further.
+	% So far, we've taken an image translator $T$ and added neural textures $\tau$ and a surface consistency constraint $\lUC$. 
+	% If we wanted to, could stop here - those formulations are sufficient to produce consistent sim-to-real translations.
+	% However, we can improve this further.
 
@@
 
-	As it turns out, $\lTR$ is sufficient to ensure surface consistency without $\lUC$, though using both yields better results than either one alone. 
-	For an explanation of why this is the case, see the appendix \ref{sec:texture_realism_theory}.
+	We can achieve surface-consistent translations just using $\lUC$, without $\lTR$.
+	The the reverse is also true: $\lTR$ is sufficient to ensure surface consistency without $\lUC$.
+	Using both, however, yields better results than either loss alone. 
+	% For an explanation of why this is the case, see the appendix \ref{sec:texture_realism_theory}.
+
 	There are some advantages to using $\lTR$ alone though: when just using $\lTR$ you can use batch sizes as small as $N=1$, allowing you to save video memory. 
-	Using $\lTR$ is also more numerically stable, as you no longer have to worry about whether the same surfaces are seen across multiple scenes in a batch.
+	Using $\lTR$ is also more numerically stable, as you no longer have to worry about whether the same surfaces are seen across multiple scenes in a batch as you would with $\lUC$.
 

### 2022-06-14 CORL/example.tex
Group Meeting June 13

@@
 
-	\begin{figure}[H]
-		\begin{center}
-			\includegraphics[width=200pt]{../images/module_translator.pdf}
-		\end{center}
-		\caption{
-			A subset of figure \ref{fig:main_diagram} focusing on the image translation module $T$.
-		}
-		% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
-		% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
-		% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
-		\label{fig:module_translator}
-	\end{figure}
+% 	\begin{figure}[H]
+% 		\begin{center}
+% 			\includegraphics[width=200pt]{../images/module_translator.pdf}
+% 		\end{center}
+% 		\caption{
+% 			A subset of figure \ref{fig:main_diagram} focusing on the image translation module $T$.
+% 		}
+% 		% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
+% 		% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
+% 		% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
+% 		\label{fig:module_translator}
+% 	\end{figure}
 
@@
 	\begin{equation}
-		u\toNL=\text{unproject}(\ph\toN,s\toN)\ \ \ \text{ and } \ \ \ \lTR \Rightarrow u_1 \approx u_2 \dots \approx u_N
+		u\toNL=\text{unproject}(\ph\toN,s\toN)\ \ \ \text{ and } \ \ \ \lUC \Rightarrow u_1 \approx u_2 \dots \approx u_N
 	\end{equation}
@@
 
-	This loss is a fairly intuitive and effective way to maintain surface consistency. There are some caveats, however.
-	In order to produce a standard deviation greater than $0$, we must have a batch size greater than $1$.
-	Furthermore, environments that rarely show a particular region of a surface will rarely have $\lUC$ applied to that region because they're unlikely to show up twice in the same batch.
-	For this reason, $\lUC$ is most useful with large batch sizes.% because observing the same surface in multiple elements of a batch becomes more likely as the batch size increases. 
-	But because video memory limits our batch sizes, first-person environments might be more of a challenge for $\lUC$ - particularly when exploring multiple rooms (a task we haven't done though - should I mention this?)
+%MOVE THIS TO APPENDIX
+% 	This loss is a fairly intuitive and effective way to maintain surface consistency. There are some caveats, howe/ver.
+% 	In order to produce a standard deviation greater than $0$, we must have a batch size greater than $1$.
+% 	Furthermore, environments that rarely show a particular region of a surface will rarely have $\lUC$ applied to that region because they're unlikely to show up twice in the same batch.
+% 	For this reason, $\lUC$ is most useful with large batch sizes.% because observing the same surface in multiple elements of a batch becomes more likely as the batch size increases. 
+% 	But because video memory limits our batch sizes, first-person environments might be more of a challenge for $\lUC$ - particularly when exploring multiple rooms (a task we haven't done though - should I mention this?)
 

### 2022-06-14 CORL/example.tex
Added ALL CURRENTLY USED TERMS
Wrote formulation section

@@
 %	Method:	Texture Reality Loss
+
+%ALL CURRENTLY USED TERMS:
+
+%RULES:
+%    - Lower case: Belongs to an upper case thing
+
+%     L - num labels
+%     N - batch size
+%     T - translator
+%     A, B - domains
+%     Tba
+%     Tab
+%     tau - texture       !!!!! MUST CHANGE
+%			TO DO: replace it with psi ψ, the triton symbol!
+%     pi - projection
+%     p - photo
+%     s - scene
+%     l_TR
+%     l_UC
+%     l_ADV
+%     l_REC
+%     l_CYC
+%     l_T
+%     i - general purpose index
+%     f_i - fourier frequency
+%     M - MLP for texture network
+%     u,v,l,r,g,b - channel values
+%     u - unprojections  !!!!!! MUST CHANGE
+%          make it capitalized. Unprojection should be denoted by U - it's too intuitive not to.
+%     sigma - standard deviation
+%     mu - mean
+%     E_A, E_B
+%     D_A, D_B
+%     G_A, G_B
+
+%     similaity(x,y) = MSSSIM(L2(x,y)
+
+% FIXING NOTATION WILL BE HARD :(
+% GO OVER WITH XIANG AND JINGHUAN TOMORROW
+%     In this paper I use 1-based indexing to make notation simpler.
+%
+%     s, pi in N,3,H,W - height width
+%              i,c,x,y
+%     All values between 0 and 1
+%
+%     I: {1/L, 2/L, ... L/L} -> {1, 2, ... L}  ;   I(l) = l*L
+%          I is a discrete mapping from continous label values l to discrete texture indices.
+%          It can be nonlinear, as long as its consistent.
+%     
+%     ψ_i: R2 -> R3   for   i \in {1,2 ... L}
+%
+%     pi_{n,c,x,y} = ψ_  {I(s_{n,1,x,y})}  (s_{n,2,x,y},s_{n,3,x,y})
+%
+%     EXPLAINING L_UC IS WAY TO BURDENSOME. We have to talk about weighted standard deviations of unprojections that have a separate unprojection resolution (128x128) etc.
+%	  l_UC = total mean across all dims of sigma
+%     sigma \in R^{L x C x 128 x 128} is the standard deviation of u in the channel dimension, weighted...
+%     !!! I shouldn't have to do this; the other paper didn't!!!
+%     u.sum_{N,C,u,v}
+%
+
+\newcommand{\msssim}{\text{msssim}}
 
@@
 
+	\begin{figure}[H]
+		\begin{center}
+			\includegraphics[width=400pt]{../images/first_diagram.pdf}
+		\end{center}
+		\caption{
+			This is an overview of what TRITON accomplishes.
+			TRITON learns the textures of 3d objects to help translate simulated images into photographs. It does this with unpaired data. Each row is a different dataset.
+			}
+		\label{fig:first_diagram}
+	\end{figure}
+
+	% TRITON stands for Texture Recovering Image Translation Network. It has two goals: to translate images, and to recover textures.
+
+	TRITON's goal is to turn 3d simulated images into realistic fake photographs without any matching pairs.
+	It does this by simultaneously learning both an image translator and a set of realistic textures.
+	In contrast to previous works involving neural textures, TRITON can handle more than just camera movements:
+	the positions of objects in the training data can be moved around or deformed as well between samples.
+
+	\begin{figure}[H]
+		\begin{center}
+			\includegraphics[width=400pt]{../images/uvl_explanation_minimal.pdf}
+		\end{center}
+		\caption{
+			% This diagram shows the purpose of a UVL image.
+			A UVL scene is an image that has three channels: RGB.
+			R and G are used for U and V, and B is used for L.
+			L stands for Label, and determines which part of the synthetic image will get which texture.
+			The U and V coordinates correspond to positions on each texture,
+			telling it how to project the textures onto the 3d objects represented in the UVL scene.
+			The darkest shade of blue corresponds to the 1st texture, and the next darkest shade of blue corresponds to the 2nd texture etc.
+			}
+		\label{fig:uvl_explanation}
+	\end{figure}
+
+	There are two components to every dataset: A set of simulated 3d scenes, and a set of photographs.
+
+	The photographs, having $(r,g,b)$ values between 0 and 1,
+		are denoted as $p \in [0,1]^{N \times 3 \times H \times W}$ where $N$ is the batch size,
+		3 refers to the three $(r,g,b)$ channels, 
+		and $H,W$ are the height and width respectively.
+
+	In this work, a scene refers to a rendered 3d simulation state - which includes the position, rotation and deformation of every object (including the camera).
+	% Using some 3d rendering software, be it Blender or Gazebo or some other 3d creates an image from these 
+	These scenes have the same datatype and dimensions as photographs and are denoted as $s \in [0,1]^{N \times 3 \times H \times W}$.
+	However, unlike $p$, $s$'s three $(r,g,b)$ channels encode a special semantic meaning: $(u,v,l)$ as depicted in diagram \ref{fig:uvl_explanation}.
+	The channels $u$ and $v$ refer to a texture coordinate, whereas $l$ refers to a label value that identifies every object in a scene.
+	In a given dataset, each object gets a different label. Likewise, each object is assigned a different texture.
+	We assume that every dataset has $L$ different label values, $L$ different objects, and $L$ different learnable textures.
+
+	In each dataset, we must also define a function $I(l)$ that maps label values to texture indices. A simple way to do this is with the following definition:
+	\begin{equation}
+		I: \left\{\frac{1}{L},\frac{2}{L},\dots \frac{L}{L}\right\} \rightarrow \left\{1,2,\dots L\right\}  \eqand  I(l)=l\cdot L
+	\end{equation}
+	However, this mapping can be changed arbitrarily if its more convenient to do so for a given dataset.
+	Also please note that this paper uses 1-based indexing for notational simplicity.
+
 	% TODO: Describe what UVL is ; 
@@
 
-\begin{figure}[H]
-	\begin{center}
-		\includegraphics[width=400pt]{../images/first_diagram.pdf}
-	\end{center}
-	\caption{
-		This is an overview of what TRITON accomplishes.
-		TRITON learns the textures of 3d objects to help translate simulated images into photographs. It does this with unpaired data. Each row is a different dataset.
-		}
-	\label{fig:first_diagram}
-\end{figure}
-
-\begin{figure}[H]
-	\begin{center}
-		\includegraphics[width=400pt]{../images/uvl_explanation_minimal.pdf}
-	\end{center}
-	\caption{
-		% This diagram shows the purpose of a UVL image.
-		A UVL scene is an image that has three channels: RGB.
-		R and G are used for U and V, and B is used for L.
-		L stands for Label, and determines which part of the synthetic image will get which texture.
-		The U and V coordinates correspond to positions on each texture,
-		telling it how to project the textures onto the 3d objects represented in the UVL scene.
-		The darkest shade of blue corresponds to the 1st texture, and the next darkest shade of blue corresponds to the 2nd texture etc.
-		}
-	\label{fig:uvl_explanation}
-\end{figure}
-
 	% In this paper, we'll mostly focus on a hand-collected dataset that involves three alphabet blocks that are moved across a table.
@@
 
-% %===============================================================================
-
 	% Domain A and B
@@
 
+% %===============================================================================
 \section{Method}

### 2022-06-14 CORL/example.tex
Indented all subsections
Added explicit loss equations into the translator submodule section and tweaked formulation

@@
 
-%     similaity(x,y) = MSSSIM(L2(x,y)
+%     similarity(x,y) = MSSSIM(L2(x,y)
 
@@
 \newcommand{\real}{\mathbb{R}}
+
+% \newcommand{\similar}{\text{similarity}}
+\newcommand{\similar}{\Omega}
 
@@
 %===============================================================================
-
 \section{Formulation}
@@
 
-	TRITON's goal is to turn 3d simulated images into realistic fake photographs without any matching pairs.
+	TRITON's goal is to turn 3d simulated images into realistic fake photographs without any matching pairs, while maintaining high surface consistency.
 	It does this by simultaneously learning both an image translator and a set of realistic textures.
+	These translations can be useful for downstream tasks, especially robotic policy learning from camera data.
+
 	In contrast to previous works involving neural textures, TRITON can handle more than just camera movements:
-	the positions of objects in the training data can be moved around or deformed as well between samples.
+	the positions of objects in the training data can be moved around or deformed as well between data samples.
+	For this reason, we chose the term ``surface consistency'' instead of ``view consistency''.
+	With high surface consistency, surfaces of translated objects will look the same even when moved around or viewed from different camera angles.
 
@@
 		\caption{
+			A scene is obtained by rendering a 3d state into an image, where the first two color channels represent $u,v$ coordinates and the third channel $l$ represents object labels.
 			% This diagram shows the purpose of a UVL image.
-			A UVL scene is an image that has three channels: RGB.
-			R and G are used for U and V, and B is used for L.
-			L stands for Label, and determines which part of the synthetic image will get which texture.
-			The U and V coordinates correspond to positions on each texture,
-			telling it how to project the textures onto the 3d objects represented in the UVL scene.
-			The darkest shade of blue corresponds to the 1st texture, and the next darkest shade of blue corresponds to the 2nd texture etc.
+			% A UVL scene is an image that has three channels: RGB.
+			% R and G are used for U and V, and B is used for L.
+			% L stands for Label, and determines which part of the synthetic image will get which texture.
+			% The U and V coordinates correspond to positions on each texture,
+			% telling it how to project the textures onto the 3d objects represented in the UVL scene.
+			% The darkest shade of blue corresponds to the 1st texture, and the next darkest shade of blue corresponds to the 2nd texture etc.
 			}
@@
 	There are two components to every dataset: A set of simulated 3d scenes, and a set of photographs.
+	Datasets usually have many more scenes than photographs, since scenes can be generated automatically.
 
@@
 
-	In this work, a scene refers to a rendered 3d simulation state - which includes the position, rotation and deformation of every object (including the camera).
+	In this work, a scene refers to a rendered 3d simulation state - which includes the position, rotation, and deformation of every object (including the camera).
 	% Using some 3d rendering software, be it Blender or Gazebo or some other 3d creates an image from these 
+	We represent each 3d state with a simple $(r,g,b)$ image, in a simple enough format that any decent robotic simulator should able to provide.
 	These scenes have the same datatype and dimensions as photographs and are denoted as $s \in [0,1]^{N \times 3 \times H \times W}$.
@@
 	In a given dataset, each object gets a different label. Likewise, each object is assigned a different texture.
-	We assume that every dataset has $L$ different label values, $L$ different objects, and $L$ different learnable textures.
+	We assume that every dataset has $L$ different label values, $L$ different objects, and that we must learn $L$ different neural textures.
 
@@
 		$T$ uses the same network architectures as MUNIT, and also inherits its adversarial losses $\ell_{adv}$, cycle consistency losses $\ell_{cyc}$ and reconstruction losses $\ell_{rec}$.
-	The main differences between our image translation model and MUNIT are that our style code is fixed making it unimodal, noise is injected into the latent codes during training to prevent overfitting, and we use a different image similarity metric.
+		The main differences between our image translation model and MUNIT are that our style code is fixed (making it unimodal), noise is injected into the latent codes during training to prevent overfitting, and we use a different image similarity metric.
 		During inference however, this intermediate noise is removed and our image translation module is completely determinstic. 
@@
 
-	To ensure cycle consistency, we have an image similarity loss $\ell_{cyc}$ to ensure
-	% $c \approx G_A(E_B(G_B(E_A(\pis)))) = T_{B\rightarrow A}(T_{A\rightarrow B}(\pis)) = T_{B\rightarrow A}(\hat{p})$
-	$\ppis \approx T_{B\rightarrow A}(\hat{p})$
-	and vice versa
-	% $p \approx G_B(E_A(G_A(E_B(p)))) = T_{A\rightarrow B}(T_{B\rightarrow A}(\pis)) = T_{A\rightarrow B}(\hat{c}) = T_{A\rightarrow B}(\hat{\pi},\hat{s})$. 
-	$p \approx T_{A\rightarrow B}(\hat{\pi},\hat{s})$.
-	%I only want to use one of the two representations; either using T_AB or GA(EB) etc. Which one should I use?
-	We also impose an image similarity loss $\ell_{rec}$ to ensure that $\ppis \approx G_A(E_A\ppis)$ and $p \approx G_B(E_B(p))$, which is effectively an autoencoder loss. 
-	In addition, we also have content similarity loss $ \ell_{con}$ to make 
-	$E_A(\pis) \approx E_B(\ph)$ and $E_A(p) \approx E_A(\pish)$.
-	% $E_A(\pis) \approx E_B(\Tab(\pis))$ and $E_A(p) \approx E_A(\Tba(p))$.
+		% For our purposes, MS-SSIM is a metric that measures the similarity of two BCHW tensors on a scale from 0 to 1.
+		% Given two tensors $x$ and $y$, their similarity loss is $\mu\left((x-y)^2\right) - \text{msssim}(x,y)$. 
+		We define an image similarity loss between two image-like tensors that returns a score between 0 and 1, where 0 means perfect similarity:
+		\begin{equation}
+			\similar(x,y) = L_2(x,y)-\msssim(x,y) 
+		\end{equation}
+		This function combines mean pixel-wise $L_2$ distance (used in MUNIT) with multi-scale structural image similarity $\msssim$, introduced in \citep{msssim}.
 
-	Our similarity losses are the sum of L2 distance and negative multi scale structural image similarity (MS-SSIM), introduced in \citep{msssim}.
-For our purposes, MS-SSIM is a metric that measures the similarity of two BCHW tensors on a scale from 0 to 1.
-Given two tensors $x$ and $y$, their similarity loss is $\mu\left((x-y)^2\right) - \text{msssim}(x,y)$.
+		% To ensure cycle consistency, we have an image similarity loss $\ell_{cyc}$ to ensure
+		% % $c \approx G_A(E_B(G_B(E_A(\pis)))) = T_{B\rightarrow A}(T_{A\rightarrow B}(\pis)) = T_{B\rightarrow A}(\hat{p})$
+		% $\ppis \approx T_{B\rightarrow A}(\hat{p})$
+		% and vice versa
+		% % $p \approx G_B(E_A(G_A(E_B(p)))) = T_{A\rightarrow B}(T_{B\rightarrow A}(\pis)) = T_{A\rightarrow B}(\hat{c}) = T_{A\rightarrow B}(\hat{\pi},\hat{s})$. 
+		% $p \approx T_{A\rightarrow B}(\hat{\pi},\hat{s})$.
+		% %I only want to use one of the two representations; either using T_AB or GA(EB) etc. Which one should I use?
+		% We also impose an image similarity loss $\ell_{rec}$ to ensure that $\ppis \approx G_A(E_A\ppis)$ and $p \approx G_B(E_B(p))$, which is effectively an autoencoder loss. 
+		% In addition, we also have content similarity loss $ \ell_{con}$ to make 
+		% $E_A(\pis) \approx E_B(\ph)$ and $E_A(p) \approx E_A(\pish)$.
+		% % $E_A(\pis) \approx E_B(\Tab(\pis))$ and $E_A(p) \approx E_A(\Tba(p))$.
 
+		To ensure cycle consistency, loss $\ell_{cyc}  =  \similar\left(\ppis,T_{B\rightarrow A}\left(\hat{p}\right)\right)  +  \similar\left(p,T_{A\rightarrow B}\left(\hat{\pi},\hat{s}\right)\right)$.
+		% $\ppis \approx T_{B\rightarrow A}(\hat{p})$
+		% and vice versa
+		% $p \approx T_{A\rightarrow B}(\hat{\pi},\hat{s})$.
+		We also impose an image similarity loss $\ell_{rec} = \similar\left(\ppis,G_A\left(E_A\ppis\right)\right) + \similar\left(p,G_B\left(E_B\left(p\right)\right)\right)$
+		%  to ensure that $\ppis \approx G_A(E_A\ppis)$ and $p \approx G_B(E_B(p))$, 
+			which is effectively an autoencoder loss. 
+		In addition, we also have content similarity loss $ \ell_{con} = \similar\left(E_A\left(\pis\right), E_B\left(\ph\right) \right)    +   \similar\left(E_A\left(p\right),E_A\left(\pish\right)\right) $.% to make
+		% $E_A(\pis) \approx E_B(\ph)$ and $E_A(p) \approx E_A(\pish)$.
 		We also have adversarial losses $\ell_{adv}$ that come from two discriminators $D_A$ and $D_B$, targeting domains A and B respectively. They use the LS-GAN loss introduced in \citep{lsgan}.
@@
 		\begin{equation}
-		u\toNL=\text{unproject}(\ph\toN,s\toN)\ \ \ \text{ and } \ \ \ \lUC \Rightarrow u_1 \approx u_2 \dots \approx u_N
+			u\toNL=\text{unproject}(\ph\toN,s\toN)   \eqand  \lUC \Rightarrow u_1 \approx u_2 \dots \approx u_N
 		\end{equation}
@@
 			The recovered texture is more crisp when we have surface consistency losses $\lUC$ and $\lTR$ enabled.
-			[[Michael, should I include CycleGAN and other algos here?]]
+			[[TODO: include cyclegan and other algorithms here]]
 		}

### 2022-06-14 CORL/example.tex
Improved texture reality subsection

@@
 		Instead of feeding input scenes $s$ directly into the image translator $\Tab$, we first apply learnable textures $\tau$ to their surfaces as shown in figure \ref{fig:main_diagram}.
-		Previous works called these learnable textures ``neural textures'', and were parametrized as a discrete grid of differentiable texels. 
+		Previous works called these learnable textures ``neural textures'', and were parametrized by a discrete grid of differentiable texels. 
 		% In contrast, we call our learnable textures ``neural nerual textures'', becuase our textures are a type of neural texture that is parametrized continuously over UV space using a neural fourier feature network.
@@
 		% Given two tensors $x$ and $y$, their similarity loss is $\mu\left((x-y)^2\right) - \text{msssim}(x,y)$. 
-		We define an image similarity loss between two image-like tensors that returns a score between 0 and 1, where 0 means perfect similarity:
+		We define an image similarity loss $\similar$ between two image-like tensors $x,y$ that returns a score between 0 and 1, where 0 means perfect similarity:
 		\begin{equation}
@@
 
-		To michael: Should we mention these caveats in this section, or mention them in the texture realism loss section? That section addresses all of these issues...
+		% To michael: Should we mention these caveats in this section, or mention them in the texture realism loss section? That section addresses all of these issues...
 
@@
 		$\lTR$ is an image similarity loss that makes $\pi$ look like its translation $\hat{p}$.
+		% As it turns out, $\lTR$ is sufficiently powerful loss to generate surface-consistent translations even without $\lUC$, although the results are better when both losses are used.
+		% This loss forces the neural textures to look realistic, instead of allowing them to have arbitrary colors.
+		% In other words, $\lTR$ makes the neural textures more realistic by making their projections look more realistic, like the final outputs.
 		\begin{equation}
-			\lTR \Rightarrow \pi \approx \ph
+			\lTR = \similar(\pi,\ph)
 		\end{equation}
-		% As it turns out, $\lTR$ is sufficiently powerful loss to generate surface-consistent translations even without $\lUC$, although the results are better when both losses are used.
-
-		This loss forces the neural textures to look realistic, instead of allowing them to have arbitrary colors.
-		In other words, $\lTR$ makes the neural textures more realistic by making their projections look more realistic, like the final outputs.
-
 		% So far, we've taken an image translator $T$ and added neural textures $\tau$ and a surface consistency constraint $\lUC$. 
@@
 		% However, we can improve this further.
-
 		% Up until now we have not put any constraints on this neural texture. 
 		Without $\lTR$, $\tau$ can look wildly different each time you train it.
-		As seen in the top row of figure \ref{fig:texture_realism_ablation}, the neural texture looks very unrealistic - the colors are completely arbitrary.
+		As seen in the top row of figure \ref{fig:texture_realism_ablation}, the neural texture looks very unrealistic – the colors are completely arbitrary.
 		After adding $\lTR$ though, $\pih \approx \ph$, and $\tau$ to represents the albedo of the surfaces in the scene.
-		The image similarity loss used in $\lTR$ is calculated the same way image similarity losses are calculated in section \ref{sec:image_translation}: L2 loss minus MSSSIM.
+		% The image similarity loss used in $\lTR$ is calculated the same way image similarity losses are calculated in section \ref{sec:image_translation}: L2 loss minus MSSSIM.
 
-		We can achieve surface-consistent translations just using $\lUC$, without $\lTR$.
+		As it turns out, we can achieve surface-consistent translations just using $\lTR$, without $\lUC$.
 		The the reverse is also true: $\lTR$ is sufficient to ensure surface consistency without $\lUC$.
@@
 
-		There are some advantages to using $\lTR$ alone though: when just using $\lTR$ you can use batch sizes as small as $N=1$, allowing you to save video memory. 
+		With that said, there are some advantages to using $\lTR$ alone: when just using $\lTR$ you can use batch sizes as small as $N=1$, allowing you to save video memory. 
 		Using $\lTR$ is also more numerically stable, as you no longer have to worry about whether the same surfaces are seen across multiple scenes in a batch as you would with $\lUC$.
@@
 		% you don't have to get lucky (the more chaotic, or even the more zoomed in a dataset becomes the less likely there is to be any collisions)
-
-	\subsection{Color Loss}
-
-		TRITON is very robust to geomtric imperfections. However, sometimes it takes this a bit too far - it can overfit textures onto the wrong objects and still maintain consistency.
-		In one example, it manages to map an apple texture onto a cube.
-
-		To help TRITON correctly match textures to objects, we introduce a small amount of supervision by adding a color loss.
-I'm going to stop writing this because I don't know if I even want to keep this in the paper...you can achieve the same result by running the algorithm multiple times, and so its not strictly nessecary.
-
-		ASK MICHAEL: I'd rather not mention this entire section and run out the page limit...it's not very important, and not used in the robot experiments.
-It's only used in the experiment with the five items including the apple.
-Can we add it to the appendix instead?
 
@@
 
+		\subsection{Color Loss}
+
+		TRITON is very robust to geomtric imperfections. However, sometimes it takes this a bit too far - it can overfit textures onto the wrong objects and still maintain consistency.
+		In one example, it manages to map an apple texture onto a cube.
+
+		To help TRITON correctly match textures to objects, we introduce a small amount of supervision by adding a color loss.
+I'm going to stop writing this because I don't know if I even want to keep this in the paper...you can achieve the same result by running the algorithm multiple times, and so its not strictly nessecary.
+
+		ASK MICHAEL: I'd rather not mention this entire section and run out the page limit...it's not very important, and not used in the robot experiments.
+It's only used in the experiment with the five items including the apple.
+Can we add it to the appendix instead?
+
 \section*{Graveyard}

### 2022-06-14 CORL/example.tex
Added formal indexing to Neural Neural Texture Projection

@@
 %     l_T
-%     i - general purpose index
+%     i - texture index
 %     f_i - fourier frequency
@@
 \newcommand{\eqand}{\ \ \ \text{ and }\ \ \ }
+\newcommand{\eqwhere}{\ \ \ \text{ where }\ \ \ }
 \newcommand{\real}{\mathbb{R}}
@@
 
-		These neural textures are represented implicitly by a neural network that maps UV values to RGB values.%, and are used to obtain projections $\pi$ from 3d scenes $s$.
+		These neural neural textures are represented implicitly by a neural network that maps UV values to RGB values. %, and are used to obtain projections $\pi$ from 3d scenes $s$.
+		For each texture $\tau_i \in \tau\toL$, 
 		\begin{equation}
-			\qquad \tau: uv \in\real^2 \rightarrow rgb \in\real^3 % \eqand 
+			\tau_i: (u,v) \in\real^2 \rightarrow (r,g,b) \in\real^3 % \eqand 
 		\end{equation}
 
-		Given a 3d UVL scene $s$, we obtain texture projection $\pi=\tau\toL(s)$ by applying $\tau\toL$ to every scene pixel $uvl \in s$ individually.
-		Each pixel in the resulting projection $rgb\in\pi$ is the result of selecting a texture index $i$ based on the rank of label value $l$, then applying $\tau_i$ to the $u,v$ values.
+		Given scenes $s$, we obtain projections $\pi$ by applying a texture $\tau_i \in \tau\toL$ to every pixel $(u,v,l) \in s$ individually, where texture index $i=I(l)$ is decided by the label value $l$ of that scene pixel.
+		% Each pixel in the resulting projection $rgb\in\pi$ is the result of selecting a texture index $i$ based on the rank of label value $l$, then applying $\tau_i$ to the $u,v$ values.
 		\begin{equation}
-			\pi=\tau\toL(s) \eqand rgb \in \pi = \tau_i(uv)
+			% \pi=\tau\toL(s) \eqand rgb \in \pi = \tau_i(uv)
+			% \pi_{n,c,x,y}=\tau_i(s_{n,1,x,y},s_{n,2,x,y}) \eqwhere 1\le n\le N,\ \  1\le c\le 3 ,\ \ 1\le x\le W,\ \ 1\le y\le H,\ \ \text{and} \ \ i=I(s_{n,3,x,y})
+			\pi_{n,c,x,y}=\tau_i(s_{n,1,x,y},s_{n,2,x,y})
 		\end{equation}
+		where $1\le n\le N,\ \ 1\le c\le 3 ,\ \ 1\le x\le W,\ \ 1\le y\le H,\ \ \text{and} \ \ i=I(s_{n,3,x,y})$.
+		% where $n\in 1\dots N,\ \ c\in 1\dots 3 ,\ \ 1\le x\le W,\ \ 1\le y\le H,\ \ \text{and} \ \ i=I(s_{n,3,x,y})$.
 
@@
 		Each neural neural texture $\tau_i$ is a function consisting of two components: a multi-layer perceptron $M_i$ and a static set of 256 random spatial frequencies $f_{1...256}$. 
-		Given a two-dimensional $uv$ vector, the spatial frequencies are used to generate a high dimensional embedding used as input for the MLP.
+		Given a two-dimensional $(u,v)$ vector, the spatial frequencies are used to generate a high dimensional embedding used as input for $M_i$.
 		\begin{equation}
-				\tau_i(uv) = 
+				\tau_i(u,v) = 
 				\
+				% M_i(
+				% 	\sin( f_1     uv  ) , \ 
+				% 	\cos( f_1     uv  ) , \ 
+				% 	\sin( f_2     uv  ) , \ 
+				% 	\cos( f_2     uv  ) , \ 
+				% 	\dots \ 
+				% 	\sin( f_{256} uv  ) , \ 
+				% 	\cos( f_{256} uv  )  \ 
+				% )
 				M_i(
-					\sin( f_1     uv  ) , \ 
-					\cos( f_1     uv  ) , \ 
-					\sin( f_2     uv  ) , \ 
-					\cos( f_2     uv  ) , \ 
+					\sin( g_1      ) , \ 
+					\cos( g_1      ) , \ 
+					\sin( g_2      ) , \ 
+					\cos( g_2      ) , \ 
 					\dots \ 
-					\sin( f_{256} uv  ) , \ 
-					\cos( f_{256} uv  )  \ 
+					\sin( g_{256}  ) , \ 
+					\cos( g_{256}  )  \ 
 				)
 		\end{equation}
-		where $uv$ and $f_i \in N_{ormal}(\mu=0,\ \sigma=10)$ are two dimensional vectors,
-		$f_i uv$ represents their dot product, 
+		where $g_i=f_i\cdot(u,v)$
+		, $f_i \in N_{ormal}(\mu=0,\ \sigma=10)$ is a two dimensional random gaussian vector,
+		$\cdot$ represents the dot product operator, 
 		%  $rgb$ represents a 3d color vector,
-		and $M_i$ maps a $uv$ embedding to an $rgb$ color value:
+		and $M_i$ maps a $(u,v)$ vector's embedding to an $(r,g,b)$ color value:
 		$M_i: \real^{256} \rightarrow \real^3$.
@@
 		%Squeeze this down - we don't need explanations for why, that can go in the appendix.
-		In practice, we found that TRITON learns faster with neural neural textures than raster neural textures. The generated textures are also smoother and less noisy. 
+		In practice, we found that TRITON learns faster and more stably with our neural neural textures than it does with raster neural textures. The generated textures are also smoother and less noisy. 
 		% The trained fourier-feature textures also exhibit less noise than its raster counterparts. 
@@
 		% Our image translation module $T$ is bidirectional: $\Tab$ translates images from domain A to domain B, and $\Tba$ translates images from domain B to domain A.
-		Our image translation module $T$ is a bidirectional: $\Tab$ translates sim to real (aka domain A to domain B), and $\Tba$ translates real to sim (aka domain B to domain A).
+		Our image translation module $T$ is bidirectional: $\Tab$ translates sim to real (aka domain A to domain B), and $\Tba$ translates real to sim (aka domain B to domain A).
 		\begin{equation}

### 2022-06-14 CORL/example.tex

@@
 
-	TRITON's goal is to turn 3d simulated images into realistic fake photographs without any matching pairs, while maintaining high surface consistency.
+	TRITON's goal is to turn 3d simulated images into realistic fake photographs by training it without any matching pairs, while maintaining high surface consistency.
 	It does this by simultaneously learning both an image translator and a set of realistic textures.
-	These translations can be useful for downstream tasks, especially robotic policy learning from camera data.
+	These translations can be useful for downstream tasks, especially robotic policy learning from camera data, enabling sim2real.
 
-	In contrast to previous works involving neural textures, TRITON can handle more than just camera movements:
+	In contrast to previous works involving `neural textures' \textbf{(mryoo: cite them here)}, TRITON can handle more than just camera movements:
 	the positions of objects in the training data can be moved around or deformed as well between data samples.

### 2022-06-14 CORL/example.tex
Changes with jinghuan

@@
 
-	The photographs, having $(r,g,b)$ values between 0 and 1,
-		are denoted as $p \in [0,1]^{N \times 3 \times H \times W}$ where $N$ is the batch size,
+	% The photographs, having $(r,g,b)$ values between 0 and 1,
+	% 	are denoted as $p \in [0,1]^{N \times 3 \times H \times W}$ where $N$ is the batch size,
+	% 	3 refers to the three $(r,g,b)$ channels, 
+	% 	and $H,W$ are the height and width respectively.
+
+	% A photograph in a set of photographs, having $(r,g,b)$ values between 0 and 1,
+	% 	is denoted as ${p^n \in [0,1]^{ 3 \times H \times W}}$ where $n$ is that photograph's index in that set,
+	% 	3 refers to the three $(r,g,b)$ channels, 
+	% 	and $H,W$ are the height and width respectively.
+
+	A photograph, having $(r,g,b)$ values between 0 and 1,
+		is denoted as ${p \in [0,1]^{ 3 \times H \times W}}$ where 
 		3 refers to the three $(r,g,b)$ channels, 
@@
 	% Using some 3d rendering software, be it Blender or Gazebo or some other 3d creates an image from these 
-	We represent each 3d state with a simple $(r,g,b)$ image, in a simple enough format that any decent robotic simulator should able to provide.
-	These scenes have the same datatype and dimensions as photographs and are denoted as $s \in [0,1]^{N \times 3 \times H \times W}$.
-	However, unlike $p$, $s$'s three $(r,g,b)$ channels encode a special semantic meaning: $(u,v,l)$ as depicted in diagram \ref{fig:uvl_explanation}.
+	We represent each 3d state with a simple $(r,g,b)$ image, in a simple enough format that any decent simulator should able to provide.
+	% These have the same datatype and dimensions as photographs and are denoted as 
+	% $s \in [0,1]^{N \times 3 \times H \times W}$.
+	% A scene has the same dimensions as a photograph and is denoted as 
+	% $s^n \in [0,1]^{3 \times H \times W}$.
+	A scene has the same dimensions as a photograph and is denoted as 
+	$s \in [0,1]^{3 \times H \times W}$.
+	However, unlike $p$, $s$'s three $(r,g,b)$ channels encode a special semantic meaning: $(u,v,l)$ as depicted in figure \ref{fig:uvl_explanation}.
 	The channels $u$ and $v$ refer to a texture coordinate, whereas $l$ refers to a label value that identifies every object in a scene.
@@
 		% Using neural neural textures, we can encode features directly onto the surfaces of the 3d objects in a scene, which the image translation module uses to maintain visual consistency between states and viewpoints.
-		Instead of feeding input scenes $s$ directly into the image translator $\Tab$, we first apply learnable textures $\tau$ to their surfaces as shown in figure \ref{fig:main_diagram}.
+		Instead of feeding a scene $s$ directly into the image translator $\Tab$, we first apply learnable textures $\psi$ to its surfaces as shown in figure \ref{fig:main_diagram}.
 		Previous works called these learnable textures ``neural textures'', and were parametrized by a discrete grid of differentiable texels. 
@@
 		In contrast, we call our learnable textures ``neural nerual textures'', becuase our textures are parametrized continuously over UV space using a neural network.
-		Like previous works, our neural textures $\tau\toL$ are learned jointly with our image translator $T$.
+		Like previous works, our neural textures $\psi\toL$ are learned jointly with our image translator $T$.
 
 		These neural neural textures are represented implicitly by a neural network that maps UV values to RGB values. %, and are used to obtain projections $\pi$ from 3d scenes $s$.
-		For each texture $\tau_i \in \tau\toL$, 
+		For each texture $\psi_i \in \psi\toL$, 
 		\begin{equation}
-			\tau_i: (u,v) \in\real^2 \rightarrow (r,g,b) \in\real^3 % \eqand 
+			\psi_i: (u,v) \in\real^2 \rightarrow (r,g,b) \in\real^3 % \eqand 
 		\end{equation}
 
-		Given scenes $s$, we obtain projections $\pi$ by applying a texture $\tau_i \in \tau\toL$ to every pixel $(u,v,l) \in s$ individually, where texture index $i=I(l)$ is decided by the label value $l$ of that scene pixel.
-		% Each pixel in the resulting projection $rgb\in\pi$ is the result of selecting a texture index $i$ based on the rank of label value $l$, then applying $\tau_i$ to the $u,v$ values.
+		Given a scene $s$, we obtain projection $\pi$ by applying a texture $\psi_i \in \psi\toL$ to every pixel $(u,v,l) \in s$ individually, where texture index $i=I(l)$ is decided by the label value $l$ of that scene pixel.
+		% Each pixel in the resulting projection $rgb\in\pi$ is the result of selecting a texture index $i$ based on the rank of label value $l$, then applying $\psi_i$ to the $u,v$ values.
 		\begin{equation}
-			% \pi=\tau\toL(s) \eqand rgb \in \pi = \tau_i(uv)
-			% \pi_{n,c,x,y}=\tau_i(s_{n,1,x,y},s_{n,2,x,y}) \eqwhere 1\le n\le N,\ \  1\le c\le 3 ,\ \ 1\le x\le W,\ \ 1\le y\le H,\ \ \text{and} \ \ i=I(s_{n,3,x,y})
-			\pi_{n,c,x,y}=\tau_i(s_{n,1,x,y},s_{n,2,x,y})
+			% \pi=\psi\toL(s) \eqand rgb \in \pi = \psi_i(uv)
+			% \pi_{n,c,x,y}=\psi_i(s_{n,1,x,y},s_{n,2,x,y}) \eqwhere 1\le n\le N,\ \  1\le c\le 3 ,\ \ 1\le x\le W,\ \ 1\le y\le H,\ \ \text{and} \ \ i=I(s_{n,3,x,y})
+			% \pi_{n,c,x,y}=\psi_i(s_{n,1,x,y},s_{n,2,x,y})
+			\pi_{c,x,y}=\psi_i(s_{1,x,y},s_{2,x,y})_c
 		\end{equation}
-		where $1\le n\le N,\ \ 1\le c\le 3 ,\ \ 1\le x\le W,\ \ 1\le y\le H,\ \ \text{and} \ \ i=I(s_{n,3,x,y})$.
-		% where $n\in 1\dots N,\ \ c\in 1\dots 3 ,\ \ 1\le x\le W,\ \ 1\le y\le H,\ \ \text{and} \ \ i=I(s_{n,3,x,y})$.
+		% where $1\le n\le N,\ \ 1\le c\le 3 ,\ \ 1\le x\le W,\ \ 1\le y\le H,\ \ \text{and} \ \ i=I(s_{n,3,x,y})$.
+		% where $n\in \{1\dots N\},\ \ c\in \{1\dots 3\} ,\ x\in \{1\dots W\},\ y\in \{1\dots H\},\ \ \text{and} \ \ i=I(s_{n,3,x,y})$.
+		where $c\in \{1\dots 3\} ,\ x\in \{1\dots W\},\ y\in \{1\dots H\},\ \ \text{and} \ \ i=I(s_{3,x,y})$.
 
 		%DISCARDED TEXT:
-		% A particular neural texture $\tau_i$ uses maps $uv \rightarrow rgb$.
-Similarly, the set of textures $\tau_{1\dots L}$ maps uvl values to rgb values: $\tau_{1\dots L}(uvl)=\tau_l(uv)$ where $uvl$ is the concatenation of a $uv$ vector with a label $l \in 1\dots L$.
+		% A particular neural texture $\psi_i$ uses maps $uv \rightarrow rgb$.
+Similarly, the set of textures $\psi_{1\dots L}$ maps uvl values to rgb values: $\psi_{1\dots L}(uvl)=\psi_l(uv)$ where $uvl$ is the concatenation of a $uv$ vector with a label $l \in 1\dots L$.
 		% TRITON's neural neural texture module lets it create features on the surfaces of objects, and thus take advantage of 3d geometric priors.
 
-				% The neural texture applied to a particular scene pixel $uvl \in s$ is multiplexed by $l$, and the respective output pixel $rgb \in \pi = \tau_luv$. 
-				% Texture projections $\pi$ are obatined by applying a set of $L$ different neural neural textures $\tau\toL$ to a UVL scene $s$ pixelwise.
+				% The neural texture applied to a particular scene pixel $uvl \in s$ is multiplexed by $l$, and the respective output pixel $rgb \in \pi = \psi_luv$. 
+				% Texture projections $\pi$ are obatined by applying a set of $L$ different neural neural textures $\psi\toL$ to a UVL scene $s$ pixelwise.
 				% [[IMPORTANT: THIS IS TECHNICALLY INCORRECT AS l IS A VALUE BETWEEN 0 and 1]]
@@
 				% where $i\in[1,L]\cap\mathbb{Z}$ is the rank of $l$
-				% When applied to a UVL scene, it is applied to each $uvl \in s$ pixel individually where every pixel $rgb \in \pi = \tau$ 
+				% When applied to a UVL scene, it is applied to each $uvl \in s$ pixel individually where every pixel $rgb \in \pi = \psi$ 
 				%What is it...then how do we use it...
 				% (as the 2nd sentence)
-				% Given a 3D scene $s$, we apply $\tau\toL$ to each UV to obtain RGB surface values...
-				% project learnable RGB textures $\tau\toL$ to their surfaces to obtain projection $\pi$. 
-				% 			Neural Neural Textures $\tau\toLuv$: Given an input scene $s$ depicting 3d objects with labels $1\dots L$, we apply a function on their surface's UV values with neural textures $\tau\toL$ to obtain projection $\pi$.
+				% Given a 3D scene $s$, we apply $\psi\toL$ to each UV to obtain RGB surface values...
+				% project learnable RGB textures $\psi\toL$ to their surfaces to obtain projection $\pi$. 
+				% 			Neural Neural Textures $\psi\toLuv$: Given an input scene $s$ depicting 3d objects with labels $1\dots L$, we apply a function on their surface's UV values with neural textures $\psi\toL$ to obtain projection $\pi$.
 
 				% \begin{equation}
-					% \pi=\tau\toL(s)
+					% \pi=\psi\toL(s)
 				% \end{equation}
@@
 		%THIS WILL BE REPLACED BY SUMMARY SECTION
-		% 	Given a batch of $N$ UVL Scenes $s_{1\dots B}$ with $L$ different label values, we project $L$ different neural textures $\tau_{1\dots L}$ onto that scene; obtaining projections $\pi_{1\dots B}$.
+		% 	Given a batch of $N$ UVL Scenes $s_{1\dots B}$ with $L$ different label values, we project $L$ different neural textures $\psi_{1\dots L}$ onto that scene; obtaining projections $\pi_{1\dots B}$.
 This projection mechanism is illustrated in figure \ref{fig:uvl_explanation}.
 
-		% Each neural texture $\tau_i$ is a function consisting of two components: a multi-layer perceptron $M_i$ and a static set of 256 random spatial frequencies $f_{1...256}$. 
+		% Each neural texture $\psi_i$ is a function consisting of two components: a multi-layer perceptron $M_i$ and a static set of 256 random spatial frequencies $f_{1...256}$. 
 		% Given a two-dimensional $uv$ vector, the spatial frequencies are used to generate a high dimensional embedding used as input for the MLP.
 		% \begin{equation}
-		% 		\tau_i(uv) = 
+		% 		\psi_i(uv) = 
 		% 		\
@@
 
-		Each neural neural texture $\tau_i$ is a function consisting of two components: a multi-layer perceptron $M_i$ and a static set of 256 random spatial frequencies $f_{1...256}$. 
+		We now discuss the implementation of our neural neural networks $\psi\toL$.
+		Each neural neural texture $\psi_i$ is a function consisting of two components: a multi-layer perceptron $M_i$ and a static set of 256 random spatial frequencies $f_{1...256} \in \real ^ {256 \times 2}$.
 		Given a two-dimensional $(u,v)$ vector, the spatial frequencies are used to generate a high dimensional embedding used as input for $M_i$.
 		\begin{equation}
-				\tau_i(u,v) = 
+				\psi_i(u,v) = 
 				\
@@
 		where $g_i=f_i\cdot(u,v)$
-		, $f_i \in N_{ormal}(\mu=0,\ \sigma=10)$ is a two dimensional random gaussian vector,
+		% , $f_i \in N_{ormal}(\mu=0,\ \sigma=10)$ is a two dimensional random gaussian vector,
+		, $f_i \in \mathcal{N}(\mu=0,\ \sigma=10)$ is a two dimensional random gaussian vector,
 		$\cdot$ represents the dot product operator, 
@@
 		\end{equation}
-		% So far, we've taken an image translator $T$ and added neural textures $\tau$ and a surface consistency constraint $\lUC$. 
+		% So far, we've taken an image translator $T$ and added neural textures $\psi$ and a surface consistency constraint $\lUC$. 
 		% If we wanted to, could stop here - those formulations are sufficient to produce consistent sim-to-real translations.
@@
 		% Up until now we have not put any constraints on this neural texture. 
-		Without $\lTR$, $\tau$ can look wildly different each time you train it.
+		Without $\lTR$, $\psi$ can look wildly different each time you train it.
 		As seen in the top row of figure \ref{fig:texture_realism_ablation}, the neural texture looks very unrealistic – the colors are completely arbitrary.
-		After adding $\lTR$ though, $\pih \approx \ph$, and $\tau$ to represents the albedo of the surfaces in the scene.
+		After adding $\lTR$ though, $\pih \approx \ph$, and $\psi$ to represents the albedo of the surfaces in the scene.
 		% The image similarity loss used in $\lTR$ is calculated the same way image similarity losses are calculated in section \ref{sec:image_translation}: L2 loss minus MSSSIM.
@@
 		Algorithm                              & \multicolumn{1}{c|}{Sync} & \multicolumn{1}{c|}{Unsync} & \multicolumn{1}{c|}{Sync} & \multicolumn{1}{c|}{Unsync} & \multicolumn{1}{c|}{Sync} & \multicolumn{1}{c|}{Unsync} & \multicolumn{1}{c|}{Sync} & \multicolumn{1}{c}{Unsync} \\ \hline
-		\textbf{TRITON w/o $\tau, \lUC, \lTR$} & 0.0437                    & 0.0373                      & 0.00500                   & 0.00490                     & 0.434                     & 0.402                       & 0.0425                    & 0.0392                     \\
+		\textbf{TRITON w/o $\psi, \lUC, \lTR$} & 0.0437                    & 0.0373                      & 0.00500                   & 0.00490                     & 0.434                     & 0.402                       & 0.0425                    & 0.0392                     \\
 		\textbf{TRITON w/o $\lUC, \lTR$}       & 0.0442                    & 0.0386                      & 0.00586                   & 0.00589                     & 0.285                     & 0.255                       & 0.0364                    & 0.0310                     \\

### 2022-06-14 CORL/example.tex
With Jinghuan: finished image_translation

@@
 		Each neural neural texture $\psi_i$ is a function consisting of two components: a multi-layer perceptron $M_i$ and a static set of 256 random spatial frequencies $f_{1...256} \in \real ^ {256 \times 2}$.
-		Given a two-dimensional $(u,v)$ vector, the spatial frequencies are used to generate a high dimensional embedding used as input for $M_i$.
+		Given a two-dimensional $(u,v)$ vector, the spatial frequencies are used to generate a high dimensional embedding of $(u,v)$ as input for $M_i$, where $M_i$ is a function $\real^{256} \to \real^{3}$ mapping that embedding to an $(r,g,b)$ color value:
 		\begin{equation}
@@
 		, $f_i \in \mathcal{N}(\mu=0,\ \sigma=10)$ is a two dimensional random gaussian vector,
-		$\cdot$ represents the dot product operator, 
+		and $\cdot$ is the dot product operator.
 		%  $rgb$ represents a 3d color vector,
-		and $M_i$ maps a $(u,v)$ vector's embedding to an $(r,g,b)$ color value:
-		$M_i: \real^{256} \rightarrow \real^3$.
+		% :
+		% $M_i: \real^{256} \rightarrow \real^3$.
 		Note that there is nothing special about 256 or 10: these hyperparameter values just happen to work nicely.
@@
 		%Squeeze this down - we don't need explanations for why, that can go in the appendix.
-		In practice, we found that TRITON learns faster and more stably with our neural neural textures than it does with raster neural textures. The generated textures are also smoother and less noisy. 
+		In practice, we found that TRITON learns faster and more stably with our neural neural textures than it does with raster neural textures.
+The generated textures are also smoother and less noisy.
+See the supplementary material for more details.
 		% The trained fourier-feature textures also exhibit less noise than its raster counterparts. 
@@
 
-		$T$ is based on the image translation module used in \citep{surgical_video_translation}, which is a based on a variant \cite{surgical_image_translation} of MUNIT \cite{munit}. 
+		$T$ is based on the image translation module used in \citet{surgical_video_translation}, which is a based on a variant \cite{surgical_image_translation} of MUNIT \cite{munit}. 
 		$T$ uses the same network architectures as MUNIT, and also inherits its adversarial losses $\ell_{adv}$, cycle consistency losses $\ell_{cyc}$ and reconstruction losses $\ell_{rec}$.
-		The main differences between our image translation model and MUNIT are that our style code is fixed (making it unimodal), noise is injected into the latent codes during training to prevent overfitting, and we use a different image similarity metric.
+		The main differences between our image translation model and MUNIT are that we use a different image similarity loss $\Omega$, and like \citet[]{surgical_image_translation} and \citet[]{surgical_video_translation} our style code is fixed (making it unimodal) and noise is injected into the latent codes during training to prevent overfitting.
 		During inference however, this intermediate noise is removed and our image translation module is completely determinstic. 
@@
 
-		MUNIT translates images by encoding both image domains into a common latent space, then decoding them into their respective domains.
+		MUNIT translates images by encoding both domains $A$ and $B$ into a common latent space, then decoding them into their respective domains  $B$ and $A$.
 		In our translation module, we define fake photos $\ph = \Tab(\pis) = G_B(E_A(\pis))$ and fake projection/uvl scenes $\ppish = \Tba(p) = G_A(E_B(p))$
@@
 		% Given two tensors $x$ and $y$, their similarity loss is $\mu\left((x-y)^2\right) - \text{msssim}(x,y)$. 
-		We define an image similarity loss $\similar$ between two image-like tensors $x,y$ that returns a score between 0 and 1, where 0 means perfect similarity:
+		We define an image similarity loss $\similar$ between two images $x,y$ that returns a score between 0 and 1, where 0 means perfect similarity:
 		\begin{equation}
@@
 		This function combines mean pixel-wise $L_2$ distance (used in MUNIT) with multi-scale structural image similarity $\msssim$, introduced in \citep{msssim}.
+Note that this loss can also be applied to the latent representations obtained by $E_A$ and $E_B$, because like images those tensors are also three dimensional.
 
@@
 
-		To ensure cycle consistency, loss $\ell_{cyc}  =  \similar\left(\ppis,T_{B\rightarrow A}\left(\hat{p}\right)\right)  +  \similar\left(p,T_{A\rightarrow B}\left(\hat{\pi},\hat{s}\right)\right)$.
+		We have cycle consistency loss ${\ell_{cyc}  =  \similar\left(\ppis,T_{B\rightarrow A}\left(\hat{p}\right)\right)  +  \similar\left(p,T_{A\rightarrow B}\left(\hat{\pi},\hat{s}\right)\right)}$
 		% $\ppis \approx T_{B\rightarrow A}(\hat{p})$
@@
 		% $p \approx T_{A\rightarrow B}(\hat{\pi},\hat{s})$.
-		We also impose an image similarity loss $\ell_{rec} = \similar\left(\ppis,G_A\left(E_A\ppis\right)\right) + \similar\left(p,G_B\left(E_B\left(p\right)\right)\right)$
+		, similarity loss ${\ell_{rec} = \similar\left(\ppis,G_A\left(E_A\ppis\right)\right) + \similar\left(p,G_B\left(E_B\left(p\right)\right)\right)}$
 		%  to ensure that $\ppis \approx G_A(E_A\ppis)$ and $p \approx G_B(E_B(p))$, 
-			which is effectively an autoencoder loss. 
-		In addition, we also have content similarity loss $ \ell_{con} = \similar\left(E_A\left(\pis\right), E_B\left(\ph\right) \right)    +   \similar\left(E_A\left(p\right),E_A\left(\pish\right)\right) $.% to make
+			(which is effectively an autoencoder loss),   
+		and content similarity loss ${ \ell_{con} = \similar\left(E_A\left(\pis\right), E_B\left(\ph\right) \right)    +   \similar\left(E_A\left(p\right),E_A\left(\pish\right)\right) }$.
 		% $E_A(\pis) \approx E_B(\ph)$ and $E_A(p) \approx E_A(\pish)$.
 		We also have adversarial losses $\ell_{adv}$ that come from two discriminators $D_A$ and $D_B$, targeting domains A and B respectively. They use the LS-GAN loss introduced in \citep{lsgan}. 
+		In total, our image translator loss is $\ell_T=\ell_{cyc}+\ell_{rec}+\ell_{con}+\ell_{adv}$.
 
-		In total, the loss for the image translator module $T$ is $\ell_T=\ell_{cyc}+\ell_{rec}+\ell_{con}+\ell_{adv}$.
+		% PRETTIEST BUT TOO MUCH SPACE
+		% 		Inheriting from MUNIT, we have three losses: cycle consistency loss $\ell_{cyc}$, content similarity loss $\ell_{con}$, and reconstruction loss $\ell_{rec}$ which functions as an autoencoder loss.
+		% 		\begin{eqnarray}
+		% \begin{center}
+		% 	\begin{align}
 
-		% NOTE: THe other paper \citep{surgical_video_translation} didn't do into this much detail; instead putting most of these losses in teh appendix.
+		% 		\ell_{cyc}  =  \similar\left(\ppis,T_{B\rightarrow A}\left(\hat{p}\right)\right)  +  \similar\left(p,T_{A\rightarrow B}\left(\hat{\pi},\hat{s}\right)\right)
+
+		% 		\ell_{con} = \similar\left(E_A\left(\pis\right), E_B\left(\ph\right) \right)    +   \similar\left(E_A\left(p\right),E_A\left(\pish\right)\right)
+
+		% 		\ell_{rec} = \similar\left(\ppis,G_A\left(E_A\ppis\right)\right) + \similar\left(p,G_B\left(E_B\left(p\right)\right)\right)
+		% 	\end{align}
+		% \end{center}
+		% 		\end{eqnarray}
+
+		% In total, the loss for the image translator module $T$ is $\ell_T=\ell_{cyc}+\ell_{rec}+\ell_{con}+\ell_{adv}$.
+
+		% % NOTE: THe other paper \citep{surgical_video_translation} didn't do into this much detail; instead putting most of these losses in teh appendix.
 I think we can cut this down?
@@
 			\begin{center}
-				\includegraphics[width=400pt]{../images/unprojection_consistency_loss_without_reprojection.pdf}
+				\includegraphics[width=.8\textwidth]{../images/unprojection_consistency_loss_without_reprojection.pdf}
 			\end{center}

### 2022-06-15 CORL/example.tex
Started Intro

@@
 
-	I introduce you to TRITON. The rest of the introduction text goes here; I've commented out my old incomplete introduction.
+Problem: 
+Why is this problem important?
+No view consistency.
+
+Introducing our intuition of what improvements can solve this problem.
+
+Our exact method - introducing our components and what we're doing
+
+Conclusion: This works well, and our contributions are x
+
+% I introduce you to TRITON. The rest of the introduction text goes here; I've commented out my old incomplete introduction.
 
@@
 		% $E_A(\pis) \approx E_B(\ph)$ and $E_A(p) \approx E_A(\pish)$.
-		We also have adversarial losses $\ell_{adv}$ that come from two discriminators $D_A$ and $D_B$, targeting domains A and B respectively. They use the LS-GAN loss introduced in \citep{lsgan}. 
+		We also have adversarial losses $\ell_{adv}$ that come from two discriminators $D_A$ and $D_B$, targeting domains A and B respectively, using the LS-GAN loss introduced in \citet{lsgan}. 
 		In total, our image translator loss is $\ell_T=\ell_{cyc}+\ell_{rec}+\ell_{con}+\ell_{adv}$.

### 2022-06-15 CORL/example.tex
Made to l and to n superscripts
Changed _i and _n to ^i and ^n

@@
 
-\newcommand{\toN}{_{1\dots N}}
+\newcommand{\toN}{^{1\dots N}}
 % \newcommand{\toNL}{_{1\dots B,\text{ } 1\dots L}}
-\newcommand{\toNL}{_{1\dots N, 1\dots L}}
-\newcommand{\toL}{_{1\dots L}}
+\newcommand{\toNL}{^{1\dots N, 1\dots L}}
+\newcommand{\toL}{^{1\dots L}}
 
@@
 		These neural neural textures are represented implicitly by a neural network that maps UV values to RGB values. %, and are used to obtain projections $\pi$ from 3d scenes $s$.
-		For each texture $\psi_i \in \psi\toL$, 
+		For each texture $\psi^i \in \psi\toL$, 
 		\begin{equation}
-			\psi_i: (u,v) \in\real^2 \rightarrow (r,g,b) \in\real^3 % \eqand 
+			\psi^i: (u,v) \in\real^2 \rightarrow (r,g,b) \in\real^3 % \eqand 
 		\end{equation}
 
-		Given a scene $s$, we obtain projection $\pi$ by applying a texture $\psi_i \in \psi\toL$ to every pixel $(u,v,l) \in s$ individually, where texture index $i=I(l)$ is decided by the label value $l$ of that scene pixel.
-		% Each pixel in the resulting projection $rgb\in\pi$ is the result of selecting a texture index $i$ based on the rank of label value $l$, then applying $\psi_i$ to the $u,v$ values.
+		Given a scene $s$, we obtain projection $\pi$ by applying a texture $\psi^i \in \psi\toL$ to every pixel $(u,v,l) \in s$ individually, where texture index $i=I(l)$ is decided by the label value $l$ of that scene pixel.
+		% Each pixel in the resulting projection $rgb\in\pi$ is the result of selecting a texture index $i$ based on the rank of label value $l$, then applying $\psi^i$ to the $u,v$ values.
 		\begin{equation}
-			% \pi=\psi\toL(s) \eqand rgb \in \pi = \psi_i(uv)
-			% \pi_{n,c,x,y}=\psi_i(s_{n,1,x,y},s_{n,2,x,y}) \eqwhere 1\le n\le N,\ \  1\le c\le 3 ,\ \ 1\le x\le W,\ \ 1\le y\le H,\ \ \text{and} \ \ i=I(s_{n,3,x,y})
-			% \pi_{n,c,x,y}=\psi_i(s_{n,1,x,y},s_{n,2,x,y})
-			\pi_{c,x,y}=\psi_i(s_{1,x,y},s_{2,x,y})_c
+			% \pi=\psi\toL(s) \eqand rgb \in \pi = \psi^i(uv)
+			% \pi_{n,c,x,y}=\psi^i(s_{n,1,x,y},s_{n,2,x,y}) \eqwhere 1\le n\le N,\ \  1\le c\le 3 ,\ \ 1\le x\le W,\ \ 1\le y\le H,\ \ \text{and} \ \ i=I(s_{n,3,x,y})
+			% \pi_{n,c,x,y}=\psi^i(s_{n,1,x,y},s_{n,2,x,y})
+			\pi_{c,x,y}=\psi^i(s_{1,x,y},s_{2,x,y})_c
 		\end{equation}
@@
 		% where $n\in \{1\dots N\},\ \ c\in \{1\dots 3\} ,\ x\in \{1\dots W\},\ y\in \{1\dots H\},\ \ \text{and} \ \ i=I(s_{n,3,x,y})$.
-		where $c\in \{1\dots 3\} ,\ x\in \{1\dots W\},\ y\in \{1\dots H\},\ \ \text{and} \ \ i=I(s_{3,x,y})$.
+		where channel $c\in \{1\dots 3\} ,\ x\in \{1\dots W\},\ y\in \{1\dots H\},\ \ \text{and texture index} \ \ i=I(s_{3,x,y})$.
 
 		%DISCARDED TEXT:
-		% A particular neural texture $\psi_i$ uses maps $uv \rightarrow rgb$.
+		% A particular neural texture $\psi^i$ uses maps $uv \rightarrow rgb$.
 Similarly, the set of textures $\psi_{1\dots L}$ maps uvl values to rgb values: $\psi_{1\dots L}(uvl)=\psi_l(uv)$ where $uvl$ is the concatenation of a $uv$ vector with a label $l \in 1\dots L$.
@@
 
-		% Each neural texture $\psi_i$ is a function consisting of two components: a multi-layer perceptron $M_i$ and a static set of 256 random spatial frequencies $f_{1...256}$. 
+		% Each neural texture $\psi^i$ is a function consisting of two components: a multi-layer perceptron $M^i$ and a static set of 256 random spatial frequencies $f_{1...256}$. 
 		% Given a two-dimensional $uv$ vector, the spatial frequencies are used to generate a high dimensional embedding used as input for the MLP.
 		% \begin{equation}
-		% 		\psi_i(uv) = 
+		% 		\psi^i(uv) = 
 		% 		\
-		% 		M_i\left(\left[
+		% 		M^i\left(\left[
 		% 			\sin \left( f_1     \cdot \left(u,v\right) \right) , \ 
@@
 		% \end{equation}
-		% where $uv$ and $f_i \in N_{ormal}(\mu=0,\ \sigma=10)$ are two dimensional vectors,
-		%  $f_i uv$ represents their dot product, 
+		% where $uv$ and $f^i \in N_{ormal}(\mu=0,\ \sigma=10)$ are two dimensional vectors,
+		%  $f^i uv$ represents their dot product, 
 		% %  $rgb$ represents a 3d color vector,
-		%  and $M_i$ maps a $uv$ embedding to an $rgb$ color value:
-		%  $M_i: \real^{256} \rightarrow \real^3$.
+		%  and $M^i$ maps a $uv$ embedding to an $rgb$ color value:
+		%  $M^i: \real^{256} \rightarrow \real^3$.
 		% Note that there is nothing special about 256 or 10: these hyperparameter values just happen to work nicely.
@@
 		We now discuss the implementation of our neural neural networks $\psi\toL$.
-		Each neural neural texture $\psi_i$ is a function consisting of two components: a multi-layer perceptron $M_i$ and a static set of 256 random spatial frequencies $f_{1...256} \in \real ^ {256 \times 2}$.
-		Given a two-dimensional $(u,v)$ vector, the spatial frequencies are used to generate a high dimensional embedding of $(u,v)$ as input for $M_i$, where $M_i$ is a function $\real^{256} \to \real^{3}$ mapping that embedding to an $(r,g,b)$ color value:
+		Each neural neural texture $\psi^i$ is a function consisting of two components: a multi-layer perceptron $M^i$ and a static set of 256 random spatial frequencies $f_{1...256} \in \real ^ {256 \times 2}$.
+		Given a two-dimensional $(u,v)$ vector, the spatial frequencies are used to generate a high dimensional embedding of $(u,v)$ as input for $M^i$, where $M^i$ is a function $\real^{256} \to \real^{3}$ mapping that embedding to an $(r,g,b)$ color value:
 		\begin{equation}
-				\psi_i(u,v) = 
+				\psi^i(u,v) = 
 				\
-				% M_i(
+				% M^i(
 				% 	\sin( f_1     uv  ) , \ 
@@
 				% )
-				M_i(
+				M^i(
 					\sin( g_1      ) , \ 
@@
 		\end{equation}
-		where $g_i=f_i\cdot(u,v)$
-		% , $f_i \in N_{ormal}(\mu=0,\ \sigma=10)$ is a two dimensional random gaussian vector,
-		, $f_i \in \mathcal{N}(\mu=0,\ \sigma=10)$ is a two dimensional random gaussian vector,
+		where $g_k=f_k\cdot(u,v)$
+		% , $f^i \in N_{ormal}(\mu=0,\ \sigma=10)$ is a two dimensional random gaussian vector,
+		, $f_k \in \mathcal{N}(\mu=0,\ \sigma=10)$ is a two dimensional random gaussian vector,
 		and $\cdot$ is the dot product operator.
@@
 		% :
-		% $M_i: \real^{256} \rightarrow \real^3$.
+		% $M^i: \real^{256} \rightarrow \real^3$.
 		Note that there is nothing special about 256 or 10: these hyperparameter values just happen to work nicely.
@@
 
+		%_i
 		% Our image translation module $T$ is bidirectional: $\Tab$ translates images from domain A to domain B, and $\Tba$ translates images from domain B to domain A.
@@
 		We sample a random batch of UVL scenes $S\toN$, and translate them into $\ph\toN$.
-		Using geometric knowledge of the scene encoded in $S\toN$, we individually unproject each $\ph_i \in \ph\toN$ back into texture space, to obtain $N$ sets of $L$ unprojected textures $u\toNL$.
+		Using geometric knowledge of the scene encoded in $S\toN$, we individually unproject each $\ph^i \in \ph\toN$ back into texture space, to obtain $N$ sets of $L$ unprojected textures $u\toNL$.
 		We then use the per-pixel, batch-wise standard deviation of the unprojections as unprojection consistency loss $\lUC = \sigma(u\toNL)\toL$.
@@
 \begin{table}[H]
+
 	\begin{tabular}{l|llllllll}

### 2022-06-15 CORL/example.tex
Added formal lUC definition
4.4 sim2real

@@
 \newcommand{\similar}{\Omega}
+\newcommand{\unprojection}{\omega}
+\newcommand{\expectation}{\mathop{\mathbb{E}}}
+\newcommand{\lsum}{\sum\limits}
 
@@
 \usepackage{amsmath}
+\usepackage{multicol}
+\usepackage{multirow}
 \usepackage[utf8]{inputenc}
@@
 
-	TRITON's goal is to turn 3d simulated images into realistic fake photographs by training it without any matching pairs, while maintaining high surface consistency.
+	TRITON's goal is to turn 3d simulated images into realistic fake photographs (by training it without any matching pairs), while maintaining high surface consistency.
 	It does this by simultaneously learning both an image translator and a set of realistic textures.
@@
 	the positions of objects in the training data can be moved around or deformed as well between data samples.
-	For this reason, we chose the term ``surface consistency'' instead of ``view consistency''.
+	For this reason, we chose the term ``surface consistency'' instead of ``view consistency'', which was the term used in [] \textbf{(mryoo: cite)}.
 	With high surface consistency, surfaces of translated objects will look the same even when moved around or viewed from different camera angles.
@@
 
-	A photograph, having $(r,g,b)$ values between 0 and 1,
+	A photograph is an image tensor, having $(r,g,b)$ values between 0 and 1,
 		is denoted as ${p \in [0,1]^{ 3 \times H \times W}}$ where 
@@
 
-	In each dataset, we must also define a function $I(l)$ that maps label values to texture indices. A simple way to do this is with the following definition:
-	\begin{equation}
-		I: \left\{\frac{1}{L},\frac{2}{L},\dots \frac{L}{L}\right\} \rightarrow \left\{1,2,\dots L\right\}  \eqand  I(l)=l\cdot L
+TODO: Say I scales and discretizes l, don't say more than that. 
+% 	In each dataset, we must also define a function $I(l)$ that maps label values to texture indices. A simple way to do this is with the following definition:
+% 	\begin{equation}
+% 		I: \left\{\frac{1}{L},\frac{2}{L},\dots \frac{L}{L}\right\} \rightarrow \left\{1,2,\dots L\right\}  \eqand  I(l)=l\cdot L
 	\end{equation}
@@
 			% \pi_{n,c,x,y}=\psi^i(s_{n,1,x,y},s_{n,2,x,y})
-			\pi_{c,x,y}=\psi^i(s_{1,x,y},s_{2,x,y})_c
+			\pi_{[x,y]}=\psi^i(s_{[x,y,1]},s_{[x,y,2]})
 		\end{equation}
@@
 		% where $n\in \{1\dots N\},\ \ c\in \{1\dots 3\} ,\ x\in \{1\dots W\},\ y\in \{1\dots H\},\ \ \text{and} \ \ i=I(s_{n,3,x,y})$.
-		where channel $c\in \{1\dots 3\} ,\ x\in \{1\dots W\},\ y\in \{1\dots H\},\ \ \text{and texture index} \ \ i=I(s_{3,x,y})$.
+		where channel $c\in \{1, 2, 3\} ,\ x\in \{1\dots W\},\ y\in \{1\dots H\},\ \ \text{and texture index} \ \ i=I(l) ~\text{where}~ l=s_{[x,y,3]}$ and subscript means multidimensional indexing.
 
@@
 
+		% %Unabbreviated
+		% \begin{equation}
+		% 	\unprojection_{c,U,V}^{n,i}=\expectation\ph_{c,x,y}^n 
+		% 	\eqand \bar{\unprojection}^i_{c,u,v}   =   
+		% 		\frac{1}{N} \lsum_{n=1}^N\unprojection^{n,i}_{c,u,v} 
+		% 	\eqand 
+		% 	\lUC=\frac{\lsum_{i=1}^L\lsum_{c=1}^3\lsum_{U=1}^{128}\lsum_{V=1}^{128}
+		% 	\sqrt[]{\frac{1}{N}\lsum_{n=1}^N\left(\bar{\unprojection}^i_{c,u,v}-\unprojection^{i,n}_{c,U,V}\right)^2}}
+		% 	{3\cdot128\cdot128\cdot L}
+		% \end{equation}
+		%
+		%Abbreviated
+		To formally define $\lUC$ we define unprojections $\unprojection^{1...N,1...L}$ and mean unprojections (aka recovered textures) $\bar{\unprojection}^{1...L}$ 
+		with each $\unprojection^{n,i}\in\real^{3\times128\times128}$:
+		\begin{equation}
+			\unprojection_{c,U,V}^{n,i}=\expectation\ph_{c,x,y}^n 
+			\eqand \bar{\unprojection}^i_{c,u,v}   =   
+				\frac{1}{N} \lsum_n\unprojection^{n,i}_{c,u,v} 
+			\eqand 
+			\lUC=\frac{\lsum_{i,c,U,V}
+			\sqrt[]{\frac{1}{N}\lsum_n\left(\bar{\unprojection}^i_{c,u,v}-\unprojection^{i,n}_{c,U,V}\right)^2}}
+			{3\cdot128\cdot128\cdot L}
+		\end{equation}
+		where $U=\lfloor128u\rfloor$ and $V=\lfloor128v\rfloor$ and $i=I(l)$ with
+		%  $(u,v,l)=s^n_{1...3,x,y}$
+		$u=s^n_{1,x,y}$, $v=s^n_{2,x,y}$, $l=s^n_{3,x,y}$
+		for all 
+		$n \in \{1...N\}$ , 
+		$i \in \{1...L\}$ , 
+		$c \in \{1,2,3}$ , 
+		$x \in \{1...W\}$ , 
+		$y \in \{1...H\}$ , 
+		$U \in \{1...128\}$ , 
+		$V \in \{1...128\}$.
+
 	\subsection{Texture Realism Loss}
@@
 
+\subsection{Sim2real Transfer for Robot Learning}
+In this section we demonstrate how TRITON improves sim2real transfer for robot learning.
+To do this, we first train TRITON on a dataset consist of unpaired UVL scenes from simulator and photos from the real robot.
+After that, we train the robot policy in the simulator only.
+The input of the policy is the fake photo $\hat{p}$ translated from the simulated UVL scene using TRITON's translator $T_{A\to B}$.
+Finally, the trained policy is evaluated on the real robot, taking real photos $p$ as input.
+Ideally, a good image translation model leads to less gap between $p$ and $\hat{p}$, so that the policy trained on synthesized photos will transfer to real domain seamlessly.
+
+\paragraph{Task} We use a robot pose imitation task for our experiments.
+Given a real robot input of target pose, the robot control its joints to replicate that target pose.
+We measure the angular error between the replicated and target poses as our evaluation metric:$\sqrt{\sum_{j} (\hat{a}_j - a_j)^2}$,
+where $\hat{a}_j$ and $a_j$ are replicated and target joint angle respectively, and $j$ is the joint index. We use an xArm robot which has 7 joints.
+
+\paragraph{Robot policy and Baselines}
+Since sim2real provides abundant training data using the simulator, we use behavior cloning which is enough to train a good robot policy.
+The policy is implemented by CNN~\cite{dqn}.
+We compare TRITON against two baseline image translation methods: CycleGAN and CUT, by replacing TRITON with each baseline method respectively in the above pipeline.
+The robot policy is the same for all methods.
+
+\paragraph{Evaluation Settings} We introduce two main evaluation settings, \textbf{Seen} and \textbf{Unseen}.
+In \textbf{Seen} setting, the policy is trained and tested using the same camera viewpoint that is used in training image translator.
+Whereas in \textbf{Unseen} setting, we introduce a camera at a new viewpoint for training and testing the policy.
+That is, the image translator has to generate the fake photos out of its training distribution (seen camera viewpoints), which becomes a challenging for the translator.
+We also vary input image resolution to show the power of photorealistic images in higher resolutions.
+
+\begin{figure}[tbhp]
+    \centering
+    \includegraphics[width=\textwidth]{images/sim2real_res.pdf}
+    \vspace{-20pt}
+    \caption{Evaluation results of sim2real robot learning.
+We compare TRITON against two baselines and one TRITON variant w/o $\ell_{UC}$ across 3 different input image resolutions.
+TRITON outperforms CycleGAN~\cite{} and CUT~\cite{} consistently across (a) all resolutions and (b) Unseen viewpoints.
+Results in (a) are from Seen setting.
+Results in (b) are from 336x336 resolution.
+}
+    \label{fig:sim2real}
+\end{figure}
+
+\paragraph{Results}
+In Figure~\ref{fig:sim2real} we show the evaluation results of sim2real transfer.
+Both evaluations show that TRITON outperforms CycleGAN and CUT consistently.
+In Figure~\ref{fig:sim2real}(a), we find that TRITON continuously improves from low to high resolutions due to generating photorealistic images.
+This is because in low resolution (eg.
+$84\times 84$) the details in images are not important, whereas in high resolution ($336\times 336$), artifacts from imperfect translator are clear and harm the policy learning.
+From Figure~\ref{fig:sim2real}(b), TRITON outperforms the others in Unseen setting, showing the power of xxxxxx.
+In the comparison against TRITON w/o $\ell_{UC}$, TRITON outperforms this variant consistently except the lowest resolution.
+This again shows the effectiveness of $\ell_{UC}$ to generate photorealistic images, and such high quality images are important in higher resolutions for sim2real transfer.
+
 %===============================================================================
@@
 		$L_{TR_{l2}} = \frac{
-			\sum\limits_{i=1}^B {
+			\lsum_{i=1}^B {
 			%  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}
@@
 		\frac{
-			\sum\limits_{i=1}^B {
+			\lsum_{i=1}^B {
 				%  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}

### 2022-06-15 CORL/example.tex
4.4 figure update

@@
 \begin{table}[H]
-
+    \caption{Ground truth comparison evaluations for TRITON. Masked and Unmasked mean xxxxxx. Sync and Unsync mean xxxxx. L2 is xxxx LPIPS is xxxxxx. TRITON is xxxxxxx. }
+	\resizebox{\textwidth}{!}{
         \begin{tabular}{l|llllllll}
@@
                                       & \multicolumn{4}{c|}{Masked}                                                                                                     & \multicolumn{4}{c}{Unmasked}                                                                                                \\
-		& \multicolumn{2}{c|}{L2}                                 & \multicolumn{2}{c|}{LPIPS}                              & \multicolumn{2}{c|}{L2}                                 & \multicolumn{2}{c}{LPIPS}                              \\
+                                      & \multicolumn{2}{c|}{LPIPS}                                    & \multicolumn{2}{c|}{L2}                                         & \multicolumn{2}{c|}{LPIPS}                                  & \multicolumn{2}{c}{L2}                                        \\
         Algorithm                     & \multicolumn{1}{c|}{Sync}     & \multicolumn{1}{c|}{Unsync}   & \multicolumn{1}{c|}{Sync}      & \multicolumn{1}{c|}{Unsync}    & \multicolumn{1}{c|}{Sync}    & \multicolumn{1}{c|}{Unsync}  & \multicolumn{1}{c|}{Sync}     & \multicolumn{1}{c}{Unsync}    \\ \hline
-		\textbf{TRITON w/o $\psi, \lUC, \lTR$} & 0.0437                    & 0.0373                      & 0.00500                   & 0.00490                     & 0.434                     & 0.402                       & 0.0425                    & 0.0392                     \\
-		\textbf{TRITON w/o $\lUC, \lTR$}       & 0.0442                    & 0.0386                      & 0.00586                   & 0.00589                     & 0.285                     & 0.255                       & 0.0364                    & 0.0310                     \\
-		\textbf{TRITON}                        & 0.0286                    & 0.0267                      & 0.00479                   & 0.00478                     & 0.117                     & 0.1157                      & 0.0123                    & 0.0122                     \\
-		\textbf{CycleGAN}                      &                           &                             &                           &                             &                           &                             &                           &                            \\
-		\textbf{CUT}                           &                           &                             &                           &                             &                           &                             &                           &
+        TRITON w/o $\psi, \lUC, \lTR$ & 0.0437                        & 0.0373                        & 0.00500                        & 0.00490                        & 0.434                        & 0.402                        & 0.0425                        & 0.0392                        \\
+        TRITON w/o $\lUC, \lTR$       & 0.0442                        & 0.0386                        & 0.00586                        & 0.00589                        & 0.285                        & 0.255                        & 0.0364                        & 0.0310                        \\
+        TRITON                        & \textbf{0.0286}               & \textbf{0.0267}               & \textbf{0.00479}               & \textbf{0.00478}               & \textbf{0.117}               & \textbf{0.1157}              & \textbf{0.0123}               & \textbf{0.0122}               \\
+        CycleGAN                      & {\color[HTML]{000000} 0.0450} & {\color[HTML]{000000} 0.0379} & {\color[HTML]{000000} 0.00559} & {\color[HTML]{000000} 0.00554} & {\color[HTML]{000000} 0.602} & {\color[HTML]{000000} 0.593} & {\color[HTML]{000000} 0.0425} & {\color[HTML]{000000} 0.0423} \\
+        CUT                           & 0.0469                        & 0.0382                        & 0.00553                        & 0.00526                        & 0.540                        & 0.534                        & 0.0637                        & 0.0629
         \end{tabular}
+	}
 \end{table}
@@
 \subsection{Sim2real Transfer for Robot Learning}
+\begin{figure}[thbp]
+    \centering
+    \vspace{-10pt}
+    \includegraphics[width=\textwidth]{images/sim2real_framework.pdf}
+    \vspace{-20pt}
+    \caption{Sim2real framework of using TRITON. }
+    \label{fig:sim2realframework}
+\end{figure}
 In this section we demonstrate how TRITON improves sim2real transfer for robot learning.
@@
 \paragraph{Task} We use a robot pose imitation task for our experiments.
-Given a real robot input of target pose, the robot control its joints to replicate that target pose.
+Given the input of a photo of real robot pose, the policy outputs robot controls to replicate that target pose.
 We measure the angular error between the replicated and target poses as our evaluation metric:$\sqrt{\sum_{j} (\hat{a}_j - a_j)^2}$,
@@
 Both evaluations show that TRITON outperforms CycleGAN and CUT consistently.
-In Figure~\ref{fig:sim2real}(a), we find that TRITON continuously improves from low to high resolutions due to generating photorealistic images.
+In Figure~\ref{fig:sim2real}(a), we find that TRITON continuously improves from low to high resolutions due to the ability to generate more photorealistic images compared to the baselines.
 This is because in low resolution (eg.
-$84\times 84$) the details in images are not important, whereas in high resolution ($336\times 336$), artifacts from imperfect translator are clear and harm the policy learning.
+$84\times 84$) the details in images are not important, whereas in high resolution ($336\times 336$), artifacts from imperfect translator are clearer and do harm to policy learning.
 From Figure~\ref{fig:sim2real}(b), TRITON outperforms the others in Unseen setting, showing the power of xxxxxx.

### 2022-06-15 CORL/example.tex
Changed table 1

@@
 	\resizebox{\textwidth}{!}{
-        \begin{tabular}{l|llllllll}
-                                      & \multicolumn{8}{c}{Three Block Dataset}                                                                                                                                                                                                                       \\
-                                      & \multicolumn{4}{c|}{Masked}                                                                                                     & \multicolumn{4}{c}{Unmasked}                                                                                                \\
-                                      & \multicolumn{2}{c|}{LPIPS}                                    & \multicolumn{2}{c|}{L2}                                         & \multicolumn{2}{c|}{LPIPS}                                  & \multicolumn{2}{c}{L2}                                        \\
-        Algorithm                     & \multicolumn{1}{c|}{Sync}     & \multicolumn{1}{c|}{Unsync}   & \multicolumn{1}{c|}{Sync}      & \multicolumn{1}{c|}{Unsync}    & \multicolumn{1}{c|}{Sync}    & \multicolumn{1}{c|}{Unsync}  & \multicolumn{1}{c|}{Sync}     & \multicolumn{1}{c}{Unsync}    \\ \hline
+        \begin{tabular}{lllllllll}
+        \toprule
+        & \multicolumn{4}{c}{Masked} & \multicolumn{4}{c}{Unmasked}  \\
+        \cmidrule(lr){2-5} \cmidrule(lr){6-9} & \multicolumn{2}{c}{LPIPS $\downarrow$} & \multicolumn{2}{c}{L2 $\downarrow$}  & \multicolumn{2}{c}{LPIPS $\downarrow$}  & \multicolumn{2}{c}{L2 $\downarrow$}   \\
+        \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
+        Algorithm  & Sync    & Unsync   & Sync      & Unsync    & Sync   & Unsync  & Sync     & Unsync \\
+        \midrule
         TRITON w/o $\psi, \lUC, \lTR$ & 0.0437                        & 0.0373                        & 0.00500                        & 0.00490                        & 0.434                        & 0.402                        & 0.0425                        & 0.0392                        \\
         TRITON w/o $\lUC, \lTR$       & 0.0442                        & 0.0386                        & 0.00586                        & 0.00589                        & 0.285                        & 0.255                        & 0.0364                        & 0.0310                        \\
-        TRITON                        & \textbf{0.0286}               & \textbf{0.0267}               & \textbf{0.00479}               & \textbf{0.00478}               & \textbf{0.117}               & \textbf{0.1157}              & \textbf{0.0123}               & \textbf{0.0122}               \\
+        \textbf{TRITON}                        & \textbf{0.0286}               & \textbf{0.0267}               & \textbf{0.00479}               & \textbf{0.00478}               & \textbf{0.117}               & \textbf{0.1157}              & \textbf{0.0123}               & \textbf{0.0122}               \\
+        \midrule
         CycleGAN                      & {\color[HTML]{000000} 0.0450} & {\color[HTML]{000000} 0.0379} & {\color[HTML]{000000} 0.00559} & {\color[HTML]{000000} 0.00554} & {\color[HTML]{000000} 0.602} & {\color[HTML]{000000} 0.593} & {\color[HTML]{000000} 0.0425} & {\color[HTML]{000000} 0.0423} \\
-        CUT                           & 0.0469                        & 0.0382                        & 0.00553                        & 0.00526                        & 0.540                        & 0.534                        & 0.0637                        & 0.0629
+        CUT                           & 0.0469                        & 0.0382                        & 0.00553                        & 0.00526                        & 0.540                        & 0.534                        & 0.0637                        & 0.0629\\
+        \bottomrule
         \end{tabular}
@@
     \vspace{-20pt}
-    \caption{Sim2real framework of using TRITON. }
+    \caption{Sim2real framework of using TRITON.
+We evaluate in two settings: Seen and Unseen.
+In Unseen, we use a new camera viewpoint to train and evaluate the policy.
+This new viewpoint is not used for training TRITON.
+}
     \label{fig:sim2realframework}

### 2022-06-15 CORL/example.tex
Updates from Overleaf

@@
 	% Abstracts should be a single paragraph, between 4--6 sentences long, ideally. Gross violations will trigger corrections at the camera-ready phase.
-
 	% Because of the 6 sentence limit, I've commented out some of the sentences...
-
 	Unpaired image translation algorithms can be used for sim-to-real tasks, but most fail to generate temporally consistent results.
@@
 	Our experiments show that in addition to achieving higher temporal consistency, the translations are closer to ground truth photographs than previous techniques.
-
 \end{abstract}
-
-% Two or three meaningful keywords should be added here
 \keywords{sim to real, image translation, differentiable rendering}
@@
 %===============================================================================
-
 \section{Introduction}
-
 Problem: 
@@
 \label{sec:data}
-
 	\begin{figure}[H]
+	\vspace{-10pt}
 		\begin{center}
@@
 		\end{center}
+		\vspace{-5pt}
 		\caption{
@@
 	\end{figure}
-
 	% TRITON stands for Texture Recovering Image Translation Network. It has two goals: to translate images, and to recover textures.
@@
 % 		I: \left\{\frac{1}{L},\frac{2}{L},\dots \frac{L}{L}\right\} \rightarrow \left\{1,2,\dots L\right\}  \eqand  I(l)=l\cdot L
-	\end{equation}
+% 	\end{equation}
 	However, this mapping can be changed arbitrarily if its more convenient to do so for a given dataset.
@@
 % %===============================================================================
-\section{Method}
-\label{sec:method}
-
-	\begin{figure}[H]
+\section{Method} \label{sec:method}
+	\begin{figure}[thbp]
+	    \vspace{-20pt}
 		\begin{center}
@@
 			% \includegraphics[width=400pt]{../images/main_diagram_condensed_with_domains.pdf}
-			\includegraphics[width=400pt]{../images/main_diagram_beautiful.pdf}
+			\includegraphics[width=\textwidth]{../images/main_diagram_beautiful.pdf}
 		\end{center}
+		\vspace{-10pt}
 		\caption{
@@
 	\subsection{Neural Neural Texture Projection}
-
-		\begin{figure}[H]
+		\begin{figure}[thbp]
+		    \vspace{-5pt}
 			\begin{center}
@@
 		% where $n\in \{1\dots N\},\ \ c\in \{1\dots 3\} ,\ x\in \{1\dots W\},\ y\in \{1\dots H\},\ \ \text{and} \ \ i=I(s_{n,3,x,y})$.
-		where channel $c\in \{1, 2, 3\} ,\ x\in \{1\dots W\},\ y\in \{1\dots H\},\ \ \text{and texture index} \ \ i=I(l) ~\text{where}~ l=s_{[x,y,3]}$ and subscript means multidimensional indexing.
+		where $ x\in \{1\dots W\},\ y\in \{1\dots H\}$, and texture index $i=I(l)$ where $l=s_{[x,y,3]}$ and subscript means multidimensional indexing.
 
@@
 
-		\begin{figure}[H]
+		\begin{figure}[thbp]
+		    \vspace{-10pt}
 			\begin{center}
@@
 			\end{center}
+			\vspace{-5pt}
 			\caption{
@@
 		\begin{equation}
-			\unprojection_{c,U,V}^{n,i}=\expectation\ph_{c,x,y}^n 
-			\eqand \bar{\unprojection}^i_{c,u,v}   =   
-				\frac{1}{N} \lsum_n\unprojection^{n,i}_{c,u,v} 
+			\unprojection_{U,V}^{n,i}=\expectation\ph_{x,y}^n 
+			\eqand \bar{\unprojection}^i_{u,v}   =   
+				\frac{1}{N} \lsum_n\unprojection^{n,i}_{u,v} 
 			\eqand 
-			\lUC=\frac{\lsum_{i,c,U,V}
-			\sqrt[]{\frac{1}{N}\lsum_n\left(\bar{\unprojection}^i_{c,u,v}-\unprojection^{i,n}_{c,U,V}\right)^2}}
-			{3\cdot128\cdot128\cdot L}
+			%\lUC=\frac{\lsum_{i,U,V}
+			%\sqrt[]{\frac{1}{N}\lsum_n\left(\bar{\unprojection}^i_{u,v}-\unprojection^{i,n}_{U,V}\right)^2}}
+			%{128\cdot128\cdot L}
+			\lUC=\mathbb{E}\left[
+			\sqrt[]{\frac{1}{N}\lsum_n\left(\bar{\unprojection}^i_{u,v}-\unprojection^{i,n}_{U,V}\right)^2} \right]
 		\end{equation}
@@
 		$i \in \{1...L\}$ , 
-		$c \in \{1,2,3}$ , 
 		$x \in \{1...W\}$ , 
@@
 	\label{sec:texture_realism_loss}
-
-		\begin{figure}[H]
+        \vspace{-10pt}
+		\begin{figure}[thbp]
 			\begin{center}
@@
 
-\section{Results}
+\section{Results}\label{sec:results}
 
 \subsection{Data}
-
 Here I detail the datasets used in the results section. 
@@
 
-\label{sec:results}
-
 \subsection{Qualitative Differences}
 \begin{figure}[H]
+    \vspace{-30pt}
 	\begin{center}
-		\includegraphics[width=400pt]{../images/frame_inconsistency_diagram.pdf}
+		\includegraphics[width=\textwidth]{../images/frame_inconsistency_diagram.pdf}
 	\end{center}
-
 	% Each outline color corresponds to the same cube.
@@
 	% For the same cube, we expect to see the same number on the top of the cube regardless of its placement.
-
 	\caption{
@@
 We measure the angular error between the replicated and target poses as our evaluation metric:$\sqrt{\sum_{j} (\hat{a}_j - a_j)^2}$,
-where $\hat{a}_j$ and $a_j$ are replicated and target joint angle respectively, and $j$ is the joint index. We use an xArm robot which has 7 joints.
+where $\hat{a}_j$ and $a_j$ are replicated and target joint angle respectively, and $j$ is the joint index.
+We use an xArm robot which has 7 joints.
+Moreover, we attach patterns and tapes on it to make its texture complex.
 

### 2022-06-16 CORL/example.tex
minor things

@@
 		\begin{figure}[thbp]
-		    \vspace{-5pt}
+		    \vspace{-15pt}
 			\begin{center}
@@
 			\end{center}
+			\vspace{-3pt}
 			\caption{
-				This figure illustrates how the neural textures are calculated in figure \ref{fig:main_diagram}.
-They are fully differentiable, and represented continuously along the texture's U and V axes using fourier feature networks.
-			}
+				This figure illustrates how the our neural neural textures are calculated in figure \ref{fig:main_diagram}.
+They are fully differentiable, and represented continuously along the texture's U and V axes using Fourier feature networks.
+			}
+			\vspace{-10pt}
 			% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
@@
 	\label{sec:texture_realism_loss}
-        \vspace{-10pt}
+        \vspace{-12pt}
 		\begin{figure}[thbp]
@@
 			}
+			\vspace{-10pt}
 			\label{fig:texture_realism_ablation}
@@
 
-\section{Results}\label{sec:results}
-
-\subsection{Data}
-Here I detail the datasets used in the results section. 
-Every dataset has two sets of images: UVL scenes and photographs. They are all unpaired, and have RGB values ranging from 0 to 1.
+\section{Experiments}\label{sec:results}
+
+\subsection{Datasets}
+Here we detail the datasets used in our experiments. 
+Every dataset has two sets of images: UVL scenes and real photographs. They are all unpaired, and have RGB values ranging from 0 to 1.
 
@@
 
-\subsection{Qualitative Differences}
-\begin{figure}[H]
+\subsection{Qualitative Evaluation Results}
+\begin{figure}[thbp]
     \vspace{-30pt}
@@
 
-	\begin{figure}[H]
+    \begin{figure}[thbp]
     	\begin{center}
-			\includegraphics[width=400pt]{../images/blurry_recovery.pdf}
+    		\includegraphics[width=\textwidth]{../images/blurry_recovery.pdf}
     	\end{center}
@@
 }
+    \vspace{-5pt}
     \label{fig:sim2realframework}
@@
     \centering
+    \vspace{-8pt}
     \includegraphics[width=\textwidth]{images/sim2real_res.pdf}
@@
     \label{fig:sim2real}
+    \vspace{-8pt}
 \end{figure}

### 2022-06-16 CORL/example.tex
updated table 1

@@
 	\resizebox{\textwidth}{!}{
-        \begin{tabular}{lllllllll}
+        \begin{tabular}{lcccccccc}
         \toprule
         & \multicolumn{4}{c}{Masked} & \multicolumn{4}{c}{Unmasked}  \\
-        \cmidrule(lr){2-5} \cmidrule(lr){6-9} & \multicolumn{2}{c}{LPIPS $\downarrow$} & \multicolumn{2}{c}{L2 $\downarrow$}  & \multicolumn{2}{c}{LPIPS $\downarrow$}  & \multicolumn{2}{c}{L2 $\downarrow$}   \\
+        \cmidrule(lr){2-5} \cmidrule(lr){6-9} & \multicolumn{2}{c}{LPIPS ($\times 10^{-1}$) $\downarrow$} & \multicolumn{2}{c}{L2 ($\times 10^{-2}$) $\downarrow$}  & \multicolumn{2}{c}{LPIPS ($\times 10^{-1}$) $\downarrow$}  & \multicolumn{2}{c}{L2 ($\times 10^{-2}$) $\downarrow$}   \\
         \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
@@
         \midrule
-        TRITON w/o $\psi, \lUC, \lTR$ & 0.0437                        & 0.0373                        & 0.00500                        & 0.00490                        & 0.434                        & 0.402                        & 0.0425                        & 0.0392                        \\
-        TRITON w/o $\lUC, \lTR$       & 0.0442                        & 0.0386                        & 0.00586                        & 0.00589                        & 0.285                        & 0.255                        & 0.0364                        & 0.0310                        \\
-        \textbf{TRITON}                        & \textbf{0.0286}               & \textbf{0.0267}               & \textbf{0.00479}               & \textbf{0.00478}               & \textbf{0.117}               & \textbf{0.1157}              & \textbf{0.0123}               & \textbf{0.0122}               \\
+        TRITON w/o $\psi, \lUC, \lTR$ & 0.437                        & 0.373                        & 0.500                        & 0.490                        & 4.34                        & 4.02                        & 4.25                        & 3.92                        \\
+        TRITON w/o $\lUC, \lTR$       & 0.442                        & 0.386                        & 0.586                        & 0.589                        & 2.85                        & 2.55                        & 3.64                        & 3.10                        \\
+        \textbf{TRITON}                        & \textbf{0.286}               & \textbf{0.267}               & \textbf{0.479}               & \textbf{0.478}               & \textbf{1.17}               & \textbf{1.16}              & \textbf{1.23}               & \textbf{1.22}               \\
         \midrule
-        CycleGAN                      & {\color[HTML]{000000} 0.0450} & {\color[HTML]{000000} 0.0379} & {\color[HTML]{000000} 0.00559} & {\color[HTML]{000000} 0.00554} & {\color[HTML]{000000} 0.602} & {\color[HTML]{000000} 0.593} & {\color[HTML]{000000} 0.0425} & {\color[HTML]{000000} 0.0423} \\
-        CUT                           & 0.0469                        & 0.0382                        & 0.00553                        & 0.00526                        & 0.540                        & 0.534                        & 0.0637                        & 0.0629\\
+        CycleGAN & 0.450 & 0.379 &  0.559 &  0.554 &  6.02 &  5.93 &  4.25 &  4.23 \\
+        CUT                           & 0.469                        & 0.382                        & 0.553                        & 0.526                        & 5.40                        & 5.34                        & 6.37                        & 6.29\\
         \bottomrule

### 2022-06-16 CORL/example.tex

@@
 	By settling on a particular albedo for the objects in a scene, we ensure consistency between frames statelessly.
-	Unlike previous algorithms, TRITON is not limited to camera movements - it can handle the movement of objects as well, making it useful for downstream tasks such as robotic manipulation.
+	Unlike previous algorithms, TRITON is not limited to camera movements --- it can handle the movement of objects as well, making it useful for downstream tasks such as robotic manipulation.
 	Our experiments show that in addition to achieving higher temporal consistency, the translations are closer to ground truth photographs than previous techniques.
@@
 \label{sec:data}
-	\begin{figure}[H]
+	\begin{figure}[thbp]
 	\vspace{-10pt}
 		\begin{center}
-			\includegraphics[width=400pt]{../images/first_diagram.pdf}
+			\includegraphics[width=\textwidth]{../images/first_diagram.pdf}
 		\end{center}
@@
 
-		To keep the object surfaces consistent between a batch of $N$ outputs, we impose a pixel-wise ``unprojection consistency loss'' between these surfaces by unprojecting them back into a common texture space.
+		To keep the object surfaces consistent, we impose a pixel-wise ``unprojection consistency loss'' by unprojecting surfaces in fake photos back into the common texture space.
+% 		\begin{equation}
+% 			u\toNL=\text{unproject}(\ph\toN,s\toN)   \eqand  \lUC \Rightarrow u_1 \approx u_2 \dots \approx u_N
+% 		\end{equation}
+        Given a UVL scene $s$ and its respective fake photo $\ph$, the unprojection $\unprojection$ is obtained from assigning $(r,g,b)$ values at each pixel location $(x, y)$ of $\ph$ to its corresponding $(u, v, l)$ coordinates according to $s$.
+        % That is, we convert $s$ and $\ph$ to a key-value dictionary where the key is $(u,v,l)$ and the value is $(r,g,b)$, and such dictionary is $\unprojection$.
+        For simplicity, we note
         \begin{equation}
-			u\toNL=\text{unproject}(\ph\toN,s\toN)   \eqand  \lUC \Rightarrow u_1 \approx u_2 \dots \approx u_N
+            	\unprojection_{[u,v]}^{l}=\expectation\ph_{[x,y]} \quad s.t.~ (u,v,l) = s_{[x,y]},
         \end{equation}
-
-		We sample a random batch of UVL scenes $S\toN$, and translate them into $\ph\toN$.
-		Using geometric knowledge of the scene encoded in $S\toN$, we individually unproject each $\ph^i \in \ph\toN$ back into texture space, to obtain $N$ sets of $L$ unprojected textures $u\toNL$.
-		We then use the per-pixel, batch-wise standard deviation of the unprojections as unprojection consistency loss $\lUC = \sigma(u\toNL)\toL$.
-		This loss observes how different these unprojections are from one another, and thus how different the object surfaces appear between translations.
+        where the expectation $\mathbb{E}$ means we aggregate multiple $(r,g,b)$ vectors being assigned to the same $(u,v,l)$ location by averaging them. 
+        In practice, $(u,v,l)$ are real numbers between $[0,1]$, where as each $\unprojection$ have to be rasterized, i.e represented by $L$ $(128\times 128\times 3)$ images, where $L$ is the number of labels and $128\times 128$ is the resolution of the unprojection.
+Therefore, we discretize and scale corresponding $(u,v,l)$ to integers so that each $(r,g,b)$ vector will be assigned to a pixel on $\unprojection$.
+For the exact implementation, please see our supplementary material.
+
+        We obtain $N$ unprojections $\{\unprojection_{[u,v]}^{l,i}\}_{i=1}^{N}$ from a batch of $N$ UVL scenes and fake photos. The unprojection consistency loss is defined as the per-pixel
+        \begin{equation}
+
+        \end{equation}
+
+		%We sample a random batch of UVL scenes $S\toN$, and translate them into $\ph\toN$.
+		%Using geometric knowledge of the scene encoded in $S\toN$, we individually unproject each $\ph^i \in \ph\toN$ back into texture space, to obtain $N$ sets of $L$ unprojected textures $u\toNL$.
+		%We then use the per-pixel, batch-wise standard deviation of the unprojections as unprojection consistency loss $\lUC = \sigma(u\toNL)\toL$.
+		%This loss observes how different these unprojections are from one another, and thus how different the object surfaces appear between translations.
 
@@
 		%Abbreviated
-		To formally define $\lUC$ we define unprojections $\unprojection^{1...N,1...L}$ and mean unprojections (aka recovered textures) $\bar{\unprojection}^{1...L}$ 
-		with each $\unprojection^{n,i}\in\real^{3\times128\times128}$:
-		\begin{equation}
-			\unprojection_{U,V}^{n,i}=\expectation\ph_{x,y}^n 
-			\eqand \bar{\unprojection}^i_{u,v}   =   
-				\frac{1}{N} \lsum_n\unprojection^{n,i}_{u,v} 
-			\eqand 
-			%\lUC=\frac{\lsum_{i,U,V}
-			%\sqrt[]{\frac{1}{N}\lsum_n\left(\bar{\unprojection}^i_{u,v}-\unprojection^{i,n}_{U,V}\right)^2}}
-			%{128\cdot128\cdot L}
-			\lUC=\mathbb{E}\left[
-			\sqrt[]{\frac{1}{N}\lsum_n\left(\bar{\unprojection}^i_{u,v}-\unprojection^{i,n}_{U,V}\right)^2} \right]
-		\end{equation}
-		where $U=\lfloor128u\rfloor$ and $V=\lfloor128v\rfloor$ and $i=I(l)$ with
-		%  $(u,v,l)=s^n_{1...3,x,y}$
-		$u=s^n_{1,x,y}$, $v=s^n_{2,x,y}$, $l=s^n_{3,x,y}$
-		for all 
-		$n \in \{1...N\}$ , 
-		$i \in \{1...L\}$ , 
-		$x \in \{1...W\}$ , 
-		$y \in \{1...H\}$ , 
-		$U \in \{1...128\}$ , 
-		$V \in \{1...128\}$.
+		%To formally define $\lUC$ we define unprojections $\unprojection^{1...N,1...L}$ and mean unprojections (aka recovered textures) $\bar{\unprojection}^{1...L}$ 
+		%with each $\unprojection^{n,i}\in\real^{3\times128\times128}$:
+% 		\begin{equation}
+% 			\unprojection_{U,V}^{n,i}=\expectation\ph_{x,y}^n 
+% 			\eqand \bar{\unprojection}^i_{u,v}   =   
+% 				\frac{1}{N} \lsum_n\unprojection^{n,i}_{u,v} 
+% 			\eqand 
+% 			%\lUC=\frac{\lsum_{i,U,V}
+% 			%\sqrt[]{\frac{1}{N}\lsum_n\left(\bar{\unprojection}^i_{u,v}-\unprojection^{i,n}_{U,V}\right)^2}}
+% 			%{128\cdot128\cdot L}
+% 			\lUC=\mathbb{E}\left[
+% 			\sqrt[]{\frac{1}{N}\lsum_n\left(\bar{\unprojection}^i_{u,v}-\unprojection^{i,n}_{U,V}\right)^2} \right]
+% 		\end{equation}
+% 		where $U=\lfloor128u\rfloor$ and $V=\lfloor128v\rfloor$ and $i=I(l)$ with
+% 		%  $(u,v,l)=s^n_{1...3,x,y}$
+% 		$u=s^n_{1,x,y}$, $v=s^n_{2,x,y}$, $l=s^n_{3,x,y}$
+% 		for all 
+% 		$n \in \{1...N\}$ , 
+% 		$i \in \{1...L\}$ , 
+% 		$x \in \{1...W\}$ , 
+% 		$y \in \{1...H\}$ , 
+% 		$U \in \{1...128\}$ , 
+% 		$V \in \{1...128\}$.
 
@@
 	\label{sec:texture_realism_loss}
-        \vspace{-12pt}
+        \vspace{-7pt}
 		\begin{figure}[thbp]
@@
 \subsection{Qualitative Evaluation Results}
+We show qualitative evaluation results 
 \begin{figure}[thbp]
@@
 	%CREATED WITH https://www.tablesgenerator.com/# -- this website is wonderful!!
-\begin{table}[H]
+\begin{table}[thbp]
     \caption{Ground truth comparison evaluations for TRITON. Masked and Unmasked mean xxxxxx. Sync and Unsync mean xxxxx. L2 is xxxx LPIPS is xxxxxx. TRITON is xxxxxxx. }

### 2022-06-16 CORL/example.tex
Why wont it push images

@@
         where the expectation $\mathbb{E}$ means we aggregate multiple $(r,g,b)$ vectors being assigned to the same $(u,v,l)$ location by averaging them. 
-        In practice, $(u,v,l)$ are real numbers between $[0,1]$, where as each $\unprojection$ have to be rasterized, i.e represented by $L$ $(128\times 128\times 3)$ images, where $L$ is the number of labels and $128\times 128$ is the resolution of the unprojection.
+        In practice, $(u,v,l)$ are real numbers between $[0,1]$, where as each $\unprojection$ have to be rasterized, i.e represented by $L$ $(D\times D\times 3)$ images, where $L$ is the number of labels and $D\times D$ is the resolution of the unprojection.
 Therefore, we discretize and scale corresponding $(u,v,l)$ to integers so that each $(r,g,b)$ vector will be assigned to a pixel on $\unprojection$.
@@
 
-        We obtain $N$ unprojections $\{\unprojection_{[u,v]}^{l,i}\}_{i=1}^{N}$ from a batch of $N$ UVL scenes and fake photos. The unprojection consistency loss is defined as the per-pixel
+        We obtain $N$ unprojections $\{\unprojection_{[u,v]}^{l,i}\}_{i=1}^{N}$ from a batch of $N$ UVL scenes and fake photos.
+The unprojection consistency loss is defined as the per pixel-channel standard deviation of $\unprojection$ over the batch
         \begin{equation}
-
+            \ell_{UC} = \frac{1}{L\times D\times D\times 3}\sum_{l,u,v,c}\sigma(\{\unprojection^{l,i}_{[u,v,c]}\}_{i=1}^{N}),
         \end{equation}
-
+        where $\sigma(\cdot)$ stands for the variance function and $c \in \{1\dots 3\}$ is the channel index of $\unprojection$.
 		%We sample a random batch of UVL scenes $S\toN$, and translate them into $\ph\toN$.
@@
 		%This loss observes how different these unprojections are from one another, and thus how different the object surfaces appear between translations. 
-
+		We minimize $\lUC$ to encourage unprojections to be consistent across the batch.
 Intuitively, if $\lUC$ were $0$, it would mean the object surfaces in translations $\ph$ appear exactly the same in every scene.
+In addition, we call the mean of unprojections $\mu(\{\unprojection^{(l,i)}\}_{i=1}^N)$ as ``Recovered Textures'', visualzed in Figure~\ref{fig:first_diagram} and \ref{fig:unprojection_consistency_loss}.
 

### 2022-06-18 CORL/example.tex
Submitted Paper

@@
 
+\addtolength{\floatsep}{-2mm}
+\addtolength{\textfloatsep}{-1mm}
+\addtolength{\intextsep}{-1mm}
+\renewcommand{\baselinestretch}{0.99}
+
 \documentclass{article}
@@
 \usepackage{array, booktabs, ragged2e}
+\usepackage{comment}
 
@@
 % \title{TRITON: Globally Consistent Sim-to-Real Transfer
-\title{Neural Neural Textures Make Better Simulators
-
-``I Can't Believe It's Not Real!''%Definitely gonna delete this lol
+\title{\mbox{TRITON: Neural Neural Textures for Better Sim2Real}
+%``I Can't Believe It's Not Real!''%Definitely gonna delete this lol
 %via Neural Textures
@@
 \begin{abstract}
-	% Abstracts should be a single paragraph, between 4--6 sentences long, ideally. Gross violations will trigger corrections at the camera-ready phase.
-	% Because of the 6 sentence limit, I've commented out some of the sentences...
-	Unpaired image translation algorithms can be used for sim-to-real tasks, but most fail to generate temporally consistent results.
-	% Because of this, the details or even identity of a particular object might change as it moves across a scene.
-	We present a new approach that combines differential rendering with image translation to achieve temporal consistency over indefinite timescales.
-%
-	%TURNING TWO SENTENCES INTO ONE:
-	% We call this algorithm TRITON (Texture Recovering Image Translation Network): an unsupervised, end-to-end, stateless sim-to-real algorithm.
-	% Unlike previous techniques, TRITON leverages the underlying 3d geometry of input scenes by generating realistic-looking learnable neural textures.
-	We call this algorithm TRITON (Texture Recovering Image Translation Network): an unsupervised, end-to-end, stateless sim-to-real algorithm that 
+	%Current sim-to-real image translation algorithms do not generate consistent results across large timeframes when the objects in an environment are allowed to move, making it difficult to train good robotic policies using them.
+	%To address this problem, we introduce a new algorithm called TRITON (Texture Recovering Image Translation Network): an unsupervised end-to-end image translation algorithm that combines neural rendering with image translation to maintain temporal consistency over arbitrarily long timeframes.
+	%Unlike previous sim-to-real image translation algoithms, TRITON leverages the underlying 3d structure of the simulated images to learn realistic textures on the surfaces of objects.
+	%We introduce a new type of nerual texture called a ``neural neural texture'', as well as separate losses each of which are capable of accomplishing this consistency goal.
+% 	As far as we are aware, this is the first algorihtm to attempt to learn the albedo of dynamically moving 3d objects without supervision.
+	%We demonstrate the supeiority of our approach both qualitatively and quantitatively, using robotic experiments and comparisons to ground truth photographs.
+We show that TRITON generates more realistic images than other algoithms do.
+	Unpaired image translation algorithms can be used for sim2real tasks, but most fail to generate temporally consistent results.
+	We present a new approach that combines differentiable rendering with image translation to achieve temporal consistency over indefinite timescales, using surface consistency losses and \emph{neural neural textures}.
+	We call this algorithm TRITON (Texture Recovering Image Translation Network): an unsupervised, end-to-end, stateless sim2real algorithm that 
 	leverages the underlying 3d geometry of input scenes by generating realistic-looking learnable neural textures.
-%
-	% These textures are projected onto the surfaces of input scenes, which are then fed through an image translation network to obtain the final outputs.
-	By settling on a particular albedo for the objects in a scene, we ensure consistency between frames statelessly.
+	By settling on a particular texture for the objects in a scene, we ensure consistency between frames statelessly.
 	Unlike previous algorithms, TRITON is not limited to camera movements --- it can handle the movement of objects as well, making it useful for downstream tasks such as robotic manipulation.
-	Our experiments show that in addition to achieving higher temporal consistency, the translations are closer to ground truth photographs than previous techniques.
+% 	Our experiments show that in addition to achieving higher temporal consistency, the translations are closer to ground truth photographs than previous techniques.
+		We demonstrate the superiority of our approach both qualitatively and quantitatively, using robotic experiments and comparisons to ground truth photographs.
+We show that TRITON generates more useful images than other algorithms do.
 \end{abstract}
-\keywords{sim to real, image translation, differentiable rendering}
+\keywords{sim2real, image translation, differentiable rendering}
 
@@
 \section{Introduction}
-Problem: 
-Why is this problem important?
-No view consistency.
-
-Introducing our intuition of what improvements can solve this problem.
-
-Our exact method - introducing our components and what we're doing
-
-Conclusion: This works well, and our contributions are x
-
-% I introduce you to TRITON. The rest of the introduction text goes here; I've commented out my old incomplete introduction.
-
-	% TODO: Note that the simple input of UVL, or an RGB neural texture, means any simulator should be plug-and-play with this algorithm.
-
-	% Recently, several sim-to-real algorithms have come out that are based on image-to-image translation. [Citations]
-	% These are used for training robots using pixel-based reinforcement learning.
-	% They demonstrated that better image translation algorithms yielded notable improvements in robotic benchmarks.
-	% At the same time, there is a lot of research on differentiable rendering,
-	% a topic which produced papers such as NERF which attempt to capture 3d representations of the real world.
-	% However, most of these approaches are either supervised or involve only camera movements [citations].
-	% One paper that came out recently combined both image translation and differentiable rendering in an unsupervised manner to create view-consistent models of human organs [citation].
-	% This paper too, though, was limited to only camera movements.
-
-	% This algorithm unlocks a new capability: learning textures to match photos for given 3d models without supervision.
-
-	% The motivation for this paper is to create a temporally consistent sim-to-real image translation algorithm that will look the same from multiple camera angles simultaneously, keeps all semantic details
-	% [[I'll finish this later... let's work on the meat of the paper first...]]
-
-%===============================================================================
-\section{Formulation}
-\label{sec:data}
+
+% INTRODUCE:
+%     Image Translation
+%         For Videos
+%     Differentiable Rendering
+%         Neural Textures
+%             They combine image translation
+%     Most similar to our work is blah
+
+Current sim2real image translation algorithms used for robotics \cite{retina_gan,rl_cyclegan} often have difficulty generating consistent results across large time-frames particularly when the objects in an environment are allowed to move.
+This makes training good robotic policies using such sim2real challenging.
+In this paper, we discuss an algorithm called TRITON (Texture Recovering Image Translation Network) that combines neural rendering, image translation, and two special surface consistency losses to create surface-consistent translations.
+We use the term surface-consistent to refer to the desirable quality of preserving the visual appearance of object surfaces as they move, or are viewed from another angles.
+
+TRITON is applicable when we have a simulator capable of generating a realistic distribution of geometric data, but when we do not have any information about the surfaces of those objects (which we need to render realistic images).
+For example, in our experiments we use a robotic arm model provided by the manufacturer that contains no material information, and then learn to render the materials of the arm using TRITON.
+As opposed to requiring an artist to create 3d models with meaningful textures, TRITON can generate these from scratch using a set of photographs capturing the distribution of states in a simulation, without requiring any matches between domains.
+% TRITON is robust to small camera variations, and can recover crisp textures even if the geometry isn't perfect.
+
+We conduct multiple experiments to confirm TRITON's advantage over prior image translation approaches commonly used for sim2real including CycleGAN~\cite{cyclegan} and CUT~\cite{cut}.
+%First, we train it on a dataset with alphabet blocks, then compare photographs in that dataset to TRITON outputs by manually aligning the simulated 3d cubes with the photographs.
+Important, we show the advantages of the proposed approach in real-robot sim2real experiments, learning the textures and training a robot policy solely based on the images generated by TRITON. 
+%We also perform a robotic experiment, where we learn a policy completely in a simulation, and then verify it in the real world.
+In both of these tests, TRITON outperforms other image translation algorithms.
+
 \begin{figure}[thbp]
@@
 		\label{fig:first_diagram}
+	\vspace{-5pt}
 	\end{figure}
+
+\vspace{-5pt}	
+\section{Related Works}
+\vspace{-3pt}
+\paragraph{Unsupervised Image to Image and Video to Video Translation}
+Generative models have been very successful in creating images unconditionally~\cite{gan,stylegan}, creating images conditioned on text~\cite{dalle,imagen} and creating images when trained on paired data~\cite{pixtopix}.
+Generative models that translate images between unpaired data is a challenging task as well, but has been done before~\cite{dual_diffusion,cyclegan,munit,unit}.
+Of particular interest are sim2real image to image translation algorithms such as~\cite{retina_gan,rl_cyclegan,surgical_image_translation,enhancing_photorealism_enhancement}.
+These algorithms aim to translate simulated images into realistic ones, for various purposes such as data augmentation or video game enhancement.
+In particular, \citet{retina_gan,rl_cyclegan} are used to help train robots.
+Our paper uses an architecture based on~\citet{surgical_image_translation}, which is based on MUNIT~\cite{munit}.
+This area of research has been extended to video to video translation, where optical flow is often used to create a stateful translation where temporal coherence is preserved~\cite{tecogan,mocyclegan}.
+These algorithms fail to provide temporal coherence over long time periods, however.
+Another work from~\citet{surgical_video_translation}, is closely related to ours and uses neural rendering to translate videos with temporal coherence even when the camera spins around all the way.
+
+\vspace{-8pt}
+\paragraph{View Synthesis}
+View synthesis is a field of research where we predict the outputs of unseen camera viewpoints.
+NeRF \cite{nerf} has spawned a large body of research on end to end view synthesis, resulting in works such as \cite{nerv,fast_nerf,barf}.
+Related to our work, which also uses geometry based backbone are \cite{free_view_synthesis,stable_view_synthesis,ners}.
+All of these works, however, only work with static scenes.
+There are NeRF-based approaches that work on dynamic scenes \cite{dnerf,nerfies,nerualradianceflow} but none of these interactive.
+\citet{playable_environments} is interactive, but its conditioned on learned actions and not compatible with physics simulators that would be used to train robots.
+
+\vspace{-8pt}
+\paragraph{Neural Textures}
+\citet{deferred_neural_rendering} introduced the concept of neural textures and image translators in the context of a deferred rendering pipeline, used in other works such as \cite{surgical_video_translation} which is closely related to our project.
+\citet{surgical_video_translation} differs from TRITON in a few very important aspects though, the biggest being that it only synthesizes new camera views, where the only difference between each scene is the placement of the camera.
+In contrast, our algorithm takes in scenes where several objects are placed in different places or deformed, so that one static  global 3d model of the environment is not sufficient to accomplish our tasks.
+In addition, TRITON uses a new type of neural texture called a ``neural neural texture'', which is represented continuously using a fourier feature network, as described in \citep{fourier_feature_networks}.
+
+% Problem: 
+% Why is this problem important?
+% No view consistency.
+
+% Introducing our intuition of what improvements can solve this problem.
+
+% Our exact method - introducing our components and what we're doing
+
+% Conclusion: This works well, and our contributions are x
+
+% I introduce you to TRITON. The rest of the introduction text goes here; I've commented out my old incomplete introduction.
+
+	% TODO: Note that the simple input of UVL, or an RGB neural texture, means any simulator should be plug-and-play with this algorithm.
+
+	% Recently, several sim-to-real algorithms have come out that are based on image-to-image translation. [Citations]
+	% These are used for training robots using pixel-based reinforcement learning.
+	% They demonstrated that better image translation algorithms yielded notable improvements in robotic benchmarks.
+	% At the same time, there is a lot of research on differentiable rendering,
+	% a topic which produced papers such as NERF which attempt to capture 3d representations of the real world.
+	% However, most of these approaches are either supervised or involve only camera movements [citations].
+	% One paper that came out recently combined both image translation and differentiable rendering in an unsupervised manner to create view-consistent models of human organs [citation].
+	% This paper too, though, was limited to only camera movements.
+
+	% This algorithm unlocks a new capability: learning textures to match photos for given 3d models without supervision.
+
+	% The motivation for this paper is to create a temporally consistent sim-to-real image translation algorithm that will look the same from multiple camera angles simultaneously, keeps all semantic details
+	% [[I'll finish this later... let's work on the meat of the paper first...]]
+
+%===============================================================================
+% \vspace{-5pt}
+\section{Formulation}
+\label{sec:data}
+\vspace{-3pt}
 	% TRITON stands for Texture Recovering Image Translation Network. It has two goals: to translate images, and to recover textures.
-
 	TRITON's goal is to turn 3d simulated images into realistic fake photographs (by training it without any matching pairs), while maintaining high surface consistency.
@@
 
-	In contrast to previous works involving `neural textures' \textbf{(mryoo: cite them here)}, TRITON can handle more than just camera movements:
+	In contrast to previous works involving ``neural textures'' \cite{deferred_neural_rendering,surgical_video_translation}, TRITON can handle more than just camera movements:
 	the positions of objects in the training data can be moved around or deformed as well between data samples.
-	For this reason, we chose the term ``surface consistency'' instead of ``view consistency'', which was the term used in [] \textbf{(mryoo: cite)}.
+% 	For this reason, we chose the term ``surface consistency'' instead of ``view consistency'', which was the term used in [] \textbf{(mryoo: cite)}.
 	With high surface consistency, surfaces of translated objects will look the same even when moved around or viewed from different camera angles.
@@
 	\begin{figure}[H]
+	    \vspace{-5pt}
 		\begin{center}
-			\includegraphics[width=400pt]{../images/uvl_explanation_minimal.pdf}
+			\includegraphics[width=.8\textwidth]{../images/uvl_explanation_minimal.pdf}
 		\end{center}
+		\vspace{-10pt}
 		\caption{
@@
 		\label{fig:uvl_explanation}
+		\vspace{-15pt}
 	\end{figure}
 
-	There are two components to every dataset: A set of simulated 3d scenes, and a set of photographs.
+	There are two components in every dataset: A set of simulated 3d scenes, and a set of photographs.
 	Datasets usually have many more scenes than photographs, since scenes can be generated automatically.
-
 	% The photographs, having $(r,g,b)$ values between 0 and 1,
@@
 	% 	and $H,W$ are the height and width respectively.
-
 	% A photograph in a set of photographs, having $(r,g,b)$ values between 0 and 1,
@@
 	% 	and $H,W$ are the height and width respectively.
-
 	A photograph is an image tensor, having $(r,g,b)$ values between 0 and 1,
-		is denoted as ${p \in [0,1]^{ 3 \times H \times W}}$ where 
+		is denoted as ${p \in [0,1]^{H \times W \times 3}}$ where 
 		3 refers to the three $(r,g,b)$ channels, 
@@
 	A scene has the same dimensions as a photograph and is denoted as 
-	$s \in [0,1]^{3 \times H \times W}$.
-	However, unlike $p$, $s$'s three $(r,g,b)$ channels encode a special semantic meaning: $(u,v,l)$ as depicted in figure \ref{fig:uvl_explanation}.
+	$s \in [0,1]^{H \times W \times 3}$.
+	However, unlike $p$, $s$'s three $(r,g,b)$ channels encode a special semantic meaning: $(u,v,l)$ as depicted in Figure \ref{fig:uvl_explanation}.
 	The channels $u$ and $v$ refer to a texture coordinate, whereas $l$ refers to a label value that identifies every object in a scene.
@@
 	We assume that every dataset has $L$ different label values, $L$ different objects, and that we must learn $L$ different neural textures.
-
-TODO: Say I scales and discretizes l, don't say more than that. 
+    % TODO: Say I scales and discretizes l, don't say more than that. 
 % 	In each dataset, we must also define a function $I(l)$ that maps label values to texture indices. A simple way to do this is with the following definition:
@@
 % 	\end{equation}
-	However, this mapping can be changed arbitrarily if its more convenient to do so for a given dataset.
-	Also please note that this paper uses 1-based indexing for notational simplicity.
+% 	However, this mapping can be changed arbitrarily if its more convenient to do so for a given dataset.
+% 	Also please note that this paper uses 1-based indexing for notational simplicity.
 
@@
 % %===============================================================================
+\vspace{-8pt}
 \section{Method} \label{sec:method}
 	\begin{figure}[thbp]
-	    \vspace{-20pt}
+	    \vspace{-15pt}
 		\begin{center}
@@
 			% \includegraphics[width=400pt]{../images/main_diagram_condensed_with_domains.pdf}
-			\includegraphics[width=\textwidth]{../images/main_diagram_beautiful.pdf}
+			\includegraphics[width=0.9\textwidth]{../images/main_diagram_beautiful.pdf}
 		\end{center}
@@
 	\end{figure}
-
 		In this section, we describe how TRITON works to translate images from domain A (simulation) to domain B (photos) while maintaining surface consistency. 
-		TRITON has four main components: a neural texture, an image translator, and two surface consistency losses. [[One or two sentences summarizing the flow - nothing more than that]].
-
+		TRITON introduces a learneable neural neural texture with two novel surface consistency losses to an existing image translator.
+In the end, TRITON is able to effectively generate photorealistic images.
 		%JUNE 12:
 		%TODO: MIgrate all four of these teasers into their respective subsections to save space.
-
+\vspace{-3pt}
 	\subsection{Neural Neural Texture Projection}
+	\vspace{-3pt}
 		\begin{figure}[thbp]
-		    \vspace{-15pt}
+		    \vspace{-5pt}
 			\begin{center}
-				\includegraphics[width=300pt]{../images/learnable_textures.pdf}
+				\includegraphics[width=0.6\textwidth]{../images/learnable_textures.pdf}
 			\end{center}
@@
 			\caption{
-				This figure illustrates how the our neural neural textures are calculated in figure \ref{fig:main_diagram}.
-They are fully differentiable, and represented continuously along the texture's U and V axes using Fourier feature networks.
+				This figure details how our neural neural textures are calculated in Figure~\ref{fig:main_diagram}.
+They are fully differentiable, and represented continuously along the texture's u and v axes using Fourier feature networks.
 			}
@@
 		% Using neural neural textures, we can encode features directly onto the surfaces of the 3d objects in a scene, which the image translation module uses to maintain visual consistency between states and viewpoints.
-		Instead of feeding a scene $s$ directly into the image translator $\Tab$, we first apply learnable textures $\psi$ to its surfaces as shown in figure \ref{fig:main_diagram}.
+		Instead of feeding a scene $s$ directly into the image translator $\Tab$, we first apply learnable textures $\psi$ to its surfaces as shown in Figure \ref{fig:main_diagram}.
 		Previous works called these learnable textures ``neural textures'', and were parametrized by a discrete grid of differentiable texels. 
 		% In contrast, we call our learnable textures ``neural nerual textures'', becuase our textures are a type of neural texture that is parametrized continuously over UV space using a neural fourier feature network.
-		In contrast, we call our learnable textures ``neural nerual textures'', becuase our textures are parametrized continuously over UV space using a neural network.
-		Like previous works, our neural textures $\psi\toL$ are learned jointly with our image translator $T$.
+		In contrast, we call our learnable textures as ``neural nerual textures'', because our textures themselves are represented as a neural network function, parameterized continuously over UV space.
+		Our neural textures $\psi\toL$ are learned jointly with our image translator $T$.
 
@@
 		\end{equation}
-
 		Given a scene $s$, we obtain projection $\pi$ by applying a texture $\psi^i \in \psi\toL$ to every pixel $(u,v,l) \in s$ individually, where texture index $i=I(l)$ is decided by the label value $l$ of that scene pixel.
@@
 		% where $n\in \{1\dots N\},\ \ c\in \{1\dots 3\} ,\ x\in \{1\dots W\},\ y\in \{1\dots H\},\ \ \text{and} \ \ i=I(s_{n,3,x,y})$.
-		where $ x\in \{1\dots W\},\ y\in \{1\dots H\}$, and texture index $i=I(l)$ where $l=s_{[x,y,3]}$ and subscript means multidimensional indexing.
+		where $ x\in \{1\dots W\},\ y\in \{1\dots H\}$.
+Texture index $i = I(l)$ where $l=s_{[x,y,3]}$ and the function $I(\cdot)$ scales and discretizes $l$ into integers.
+Subscripts mean multidimensional indexing.
 
@@
 		, $f_k \in \mathcal{N}(\mu=0,\ \sigma=10)$ is a two dimensional random gaussian vector,
-		and $\cdot$ is the dot product operator.
+		\mbox{and $\cdot$} is the dot product operator.
 		%  $rgb$ represents a 3d color vector,
@@
 		% $M^i: \real^{256} \rightarrow \real^3$.
-		Note that there is nothing special about 256 or 10: these hyperparameter values just happen to work nicely.
+		The hyperparamters 256 and 10 are selected empirically.
+		%Note that there is nothing special about 256 or 10: these hyperparameter values just happen to work nicely.
 
@@
 
+\vspace{-3pt}
 	\subsection{Image Translation}
 	\label{sec:image_translation}
-
+\vspace{-3pt}
 	% 	\begin{figure}[H]
@@
 		The main differences between our image translation model and MUNIT are that we use a different image similarity loss $\Omega$, and like \citet[]{surgical_image_translation} and \citet[]{surgical_video_translation} our style code is fixed (making it unimodal) and noise is injected into the latent codes during training to prevent overfitting.
-		During inference however, this intermediate noise is removed and our image translation module is completely determinstic. 
+		During inference however, this intermediate noise is removed and our image translation module is deterministic. 
 		% Apart from these differences, our image translation module has the same loss formulations and generator/encoder/discriminator network architectures as MUNIT.
@@
 
-	\subsection{Unprojection Consistency Loss}
-	\label{sec:unprojection_consistency_loss}
-
-		\begin{figure}[thbp]
-		    \vspace{-10pt}
-			\begin{center}
-				\includegraphics[width=.8\textwidth]{../images/unprojection_consistency_loss_without_reprojection.pdf}
-			\end{center}
+\begin{figure}
+    \centering
+    \begin{minipage}{0.57\textwidth}
+		\includegraphics[width=1\linewidth]{../images/unprojection_consistency_loss_without_reprojection.pdf}\label{fig:unprojection_consistency_loss}
 		\vspace{-5pt}
 	\caption{
-				This is the unprojection consistency loss used in figure \ref{fig:main_diagram}.
-				The Unprojection Mean and Reprojection nodes are not used in any losses, and help to illustrate the next section \ref{sec:texture_realism_loss}.
-				% After calculating fake photos $\hat{p}_{1...B}$ from UVL scenes $s_{1...B}$ as seen in figure \ref{fig:main_diagram}, 
-				% we can unproject fake photos $\hat{p}_{1...B}$ back into texture space to obtain $u_{1...B,\ 1...L}$ .
-				% If the fake photos display consistent textures along their 3d surfaces, then the unprojected textures should be similar.
-				% We can measure this similarity by taking the per-channel standard deviation of these unprojections, aka $\sigma(u)$, then averaging the result.
-				% When the fake photos display similar surfaces, the unprojections will be similar making the unprojection consistency loss low.
-				% Additionally, we can also calculate the average unprojection, which is useful for visualization purposes (it will look blurry if $\hat{p}$ is inconsistent).
-			}
-			\label{fig:unprojection_consistency_loss}
+		This is the unprojection consistency loss used in Figure~\ref{fig:main_diagram}.
+		The Unprojection Mean is not used in any losses, but help to illustrate the content in Section \ref{sec:texture_realism_loss}.
+	}
+	\end{minipage}
+	\hfill
+    % \hspace{1cm}
+    \begin{minipage}{0.39\textwidth}
+        \includegraphics[width=1\linewidth]{../images/texture_realism_ablation.pdf}
+% 			\vspace{-5pt}
+            \vspace{-5pt}
+			\caption{
+				The neural texture looks more realistic with texture realism loss enabled.
+Note that the blocks show different letters because of different initializations and the symmetry of a cube - both solutions are valid texture assignments.
+			}
+% 			\vspace{-10pt}
+			\label{fig:texture_realism_ablation}
+    \end{minipage}
+    \vspace{-15pt}
 \end{figure}
+% \begin{figure}[thbp]
+%     \vspace{-10pt}
+% 	\begin{center}
+% 		\includegraphics[width=.75\textwidth]{../images/unprojection_consistency_loss_without_reprojection.pdf}
+% 	\end{center}
+% 	\vspace{-5pt}
+% 	\caption{
+% 		This is the unprojection consistency loss used in Figure~\ref{fig:main_diagram}.
+% 		The Unprojection Mean is not used in any losses, but help to illustrate the content in Section \ref{sec:texture_realism_loss}.
+% 		% After calculating fake photos $\hat{p}_{1...B}$ from UVL scenes $s_{1...B}$ as seen in figure \ref{fig:main_diagram}, 
+% 		% we can unproject fake photos $\hat{p}_{1...B}$ back into texture space to obtain $u_{1...B,\ 1...L}$ .
+% 		% If the fake photos display consistent textures along their 3d surfaces, then the unprojected textures should be similar.
+% 		% We can measure this similarity by taking the per-channel standard deviation of these unprojections, aka $\sigma(u)$, then averaging the result.
+% 		% When the fake photos display similar surfaces, the unprojections will be similar making the unprojection consistency loss low.
+% 		% Additionally, we can also calculate the average unprojection, which is useful for visualization purposes (it will look blurry if $\hat{p}$ is inconsistent).
+% 	}
+% 	\label{fig:unprojection_consistency_loss}
+% \end{figure}
+\vspace{-5pt}
+\subsection{Unprojection Consistency Loss}
+\vspace{-5pt}
+	\label{sec:unprojection_consistency_loss}
 
@@
         \end{equation}
-        where the expectation $\mathbb{E}$ means we aggregate multiple $(r,g,b)$ vectors being assigned to the same $(u,v,l)$ location by averaging them. 
-        In practice, $(u,v,l)$ are real numbers between $[0,1]$, where as each $\unprojection$ have to be rasterized, i.e represented by $L$ $(D\times D\times 3)$ images, where $L$ is the number of labels and $D\times D$ is the resolution of the unprojection.
+        where the expectation $\mathbb{E}$ means we aggregate multiple $(r,g,b)$ vectors being assigned to the same $(u,v,l)$ coordinate by averaging them.
+        In practice, $(u,v,l)$ are real numbers between $[0,1]$, where as each $\unprojection$ have to be rasterized, i.e., represented by $L$ images with a size of $(D\times D\times 3)$, where $L$ is the number of labels and $D\times D$ is the resolution of the unprojection.
 Therefore, we discretize and scale corresponding $(u,v,l)$ to integers so that each $(r,g,b)$ vector will be assigned to a pixel on $\unprojection$.
@@
         \end{equation}
-        where $\sigma(\cdot)$ stands for the variance function and $c \in \{1\dots 3\}$ is the channel index of $\unprojection$.
+        where $\sigma(\cdot)$ stands for the standard deviation function and $c \in \{1\dots 3\}$ is the channel index of $\unprojection$.
 		%We sample a random batch of UVL scenes $S\toN$, and translate them into $\ph\toN$.
@@
 Intuitively, if $\lUC$ were $0$, it would mean the object surfaces in translations $\ph$ appear exactly the same in every scene.
-In addition, we call the mean of unprojections $\mu(\{\unprojection^{(l,i)}\}_{i=1}^N)$ as ``Recovered Textures'', visualzed in Figure~\ref{fig:first_diagram} and \ref{fig:unprojection_consistency_loss}.
+In addition, we call the mean of unprojections $\mu(\{\unprojection^{l,i}\}_{i=1}^N)$ as ``Recovered Textures'', visualzed in Figure~\ref{fig:first_diagram} and Section~\ref{fig:unprojection_consistency_loss}.
 
@@
 % 		\end{equation}
-		%
+
 		%Abbreviated
@@
 	\label{sec:texture_realism_loss}
-        \vspace{-7pt}
-		\begin{figure}[thbp]
-			\begin{center}
-				\includegraphics[width=250pt]{../images/texture_realism_ablation.pdf}
-			\end{center}
-			\vspace{-5pt}
-			\caption{
-				The neural texture looks more realistic with texture realism loss enabled.
+        % \vspace{-7pt}
+% 		\begin{figure}[thbp]
+% 			\centering
+% 				\includegraphics[width=0.5\textwidth]{../images/texture_realism_ablation.pdf}
+
+% 			\vspace{-5pt}
+% 			\caption{
+% 				The neural texture looks more realistic with texture realism loss enabled.
 Note that the blocks show different letters because of different initializations and the symmetry of a cube - both solutions are valid texture assignments.
-			}
-			\vspace{-10pt}
-			\label{fig:texture_realism_ablation}
-		\end{figure}
+% 			}
+% 			\vspace{-10pt}
+% 			\label{fig:texture_realism_ablation}
+% 		\end{figure}
 
@@
 		Without $\lTR$, $\psi$ can look wildly different each time you train it.
-		As seen in the top row of figure \ref{fig:texture_realism_ablation}, the neural texture looks very unrealistic – the colors are completely arbitrary.
-		After adding $\lTR$ though, $\pih \approx \ph$, and $\psi$ to represents the albedo of the surfaces in the scene.
+		As seen in the top row of Figure \ref{fig:texture_realism_ablation}, the neural texture looks very unrealistic --- the colors are completely arbitrary.
+% 		After adding $\lTR$ though, $\pih \approx \ph$ and thus the neural texture represents the textures of the objects in real life. 
+        By adding texture realism loss $\lTR$, we make the textures $\psi$ more realistic. In practice, this makes TRITON less likely to mismatch the identity of translated objects.
 		% The image similarity loss used in $\lTR$ is calculated the same way image similarity losses are calculated in section \ref{sec:image_translation}: L2 loss minus MSSSIM.
-
-		As it turns out, we can achieve surface-consistent translations just using $\lTR$, without $\lUC$.
-		The the reverse is also true: $\lTR$ is sufficient to ensure surface consistency without $\lUC$.
-		Using both, however, yields better results than either loss alone. 
+		%As it turns out, we can achieve surface-consistent translations just using $\lTR$, without $\lUC$.
+		%The the reverse is also true: $\lTR$ is sufficient to ensure surface consistency without $\lUC$.
+		%Using both, however, yields better results than either loss alone. \\
 		% For an explanation of why this is the case, see the appendix \ref{sec:texture_realism_theory}.
-
-		With that said, there are some advantages to using $\lTR$ alone: when just using $\lTR$ you can use batch sizes as small as $N=1$, allowing you to save video memory. 
-		Using $\lTR$ is also more numerically stable, as you no longer have to worry about whether the same surfaces are seen across multiple scenes in a batch as you would with $\lUC$.
+		%With that said, there are some advantages to using $\lTR$ alone: when just using $\lTR$ you can use batch sizes as small as $N=1$, allowing you to save video memory. 
+		%Using $\lTR$ is also more numerically stable, as you no longer have to worry about whether the same surfaces are seen across multiple scenes in a batch as you would with $\lUC$.
 
@@
 	%===============================================================================
-
+\vspace{-8pt}
 \section{Experiments}\label{sec:results}
-
+\vspace{-3pt}
 \subsection{Datasets}
-Here we detail the datasets used in our experiments. 
-Every dataset has two sets of images: UVL scenes and real photographs. They are all unpaired, and have RGB values ranging from 0 to 1.
-
-The first dataset to mention is the three-block dataset.  
-It has 300 photos and 2000 UVL scenes.
-It features a table with three alphabet blocks on a table, which are randomly translated along the X and Y axes and rotated randomly along the Z axis.
-Each photograph features these three cubes with a random position and rotation.
-
-[[Insert photographs and UVL maps here; a digram showing each dataset we describe here and 1 or two samples of each domain in each dataset]]
+\vspace{-2pt}
+%Here we detail the datasets used in our experiments.
+% We constructed multiple datasets for our experiments.
+We constructed two datasets AlphabetCube-3 and RobotPose-xArm to benchmark different image translators in many perspectives.
+In our setting, each dataset is composed of two sets of unpaired images: UVL scenes from a simulator and real photographs.
+Note that the images in all datasets are unpaired and UVL scenes only rely on rough 3d models of the objects in the scene without need of precisely aligning objects in the simulator to the real world.
+% . They are all unpaired, and have RGB values ranging from 0 to 1.
+We use AlphabetCube-3 for image translation quality evaluation, and RobotPose-xArm for sim2real policy learning evaluation.
+
+% The first dataset we particularly use for the offline evaluation is the three-block dataset.
+
+% [[Insert photographs and UVL maps here; a digram showing each dataset we describe here and 1 or two samples of each domain in each dataset]]
 
@@
 
-\subsection{Qualitative Evaluation Results}
-We show qualitative evaluation results 
-\begin{figure}[thbp]
-    \vspace{-30pt}
+%\subsection{Qualitative Evaluation Results}
+%We show qualitative evaluation results ....[TODO]
+\begin{figure}[th]
 	\begin{center}
-		\includegraphics[width=\textwidth]{../images/frame_inconsistency_diagram.pdf}
+		\includegraphics[width=.9\textwidth]{../images/frame_inconsistency.pdf}
 	\end{center}
+	\vspace{-7pt}
 	% Each outline color corresponds to the same cube.
@@
 	\caption{
+	    Comparison of image translation methods.
+	    The first column is the UVL map as the input.
+	    The other columns are results using different image translation methods.
 		Each row of images shows a different random placement of objects in the scene.
-		Each column of images is a different image translation algorithm.
-		The same cube is marked with the same color outline across all photos.
-		TRITON is consistent: for example, the cube outlined as yellow always has an 8 on the top.
-		Meanwhile, CycleGan for example shows a 4 on the top of that cube in the top two rows, but an 8 and a 7 in the next two rows.
-		Because of the symmetry of the cubes, and the unsupervised training, it is arbitrary which synthetic cube gets which symbol after training - but whatever it chooses, it should be consistent between placements.
-		CUT and CycleGan are not consistent, while TRITON is.
+		TRITON consistently outputs high quality results over different object arrangements. 
+		``TRITON texture only'' stands for TRITON without two surface consistency losses $\lUC$ and $\lTR$.
+		% Each column of images is a different image translation algorithm.
+		% The same cube is marked with the same color outline across all photos.
+		% TRITON is consistent: for example, the cube outlined as yellow always has an 8 on the top.
+		% Meanwhile, CycleGAN for example shows a 4 on the top of that cube in the top two rows, but an 8 and a 7 in the next two rows.
+		% Because of the symmetry of the cubes, and the unsupervised training, it is arbitrary which synthetic cube gets which symbol after training - but whatever it chooses, it should be consistent between placements.
+		% CUT and CycleGAN are not consistent, while TRITON is.
 		% TODO: Update the images in this to have the latest training iteration...
 		}
+		\vspace{-15pt}
 		\label{fig:frame_inconsistency_diagram}
@@
 
-    \begin{figure}[thbp]
-    	\begin{center}
-    		\includegraphics[width=\textwidth]{../images/blurry_recovery.pdf}
-    	\end{center}
-    	\caption{
-    		The recovered texture is more crisp when we have surface consistency losses $\lUC$ and $\lTR$ enabled.
-    		[[TODO: include cyclegan and other algorithms here]]
-    	}
-    	\label{fig:blurry_recovery}
-    \end{figure}
+    % \begin{figure}[thbp]
+    % 	\begin{center}
+    % 		\includegraphics[width=\textwidth]{../images/blurry_recovery.pdf}
+    % 	\end{center}
+    % 	\caption{
+    % 		The recovered texture is more crisp when we have surface consistency losses $\lUC$ and $\lTR$ enabled.
+    % 		[[TODO: include cyclegan and other algorithms here]]
+    % 	}
+    % 	\label{fig:blurry_recovery}
+    % \end{figure}
 	% 	Alphabet Three							
@@
 
-\subsection{Ground Truth Comaprison}
+% \subsection{TRITON evaluation}
+% \vspace{-1pt}
+\subsection{Image Translation Evaluation on AlphabetCube-3}
+% \vspace{-3pt}
+AlphabetCube-3 dataset features a table with three different alphabet blocks on the top.
+% All blocks are randomly translated along the X and Y axes and rotated randomly along the Z axis.
+The dataset contains 300 real photos and 2000 UVL scenes from a simulator.  
+Each photograph features these three cubes with a random position and rotation.
+In this section, we evaluate the image translation accuracy of the TRITON and other image translation methods using AlphabetCube-3.
+
+Figure~\ref{fig:frame_inconsistency_diagram} shows qualitative results on the dataset.
+% The first column is the input UVL map for all the image translators and other columns are the results.
+% ``TRITON texture only'' stands for TRITON without two view consistency losses $\lUC$ and $\lTR$.
+% Each row of images shows a different random placement of objects in the scene except for the last row where we collect all the translated cubes from different scenes.
+% We use contours in different colors to help identify three cubes.
+From Figure~\ref{fig:frame_inconsistency_diagram} we find that TRITON consistently outputs high quality results over different object arrangements.
+The textures keep aligned even when the position of blocks change dramatically over multiple scenes (See examples in green rectangle in Figure~\ref{fig:frame_inconsistency_diagram}).
+In contrast, though MUNIT~\cite{munit} and CycleGAN~\cite{cyclegan} manage to generate realistic images, the surfaces of the cubes are either consistent over scenes (See exsamples in the red rectangle) or replicated by mistake (See examples in the orange rectangle).
+Also note that the floor background of the outputs from CycleGAN are quite different from the ground truth.
+CUT~\cite{cut} fails to generate meaningful images regarding both the foreground blocks and the background.
+
+We further conduct quantitative experiments and the results are shown as Table~\ref{tab:quantitative}.
+In this evaluation we manually align the simulator with 14 photos of different real world scenes and generate the UVL maps for translation.
+We measured the LPIPS~\cite{lpips} and $l2$-norm between the translated images and the real images using multiple configurations.
+`Masked' means we mask out the background (which is the floor in AlphabetCube-3 dataset) and only measure the translation quality w.r.t three foreground blocks.
+For the `unmasked' tests, we compare the whole image without any masking instead, and the background contributes much more to the losses due to its larger area.
+Similar to the qualitative results, TRITON consistently outperforms other methods under different metrics and configurations.
+Further ablations TRITON w/o $\psi, \lUC, \lTR$ and TRITON w/o $\lUC, \lTR$ show the importance of the new losses we introduce.
+
+\begin{comment}
+Comment from Xiang: it might be better to have a short introduction on training details if we have space.
+\end{comment}
+
+% ... shows ...
 
 	%CREATED WITH https://www.tablesgenerator.com/# -- this website is wonderful!!
+\begin{comment}
 \begin{table}[thbp]
     \caption{Ground truth comparison evaluations for TRITON. Masked and Unmasked mean xxxxxx. Sync and Unsync mean xxxxx. L2 is xxxx LPIPS is xxxxxx. TRITON is xxxxxxx. }
+    \label{tab:quantitative}
 	\resizebox{\textwidth}{!}{
@@
         \midrule
+        CycleGAN & 0.450 & 0.379 &  0.559 &  0.554 &  6.02 &  5.93 &  4.25 &  4.23 \\
+        CUT                           & 0.469                        & 0.382                        & 0.553                        & 0.526                        & 5.40                        & 5.34                        & 6.37                        & 6.29\\
+        \midrule
         TRITON w/o $\psi, \lUC, \lTR$ & 0.437                        & 0.373                        & 0.500                        & 0.490                        & 4.34                        & 4.02                        & 4.25                        & 3.92                        \\
@@
         \textbf{TRITON}                        & \textbf{0.286}               & \textbf{0.267}               & \textbf{0.479}               & \textbf{0.478}               & \textbf{1.17}               & \textbf{1.16}              & \textbf{1.23}               & \textbf{1.22}               \\
-        \midrule
-        CycleGAN & 0.450 & 0.379 &  0.559 &  0.554 &  6.02 &  5.93 &  4.25 &  4.23 \\
-        CUT                           & 0.469                        & 0.382                        & 0.553                        & 0.526                        & 5.40                        & 5.34                        & 6.37                        & 6.29\\
         \bottomrule
@@
 \end{table}
-
-[[Figures: Show these results and explain why we have a mask on some of them]]
-
-TODO: Explain what sync and unsync mean, retrieve the results for CycleGAN and CUT
-
+\end{comment}
+
+\begin{table}[thbp]
+    \centering
+    \setlength{\tabcolsep}{2pt}
+    \caption{Quantitative results on AlphabetCube-3.
+LPIPS~\cite{lpips} and $l2$-norm between the translated images and the real images are reported.
+We exclude backgrounds in the `Masked' configuration.
+TRITON consistently outperforms other methods in different metrics and configurations}
+    \label{tab:quantitative}
+\resizebox{.80\textwidth}{!}{
+        \begin{tabular}{lcccc}
+        \toprule
+        & \multicolumn{2}{c}{Masked} & \multicolumn{2}{c}{Unmasked}  \\
+        \cmidrule(lr){2-3} \cmidrule(lr){4-5} & LPIPS ($\times 10^{-1}$) $\downarrow$ & L2 ($\times 10^{-2}$) $\downarrow$  & LPIPS ($\times 10^{-1}$) $\downarrow$  & L2 ($\times 10^{-2}$) $\downarrow$   \\
+        \midrule
+        CycleGAN & 0.450 &   0.559 &    6.02 &    4.25  \\
+        CUT & 0.469 & 0.553  & 5.40  & 6.37 \\
+        \midrule
+        TRITON w/o $\psi, \lUC, \lTR$ & 0.437   & 0.500  & 4.34  & 4.25  \\
+        TRITON w/o $\lUC, \lTR$       & 0.442  & 0.586  & 2.85 & 3.64 \\
+        \textbf{TRITON} & \textbf{0.286}  & \textbf{0.479}  & \textbf{1.17}  & \textbf{1.23} \\
+        \bottomrule
+        \end{tabular}
+	}
+\end{table}
+
+% [[Figures: Show these results and explain why we have a mask on some of them]]
+
+% TODO: Explain what sync and unsync mean, retrieve the results for CycleGAN and CUT
+\vspace{-5pt}
 \subsection{Sim2real Transfer for Robot Learning}
@@
     \vspace{-10pt}
-    \includegraphics[width=\textwidth]{images/sim2real_framework.pdf}
-    \vspace{-20pt}
+    \includegraphics[width=.8\textwidth]{images/sim2real_framework.pdf}
+    \vspace{-10pt}
     \caption{Sim2real framework of using TRITON.
@@
 \end{figure}
-In this section we demonstrate how TRITON improves sim2real transfer for robot learning.
-To do this, we first train TRITON on a dataset consist of unpaired UVL scenes from simulator and photos from the real robot.
-After that, we train the robot policy in the simulator only.
-The input of the policy is the fake photo $\hat{p}$ translated from the simulated UVL scene using TRITON's translator $T_{A\to B}$.
-Finally, the trained policy is evaluated on the real robot, taking real photos $p$ as input.
-Ideally, a good image translation model leads to less gap between $p$ and $\hat{p}$, so that the policy trained on synthesized photos will transfer to real domain seamlessly.
-
-\paragraph{Task} We use a robot pose imitation task for our experiments.
+In this section we demonstrate how TRITON improves sim2real transfer for robot policy learning.
+To this end, we first train TRITON on a dataset consist of unpaired UVL scenes from a robot simulator (Gazebo) and photos from the real robot.
+Once TRITON is trained, we learn the robot policy while only utilizing the simulator.
+The input of the policy is the fake photo $\ph$ translated from the simulated UVL scene using TRITON's translator $T_{A\to B}$.
+Finally, the trained policy is directly evaluated on the real robot, taking real photos $p$ as input.
+
+Ideally, a good image translation model makes $\ph$ similar to $p$, so that the policy trained on synthesized photos will transfer to real domain seamlessly and will have better performance.
+All our policies are learned with zero real-world robot interaction with the environment.
+
+\textbf{Task} We use a robot pose imitation task for our experiments.
 Given the input of a photo of real robot pose, the policy outputs robot controls to replicate that target pose.
 We measure the angular error between the replicated and target poses as our evaluation metric:$\sqrt{\sum_{j} (\hat{a}_j - a_j)^2}$,
-where $\hat{a}_j$ and $a_j$ are replicated and target joint angle respectively, and $j$ is the joint index.
+where $\hat{a}_j$ and $a_j$ are replicated and target joint angles respectively, and $j$ is the joint index.
 We use an xArm robot which has 7 joints.
-Moreover, we attach patterns and tapes on it to make its texture complex.
-
-\paragraph{Robot policy and Baselines}
-Since sim2real provides abundant training data using the simulator, we use behavior cloning which is enough to train a good robot policy.
-The policy is implemented by CNN~\cite{dqn}.
-We compare TRITON against two baseline image translation methods: CycleGAN and CUT, by replacing TRITON with each baseline method respectively in the above pipeline.
-The robot policy is the same for all methods.
-
-\paragraph{Evaluation Settings} We introduce two main evaluation settings, \textbf{Seen} and \textbf{Unseen}.
-In \textbf{Seen} setting, the policy is trained and tested using the same camera viewpoint that is used in training image translator.
+We also attached patterns and tapes on the robot to make its texture more challenging to model.
+
+\textbf{Robot policy and Baselines}
+Since the sim2real formulation allows benefiting from abundant training data using the simulator, we use behavior cloning to train a good robot policy.
+The policy is implemented with a CNN~\cite{dqn}.
+We compare TRITON against two baseline image translation methods: CycleGAN~\cite{cyclegan} and CUT~\cite{cut}, by replacing TRITON with each baseline method respectively in the above pipeline.
+The robot policy learning method is same for all the methods.
+
+\textbf{Evaluation Settings} We introduce two main evaluation settings, \textbf{Seen} and \textbf{Unseen}.
+In the \textbf{Seen} setting, the policy is trained and tested using the same camera viewpoint that is used during TRITON (or a baseline translator) training.
 Whereas in \textbf{Unseen} setting, we introduce a camera at a new viewpoint for training and testing the policy.
-That is, the image translator has to generate the fake photos out of its training distribution (seen camera viewpoints), which becomes a challenging for the translator.
-We also vary input image resolution to show the power of photorealistic images in higher resolutions.
+That is, the image translator has to generate the fake photos out of its training distribution (seen camera viewpoints), which becomes a challenging task for the translator.
+We also vary input image resolutions to show the power of photo-realistic images in higher resolutions.
 
@@
     \centering
-    \vspace{-8pt}
-    \includegraphics[width=\textwidth]{images/sim2real_res.pdf}
-    \vspace{-20pt}
+    \vspace{-3pt}
+    \includegraphics[width=.95\textwidth]{images/sim2real_res.pdf}
+    \vspace{-5pt}
     \caption{Evaluation results of sim2real robot learning.
 We compare TRITON against two baselines and one TRITON variant w/o $\ell_{UC}$ across 3 different input image resolutions.
-TRITON outperforms CycleGAN~\cite{} and CUT~\cite{} consistently across (a) all resolutions and (b) Unseen viewpoints.
-Results in (a) are from Seen setting.
+TRITON outperforms CycleGAN~\cite{cyclegan} and CUT~\cite{cut} consistently across (a) all resolutions and (b) unseen viewpoints.
+Results in (a) are from Seen setting only.
 Results in (b) are from 336x336 resolution.
@@
     \label{fig:sim2real}
+    \vspace{-3pt}
+\end{figure}
+
+\textbf{Results} Figure~\ref{fig:sim2real} shows the evaluation results of the sim2real transfer.
+Both Seen and Unseen evaluations show that TRITON outperforms baselines consistently.
+In Figure~\ref{fig:sim2real}(a), we find that TRITON continuously improves from low to high resolutions due to its ability to generate more photo-realistic images compared to the baselines.
+%This is because in low resolution (eg.
+$84\times 84$), the details in images are not important, whereas in high resolution ($336\times 336$), artifacts from imperfect translator are clearer and may harm policy learning.
+From Figure~\ref{fig:sim2real}(b), we confirm that TRITON outperforms the others also in the Unseen setting, showing that TRITON learns image translations that are generalizable to new viewpoints while others are limited.
+In the comparison against TRITON w/o $\ell_{UC}$, TRITON outperforms this variant consistently except the lowest resolution.
+This again shows the effectiveness of $\ell_{UC}$ to generate photo-realistic images, and such high quality images are important in higher resolutions for sim2real transfer.
+
+%===============================================================================
 \vspace{-8pt}
-\end{figure}
-
-\paragraph{Results}
-In Figure~\ref{fig:sim2real} we show the evaluation results of sim2real transfer.
-Both evaluations show that TRITON outperforms CycleGAN and CUT consistently.
-In Figure~\ref{fig:sim2real}(a), we find that TRITON continuously improves from low to high resolutions due to the ability to generate more photorealistic images compared to the baselines.
-This is because in low resolution (eg.
-$84\times 84$) the details in images are not important, whereas in high resolution ($336\times 336$), artifacts from imperfect translator are clearer and do harm to policy learning.
-From Figure~\ref{fig:sim2real}(b), TRITON outperforms the others in Unseen setting, showing the power of xxxxxx.
-In the comparison against TRITON w/o $\ell_{UC}$, TRITON outperforms this variant consistently except the lowest resolution.
-This again shows the effectiveness of $\ell_{UC}$ to generate photorealistic images, and such high quality images are important in higher resolutions for sim2real transfer.
-
-%===============================================================================
-
 \section{Limitaions}
 \label{sec:Limitations} 
-
-Can't handle transparent objects.
-
-A limited number of objects can be learned at once before supervision is necessary with color loss (but there are workarounds).
-
-Takes a long time to train.
+% There are limitations of TRITON. 
+TRITON relies on 3D models of objects in order to generate photo-realistic images, making it less applicable when the geometry of an environment is unknown.
+Acquiring such 3D models could be challenging in the wild, especially in robots allowed to roam the world.
+TRITON is not able to handle transparent objects, because the UVL format is opaque.
+Moreover, the probability of incorrectly matching textures to objects increases as the number of object classes increases.
 
@@
 \bibliography{example}  % .bib
+
+\begin{comment}
 
@@
 
-		Becuase $\bar{p}$ is created from the average recovered texturs of $\hat{p}$, $\bar{p} \approx \hat{p}$.
-
-		Becuse of texture realism loss, $\pi \approx \hat{p}$.
+		Because $\bar{p}$ is created from the average recovered textures of $\hat{p}$, $\bar{p} \approx \hat{p}$.
+
+		Because of texture realism loss, $\pi \approx \hat{p}$.
 
@@
 
+\end{comment}
+
 \end{document}

### 2022-06-22 CORL/example.tex
Fixed two image filepaths (it worked in overleaf but not on my local computer)
Sync from Overleaf (Michael Edit)

@@
 
-\usepackage{corl_2022} % Use this for the initial submission.
+\usepackage[final]{corl_2022} % Use this for the initial submission.
 % \usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
@@
 \author{%
-	Ryan Burgert \\
+	Ryan Burgert, Jinghuan Shang, Xiang Li, Michael S. Ryoo\\
 	Department of Computer Science\\
@@
 	Stony Brook, NY 11794 \\
-	\texttt{rburgert@cs.stonybrook.edu} \\
+	\texttt{\{rburgert,mryoo\}@cs.stonybrook.edu} \\
 	% \And
@@
 	% \texttt{mryoo@cs.stonybrook.edu} \\
-	\And
-	Emma Burgert \\
-	Ryan Burgert's Dog\\
+	%\And
+%	Emma Burgert \\
+%	Ryan Burgert's Dog\\
 }

### 2022-06-22 CORL/appendix.tex
Added appendix.tex

--- 2022-06-16 CORL/example.tex
@@
-%TODO: Revise method section
-%TODO: Create formulation section
-%TODO: Create results section
+\section{Appendix}
 
-%TODO:
-%	Formulation Section
-%	Figures
-%		Main diagram - break it up into pieces with just text
-%		UVL three-axis diagram
-%		Replace C with (pi,s)
-%	Method:
-%		Unprojection Consistency Loss
-%		Texture Reality Loss
+\subsection{Neural Neural Textures}
 
-%TODO:
-%	Formulation Section
-%	Figures: Main diagram - break it up into pieces with just text
-%	Figures: UVL three-axis diagram
-%	Method:	Unprojection Consistency Loss
-%	Method:	Texture Reality Loss
+	In section \ref{sec:neural_tex}, we mentioned that neural neural textures learn better than raster neural textures. 
+	Neural neural textures don't have a specific resolution: they are continuously defined over the UV domain.
+	With raster-based textures, only the side of an object that currently is seen in a view is allowed to change during each update, because the gradient can't be propogated into pixels
 
-%ALL CURRENTLY USED TERMS:
+	The trained fourier-feature textures also exhibit less noise than its raster counterparts.
 
-%RULES:
-%    - Lower case: Belongs to an upper case thing
+	[[Insert figure showing the raster textures after training]]
 
-%     L - num labels
-%     N - batch size
-%     T - translator
-%     A, B - domains
-%     Tba
-%     Tab
-%     tau - texture       !!!!! MUST CHANGE
-%			TO DO: replace it with psi ψ, the triton symbol!
-%     pi - projection
-%     p - photo
-%     s - scene
-%     l_TR
-%     l_UC
-%     l_ADV
-%     l_REC
-%     l_CYC
-%     l_T
-%     i - texture index
-%     f_i - fourier frequency
-%     M - MLP for texture network
-%     u,v,l,r,g,b - channel values
-%     u - unprojections  !!!!!! MUST CHANGE
-%          make it capitalized. Unprojection should be denoted by U - it's too intuitive not to.
-%     sigma - standard deviation
-%     mu - mean
-%     E_A, E_B
-%     D_A, D_B
-%     G_A, G_B
-
-%     similarity(x,y) = MSSSIM(L2(x,y)
-
-% FIXING NOTATION WILL BE HARD :(
-% GO OVER WITH XIANG AND JINGHUAN TOMORROW
-%     In this paper I use 1-based indexing to make notation simpler.
-%
-%     s, pi in N,3,H,W - height width
-%              i,c,x,y
-%     All values between 0 and 1
-%
-%     I: {1/L, 2/L, ... L/L} -> {1, 2, ... L}  ;   I(l) = l*L
-%          I is a discrete mapping from continous label values l to discrete texture indices.
-%          It can be nonlinear, as long as its consistent.
-%     
-%     ψ_i: R2 -> R3   for   i \in {1,2 ... L}
-%
-%     pi_{n,c,x,y} = ψ_  {I(s_{n,1,x,y})}  (s_{n,2,x,y},s_{n,3,x,y})
-%
-%     EXPLAINING L_UC IS WAY TO BURDENSOME. We have to talk about weighted standard deviations of unprojections that have a separate unprojection resolution (128x128) etc.
-%	  l_UC = total mean across all dims of sigma
-%     sigma \in R^{L x C x 128 x 128} is the standard deviation of u in the channel dimension, weighted...
-%     !!! I shouldn't have to do this; the other paper didn't!!!
-%     u.sum_{N,C,u,v}
-%
-
-\newcommand{\msssim}{\text{msssim}}
-
-\newcommand{\Tab}{T_{A\rightarrow B}}
-\newcommand{\Tba}{T_{B\rightarrow A}}
-\newcommand{\pih}{\hat{\pi}}
-\newcommand{\sh}{\hat{s}}
-\newcommand{\ph}{\hat{p}}
-\newcommand{\pis}{\pi,s} % pi and s pairs from domain A
-\newcommand{\pish}{\pih,\sh} % pi and s pairs from domain A
-\newcommand{\ppis}{(\pis)} %Parenthesized pis
-\newcommand{\ppish}{(\pish)} %Parenthesized pis
-
-\newcommand{\toN}{^{1\dots N}}
-% \newcommand{\toNL}{_{1\dots B,\text{ } 1\dots L}}
-\newcommand{\toNL}{^{1\dots N, 1\dots L}}
-\newcommand{\toL}{^{1\dots L}}
-
-\newcommand{\lUC}{\ell_{UC}}
-\newcommand{\lTR}{\ell_{TR}}
-\newcommand{\eqand}{\ \ \ \text{ and }\ \ \ }
-\newcommand{\eqwhere}{\ \ \ \text{ where }\ \ \ }
-\newcommand{\real}{\mathbb{R}}
-
-% \newcommand{\similar}{\text{similarity}}
-\newcommand{\similar}{\Omega}
-\newcommand{\unprojection}{\omega}
-\newcommand{\expectation}{\mathop{\mathbb{E}}}
-\newcommand{\lsum}{\sum\limits}
-
-%%%%%%%%%%%%BIG TODO::::
-%%%%%% MAKE BATCH SIZE N INSTEAD OF B - B is a domain!
-
-\documentclass{article}
-
-\usepackage{corl_2022} % Use this for the initial submission.
-% \usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
-\usepackage{graphicx}
-\usepackage{float}
-\usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{multicol}
-\usepackage{multirow}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{array, booktabs, ragged2e}
-
-%\usepackage[preprint]{corl_2022} % Uncomment for pre-prints (e.g., arxiv); This is like ``final'', but will remove the CORL footnote.
-
-% \title{TRITON: Globally Consistent Sim-to-Real Transfer
-\title{Neural Neural Textures Make Better Simulators
-
-``I Can't Believe It's Not Real!''%Definitely gonna delete this lol
- %via Neural Textures
- }
-
-\author{%
-	Ryan Burgert \\
-	Department of Computer Science\\
-	Stony Brook University\\
-	Stony Brook, NY 11794 \\
-	\texttt{rburgert@cs.stonybrook.edu} \\
-	% \And
-	% Michael Ryoo \\
-	% Department of Computer Science\\
-	% Stony Brook University\\
-	% Stony Brook, NY 11794 \\
-	% \texttt{mryoo@cs.stonybrook.edu} \\
-	\And
-	Emma Burgert \\
-	Ryan Burgert's Dog\\
-}
-
-\begin{document}
-\maketitle
-
-%===============================================================================
-
-\begin{abstract}
-	% Abstracts should be a single paragraph, between 4--6 sentences long, ideally. Gross violations will trigger corrections at the camera-ready phase.
-	% Because of the 6 sentence limit, I've commented out some of the sentences...
-	Unpaired image translation algorithms can be used for sim-to-real tasks, but most fail to generate temporally consistent results.
-	% Because of this, the details or even identity of a particular object might change as it moves across a scene.
-	We present a new approach that combines differential rendering with image translation to achieve temporal consistency over indefinite timescales.
-%
-	%TURNING TWO SENTENCES INTO ONE:
-	% We call this algorithm TRITON (Texture Recovering Image Translation Network): an unsupervised, end-to-end, stateless sim-to-real algorithm.
-	% Unlike previous techniques, TRITON leverages the underlying 3d geometry of input scenes by generating realistic-looking learnable neural textures.
-	We call this algorithm TRITON (Texture Recovering Image Translation Network): an unsupervised, end-to-end, stateless sim-to-real algorithm that 
-	leverages the underlying 3d geometry of input scenes by generating realistic-looking learnable neural textures.
-%
-	% These textures are projected onto the surfaces of input scenes, which are then fed through an image translation network to obtain the final outputs.
-	By settling on a particular albedo for the objects in a scene, we ensure consistency between frames statelessly.
-	Unlike previous algorithms, TRITON is not limited to camera movements --- it can handle the movement of objects as well, making it useful for downstream tasks such as robotic manipulation.
-	Our experiments show that in addition to achieving higher temporal consistency, the translations are closer to ground truth photographs than previous techniques.
-\end{abstract}
-\keywords{sim to real, image translation, differentiable rendering}
-
-%===============================================================================
-\section{Introduction}
-Problem: 
-Why is this problem important?
-No view consistency.
-
-Introducing our intuition of what improvements can solve this problem.
-
-Our exact method - introducing our components and what we're doing
-
-Conclusion: This works well, and our contributions are x
-
-% I introduce you to TRITON. The rest of the introduction text goes here; I've commented out my old incomplete introduction.
-
-	% TODO: Note that the simple input of UVL, or an RGB neural texture, means any simulator should be plug-and-play with this algorithm.
-
-	% Recently, several sim-to-real algorithms have come out that are based on image-to-image translation. [Citations]
-	% These are used for training robots using pixel-based reinforcement learning.
-	% They demonstrated that better image translation algorithms yielded notable improvements in robotic benchmarks.
-	% At the same time, there is a lot of research on differentiable rendering,
-	% a topic which produced papers such as NERF which attempt to capture 3d representations of the real world.
-	% However, most of these approaches are either supervised or involve only camera movements [citations].
-	% One paper that came out recently combined both image translation and differentiable rendering in an unsupervised manner to create view-consistent models of human organs [citation].
-	% This paper too, though, was limited to only camera movements.
-
-	% This algorithm unlocks a new capability: learning textures to match photos for given 3d models without supervision.
-
-	% The motivation for this paper is to create a temporally consistent sim-to-real image translation algorithm that will look the same from multiple camera angles simultaneously, keeps all semantic details
-	% [[I'll finish this later... let's work on the meat of the paper first...]]
-
-%===============================================================================
-\section{Formulation}
-\label{sec:data}
-	\begin{figure}[thbp]
-	\vspace{-10pt}
-		\begin{center}
-			\includegraphics[width=\textwidth]{../images/first_diagram.pdf}
-		\end{center}
-		\vspace{-5pt}
-		\caption{
-			This is an overview of what TRITON accomplishes.
-			TRITON learns the textures of 3d objects to help translate simulated images into photographs. It does this with unpaired data. Each row is a different dataset.
-			}
-		\label{fig:first_diagram}
-	\end{figure}
-	% TRITON stands for Texture Recovering Image Translation Network. It has two goals: to translate images, and to recover textures.
-
-	TRITON's goal is to turn 3d simulated images into realistic fake photographs (by training it without any matching pairs), while maintaining high surface consistency.
-	It does this by simultaneously learning both an image translator and a set of realistic textures.
-	These translations can be useful for downstream tasks, especially robotic policy learning from camera data, enabling sim2real.
-
-	In contrast to previous works involving `neural textures' \textbf{(mryoo: cite them here)}, TRITON can handle more than just camera movements:
-	the positions of objects in the training data can be moved around or deformed as well between data samples.
-	For this reason, we chose the term ``surface consistency'' instead of ``view consistency'', which was the term used in [] \textbf{(mryoo: cite)}.
-	With high surface consistency, surfaces of translated objects will look the same even when moved around or viewed from different camera angles.
-
-	\begin{figure}[H]
-		\begin{center}
-			\includegraphics[width=400pt]{../images/uvl_explanation_minimal.pdf}
-		\end{center}
-		\caption{
-			A scene is obtained by rendering a 3d state into an image, where the first two color channels represent $u,v$ coordinates and the third channel $l$ represents object labels.
-			% This diagram shows the purpose of a UVL image.
-			% A UVL scene is an image that has three channels: RGB.
-			% R and G are used for U and V, and B is used for L.
-			% L stands for Label, and determines which part of the synthetic image will get which texture.
-			% The U and V coordinates correspond to positions on each texture,
-			% telling it how to project the textures onto the 3d objects represented in the UVL scene.
-			% The darkest shade of blue corresponds to the 1st texture, and the next darkest shade of blue corresponds to the 2nd texture etc.
-			}
-		\label{fig:uvl_explanation}
-	\end{figure}
-
-	There are two components to every dataset: A set of simulated 3d scenes, and a set of photographs.
-	Datasets usually have many more scenes than photographs, since scenes can be generated automatically.
-
-	% The photographs, having $(r,g,b)$ values between 0 and 1,
-	% 	are denoted as $p \in [0,1]^{N \times 3 \times H \times W}$ where $N$ is the batch size,
-	% 	3 refers to the three $(r,g,b)$ channels, 
-	% 	and $H,W$ are the height and width respectively.
-
-	% A photograph in a set of photographs, having $(r,g,b)$ values between 0 and 1,
-	% 	is denoted as ${p^n \in [0,1]^{ 3 \times H \times W}}$ where $n$ is that photograph's index in that set,
-	% 	3 refers to the three $(r,g,b)$ channels, 
-	% 	and $H,W$ are the height and width respectively.
-
-	A photograph is an image tensor, having $(r,g,b)$ values between 0 and 1,
-		is denoted as ${p \in [0,1]^{ 3 \times H \times W}}$ where 
-		3 refers to the three $(r,g,b)$ channels, 
-		and $H,W$ are the height and width respectively.
-
-	In this work, a scene refers to a rendered 3d simulation state - which includes the position, rotation, and deformation of every object (including the camera).
-	% Using some 3d rendering software, be it Blender or Gazebo or some other 3d creates an image from these 
-	We represent each 3d state with a simple $(r,g,b)$ image, in a simple enough format that any decent simulator should able to provide.
-	% These have the same datatype and dimensions as photographs and are denoted as 
-	% $s \in [0,1]^{N \times 3 \times H \times W}$.
-	% A scene has the same dimensions as a photograph and is denoted as 
-	% $s^n \in [0,1]^{3 \times H \times W}$.
-	A scene has the same dimensions as a photograph and is denoted as 
-	$s \in [0,1]^{3 \times H \times W}$.
-	However, unlike $p$, $s$'s three $(r,g,b)$ channels encode a special semantic meaning: $(u,v,l)$ as depicted in figure \ref{fig:uvl_explanation}.
-	The channels $u$ and $v$ refer to a texture coordinate, whereas $l$ refers to a label value that identifies every object in a scene.
-	In a given dataset, each object gets a different label. Likewise, each object is assigned a different texture.
-	We assume that every dataset has $L$ different label values, $L$ different objects, and that we must learn $L$ different neural textures.
-
-TODO: Say I scales and discretizes l, don't say more than that. 
-% 	In each dataset, we must also define a function $I(l)$ that maps label values to texture indices. A simple way to do this is with the following definition:
-% 	\begin{equation}
-% 		I: \left\{\frac{1}{L},\frac{2}{L},\dots \frac{L}{L}\right\} \rightarrow \left\{1,2,\dots L\right\}  \eqand  I(l)=l\cdot L
-% 	\end{equation}
-	However, this mapping can be changed arbitrarily if its more convenient to do so for a given dataset.
-	Also please note that this paper uses 1-based indexing for notational simplicity.
-
-	% TODO: Describe what UVL is ; 
-	% Formulate the setting: What our inputs are and the targets are and what we learn (a neural texture function) and how we can take advantage of it for robotic learning.
-	% Don't go into details; just say 'its a black box function'
-
-	% TODO: Add UV to the fourier feature diagram.
-
-	% TODO: Create subfigures with subcaptions. 
-	% 2a: Nothing but UVL=UV+L
-	% 2b. 3d uvl axis to texture pack (drew on whiteboard)
-	% 2c. Skip over the translation network and show a pretty robot arm picture
-
-	% This is the formulatoin section; not data section. Dont talk about how many photos we use etc.
-
-	% JUST IN CASE THINGS ARE ERASED:
-	% We learn neural texture corresponding to each object, where each texture is represented as a function mapping... 
-	% The idea is to learn object textures as a set of continuous functions from a set of (unlabeled) real images, and use them to generate realistic images.
-	% Given a 3D structure of the scene represented with a UVL image, the learned neural textures will translate them into a realistic image.
-	% When used for the robot learning, this enables learnable, realistic sim2real of robot training images.
-
-	% IN THE INTRODUCTION: How we're using a neural neural network network texture. Also in related works.
-
-	% TODO: Replace neural texture in figure 3 with axis, and treat it as a function that takes UV in with an arrow pointing to it.
-
-	% BREAK IT DOWN APPROACH:
-	% Don't have any pictures. Have breakdown where we add new things in multiple figures.
-	% First figure: Just image translation. 
-	% Seconf:
-	% Third:
-	% Etc...
-
-	% In this paper, we'll mostly focus on a hand-collected dataset that involves three alphabet blocks that are moved across a table.
-	% Alphabet blocks were chosen because they all have the same geometry (a cube), but have very distinct semantic textures that will make temporal inconsistency obvious to the human eye.
-	% This dataset is analogous to data that would be collected for a third-person robotic grasping task.
-	% However, other objects (such as cans of soda, apples, cloves of garlic, etc) are also for generating other results in this paper.
-((TODO: Detail the five object tests and five cube tests and other stuff like shiny cans etc)).
-
-	% There are two components to this dataset: Simulated data in the form of UVL scenes, and photographs.
-	% The camera in the simulation is positioned in approximately the same place as the real camera, with approximately the same field of view.
-	% In both domains of this dataset, the camera never moves. Instead, the objects are randomly positioned and rotated on the table.
-	% In both the simulation and in real life, these objects are randomly translated along the x and y-axis of the table, as well as rotated on the z-axis.
-
-	% There are 200 photographs in this dataset, and they are recorded as RGB jpg images.
-	% There are 3000 synthetic images in this dataset, in the form of UVL images.
-	% These UVL images are also encoded as RGB images, but provide information about the geometry of a scene.
-	% UVL images are composed of both a UV map and a label map and are summarized in figure \ref{fig:uvl_explanation}.
-	% To avoid positional rounding errors, UVL images are encoded as EXR files: an image format that supports floating-point values.
-
-	% The pixels in a UVL image are visualizable in RGB space because, like RGB images, each pixel is a vector with 3 values.
-The first two channels, U and V, are floating point values between 0 and 1.
-The L channel is also a floating point value between 0 and 1, it has a second meaning.
-There are only a finite number of label values (corresponding to the number of learnable textures).
-The rank of a particular L value is used to index these textures.
-
-	% In the three-cube dataset we have 4 textures, and UVL scenes contain label values $l \in [\frac{0}{3}, \frac{1}{3},\frac{2}{3}, \frac{3}{3}]$.
-A pixel in a UVL scene $l=\frac{2}{3}$ will get indexed to the third texture, because $\frac{2}{3}$ is the third smallest label value.
-
-	% Domain A and B
-	% p hat
-	% s hat
-
-% %===============================================================================
-\section{Method} \label{sec:method}
-	\begin{figure}[thbp]
-	    \vspace{-20pt}
-		\begin{center}
-			% \includegraphics[width=400pt]{../images/main_diagram_condensed.pdf}
-			% \includegraphics[width=400pt]{../images/main_diagram_condensed_with_domains.pdf}
-			\includegraphics[width=\textwidth]{../images/main_diagram_beautiful.pdf}
-		\end{center}
-		\vspace{-10pt}
-		\caption{
-			% We use differentiable rendering paired with unpaired image translation to consistently= transform synthetic scenes into realistic images.
-			% To ensure all objects look consistent in different positions and views, we learn the albedo of each object's surface by using a learnable latent texture.
-			% This texture is parametrized as an image generated by an MLP which is fed Fourier features, as shown in figure \ref{fig:learnable_textures}.
-			% $N$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
-			%
-			%JUNE 12:
-			%Don't say 4 main components; say 2 components and 2 losses
-			%TODO: Try to use right-angled arrows
-			%TODO: Use tau as a function
-			%Copy paste the figure multiple times, deleting things
-			%Mention "Neural Neural Texture": Its a function mapping UV to RGB
-			%Formulation doesnt mentino texture; just uvl inputs and final outputs
-			%Always use function notation tauuv instead of just tau (in figure as well) 
-			%The arrow should be running through tau. It's not a variable its a function...
-			%Rename 'B' to "N" for batch size
-			%Figure 8: Align consistent with inconsistent and use all 5 green ones
-			%
-			This figure is an overview TRITON.
-			Inputs are on the left, and outputs are on the right.
-			The dashed arrows indicate losses.
-			Although $\pi\toN$ and $\ph\toN$ look similar, they are not identical - $\lTR$ encourages them to look as similar as possible.
-			% $\pi$ is simply projected textures, whereas $\hat{p}$ has been run through an image translator, allowing it to have shadows and specularities.
-			% TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
-			% TODO: Use variables instead of 3,4
-			% TODO: Make the text larger and easier to read
-			% TODO: Simplify the diagram?
-		}
-		\label{fig:main_diagram}
-	\end{figure}
-
-		In this section, we describe how TRITON works to translate images from domain A (simulation) to domain B (photos) while maintaining surface consistency. 
-		TRITON has four main components: a neural texture, an image translator, and two surface consistency losses. [[One or two sentences summarizing the flow - nothing more than that]].
-
-		%JUNE 12:
-		%TODO: MIgrate all four of these teasers into their respective subsections to save space.
-
-	\subsection{Neural Neural Texture Projection}
-		\begin{figure}[thbp]
-		    \vspace{-15pt}
-			\begin{center}
-				\includegraphics[width=300pt]{../images/learnable_textures.pdf}
-			\end{center}
-			\vspace{-3pt}
-			\caption{
-				This figure illustrates how the our neural neural textures are calculated in figure \ref{fig:main_diagram}.
-They are fully differentiable, and represented continuously along the texture's U and V axes using Fourier feature networks.
-			}
-			\vspace{-10pt}
-			% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
-			% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
-			% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
-			\label{fig:learnable_textures}
-		\end{figure}
-
-		%JUNE 12:
-		%Defining what it is and how it's used.
-		%
-		%Justify why we're calling it neural neural texture.
-Unlike previous papers [citations], we learn a neural network instead of a grid of pixels.
-To be explicit we call it neural neural texture.
-%%%%%% Previous papers were more like latent textures but ours is different: it is a funciton.
-Previous works were called "Neural Textures" but we're going to call ours "Neural Neural Textures" - a subtype of neural textures.
-
-		% Using neural neural textures, we can encode features directly onto the surfaces of the 3d objects in a scene, which the image translation module uses to maintain visual consistency between states and viewpoints.
-		Instead of feeding a scene $s$ directly into the image translator $\Tab$, we first apply learnable textures $\psi$ to its surfaces as shown in figure \ref{fig:main_diagram}.
-		Previous works called these learnable textures ``neural textures'', and were parametrized by a discrete grid of differentiable texels. 
-		% In contrast, we call our learnable textures ``neural nerual textures'', becuase our textures are a type of neural texture that is parametrized continuously over UV space using a neural fourier feature network.
-		In contrast, we call our learnable textures ``neural nerual textures'', becuase our textures are parametrized continuously over UV space using a neural network.
-		Like previous works, our neural textures $\psi\toL$ are learned jointly with our image translator $T$.
-
-		These neural neural textures are represented implicitly by a neural network that maps UV values to RGB values. %, and are used to obtain projections $\pi$ from 3d scenes $s$.
-		For each texture $\psi^i \in \psi\toL$, 
-		\begin{equation}
-			\psi^i: (u,v) \in\real^2 \rightarrow (r,g,b) \in\real^3 % \eqand 
-		\end{equation}
-
-		Given a scene $s$, we obtain projection $\pi$ by applying a texture $\psi^i \in \psi\toL$ to every pixel $(u,v,l) \in s$ individually, where texture index $i=I(l)$ is decided by the label value $l$ of that scene pixel.
-		% Each pixel in the resulting projection $rgb\in\pi$ is the result of selecting a texture index $i$ based on the rank of label value $l$, then applying $\psi^i$ to the $u,v$ values.
-		\begin{equation}
-			% \pi=\psi\toL(s) \eqand rgb \in \pi = \psi^i(uv)
-			% \pi_{n,c,x,y}=\psi^i(s_{n,1,x,y},s_{n,2,x,y}) \eqwhere 1\le n\le N,\ \  1\le c\le 3 ,\ \ 1\le x\le W,\ \ 1\le y\le H,\ \ \text{and} \ \ i=I(s_{n,3,x,y})
-			% \pi_{n,c,x,y}=\psi^i(s_{n,1,x,y},s_{n,2,x,y})
-			\pi_{[x,y]}=\psi^i(s_{[x,y,1]},s_{[x,y,2]})
-		\end{equation}
-		% where $1\le n\le N,\ \ 1\le c\le 3 ,\ \ 1\le x\le W,\ \ 1\le y\le H,\ \ \text{and} \ \ i=I(s_{n,3,x,y})$.
-		% where $n\in \{1\dots N\},\ \ c\in \{1\dots 3\} ,\ x\in \{1\dots W\},\ y\in \{1\dots H\},\ \ \text{and} \ \ i=I(s_{n,3,x,y})$.
-		where $ x\in \{1\dots W\},\ y\in \{1\dots H\}$, and texture index $i=I(l)$ where $l=s_{[x,y,3]}$ and subscript means multidimensional indexing.
-
-		%DISCARDED TEXT:
-		% A particular neural texture $\psi^i$ uses maps $uv \rightarrow rgb$.
-Similarly, the set of textures $\psi_{1\dots L}$ maps uvl values to rgb values: $\psi_{1\dots L}(uvl)=\psi_l(uv)$ where $uvl$ is the concatenation of a $uv$ vector with a label $l \in 1\dots L$.
-		% TRITON's neural neural texture module lets it create features on the surfaces of objects, and thus take advantage of 3d geometric priors.
-
-				% The neural texture applied to a particular scene pixel $uvl \in s$ is multiplexed by $l$, and the respective output pixel $rgb \in \pi = \psi_luv$. 
-				% Texture projections $\pi$ are obatined by applying a set of $L$ different neural neural textures $\psi\toL$ to a UVL scene $s$ pixelwise.
-				% [[IMPORTANT: THIS IS TECHNICALLY INCORRECT AS l IS A VALUE BETWEEN 0 and 1]]
-
-				% where $i\in[1,L]\cap\mathbb{Z}$ is the rank of $l$
-				% When applied to a UVL scene, it is applied to each $uvl \in s$ pixel individually where every pixel $rgb \in \pi = \psi$ 
-				%What is it...then how do we use it...
-				% (as the 2nd sentence)
-				% Given a 3D scene $s$, we apply $\psi\toL$ to each UV to obtain RGB surface values...
-				% project learnable RGB textures $\psi\toL$ to their surfaces to obtain projection $\pi$. 
-				% 			Neural Neural Textures $\psi\toLuv$: Given an input scene $s$ depicting 3d objects with labels $1\dots L$, we apply a function on their surface's UV values with neural textures $\psi\toL$ to obtain projection $\pi$.
-
-				% \begin{equation}
-					% \pi=\psi\toL(s)
-				% \end{equation}
-				%
-
-		%THIS WILL BE REPLACED BY SUMMARY SECTION
-		% 	Given a batch of $N$ UVL Scenes $s_{1\dots B}$ with $L$ different label values, we project $L$ different neural textures $\psi_{1\dots L}$ onto that scene; obtaining projections $\pi_{1\dots B}$.
-This projection mechanism is illustrated in figure \ref{fig:uvl_explanation}.
-
-		% Each neural texture $\psi^i$ is a function consisting of two components: a multi-layer perceptron $M^i$ and a static set of 256 random spatial frequencies $f_{1...256}$. 
-		% Given a two-dimensional $uv$ vector, the spatial frequencies are used to generate a high dimensional embedding used as input for the MLP.
-		% \begin{equation}
-		% 		\psi^i(uv) = 
-		% 		\
-		% 		M^i\left(\left[
-		% 			\sin \left( f_1     \cdot \left(u,v\right) \right) , \ 
-		% 			\cos \left( f_1     \cdot \left(u,v\right) \right) , \ 
-		% 			% \sin \left( f_2     \cdot \left(u,v\right) \right) , \ 
-		% 			% \cos \left( f_2     \cdot \left(u,v\right) \right) , \ 
-		% 			\dots \ 
-		% 			\sin \left( f_{256} \cdot \left(u,v\right) \right) , \ 
-		% 			\cos \left( f_{256} \cdot \left(u,v\right) \right)  \ 
-		% 		\right]\right)
-		% \end{equation}
-		% where $uv$ and $f^i \in N_{ormal}(\mu=0,\ \sigma=10)$ are two dimensional vectors,
-		%  $f^i uv$ represents their dot product, 
-		% %  $rgb$ represents a 3d color vector,
-		%  and $M^i$ maps a $uv$ embedding to an $rgb$ color value:
-		%  $M^i: \real^{256} \rightarrow \real^3$.
-		% Note that there is nothing special about 256 or 10: these hyperparameter values just happen to work nicely.
-
-		We now discuss the implementation of our neural neural networks $\psi\toL$.
-		Each neural neural texture $\psi^i$ is a function consisting of two components: a multi-layer perceptron $M^i$ and a static set of 256 random spatial frequencies $f_{1...256} \in \real ^ {256 \times 2}$.
-		Given a two-dimensional $(u,v)$ vector, the spatial frequencies are used to generate a high dimensional embedding of $(u,v)$ as input for $M^i$, where $M^i$ is a function $\real^{256} \to \real^{3}$ mapping that embedding to an $(r,g,b)$ color value:
-		\begin{equation}
-				\psi^i(u,v) = 
-				\
-				% M^i(
-				% 	\sin( f_1     uv  ) , \ 
-				% 	\cos( f_1     uv  ) , \ 
-				% 	\sin( f_2     uv  ) , \ 
-				% 	\cos( f_2     uv  ) , \ 
-				% 	\dots \ 
-				% 	\sin( f_{256} uv  ) , \ 
-				% 	\cos( f_{256} uv  )  \ 
-				% )
-				M^i(
-					\sin( g_1      ) , \ 
-					\cos( g_1      ) , \ 
-					\sin( g_2      ) , \ 
-					\cos( g_2      ) , \ 
-					\dots \ 
-					\sin( g_{256}  ) , \ 
-					\cos( g_{256}  )  \ 
-				)
-		\end{equation}
-		where $g_k=f_k\cdot(u,v)$
-		% , $f^i \in N_{ormal}(\mu=0,\ \sigma=10)$ is a two dimensional random gaussian vector,
-		, $f_k \in \mathcal{N}(\mu=0,\ \sigma=10)$ is a two dimensional random gaussian vector,
-		and $\cdot$ is the dot product operator.
-		%  $rgb$ represents a 3d color vector,
-		% :
-		% $M^i: \real^{256} \rightarrow \real^3$.
-		Note that there is nothing special about 256 or 10: these hyperparameter values just happen to work nicely.
-
-		%Squeeze this down - we don't need explanations for why, that can go in the appendix.
-		In practice, we found that TRITON learns faster and more stably with our neural neural textures than it does with raster neural textures.
-The generated textures are also smoother and less noisy.
-See the supplementary material for more details.
-		% The trained fourier-feature textures also exhibit less noise than its raster counterparts. 
-		% We think this is because they do not suffer as much. 
-		% It cfrom aliasing artifacts in the UV maps, where the loss gradient might skip over pixels in texture-space when the UVL scene is zoomed out too far or raster resolution is too high. 
-		% Case in point: if you have a raster texture with very high resolution, the loss gradient is less likely to be passed to a given texel because the chance that a given UV value in a scene will be rounded to that pixel's coordinates is very small.
-
-		% UV Map projection
-		% We use an RGB texture, parametrized by an MLP taking fourier features as an input.
-		% We use a separate MLP for every texture.
-
-	\subsection{Image Translation}
-	\label{sec:image_translation}
-
-	% 	\begin{figure}[H]
-	% 		\begin{center}
-	% 			\includegraphics[width=200pt]{../images/module_translator.pdf}
-	% 		\end{center}
-	% 		\caption{
-	% 			A subset of figure \ref{fig:main_diagram} focusing on the image translation module $T$.
-	% 		}
-	% 		% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
-	% 		% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
-	% 		% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
-	% 		\label{fig:module_translator}
-	% 	\end{figure}
-
-		% TO PUT IN FORMULATION:
-		% The simulation domain A (UVL maps concatenated to their texture projections) has 6 channels, whereas the real image domain B (photographs) has 3 channels.
-An element of A is $\ppis \in A$ and $p \in B$.
-		% $p \in B$ is a batch of real photos,
-		% and $\ppis\in A$ is a batch of simulated projection/uvl scene concatenations.
-
-		% TODO: Why doesn't citep work? The references don't show the authors names...it used to work...did I mess up example.bib?
-
-		% TODO: Get rid of the variable "C" and replace it with $\ppis$
-
-		% TODO: Is l2 loss capitalized or lower case?
-
-		%_i
-		% Our image translation module $T$ is bidirectional: $\Tab$ translates images from domain A to domain B, and $\Tba$ translates images from domain B to domain A.
-		Our image translation module $T$ is bidirectional: $\Tab$ translates sim to real (aka domain A to domain B), and $\Tba$ translates real to sim (aka domain B to domain A).
-		\begin{equation}
-			\ph=\Tab(\pis)  \eqand  \ppish=\Tba(p)
-		\end{equation}
-
-		$T$ is based on the image translation module used in \citet{surgical_video_translation}, which is a based on a variant \cite{surgical_image_translation} of MUNIT \cite{munit}. 
-		$T$ uses the same network architectures as MUNIT, and also inherits its adversarial losses $\ell_{adv}$, cycle consistency losses $\ell_{cyc}$ and reconstruction losses $\ell_{rec}$.
-		The main differences between our image translation model and MUNIT are that we use a different image similarity loss $\Omega$, and like \citet[]{surgical_image_translation} and \citet[]{surgical_video_translation} our style code is fixed (making it unimodal) and noise is injected into the latent codes during training to prevent overfitting.
-		During inference however, this intermediate noise is removed and our image translation module is completely determinstic. 
-		% Apart from these differences, our image translation module has the same loss formulations and generator/encoder/discriminator network architectures as MUNIT.
-
-		MUNIT translates images by encoding both domains $A$ and $B$ into a common latent space, then decoding them into their respective domains  $B$ and $A$.
-		In our translation module, we define fake photos $\ph = \Tab(\pis) = G_B(E_A(\pis))$ and fake projection/uvl scenes $\ppish = \Tba(p) = G_A(E_B(p))$
-			where $E_A, E_B, G_A, G_B$ are encoders and generators for domains A and B respectively.
-		% We also define the outputs of these translators as fake photos $\hat{p} = T_{A\rightarrow B}(\pis)$ and fake projection/uvl scenes $(\hat{\pi},\hat{s}) = T_{A\rightarrow B}(\pis)$.
-
-		% TODO: Choose one of the three equation representations. Which is best? The next paragraph will look less ugly when the equations are shorter.
-
-		% For our purposes, MS-SSIM is a metric that measures the similarity of two BCHW tensors on a scale from 0 to 1.
-		% Given two tensors $x$ and $y$, their similarity loss is $\mu\left((x-y)^2\right) - \text{msssim}(x,y)$. 
-		We define an image similarity loss $\similar$ between two images $x,y$ that returns a score between 0 and 1, where 0 means perfect similarity:
-		\begin{equation}
-			\similar(x,y) = L_2(x,y)-\msssim(x,y) 
-		\end{equation}
-		This function combines mean pixel-wise $L_2$ distance (used in MUNIT) with multi-scale structural image similarity $\msssim$, introduced in \citep{msssim}.
-Note that this loss can also be applied to the latent representations obtained by $E_A$ and $E_B$, because like images those tensors are also three dimensional.
-
-		% To ensure cycle consistency, we have an image similarity loss $\ell_{cyc}$ to ensure
-		% % $c \approx G_A(E_B(G_B(E_A(\pis)))) = T_{B\rightarrow A}(T_{A\rightarrow B}(\pis)) = T_{B\rightarrow A}(\hat{p})$
-		% $\ppis \approx T_{B\rightarrow A}(\hat{p})$
-		% and vice versa
-		% % $p \approx G_B(E_A(G_A(E_B(p)))) = T_{A\rightarrow B}(T_{B\rightarrow A}(\pis)) = T_{A\rightarrow B}(\hat{c}) = T_{A\rightarrow B}(\hat{\pi},\hat{s})$. 
-		% $p \approx T_{A\rightarrow B}(\hat{\pi},\hat{s})$.
-		% %I only want to use one of the two representations; either using T_AB or GA(EB) etc. Which one should I use?
-		% We also impose an image similarity loss $\ell_{rec}$ to ensure that $\ppis \approx G_A(E_A\ppis)$ and $p \approx G_B(E_B(p))$, which is effectively an autoencoder loss. 
-		% In addition, we also have content similarity loss $ \ell_{con}$ to make 
-		% $E_A(\pis) \approx E_B(\ph)$ and $E_A(p) \approx E_A(\pish)$.
-		% % $E_A(\pis) \approx E_B(\Tab(\pis))$ and $E_A(p) \approx E_A(\Tba(p))$.
-
-		We have cycle consistency loss ${\ell_{cyc}  =  \similar\left(\ppis,T_{B\rightarrow A}\left(\hat{p}\right)\right)  +  \similar\left(p,T_{A\rightarrow B}\left(\hat{\pi},\hat{s}\right)\right)}$
-		% $\ppis \approx T_{B\rightarrow A}(\hat{p})$
-		% and vice versa
-		% $p \approx T_{A\rightarrow B}(\hat{\pi},\hat{s})$.
-		, similarity loss ${\ell_{rec} = \similar\left(\ppis,G_A\left(E_A\ppis\right)\right) + \similar\left(p,G_B\left(E_B\left(p\right)\right)\right)}$
-		%  to ensure that $\ppis \approx G_A(E_A\ppis)$ and $p \approx G_B(E_B(p))$, 
-			(which is effectively an autoencoder loss),   
-		and content similarity loss ${ \ell_{con} = \similar\left(E_A\left(\pis\right), E_B\left(\ph\right) \right)    +   \similar\left(E_A\left(p\right),E_A\left(\pish\right)\right) }$.
-		% $E_A(\pis) \approx E_B(\ph)$ and $E_A(p) \approx E_A(\pish)$.
-		We also have adversarial losses $\ell_{adv}$ that come from two discriminators $D_A$ and $D_B$, targeting domains A and B respectively, using the LS-GAN loss introduced in \citet{lsgan}. 
-		In total, our image translator loss is $\ell_T=\ell_{cyc}+\ell_{rec}+\ell_{con}+\ell_{adv}$.
-
-		% PRETTIEST BUT TOO MUCH SPACE
-		% 		Inheriting from MUNIT, we have three losses: cycle consistency loss $\ell_{cyc}$, content similarity loss $\ell_{con}$, and reconstruction loss $\ell_{rec}$ which functions as an autoencoder loss.
-		% 		\begin{eqnarray}
-		% \begin{center}
-		% 	\begin{align}
-
-		% 		\ell_{cyc}  =  \similar\left(\ppis,T_{B\rightarrow A}\left(\hat{p}\right)\right)  +  \similar\left(p,T_{A\rightarrow B}\left(\hat{\pi},\hat{s}\right)\right)
-
-		% 		\ell_{con} = \similar\left(E_A\left(\pis\right), E_B\left(\ph\right) \right)    +   \similar\left(E_A\left(p\right),E_A\left(\pish\right)\right)
-
-		% 		\ell_{rec} = \similar\left(\ppis,G_A\left(E_A\ppis\right)\right) + \similar\left(p,G_B\left(E_B\left(p\right)\right)\right)
-		% 	\end{align}
-		% \end{center}
-		% 		\end{eqnarray}
-
-		% In total, the loss for the image translator module $T$ is $\ell_T=\ell_{cyc}+\ell_{rec}+\ell_{con}+\ell_{adv}$.
-
-		% % NOTE: THe other paper \citep{surgical_video_translation} didn't do into this much detail; instead putting most of these losses in teh appendix.
-I think we can cut this down?
-I'll check with michael first...right now I'll include everything.
-
-	\subsection{Unprojection Consistency Loss}
-	\label{sec:unprojection_consistency_loss}
-
-		\begin{figure}[thbp]
-		    \vspace{-10pt}
-			\begin{center}
-				\includegraphics[width=.8\textwidth]{../images/unprojection_consistency_loss_without_reprojection.pdf}
-			\end{center}
-			\vspace{-5pt}
-			\caption{
-				This is the unprojection consistency loss used in figure \ref{fig:main_diagram}.
-				The Unprojection Mean and Reprojection nodes are not used in any losses, and help to illustrate the next section \ref{sec:texture_realism_loss}.
-				% After calculating fake photos $\hat{p}_{1...B}$ from UVL scenes $s_{1...B}$ as seen in figure \ref{fig:main_diagram}, 
-				% we can unproject fake photos $\hat{p}_{1...B}$ back into texture space to obtain $u_{1...B,\ 1...L}$ .
-				% If the fake photos display consistent textures along their 3d surfaces, then the unprojected textures should be similar.
-				% We can measure this similarity by taking the per-channel standard deviation of these unprojections, aka $\sigma(u)$, then averaging the result.
-				% When the fake photos display similar surfaces, the unprojections will be similar making the unprojection consistency loss low.
-				% Additionally, we can also calculate the average unprojection, which is useful for visualization purposes (it will look blurry if $\hat{p}$ is inconsistent).
-			}
-			\label{fig:unprojection_consistency_loss}
-		\end{figure}
-
-		To keep the object surfaces consistent, we impose a pixel-wise ``unprojection consistency loss'' by unprojecting surfaces in fake photos back into the common texture space.
-% 		\begin{equation}
-% 			u\toNL=\text{unproject}(\ph\toN,s\toN)   \eqand  \lUC \Rightarrow u_1 \approx u_2 \dots \approx u_N
-% 		\end{equation}
-        Given a UVL scene $s$ and its respective fake photo $\ph$, the unprojection $\unprojection$ is obtained from assigning $(r,g,b)$ values at each pixel location $(x, y)$ of $\ph$ to its corresponding $(u, v, l)$ coordinates according to $s$.
-        % That is, we convert $s$ and $\ph$ to a key-value dictionary where the key is $(u,v,l)$ and the value is $(r,g,b)$, and such dictionary is $\unprojection$.
-        For simplicity, we note
-        \begin{equation}
-            	\unprojection_{[u,v]}^{l}=\expectation\ph_{[x,y]} \quad s.t.~ (u,v,l) = s_{[x,y]},
-        \end{equation}
-        where the expectation $\mathbb{E}$ means we aggregate multiple $(r,g,b)$ vectors being assigned to the same $(u,v,l)$ location by averaging them. 
-        In practice, $(u,v,l)$ are real numbers between $[0,1]$, where as each $\unprojection$ have to be rasterized, i.e represented by $L$ $(D\times D\times 3)$ images, where $L$ is the number of labels and $D\times D$ is the resolution of the unprojection.
-Therefore, we discretize and scale corresponding $(u,v,l)$ to integers so that each $(r,g,b)$ vector will be assigned to a pixel on $\unprojection$.
-For the exact implementation, please see our supplementary material.
-
-        We obtain $N$ unprojections $\{\unprojection_{[u,v]}^{l,i}\}_{i=1}^{N}$ from a batch of $N$ UVL scenes and fake photos.
-The unprojection consistency loss is defined as the per pixel-channel standard deviation of $\unprojection$ over the batch
-        \begin{equation}
-            \ell_{UC} = \frac{1}{L\times D\times D\times 3}\sum_{l,u,v,c}\sigma(\{\unprojection^{l,i}_{[u,v,c]}\}_{i=1}^{N}),
-        \end{equation}
-        where $\sigma(\cdot)$ stands for the variance function and $c \in \{1\dots 3\}$ is the channel index of $\unprojection$.
-		%We sample a random batch of UVL scenes $S\toN$, and translate them into $\ph\toN$.
-		%Using geometric knowledge of the scene encoded in $S\toN$, we individually unproject each $\ph^i \in \ph\toN$ back into texture space, to obtain $N$ sets of $L$ unprojected textures $u\toNL$.
-		%We then use the per-pixel, batch-wise standard deviation of the unprojections as unprojection consistency loss $\lUC = \sigma(u\toNL)\toL$.
-		%This loss observes how different these unprojections are from one another, and thus how different the object surfaces appear between translations. 
-		We minimize $\lUC$ to encourage unprojections to be consistent across the batch.
-Intuitively, if $\lUC$ were $0$, it would mean the object surfaces in translations $\ph$ appear exactly the same in every scene.
-In addition, we call the mean of unprojections $\mu(\{\unprojection^{(l,i)}\}_{i=1}^N)$ as ``Recovered Textures'', visualzed in Figure~\ref{fig:first_diagram} and \ref{fig:unprojection_consistency_loss}.
-
-	%MOVE THIS TO APPENDIX
-	% 	This loss is a fairly intuitive and effective way to maintain surface consistency. There are some caveats, howe/ver.
-	% 	In order to produce a standard deviation greater than $0$, we must have a batch size greater than $1$.
-	% 	Furthermore, environments that rarely show a particular region of a surface will rarely have $\lUC$ applied to that region because they're unlikely to show up twice in the same batch.
-	% 	For this reason, $\lUC$ is most useful with large batch sizes.% because observing the same surface in multiple elements of a batch becomes more likely as the batch size increases. 
-	% 	But because video memory limits our batch sizes, first-person environments might be more of a challenge for $\lUC$ - particularly when exploring multiple rooms (a task we haven't done though - should I mention this?)
-
-		% To michael: Should we mention these caveats in this section, or mention them in the texture realism loss section? That section addresses all of these issues...
-
-		% Also, you have to get lucky - two scene pictures have to show the same side of a cube for example. First person scenarios would be even worse.
-
-		% %Unabbreviated
-		% \begin{equation}
-		% 	\unprojection_{c,U,V}^{n,i}=\expectation\ph_{c,x,y}^n 
-		% 	\eqand \bar{\unprojection}^i_{c,u,v}   =   
-		% 		\frac{1}{N} \lsum_{n=1}^N\unprojection^{n,i}_{c,u,v} 
-		% 	\eqand 
-		% 	\lUC=\frac{\lsum_{i=1}^L\lsum_{c=1}^3\lsum_{U=1}^{128}\lsum_{V=1}^{128}
-		% 	\sqrt[]{\frac{1}{N}\lsum_{n=1}^N\left(\bar{\unprojection}^i_{c,u,v}-\unprojection^{i,n}_{c,U,V}\right)^2}}
-		% 	{3\cdot128\cdot128\cdot L}
-		% \end{equation}
-		%
-		%Abbreviated
-		%To formally define $\lUC$ we define unprojections $\unprojection^{1...N,1...L}$ and mean unprojections (aka recovered textures) $\bar{\unprojection}^{1...L}$ 
-		%with each $\unprojection^{n,i}\in\real^{3\times128\times128}$:
-% 		\begin{equation}
-% 			\unprojection_{U,V}^{n,i}=\expectation\ph_{x,y}^n 
-% 			\eqand \bar{\unprojection}^i_{u,v}   =   
-% 				\frac{1}{N} \lsum_n\unprojection^{n,i}_{u,v} 
-% 			\eqand 
-% 			%\lUC=\frac{\lsum_{i,U,V}
-% 			%\sqrt[]{\frac{1}{N}\lsum_n\left(\bar{\unprojection}^i_{u,v}-\unprojection^{i,n}_{U,V}\right)^2}}
-% 			%{128\cdot128\cdot L}
-% 			\lUC=\mathbb{E}\left[
-% 			\sqrt[]{\frac{1}{N}\lsum_n\left(\bar{\unprojection}^i_{u,v}-\unprojection^{i,n}_{U,V}\right)^2} \right]
-% 		\end{equation}
-% 		where $U=\lfloor128u\rfloor$ and $V=\lfloor128v\rfloor$ and $i=I(l)$ with
-% 		%  $(u,v,l)=s^n_{1...3,x,y}$
-% 		$u=s^n_{1,x,y}$, $v=s^n_{2,x,y}$, $l=s^n_{3,x,y}$
-% 		for all 
-% 		$n \in \{1...N\}$ , 
-% 		$i \in \{1...L\}$ , 
-% 		$x \in \{1...W\}$ , 
-% 		$y \in \{1...H\}$ , 
-% 		$U \in \{1...128\}$ , 
-% 		$V \in \{1...128\}$.
-
-	\subsection{Texture Realism Loss}
-	\label{sec:texture_realism_loss}
-        \vspace{-7pt}
-		\begin{figure}[thbp]
-			\begin{center}
-				\includegraphics[width=250pt]{../images/texture_realism_ablation.pdf}
-			\end{center}
-			\vspace{-5pt}
-			\caption{
-				The neural texture looks more realistic with texture realism loss enabled.
-Note that the blocks show different letters because of different initializations and the symmetry of a cube - both solutions are valid texture assignments.
-			}
-			\vspace{-10pt}
-			\label{fig:texture_realism_ablation}
-		\end{figure}
-
-		To encourage the neural textures to look as realistic as possible, we try to make the projections look like the final output by introducing a ``texture realism'' loss $\lTR$. 
-		$\lTR$ is an image similarity loss that makes $\pi$ look like its translation $\hat{p}$.
-		% As it turns out, $\lTR$ is sufficiently powerful loss to generate surface-consistent translations even without $\lUC$, although the results are better when both losses are used.
-		% This loss forces the neural textures to look realistic, instead of allowing them to have arbitrary colors.
-		% In other words, $\lTR$ makes the neural textures more realistic by making their projections look more realistic, like the final outputs.
-		\begin{equation}
-			\lTR = \similar(\pi,\ph)
-		\end{equation}
-		% So far, we've taken an image translator $T$ and added neural textures $\psi$ and a surface consistency constraint $\lUC$. 
-		% If we wanted to, could stop here - those formulations are sufficient to produce consistent sim-to-real translations.
-		% However, we can improve this further.
-		% Up until now we have not put any constraints on this neural texture. 
-		Without $\lTR$, $\psi$ can look wildly different each time you train it.
-		As seen in the top row of figure \ref{fig:texture_realism_ablation}, the neural texture looks very unrealistic – the colors are completely arbitrary.
-		After adding $\lTR$ though, $\pih \approx \ph$, and $\psi$ to represents the albedo of the surfaces in the scene.
-		% The image similarity loss used in $\lTR$ is calculated the same way image similarity losses are calculated in section \ref{sec:image_translation}: L2 loss minus MSSSIM.
-
-		As it turns out, we can achieve surface-consistent translations just using $\lTR$, without $\lUC$.
-		The the reverse is also true: $\lTR$ is sufficient to ensure surface consistency without $\lUC$.
-		Using both, however, yields better results than either loss alone. 
-		% For an explanation of why this is the case, see the appendix \ref{sec:texture_realism_theory}.
-
-		With that said, there are some advantages to using $\lTR$ alone: when just using $\lTR$ you can use batch sizes as small as $N=1$, allowing you to save video memory. 
-		Using $\lTR$ is also more numerically stable, as you no longer have to worry about whether the same surfaces are seen across multiple scenes in a batch as you would with $\lUC$.
-
-		% We introduce a new loss, called texture realism loss that fixes this: $\lTR$ is an image similarity loss that encourages $\pi \approx \ph$.
-		% This loss forces the neural texture to approximate the albedo of the surfaces in a scene.
-
-		% These images could be regularized so that they're the same every time.
-		% 
-		% To do this we put a penalty on the latent texture that makes it $\pi$ look like its translation $\hat{p}$. 
-		% 
-		% We use l2 and msssim losses to do this.
-		% 
-		% This helps improve the translations.
-		% 
-		% There are some advantages over unprojection consistency though: 
-		% smaller batch sizes (even a batch size of 1, which UC cant do),
-		% you don't have to get lucky (the more chaotic, or even the more zoomed in a dataset becomes the less likely there is to be any collisions)
-
-	%===============================================================================
-
-\section{Experiments}\label{sec:results}
-
-\subsection{Datasets}
-Here we detail the datasets used in our experiments. 
-Every dataset has two sets of images: UVL scenes and real photographs. They are all unpaired, and have RGB values ranging from 0 to 1.
-
-The first dataset to mention is the three-block dataset.  
-It has 300 photos and 2000 UVL scenes.
-It features a table with three alphabet blocks on a table, which are randomly translated along the X and Y axes and rotated randomly along the Z axis.
-Each photograph features these three cubes with a random position and rotation.
-
-[[Insert photographs and UVL maps here; a digram showing each dataset we describe here and 1 or two samples of each domain in each dataset]]
-
-% In this paper, we'll mostly focus on a hand-collected dataset that involves three alphabet blocks that are moved across a table.
-% Alphabet blocks were chosen because they all have the same geometry (a cube), but have very distinct semantic textures that will make temporal inconsistency obvious to the human eye.
-% This dataset is analogous to data that would be collected for a third-person robotic grasping task.
-% However, other objects (such as cans of soda, apples, cloves of garlic, etc) are also for generating other results in this paper.
-((TODO: Detail the five object tests and five cube tests and other stuff like shiny cans etc)).
-
-% There are two components to this dataset: Simulated data in the form of UVL scenes, and photographs.
-% The camera in the simulation is positioned in approximately the same place as the real camera, with approximately the same field of view.
-% In both domains of this dataset, the camera never moves. Instead, the objects are randomly positioned and rotated on the table.
-% In both the simulation and in real life, these objects are randomly translated along the x and y-axis of the table, as well as rotated on the z-axis.
-
-% There are 200 photographs in this dataset, and they are recorded as RGB jpg images.
-% There are 3000 synthetic images in this dataset, in the form of UVL images.
-% These UVL images are also encoded as RGB images, but provide information about the geometry of a scene.
-% UVL images are composed of both a UV map and a label map and are summarized in figure \ref{fig:uvl_explanation}.
-% To avoid positional rounding errors, UVL images are encoded as EXR files: an image format that supports floating-point values.
-
-% The pixels in a UVL image are visualizable in RGB space because, like RGB images, each pixel is a vector with 3 values.
-The first two channels, U and V, are floating point values between 0 and 1.
-The L channel is also a floating point value between 0 and 1, it has a second meaning.
-There are only a finite number of label values (corresponding to the number of learnable textures).
-The rank of a particular L value is used to index these textures.
-
-% In the three-cube dataset we have 4 textures, and UVL scenes contain label values $l \in [\frac{0}{3}, \frac{1}{3},\frac{2}{3}, \frac{3}{3}]$.
-A pixel in a UVL scene $l=\frac{2}{3}$ will get indexed to the third texture, because $\frac{2}{3}$ is the third smallest label value.
-
-% %===============================================================================
-
-% Domain A and B
-% p hat
-% s hat
-
-\subsection{Qualitative Evaluation Results}
-We show qualitative evaluation results 
-\begin{figure}[thbp]
-    \vspace{-30pt}
-	\begin{center}
-		\includegraphics[width=\textwidth]{../images/frame_inconsistency_diagram.pdf}
-	\end{center}
-	% Each outline color corresponds to the same cube.
-	% The same cubes are marked with the same colored outlines across all photos.
-	% For the same cube, we expect to see the same number on the top of the cube regardless of its placement.
-	\caption{
-		Each row of images shows a different random placement of objects in the scene.
-		Each column of images is a different image translation algorithm.
-		The same cube is marked with the same color outline across all photos.
-		TRITON is consistent: for example, the cube outlined as yellow always has an 8 on the top.
-		Meanwhile, CycleGan for example shows a 4 on the top of that cube in the top two rows, but an 8 and a 7 in the next two rows.
-		Because of the symmetry of the cubes, and the unsupervised training, it is arbitrary which synthetic cube gets which symbol after training - but whatever it chooses, it should be consistent between placements.
-		CUT and CycleGan are not consistent, while TRITON is.
-		% TODO: Update the images in this to have the latest training iteration...
-		}
-		\label{fig:frame_inconsistency_diagram}
-	\end{figure}
-
-    \begin{figure}[thbp]
-    	\begin{center}
-    		\includegraphics[width=\textwidth]{../images/blurry_recovery.pdf}
-    	\end{center}
-    	\caption{
-    		The recovered texture is more crisp when we have surface consistency losses $\lUC$ and $\lTR$ enabled.
-    		[[TODO: include cyclegan and other algorithms here]]
-    	}
-    	\label{fig:blurry_recovery}
-    \end{figure}
-	% 	Alphabet Three							
-	% 	Masked				Unmasked			
-	% 	LPIPS		L2		LPIPS		L2	
-	% 	Sync	Unsync	Sync	Unsync	Sync	Unsync	Sync	Unsync
-	% Pure MUNIT	0.0437	0.0373	0.00500	0.00490	0.434	0.402	0.0425	0.0392
-	% Texture Only	0.0442	0.0386	0.00586	0.00589	0.285	0.255	0.0364	0.0310
-	% Texture Reality	0.0286	0.0267	0.00479	0.00478	0.117	0.1157	0.0123	0.0122
-	% CycleGAN			TODO: Sync with respect to L2, so sync is always ≥ unsync					
-	% CUT				TODO: Google Synthetic Dataset
-
-\subsection{Ground Truth Comaprison}
-
-	%CREATED WITH https://www.tablesgenerator.com/# -- this website is wonderful!!
-\begin{table}[thbp]
-    \caption{Ground truth comparison evaluations for TRITON. Masked and Unmasked mean xxxxxx. Sync and Unsync mean xxxxx. L2 is xxxx LPIPS is xxxxxx. TRITON is xxxxxxx. }
-	\resizebox{\textwidth}{!}{
-        \begin{tabular}{lcccccccc}
-        \toprule
-        & \multicolumn{4}{c}{Masked} & \multicolumn{4}{c}{Unmasked}  \\
-        \cmidrule(lr){2-5} \cmidrule(lr){6-9} & \multicolumn{2}{c}{LPIPS ($\times 10^{-1}$) $\downarrow$} & \multicolumn{2}{c}{L2 ($\times 10^{-2}$) $\downarrow$}  & \multicolumn{2}{c}{LPIPS ($\times 10^{-1}$) $\downarrow$}  & \multicolumn{2}{c}{L2 ($\times 10^{-2}$) $\downarrow$}   \\
-        \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
-        Algorithm  & Sync    & Unsync   & Sync      & Unsync    & Sync   & Unsync  & Sync     & Unsync \\
-        \midrule
-        TRITON w/o $\psi, \lUC, \lTR$ & 0.437                        & 0.373                        & 0.500                        & 0.490                        & 4.34                        & 4.02                        & 4.25                        & 3.92                        \\
-        TRITON w/o $\lUC, \lTR$       & 0.442                        & 0.386                        & 0.586                        & 0.589                        & 2.85                        & 2.55                        & 3.64                        & 3.10                        \\
-        \textbf{TRITON}                        & \textbf{0.286}               & \textbf{0.267}               & \textbf{0.479}               & \textbf{0.478}               & \textbf{1.17}               & \textbf{1.16}              & \textbf{1.23}               & \textbf{1.22}               \\
-        \midrule
-        CycleGAN & 0.450 & 0.379 &  0.559 &  0.554 &  6.02 &  5.93 &  4.25 &  4.23 \\
-        CUT                           & 0.469                        & 0.382                        & 0.553                        & 0.526                        & 5.40                        & 5.34                        & 6.37                        & 6.29\\
-        \bottomrule
-        \end{tabular}
-	}
-\end{table}
-
-[[Figures: Show these results and explain why we have a mask on some of them]]
-
-TODO: Explain what sync and unsync mean, retrieve the results for CycleGAN and CUT
-
-\subsection{Sim2real Transfer for Robot Learning}
-\begin{figure}[thbp]
-    \centering
-    \vspace{-10pt}
-    \includegraphics[width=\textwidth]{images/sim2real_framework.pdf}
-    \vspace{-20pt}
-    \caption{Sim2real framework of using TRITON.
-We evaluate in two settings: Seen and Unseen.
-In Unseen, we use a new camera viewpoint to train and evaluate the policy.
-This new viewpoint is not used for training TRITON.
-}
-    \vspace{-5pt}
-    \label{fig:sim2realframework}
-\end{figure}
-In this section we demonstrate how TRITON improves sim2real transfer for robot learning.
-To do this, we first train TRITON on a dataset consist of unpaired UVL scenes from simulator and photos from the real robot.
-After that, we train the robot policy in the simulator only.
-The input of the policy is the fake photo $\hat{p}$ translated from the simulated UVL scene using TRITON's translator $T_{A\to B}$.
-Finally, the trained policy is evaluated on the real robot, taking real photos $p$ as input.
-Ideally, a good image translation model leads to less gap between $p$ and $\hat{p}$, so that the policy trained on synthesized photos will transfer to real domain seamlessly.
-
-\paragraph{Task} We use a robot pose imitation task for our experiments.
-Given the input of a photo of real robot pose, the policy outputs robot controls to replicate that target pose.
-We measure the angular error between the replicated and target poses as our evaluation metric:$\sqrt{\sum_{j} (\hat{a}_j - a_j)^2}$,
-where $\hat{a}_j$ and $a_j$ are replicated and target joint angle respectively, and $j$ is the joint index.
-We use an xArm robot which has 7 joints.
-Moreover, we attach patterns and tapes on it to make its texture complex.
-
-\paragraph{Robot policy and Baselines}
-Since sim2real provides abundant training data using the simulator, we use behavior cloning which is enough to train a good robot policy.
-The policy is implemented by CNN~\cite{dqn}.
-We compare TRITON against two baseline image translation methods: CycleGAN and CUT, by replacing TRITON with each baseline method respectively in the above pipeline.
-The robot policy is the same for all methods.
-
-\paragraph{Evaluation Settings} We introduce two main evaluation settings, \textbf{Seen} and \textbf{Unseen}.
-In \textbf{Seen} setting, the policy is trained and tested using the same camera viewpoint that is used in training image translator.
-Whereas in \textbf{Unseen} setting, we introduce a camera at a new viewpoint for training and testing the policy.
-That is, the image translator has to generate the fake photos out of its training distribution (seen camera viewpoints), which becomes a challenging for the translator.
-We also vary input image resolution to show the power of photorealistic images in higher resolutions.
-
-\begin{figure}[tbhp]
-    \centering
-    \vspace{-8pt}
-    \includegraphics[width=\textwidth]{images/sim2real_res.pdf}
-    \vspace{-20pt}
-    \caption{Evaluation results of sim2real robot learning.
-We compare TRITON against two baselines and one TRITON variant w/o $\ell_{UC}$ across 3 different input image resolutions.
-TRITON outperforms CycleGAN~\cite{} and CUT~\cite{} consistently across (a) all resolutions and (b) Unseen viewpoints.
-Results in (a) are from Seen setting.
-Results in (b) are from 336x336 resolution.
-}
-    \label{fig:sim2real}
-    \vspace{-8pt}
-\end{figure}
-
-\paragraph{Results}
-In Figure~\ref{fig:sim2real} we show the evaluation results of sim2real transfer.
-Both evaluations show that TRITON outperforms CycleGAN and CUT consistently.
-In Figure~\ref{fig:sim2real}(a), we find that TRITON continuously improves from low to high resolutions due to the ability to generate more photorealistic images compared to the baselines.
-This is because in low resolution (eg.
-$84\times 84$) the details in images are not important, whereas in high resolution ($336\times 336$), artifacts from imperfect translator are clearer and do harm to policy learning.
-From Figure~\ref{fig:sim2real}(b), TRITON outperforms the others in Unseen setting, showing the power of xxxxxx.
-In the comparison against TRITON w/o $\ell_{UC}$, TRITON outperforms this variant consistently except the lowest resolution.
-This again shows the effectiveness of $\ell_{UC}$ to generate photorealistic images, and such high quality images are important in higher resolutions for sim2real transfer.
-
-%===============================================================================
-
-\section{Limitaions}
-\label{sec:Limitations}
-
-Can't handle transparent objects.
-
-A limited number of objects can be learned at once before supervision is necessary with color loss (but there are workarounds).
-
-Takes a long time to train.
-
-%===============================================================================
-
-% \section{Citations} 
-% \label{sec:citations}
-
-% Citations can be made using either \textbackslash citep\{\} or \textbackslash citet\{\}, depending on the appropriateness.
-To avoid the citation moving to the next line, it is often a good practice to replace the space before with a tilde (\~{}) character.
-% Example 1: ``CoRL is the best conference ever~\citep{fourier_feature_networks}.''
-% Example 2: ``\citet{fourier_feature_networks} proved, both theoretically and numerically, that CoRL is the best conference ever.''
-
-%===============================================================================
-
-\clearpage
-% The acknowledgments are automatically included only in the final and preprint versions of the paper.
-\acknowledgments{}
-
-%===============================================================================
-
-\bibliography{example}  % .bib
-
-\clearpage
-
-\section{Appendix} 
-\label{sec:appendix}
-
-    \subsection{Unsorted}
-     	These neural textures are not stored in raster form during training.
-Instead, as illustrated in figure \ref{fig:learnable_textures}, they're paramaterized by pixel-wise fourier feature networks \cite{fourier_feature_networks} that take in UV coordinates and returns RGB colors.
-During inference, however, these textures are rasterized to save both time and video memory.
-
-	\subsection*{Unprojection Recovery Resolution Effect}
+\subsection{Unprojection Consistency Details}
 
@@
 
-	\subsection*{Texture Realism Theory}
-		\label{sec:texture_realism_theory}
-
-		THIS SECTION IS UNPOLISHED, BUT CONTAINS  THE NESSECARY CONTENT.
-		I'll delete this section if you don't think its important enough to keep.
-
-		Texture realism loss equation:
-		$L_{TR}=L_{TR_{l2}}+L_{TR_{msssim}}$
-		where 
-		$L_{TR_{msssim}} = -msssim(\pi,\hat{p})$ and
-		$L_{TR_{l2}} = \frac{
-			\lsum_{i=1}^B {
-			%  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}
-			\left( \pi-\hat{p}  \right)^2
-				} 
-		}
-		{B}$
-
-		There's a good reason for this: it's almost equivalent to unprojection consistency.
-		In fact, it can even be used on its own without unprojection consistency loss (both are sufficient to translate things.)
-
-		(Give theoretical explation)
-		$
-		\ell_{UC} = 
-		\
-		\
-		\mu\left(\sigma\left(u_{1\dots B,\ 1\dots L}\right)_{1 \dots L}\right) = 
-		\sqrt{
-		\frac{
-			\lsum_{i=1}^B {
-				%  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}
-				\left( \hat{p}-\bar{p}  \right)^2
-				} 
-			}
-			{B}
-		}
-		$
-		Using $\bar{p}$ from figure \ref{fig:unprojection_consistency_loss}
-
-		Becuase $\bar{p}$ is created from the average recovered texturs of $\hat{p}$, $\bar{p} \approx \hat{p}$.
-
-		Becuse of texture realism loss, $\pi \approx \hat{p}$.
-
-		Therefore, $\bar{p} \approx \hat{p} \approx \pi$
-
-		% The l2 component of the texture realism loss equation:
-		% $ \
-		% \
-		% \
-		% \
-		% \ \ell_{TR_{l2}}=\sum\limits_{i=1}^B {
-		% 	%  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}
-		% 	\left( \pi-\hat{p}  \right)^2
-		% 	 } 
-		% $
-
-		Substituting one projected texture for another, aka $\pi$ for $\bar{p}$, we get 
-		$ \
-		\
-		\
-		\
-		\ \ell_{TR_{l2}}
-		\approx
-		\frac{\sum\limits_{i=1}^B {
-			%  \mu\left(u_{1\dots B,\ 1\dots L}\right)_{1...L}
-			\left( \hat{p}-\pi  \right)^2
-			}}{B} = \ell_{UC}^2
-		$
-
-		\subsection{Color Loss}
-
-		TRITON is very robust to geomtric imperfections. However, sometimes it takes this a bit too far - it can overfit textures onto the wrong objects and still maintain consistency.
-		In one example, it manages to map an apple texture onto a cube.
-
-		To help TRITON correctly match textures to objects, we introduce a small amount of supervision by adding a color loss.
-I'm going to stop writing this because I don't know if I even want to keep this in the paper...you can achieve the same result by running the algorithm multiple times, and so its not strictly nessecary.
-
-		ASK MICHAEL: I'd rather not mention this entire section and run out the page limit...it's not very important, and not used in the robot experiments.
-It's only used in the experiment with the five items including the apple.
-Can we add it to the appendix instead?
-
-\section*{Graveyard}
-
-Here I put things I won't include in the paper or appendix, but want to keep for reference until submission
-
-\begin{figure}[H]
-	\begin{center}
-		\includegraphics[width=200pt]{../images/dataset_explanation.pdf}
-	\end{center}
-	\caption{
-		Compatible datasets have two sets of images: a set of UVL scenes and a set of photographs.
-		TRITON is a sim-to-real image translation algorithm, taking in synthetic UVL scenes and aiming to create realistic fake photographs. 
-		Being an unsupervised algorithm, there are no correspondences between synthetic and real images.
-		In this dataset, three alphabet cubes are moved around the table. 
-		The synthetic and rear cameras have the same position and field of view.
-		There are many more UVL scenes than photos because synthetic scenes can be generated automatically whereas photos require real-world labor.
-		}
-	\label{fig:dataset_explanation}
-\end{figure}
-
-\section*{Things to Ask Michael}
-
-QUESTIONS FOR MICHAEL:
-\begin{itemize}
-	\item - TODO: WE MAINTAIN WHAT WE NOW CALL "SURFACE CONSISTENCY" instead of view consistency! Or texture consistency? Etc? What should we call it?
-\end{itemize}
-
-\end{document}
+\subsection{More Results}

### 2022-06-22 CORL/example.tex
Added appendix.tex
Corrected mistake: similarity loss ranges from -1 to 1

@@
 	\subsection{Neural Neural Texture Projection}
+	\label{sec:neural_tex}
 	\vspace{-3pt}
@@
 		% Given two tensors $x$ and $y$, their similarity loss is $\mu\left((x-y)^2\right) - \text{msssim}(x,y)$. 
-		We define an image similarity loss $\similar$ between two images $x,y$ that returns a score between 0 and 1, where 0 means perfect similarity:
+		We define an image similarity loss $\similar$ between two images $x,y$ that returns a score between -1 and 1, where 0 means perfect similarity:
 		\begin{equation}
@@
     \vspace{-10pt}
-    \includegraphics[width=.8\textwidth]{images/sim2real_framework.pdf}
+    \includegraphics[width=.8\textwidth]{../images/sim2real_framework.pdf}
     \vspace{-10pt}
@@
     \vspace{-3pt}
-    \includegraphics[width=.95\textwidth]{images/sim2real_res.pdf}
+    \includegraphics[width=.95\textwidth]{../images/sim2real_res.pdf}
     \vspace{-5pt}
@@
 
+\clearpage
+
+\input{appendix.tex}
+
 \begin{comment}
-
 \clearpage

### 2022-06-22 CORL/appendix.tex
Updated appendix.tex

@@
 
-\subsection{Neural Neural Textures}
+\subsection{Neural Neural Textures: More Details}
 
 	In section \ref{sec:neural_tex}, we mentioned that neural neural textures learn better than raster neural textures. 
-	Neural neural textures don't have a specific resolution: they are continuously defined over the UV domain.
-	With raster-based textures, only the side of an object that currently is seen in a view is allowed to change during each update, because the gradient can't be propogated into pixels
+	TRITON can be ablated to use raster textures. Let's call this version ``Raster TRITON''. 
+	Raster TRITON is extremely sensitive to the resolution of its neural texture, and can be numerically unstable if that resolution is too high.
+	In comparison, regular TRITON's neural neural textures don't have a specific resolution: they are continuously defined over the UV domain using fourier feature networks.
 
-	The trained fourier-feature textures also exhibit less noise than its raster counterparts.
+	\begin{figure}[H]
+		\begin{center}
+			\includegraphics[width=230pt]{../images/raster_texture_resolution_comparisons.pdf}
+		\end{center}
+		\caption{
+			The resolution of the raster neural texture seriously impacts performance in ``Raster TRITON''. Each column has a different neural texture resolution.
+			The neural texture only looks like the translation when the resolution is low.
+		}
+		\label{fig:raster_texture_resolution_comparisons}
+	\end{figure}
 
-	[[Insert figure showing the raster textures after training]]
+	In this paragraph we offer possible explanations for these observations.
+	With raster-based textures, only the side of an object that currently is seen in a view is allowed to change during each update, because the gradient can't be propogated into pixels that aren't seen.
+	If this means changing overall brightness of an object for example, the brightness of that object can't be changed over the entire object until every side has been seen - which won't happen in a single iteration, since the batch size is limited.
 
-\subsection{Unprojection Consistency Details}
+	In addition to not propogating the gradient to unseen sides of objects, it also can't propogate to texels in-between the UVL values seen in a scene image.
+	When the raster neural texture is too large, aliasing effects occur: if you have a raster texture with very high resolution, the loss gradient is less likely to be passed to a given texel because the chance that a given UV value in a scene will be rounded to that pixel's coordinates is very small.
+	In practice, this makes large raster neural textures unstable and limits us to using small amounts of detail.
+	With neural neural textures, this aliasing problem is mostly mitigated, because when a certain texture receives a gradient at particular UV coordinates, the areas of the texture between those coordinates are also changed.
 
-	Also, the resolution of the unprojection matters:
+\subsection{Unprojection Consistency Loss: More Details}
+
+	Here, we give more details about unprojection consistency loss $\lUC$.
+
+	The exact equation for $\lUC$ is as follows:
+	to formally define $\lUC$ we define unprojections $\unprojection^{1...N,1...L}$ and mean unprojections (aka recovered textures) $\bar{\unprojection}^{1...L}$ 
+	with each $\unprojection^{n,i}\in\real^{3\times128\times128}$:
+	%Jinghyan's Version (uses expectation)
+	% \begin{equation}
+	% 	\unprojection_{U,V}^{n,i}=\expectation\ph_{x,y}^n 
+	% 	\eqand \bar{\unprojection}^i_{u,v}   =   
+	% 		\frac{1}{N} \lsum_n\unprojection^{n,i}_{u,v} 
+	% 	\eqand 
+	% 	%\lUC=\frac{\lsum_{i,U,V}
+	% 	%\sqrt[]{\frac{1}{N}\lsum_n\left(\bar{\unprojection}^i_{u,v}-\unprojection^{i,n}_{U,V}\right)^2}}
+	% 	%{128\cdot128\cdot L}
+	% 	\lUC=\mathbb{E}\left[
+	% 	\sqrt[]{\frac{1}{N}\lsum_n\left(\bar{\unprojection}^i_{u,v}-\unprojection^{i,n}_{U,V}\right)^2} \right]
+	% \end{equation}
+	%
+	%
+	%Unabbreviated: Not Jinguan's version; 
+	\begin{equation}
+		\unprojection_{c,U,V}^{n,i}=\expectation\ph_{c,x,y}^n 
+		\eqand \bar{\unprojection}^i_{c,u,v}   =   
+			\frac{1}{N} \lsum_{n=1}^N\unprojection^{n,i}_{c,u,v} 
+		\eqand 
+		\lUC=\frac{\lsum_{i=1}^L\lsum_{c=1}^3\lsum_{U=1}^{128}\lsum_{V=1}^{128}
+		\sqrt[]{\frac{1}{N}\lsum_{n=1}^N\left(\bar{\unprojection}^i_{c,u,v}-\unprojection^{i,n}_{c,U,V}\right)^2}}
+		{3\cdot128\cdot128\cdot L}
+	\end{equation}
+	where $U=\lfloor128u\rfloor$ and $V=\lfloor128v\rfloor$ and $i=I(l)$ with
+	%  $(u,v,l)=s^n_{1...3,x,y}$
+	$u=s^n_{1,x,y}$, $v=s^n_{2,x,y}$, $l=s^n_{3,x,y}$
+	for all 
+	$n \in \{1...N\}$ , 
+	$i \in \{1...L\}$ , 
+	$x \in \{1...W\}$ , 
+	$y \in \{1...H\}$ , 
+	$U \in \{1...128\}$ , 
+	$V \in \{1...128\}$.
+
+	\bigskip
+
+	The hyperparameter 128 we described in section \ref{sec:unprojection_consistency_loss} refers to the resolution of the unprojections used to calculate $\lUC$.
+	In figure \ref{fig:unprojection_resolution_comparison} we see that if we were to set it higher, the gradient wouldn't affect the neural texture as densely.
 
@@
 		\caption{
-			The resolution of an unprojection matters for unprojection consistency loss.
-The larger it is, the more precise the alignment will be but the less likely a given UV value is to be assigned a loss greater than 0, lowering numerical instability.
+			Here, we unproject a single translation $\ph^i$.
+The resolution of the unprojection matters for unprojection consistency loss.
+The larger it is, the more precise the alignment will be but the less likely a given UV value is to be assigned a loss greater than 0, creating numerical instability and slowing down learning.
+			When the unprojection resolution is too high, only a few areas of the neural texture will receive a gradient during backpropogation. In practice we use the resolution $128\times128$.
 		}

### 2022-06-22 CORL/example.tex
Updates from Overleaf

--- 2022-06-22 CORL/example.tex
@@
 % \title{TRITON: Globally Consistent Sim-to-Real Transfer
-\title{\mbox{TRITON: Neural Neural Textures for Better Sim2Real}
+%\title{\mbox{TRITON: Neural Neural Textures for Better Sim2Real}}
+\title{Neural Texture Fields from Unpaired Images for Better? Realistic? Sim2Real}
 %``I Can't Believe It's Not Real!''%Definitely gonna delete this lol
 %via Neural Textures
-}
 
@@
 	\begin{center}
-		\includegraphics[width=.9\textwidth]{../images/frame_inconsistency.pdf}
+		\includegraphics[width=.9\textwidth]{../images/frame_inconsistency_diagram.png}
 	\end{center}

### 2022-06-23 CORL/appendix.tex
Appendix: Added subsection{Training Procedures}

@@
 	%Unabbreviated: Not Jinguan's version; 
-	\begin{equation}
+	\begin{multline}
 		\unprojection_{c,U,V}^{n,i}=\expectation\ph_{c,x,y}^n 
@@
 			\frac{1}{N} \lsum_{n=1}^N\unprojection^{n,i}_{c,u,v} 
-		\eqand 
+		\eqand \\
 		\lUC=\frac{\lsum_{i=1}^L\lsum_{c=1}^3\lsum_{U=1}^{128}\lsum_{V=1}^{128}
@@
 		{3\cdot128\cdot128\cdot L}
-	\end{equation}
+	\end{multline}
 	where $U=\lfloor128u\rfloor$ and $V=\lfloor128v\rfloor$ and $i=I(l)$ with
@@
 
-\subsection{More Results}
+\subsection{Training Procedures}
+
+	In this section we detail the training procedures used to create results in section \ref{sec:results} from Triton, CycleGAN, CUT,
+		TRITON w/o $\lUC$ (aka TRITON with neither unprojection consistency loss nor texture reality loss), and
+		TRITON w/o $\psi, \lUC$ (aka TRITON without textures, and therefore also without unprojection consistency loss or texture reality loss).
+
+	\subsubsection{TRITON}
+	\label{par:triton}
+	We train TRITON for 200,000 iterations on all datasets. This takes about 36-48 hours on an NVIDIA RTX A5000. 
+	The dimension of each input scene is defined by hyperparameter height $H$; the width is scaled to match the aspect ratio of the original input.
+	To avoid running out of video memory, we randomly crop each input to a $256\times256$ subset and run TRITON on that cropped input.
+	We use batch size 5 during training.
+
+	We found that the best way to train TRITON is to start with smaller $H$ values and progressively increase that value during training.
+	For the first 50,000 iterations we use $H=320$, then for the next 50,000 iterations $H=420$, then for the last 100,000 iterations $H=\text{(the height of the original input scene)}$.
+
+	\subsubsection{TRITON w/o $\lUC$}
+	\label{par:triton_without_luc}
+	This ablation is also known as ``Texture-Only'' TRITON, because it has a learnable texture $\psi$ but no consistency losses.
+	Its trained the same way that we train TRITON normally as discussed above in \ref{par:triton}, except the surface consistency losses $\lUC$ and $\lTR$ are omitted.
+	Effectively, it performs better than MUNIT-like TRITON (aka TRITON w/o $\psi, \lUC$, discussed in \ref{par:munit_triton})
+	% It still has a learnable texture $\psi$ though, which is allowed to change however it likes.
+
+	\subsubsection{TRITON w/o $\psi, \lUC$}
+	\label{par:munit_triton}
+	This ablation is very similar to MUNIT, as TRITON is based on MUNIT and this ablation has neither learnable texture nor consistency losses.
+	Like in subsection \ref{par:triton_without_luc}, this ablation shares the same training procedures as TRITON.
+
+	\subsubsection{CycleGAN}
+	\label{par:cyclegan}
+	We use the original implementation of CycleGAN, and stick to the reccomended 200 epochs, as it tends to overfit if you go further. 
+	For our tests, we run CycleGAN on multiple different scales of the input scenes, with input sizes $286\times286$ (CycleGAN's default), $320\times320$, $420\times420$ and $512\times512$. 
+	After translation, we stretch the image into the input's aspect ratio.
+	We also set $\lambda_{identity}=0$, meaning we disable the identity loss.
+	The reported results are the calculated using the best results among these resolutions.
+	This dramatically improves CycleGAN's performance when translating UVL scenes to photographs, as this loss was built with the assumption that some parts of the input should not be changed during translation (which is not true in our case).
+
+	\subsubsection{CUT}
+	\label{par:cut}
+	We use the original implementation of CUT, and stick to the reccomended 400 epochs, as it tends to overfit if you go further. 
+	Like with CycleGAN in \ref{par:cyclegan}, we run CUT on multiple different resolutions of the input scenes, with input sizes $286\times286$ (CUT's default), $320\times320$, $420\times420$ and $512\times512$.
+	After translation, we stretch the image into the input's aspect ratio.
+	The reported results are the calculated using the best results among these resolutions.

### 2022-06-23 CORL/example.tex
Updates from Overleaf

--- 2022-06-22 CORL/example.tex
@@
 
-\usepackage[final]{corl_2022} % Use this for the initial submission.
+\usepackage[preprint]{corl_2022} % Use this for the initial submission.
 % \usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
@@
 % \title{TRITON: Globally Consistent Sim-to-Real Transfer
-\title{\mbox{TRITON: Neural Neural Textures for Better Sim2Real}
+\title{Neural Neural Textures Make Sim2Real Consistent}
+% \title{Neural Texture Fields from Unpaired Images for Better? Realistic? Sim2Real}
 %``I Can't Believe It's Not Real!''%Definitely gonna delete this lol
 %via Neural Textures
-}
 
@@
 	Stony Brook, NY 11794 \\
-	\texttt{\{rburgert,mryoo\}@cs.stonybrook.edu} \\
+	\texttt{\{rburgert,jishang, xiangli8, mryoo\}@cs.stonybrook.edu} \\
 	% \And
@@
 In contrast, our algorithm takes in scenes where several objects are placed in different places or deformed, so that one static  global 3d model of the environment is not sufficient to accomplish our tasks.
-In addition, TRITON uses a new type of neural texture called a ``neural neural texture'', which is represented continuously using a fourier feature network, as described in \citep{fourier_feature_networks}.
+In addition, TRITON uses a new type of neural texture called a ``neural neural texture'', which is represented continuously using a fourier feature network, as described in \citet{fourier_feature_networks}.
 
@@
 where $\hat{a}_j$ and $a_j$ are replicated and target joint angles respectively, and $j$ is the joint index.
-We use an xArm robot which has 7 joints.
+We use an xArm robot which has seven joints.
 We also attached patterns and tapes on the robot to make its texture more challenging to model.

### 2022-06-23 CORL/appendix.tex
Updates from Overleaf
Added appendix stuff

@@
 		\begin{center}
-			\includegraphics[width=230pt]{../images/raster_texture_resolution_comparisons.pdf}
+			\includegraphics[width=400pt]{../images/raster_texture_resolution_comparisons.pdf}
 		\end{center}
@@
 		\caption{
-			Here, we unproject a single translation $\ph^i$.
+			Here, we unproject a single fake photo $\ph^i$.
 The resolution of the unprojection matters for unprojection consistency loss.
@@
 	The reported results are the calculated using the best results among these resolutions.
+
+\subsection{More Results}
+
+	\subsubsection{Unprojection Comparisons}
+
+		In this section we expand on the results in subsection \ref{sec:datasetsresults} by showing the mean unprojection for different image translation algorithms.
+With the 14 UVL images and corresponding fake photos (or photos) as calculated in \ref{sec:datasetsresults}, we average their unprojections.
+		If a translation algorithm is consistent, these unprojections should align well and the average $bar{\omega}$ should not be blurry.
+
+		\begin{figure}[H]
+			\begin{center}
+				\includegraphics[width=400pt]{../images/unprojection_comparisons.pdf}
+			\end{center}
+			\caption{
+				In this figure, we compare the mean unprojections $\bar{\omega}$ of the 14 labeled images between different algorithms, and compare it to a ground truth.
+In this diagram, we align all the unprojections to make them easier to compare.
+Note how TRITON is more crisp and matches the unprojected photographs better than the other algorithms, which are blurrier and have the wrong colors and letters on each side of the alphabet blocks.
+CycleGAN and CUT for example incorrectly duplicate letters between alphabet blocks.
+			}
+			\label{fig:unprojection_resolution_comparison}
+		\end{figure}

### 2022-06-23 CORL/appendix.tex
Fixed spelling errors

@@
 	In this paragraph we offer possible explanations for these observations.
-	With raster-based textures, only the side of an object that currently is seen in a view is allowed to change during each update, because the gradient can't be propogated into pixels that aren't seen.
+	With raster-based textures, only the side of an object that currently is seen in a view is allowed to change during each update, because the gradient can't be propagated into pixels that aren't seen.
 	If this means changing overall brightness of an object for example, the brightness of that object can't be changed over the entire object until every side has been seen - which won't happen in a single iteration, since the batch size is limited.
 
-	In addition to not propogating the gradient to unseen sides of objects, it also can't propogate to texels in-between the UVL values seen in a scene image.
+	In addition to not propagating the gradient to unseen sides of objects, it also can't propagate to texels in-between the UVL values seen in a scene image.
 	When the raster neural texture is too large, aliasing effects occur: if you have a raster texture with very high resolution, the loss gradient is less likely to be passed to a given texel because the chance that a given UV value in a scene will be rounded to that pixel's coordinates is very small.
@@
 	\label{par:cut}
-	We use the original implementation of CUT, and stick to the reccomended 400 epochs, as it tends to overfit if you go further. 
+	We use the original implementation of CUT, and stick to the recommended 400 epochs, as it tends to overfit if you go further. 
 	Like with CycleGAN in \ref{par:cyclegan}, we run CUT on multiple different resolutions of the input scenes, with input sizes $286\times286$ (CUT's default), $320\times320$, $420\times420$ and $512\times512$.

### 2022-06-23 CORL/example.tex
Added appendix stuff
Updates from Overleaf
Fixed spelling errors

@@
 \author{%
-	Ryan Burgert, Jinghuan Shang, Xiang Li, Michael S. Ryoo\\
+	Ryan Burgert \quad Jinghuan Shang \quad Xiang Li \quad Michael S. Ryoo\\
 	Department of Computer Science\\
@@
 	\vspace{-3pt}
-		\begin{figure}[thbp]
+		\begin{figure}[t]
 		    \vspace{-5pt}
 			\begin{center}
-				\includegraphics[width=0.6\textwidth]{../images/learnable_textures.pdf}
+				\includegraphics[width=0.8\textwidth]{../images/learnable_textures.pdf}
 			\end{center}
@@
 			}
-			\vspace{-10pt}
+			\vspace{-3pt}
 			% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
@@
 \subsection{Datasets}
+\label{sec:datasetsresults}
 \vspace{-2pt}
@@
 
-		TRITON is very robust to geomtric imperfections. However, sometimes it takes this a bit too far - it can overfit textures onto the wrong objects and still maintain consistency.
+		TRITON is very robust to geometric imperfections. However, sometimes it takes this a bit too far - it can over-fit textures onto the wrong objects and still maintain consistency.
 		In one example, it manages to map an apple texture onto a cube.
@@
 		To help TRITON correctly match textures to objects, we introduce a small amount of supervision by adding a color loss.
-I'm going to stop writing this because I don't know if I even want to keep this in the paper...you can achieve the same result by running the algorithm multiple times, and so its not strictly nessecary.
+I'm going to stop writing this because I don't know if I even want to keep this in the paper...you can achieve the same result by running the algorithm multiple times, and so its not strictly necessary.
 

### 2022-06-23 CORL/appendix.tex
Fixed spelling error

@@
 	Raster TRITON is extremely sensitive to the resolution of its neural texture, and can be numerically unstable if that resolution is too high.
-	In comparison, regular TRITON's neural neural textures don't have a specific resolution: they are continuously defined over the UV domain using fourier feature networks.
+	In comparison, regular TRITON's neural neural textures don't have a specific resolution: they are continuously defined over the UV domain using Fourier feature networks.
 

### 2022-06-23 CORL/appendix.tex
Added videos section
Updates from Overleaf

@@
 	In section \ref{sec:neural_tex}, we mentioned that neural neural textures learn better than raster neural textures. 
-	TRITON can be ablated to use raster textures. Let's call this version ``Raster TRITON''. 
+	We compare TRITON against its variant using raster textures (Raster TRITON).
+% 	TRITON can be ablated to use raster textures. Let's call this version ``Raster TRITON''. 
 	Raster TRITON is extremely sensitive to the resolution of its neural texture, and can be numerically unstable if that resolution is too high.
@@
 		\caption{
-			The resolution of the raster neural texture seriously impacts performance in ``Raster TRITON''. Each column has a different neural texture resolution.
-			The neural texture only looks like the translation when the resolution is low.
+			The resolution of the raster neural texture seriously impacts performance in Raster TRITON. Each column has a different neural texture resolution.
+			The neural texture in Raster TRITON only looks like the translation when the resolution is low. In comparison, TRITON with neural neural textures works better.
 		}
@@
 	In this paragraph we offer possible explanations for these observations.
-	With raster-based textures, only the side of an object that currently is seen in a view is allowed to change during each update, because the gradient can't be propagated into pixels that aren't seen.
-	If this means changing overall brightness of an object for example, the brightness of that object can't be changed over the entire object until every side has been seen - which won't happen in a single iteration, since the batch size is limited.
+	With raster-based textures, only the side of an object that currently is seen in a view is allowed to change during each update, because the gradient is not being propagated into pixels that are not seen.
+	For example, if the overall brightness of an object is changed, the brightness of that object in network representation can not be changed over the entire object until every side has been seen.
+This usually will not happen in a single iteration as the batch size is limited.
 
-	In addition to not propagating the gradient to unseen sides of objects, it also can't propagate to texels in-between the UVL values seen in a scene image.
+	In addition to not propagating the gradient to unseen sides of objects, using raster-based textures also can not propagate to texels in-between the UVL values seen in a scene image.
 	When the raster neural texture is too large, aliasing effects occur: if you have a raster texture with very high resolution, the loss gradient is less likely to be passed to a given texel because the chance that a given UV value in a scene will be rounded to that pixel's coordinates is very small.

### 2022-06-23 CORL/appendix.tex
Added neural neural texture evaluation to appendix

--- 2022-06-23 CORL/appendix.tex
@@
 
+	During evaluation, we render the neural neural texture onto a raster grid of pixels.
+Because the neural neural texture has a 2d manifold, it can be closely approximated by an RGB image.
+Using this method lets us avoid evlauating $\psi$'s fourier feature network on every frame by using a raster image as a lookup table.
+This decreases video memory usage and speeds up calulations during inference.
+
 	\subsubsection{TRITON w/o $\lUC$}
@@
 		\end{figure}
+
+	\subsubsection{Videos}
+
+		We have created animations using TRITON to see how consistency helps:
+
+		https://youtu.be/fuTSta_M6NQ

### 2022-06-23 CORL/appendix.tex
Overleaf Merge

--- 2022-06-23 CORL/appendix.tex
@@
+\appendix
+
 \section{Appendix} 
+\subsection{Videos for Qualitative Evaluation}
+
+	We have created animations using TRITON to see how consistency helps:
+
+	\url{https://youtu.be/fuTSta_M6NQ}
 
@@
 
-	In section \ref{sec:neural_tex}, we mentioned that neural neural textures learn better than raster neural textures. 
+	In Section \ref{sec:neural_tex}, we mentioned that neural neural textures learn better than raster neural textures. 
 	We compare TRITON against its variant using raster textures (Raster TRITON).
@@
 	Raster TRITON is extremely sensitive to the resolution of its neural texture, and can be numerically unstable if that resolution is too high.
-	In comparison, regular TRITON's neural neural textures don't have a specific resolution: they are continuously defined over the UV domain using Fourier feature networks.
+	In comparison, regular TRITON's neural neural textures do not have a specific resolution: they are continuously defined over the UV domain using Fourier feature networks.
 
@@
 
-	The hyperparameter 128 we described in section \ref{sec:unprojection_consistency_loss} refers to the resolution of the unprojections used to calculate $\lUC$.
-	In figure \ref{fig:unprojection_resolution_comparison} we see that if we were to set it higher, the gradient wouldn't affect the neural texture as densely.
+	The hyperparameter 128 we described in Section \ref{sec:unprojection_consistency_loss} refers to the resolution of the unprojections used to calculate $\lUC$.
+	In Figure \ref{fig:unprojection_resolution_comparison} we see that if we were to set it higher, the gradient wouldn't affect the neural texture as densely.
 
@@
 
-	In this section we detail the training procedures used to create results in section \ref{sec:results} from Triton, CycleGAN, CUT,
-		TRITON w/o $\lUC$ (aka TRITON with neither unprojection consistency loss nor texture reality loss), and
-		TRITON w/o $\psi, \lUC$ (aka TRITON without textures, and therefore also without unprojection consistency loss or texture reality loss).
+	In this section we detail the training procedures used to create results in Section \ref{sec:results} from TRITON, CycleGAN, CUT,
+		TRITON w/o $\lUC$ (i.e., TRITON with neither unprojection consistency loss nor texture reality loss), and
+		TRITON w/o $\psi, \lUC$ (i.e., TRITON without textures, and therefore also without unprojection consistency loss or texture reality loss).
 
@@
 
-	\subsubsection{TRITON w/o $\lUC$}
+	\subsubsection{TRITON w/o $\lUC, \lTR$}
 	\label{par:triton_without_luc}
@@
 
-	\subsubsection{TRITON w/o $\psi, \lUC$}
+	\subsubsection{TRITON w/o $\psi, \lUC, \lTR$}
 	\label{par:munit_triton}
@@
 
-		In this section we expand on the results in subsection \ref{sec:datasetsresults} by showing the mean unprojection for different image translation algorithms.
-With the 14 UVL images and corresponding fake photos (or photos) as calculated in \ref{sec:datasetsresults}, we average their unprojections.
-		If a translation algorithm is consistent, these unprojections should align well and the average $bar{\omega}$ should not be blurry.
+		Here, we expand on the results in Subsection \ref{sec:datasetsresults} by showing the mean unprojection for different image translation algorithms (Figure \ref{fig:unprojection_comparisons}).
+With the 14 UVL images and corresponding fake photos (or photos) as calculated in Section \ref{sec:datasetsresults}, we average their unprojections.
+		If a translation algorithm is consistent, these unprojections should align well and the average $\bar{\omega}$ should not be blurry.
 
@@
 			}
-			\label{fig:unprojection_resolution_comparison}
+			\label{fig:unprojection_comparisons}
 		\end{figure}

### 2022-06-23 CORL/example.tex
Overleaf Merge

@@
 		TRITON consistently outputs high quality results over different object arrangements. 
-		``TRITON texture only'' stands for TRITON without two surface consistency losses $\lUC$ and $\lTR$.
+		``TRITON Texture-Only'' stands for TRITON without two surface consistency losses $\lUC$ and $\lTR$.
 		% Each column of images is a different image translation algorithm.
@@
 
+\acknowledgments{We thank Srijan Das and Kanchana Ranasinghe for valuable discussions. This work was supported by the National Science Foundation (IIS-2104404 and CNS-2104416).}
 %===============================================================================
@@
 
-\clearpage
+% \clearpage
 % The acknowledgments are automatically included only in the final and preprint versions of the paper.
-\acknowledgments{}
 
@@
 
-\clearpage
+% \clearpage
 
@@
 
-\section{Appendix} 
+\section*{Appendix} 
 \label{sec:appendix}

### 2022-06-24 CORL/appendix.tex
Added optimizer details

--- 2022-06-23 CORL/appendix.tex
@@
 
+	Like in \cite{surgical_video_translation}, we use three Adam optimizers: two for the translation module's encoders and decoders, and another for the neural texture.
+	For the translation module's optimizers, we use learning rate $\num{1e-4}$, and for the neural neural texture we use learning rate $\num{1e-3}$. 
+	Every 100,000 iterations all learning rates are halved.
 	During evaluation, we render the neural neural texture onto a raster grid of pixels.

### 2022-06-24 CORL/appendix.tex
Added lTR everywhere we say w/o lUC

@@
 	In this section we detail the training procedures used to create results in section \ref{sec:results} from Triton, CycleGAN, CUT,
-		TRITON w/o $\lUC$ (aka TRITON with neither unprojection consistency loss nor texture reality loss), and
-		TRITON w/o $\psi, \lUC$ (aka TRITON without textures, and therefore also without unprojection consistency loss or texture reality loss).
+		TRITON w/o $\lUC,\lTR$ (aka TRITON with neither unprojection consistency loss nor texture reality loss), and
+		TRITON w/o $\psi, \lUC,\lTR$ (aka TRITON without textures, and therefore also without unprojection consistency loss or texture reality loss).
 
@@
 	Every 100,000 iterations all learning rates are halved.
+
 	During evaluation, we render the neural neural texture onto a raster grid of pixels.
@@
 
-	\subsubsection{TRITON w/o $\lUC$}
+	\subsubsection{TRITON w/o $\lUC,\lTR$}
 	\label{par:triton_without_luc}
@@
 	Its trained the same way that we train TRITON normally as discussed above in \ref{par:triton}, except the surface consistency losses $\lUC$ and $\lTR$ are omitted.
-	Effectively, it performs better than MUNIT-like TRITON (aka TRITON w/o $\psi, \lUC$, discussed in \ref{par:munit_triton})
+	Effectively, it performs better than MUNIT-like TRITON (aka TRITON w/o $\psi, \lUC,\lTR$, discussed in \ref{par:munit_triton})
 	% It still has a learnable texture $\psi$ though, which is allowed to change however it likes.
 
-	\subsubsection{TRITON w/o $\psi, \lUC$}
+	\subsubsection{TRITON w/o $\psi, \lUC,\lTR$}
 	\label{par:munit_triton}

### 2022-06-24 CORL/example.tex
Added optimizer details
Added lTR everywhere we say w/o lUC

@@
 \usepackage{comment}
+\usepackage{siunitx}
 
@@
     \caption{Evaluation results of sim2real robot learning.
-We compare TRITON against two baselines and one TRITON variant w/o $\ell_{UC}$ across 3 different input image resolutions.
+We compare TRITON against two baselines and one TRITON variant w/o $\psi,\ell_{UC},\lTR$ across 3 different input image resolutions.
 TRITON outperforms CycleGAN~\cite{cyclegan} and CUT~\cite{cut} consistently across (a) all resolutions and (b) unseen viewpoints.
@@
 From Figure~\ref{fig:sim2real}(b), we confirm that TRITON outperforms the others also in the Unseen setting, showing that TRITON learns image translations that are generalizable to new viewpoints while others are limited.
-In the comparison against TRITON w/o $\ell_{UC}$, TRITON outperforms this variant consistently except the lowest resolution.
-This again shows the effectiveness of $\ell_{UC}$ to generate photo-realistic images, and such high quality images are important in higher resolutions for sim2real transfer.
+In the comparison against TRITON w/o $\psi,\ell_{UC},\lTR$, TRITON outperforms this variant consistently except the lowest resolution.
+This again shows the effectiveness of $\psi$, $\ell_{UC}$ and $\lTR$ to generate photo-realistic images, and such high quality images are important in higher resolutions for sim2real transfer.
 

### 2022-06-24 CORL/example.tex
Added neural neural texture paragraph

@@
 % TRITON is robust to small camera variations, and can recover crisp textures even if the geometry isn't perfect.
+
+% The three main technical contributions of this paper are our neural neural texture, and two separately sufficient surface consistency losses.
+One of the main contributions of this paper is our `neural neural texture'.
+Inspired by previous works, TRITON uses raster-based neural textures to create realistic images \cite{deferred_neural_rendering,surgical_video_translation}.
+Unlike those works however, we do not use a pixel-based neural texture.
+Instead, we use what we call a ``neural neural texture'': a continuous implicit pixelless parametric texture represented by a neural netork using fourier features \cite{fourier_feature_networks} that takes in 2d UV coordinates and outputs colors.
 

### 2022-06-24 CORL/appendix.tex
Added robot arm animation

@@
 
-		We have created animations using TRITON to see how consistency helps:
+		In this section we have links to animations that help demonstrate various aspects of TRITON.
+		If you are viewing this document on a computer, click a thumbnail to view the video.
 
-		https://youtu.be/fuTSta_M6NQ
+		% https://youtu.be/fuTSta_M6NQ
+
+		\begin{figure}[H]
+			\begin{center}
+			\href{https://youtu.be/kecK_cJgLT8}{
+					\includegraphics[width=400pt]{../images/robot_arm_animation_thumbnail.png}
+					}
+				\end{center}
+			\caption{
+				This animation shows a side-by-side comparision of different camera viewpoints of the results discussed in section \ref{sec:robotarm_results}, as well as the inputs, ground truth video, TRITON and TRITON ablation videos.
+				Url: \href{https://youtu.be/kecK_cJgLT8}{youtu.be/kecK\_cJgLT8}
+			}
+			\label{fig:robotarm_anim}
+		\end{figure}

### 2022-06-24 CORL/appendix.tex
Added algorithm comparison video

@@
 		\end{figure}
+
+		\begin{figure}[H]
+			\begin{center}
+			\href{https://youtu.be/-GSixT4shxY}{
+					\includegraphics[width=400pt]{../images/algo_comparison_thumbnail.pdf}
+					}
+				\end{center}
+			\caption{
+				This animation shows an animation of various algorithms on a dataset with 5 alphabet blocks moving around. 
+				When watching, note how the numbers on the top of the cubes in both CycleGAN and CUT change over time, while with TRITON they stay the same.
+				Url: \href{https://youtu.be/-GSixT4shxY}{youtu.be/-GSixT4shxY}
+			}
+			\label{fig:algocomparisonvideo}
+		\end{figure}

### 2022-06-24 CORL/appendix.tex
Added threedatasets video

@@
 
+\pagebreak
 	\subsubsection{Videos}
@@
 			\href{https://youtu.be/kecK_cJgLT8}{
-					\includegraphics[width=400pt]{../images/robot_arm_animation_thumbnail.png}
+					\includegraphics[width=300pt]{../images/robot_arm_animation_thumbnail.png}
 					}
@@
 			\begin{center}
-			\href{https://youtu.be/-GSixT4shxY}{
-					\includegraphics[width=400pt]{../images/algo_comparison_thumbnail.pdf}
+			\href{https://youtu.be/0t0xiVS_8D0}{
+					\includegraphics[width=300pt]{../images/algo_comparison_thumbnail.pdf}
 					}
@@
 		\end{figure}
+
+		\begin{figure}[H]
+			\begin{center}
+			\href{https://youtu.be/0t0xiVS_8D0}{
+					\includegraphics[width=300pt]{../images/ThreeDatasets.png}
+					}
+				\end{center}
+			\caption{
+				This video shows the results of TRITON applied on three of the datasets shown in figure \ref{fig:first_diagram}.
+				Url: \href{https://youtu.be/0t0xiVS_8D0}{youtu.be/0t0xiVS\_8D0}
+			}
+			\label{fig:algocomparisonvideo}
+		\end{figure}

### 2022-06-24 CORL/example.tex
Added figure0
Added robot arm animation
Updates from Overleaf

--- 2022-06-23 CORL/example.tex
@@
     \vspace{-3pt}
-    \includegraphics[width=.95\textwidth]{../images/sim2real_res.pdf}
+    \includegraphics[width=\textwidth]{../images/sim2real_res.pdf}
     \vspace{-5pt}
     \caption{Evaluation results of sim2real robot learning.
-We compare TRITON against two baselines and one TRITON variant w/o $\ell_{UC}$ across 3 different input image resolutions.
+We compare TRITON against two baselines and one TRITON variant w/o $\psi, \ell_{UC}, \ell_{TR}$ across 3 different input image resolutions.
 TRITON outperforms CycleGAN~\cite{cyclegan} and CUT~\cite{cut} consistently across (a) all resolutions and (b) unseen viewpoints.

### 2022-06-24 CORL/appendix.tex
Added small thing
Added  (aka recovered texture) clarifications

@@
 
-		In this section we expand on the results in subsection \ref{sec:datasetsresults} by showing the mean unprojection for different image translation algorithms.
+		In this section we expand on the results in subsection \ref{sec:datasetsresults} by showing the mean unprojection (aka recovered texture) for different image translation algorithms.
 With the 14 UVL images and corresponding fake photos (or photos) as calculated in \ref{sec:datasetsresults}, we average their unprojections.
@@
 			\caption{
-				In this figure, we compare the mean unprojections $\bar{\omega}$ of the 14 labeled images between different algorithms, and compare it to a ground truth.
+				In this figure, we compare the recovered textures $\bar{\omega}$ (aka mean unprojections) of the 14 labeled images between different algorithms, and compare it to a ground truth.
 In this diagram, we align all the unprojections to make them easier to compare.
@@
 				This video shows the results of TRITON applied on three of the datasets shown in figure \ref{fig:first_diagram}.
+				The top row shows the input scenes $s$, and the bottom row shows the fake photographs $\ph$.
 				Url: \href{https://youtu.be/0t0xiVS_8D0}{youtu.be/0t0xiVS\_8D0}

### 2022-06-25 CORL/appendix.tex
Pusher

@@
+\appendix
+
 \section{Appendix}
@@
 
-	In section \ref{sec:neural_tex}, we mentioned that neural neural textures learn better than raster neural textures. 
+	In Section \ref{sec:neural_tex}, we mentioned that neural neural textures learn better than raster neural textures. 
 	TRITON can be ablated to use raster textures. Let's call this version ``Raster TRITON''. 
 	Raster TRITON is extremely sensitive to the resolution of its neural texture, and can be numerically unstable if that resolution is too high.
-	In comparison, regular TRITON's neural neural textures don't have a specific resolution: they are continuously defined over the UV domain using Fourier feature networks.
+	In comparison, regular TRITON's neural neural textures do not have a specific resolution: they are continuously defined over the UV domain using Fourier feature networks.
 
@@
 	In this paragraph we offer possible explanations for these observations.
-	With raster-based textures, only the side of an object that currently is seen in a view is allowed to change during each update, because the gradient can't be propagated into pixels that aren't seen.
-	If this means changing overall brightness of an object for example, the brightness of that object can't be changed over the entire object until every side has been seen - which won't happen in a single iteration, since the batch size is limited.
+	With raster-based textures, only the side of an object that currently is seen in a view is allowed to change during each update, because the gradient can not be propagated into pixels which are not seen.
+	If this means changing overall brightness of an object for example, the brightness of that object can not be changed over the entire object until every side has been seen - which will not happen in a single iteration, since the batch size is limited.
 
-	In addition to not propagating the gradient to unseen sides of objects, it also can't propagate to texels in-between the UVL values seen in a scene image.
+	In addition to not propagating the gradient to unseen sides of objects, it also can not propagate to texels in-between the UVL values seen in a scene image.
 	When the raster neural texture is too large, aliasing effects occur: if you have a raster texture with very high resolution, the loss gradient is less likely to be passed to a given texel because the chance that a given UV value in a scene will be rounded to that pixel's coordinates is very small.
@@
 
-	In this section we detail the training procedures used to create results in section \ref{sec:results} from Triton, CycleGAN, CUT,
+	In this section we detail the training procedures used to create results in Section \ref{sec:results} from Triton, CycleGAN, CUT,
 		TRITON w/o $\lUC,\lTR$ (aka TRITON with neither unprojection consistency loss nor texture reality loss), and
@@
 
-		In this section we expand on the results in subsection \ref{sec:datasetsresults} by showing the mean unprojection (aka recovered texture) for different image translation algorithms.
+		In this section we expand on the results in Subsection \ref{sec:datasetsresults} by showing the mean unprojection (aka recovered texture) for different image translation algorithms.
 With the 14 UVL images and corresponding fake photos (or photos) as calculated in \ref{sec:datasetsresults}, we average their unprojections.
@@
 			\caption{
-				This animation shows a side-by-side comparision of different camera viewpoints of the results discussed in section \ref{sec:robotarm_results}, as well as the inputs, ground truth video, TRITON and TRITON ablation videos.
+				This animation shows a side-by-side comparison of different camera viewpoints of the results discussed in Section \ref{sec:robotarm_results}, as well as the inputs, ground truth video, TRITON and TRITON ablation videos.
 				Url: \href{https://youtu.be/kecK_cJgLT8}{youtu.be/kecK\_cJgLT8}
@@
 				When watching, note how the numbers on the top of the cubes in both CycleGAN and CUT change over time, while with TRITON they stay the same.
-				Url: \href{https://youtu.be/-GSixT4shxY}{youtu.be/-GSixT4shxY}
+				Url: \href{https://youtu.be/0t0xiVS_8D0}{youtu.be/0t0xiVS\_8D0}
 			}
@@
 			\caption{
-				This video shows the results of TRITON applied on three of the datasets shown in figure \ref{fig:first_diagram}.
+				This video shows the results of TRITON applied on three of the datasets shown in Figure \ref{fig:first_diagram}.
 				The top row shows the input scenes $s$, and the bottom row shows the fake photographs $\ph$.

### 2022-06-25 CORL/example.tex
Pusher

--- 2022-06-24 CORL/example.tex
@@
 \usepackage{siunitx}
+\usepackage{hyperref}
 
@@
 We show that TRITON generates more realistic images than other algoithms do.
-	Unpaired image translation algorithms can be used for sim2real tasks, but most fail to generate temporally consistent results.
+	Unpaired image translation algorithms can be used for sim2real tasks, but many fail to generate temporally consistent results.
 	We present a new approach that combines differentiable rendering with image translation to achieve temporal consistency over indefinite timescales, using surface consistency losses and \emph{neural neural textures}.
 	We call this algorithm TRITON (Texture Recovering Image Translation Network): an unsupervised, end-to-end, stateless sim2real algorithm that 
-	leverages the underlying 3d geometry of input scenes by generating realistic-looking learnable neural textures.
+	leverages the underlying 3D geometry of input scenes by generating realistic-looking learnable neural textures.
 	By settling on a particular texture for the objects in a scene, we ensure consistency between frames statelessly.
@@
 
+\begin{figure}[thbp]
+	\vspace{-10pt}
+	\begin{center}
+		\includegraphics[width=\textwidth]{../images/figure0.pdf}
+	\end{center}
+	\vspace{-5pt}
+	\caption{
+		TRITON is a sim2real algorithm that makes simulated scenes look photo realistic.
+Serving as a black-box module, the only input needed is an RGB image shown in the top row, which generates the output on the bottom row.
+	}
+	\label{fig:figure0}
+	\vspace{-5pt}
+\end{figure}
+
 Current sim2real image translation algorithms used for robotics \cite{retina_gan,rl_cyclegan} often have difficulty generating consistent results across large time-frames particularly when the objects in an environment are allowed to move.
 This makes training good robotic policies using such sim2real challenging.
-In this paper, we discuss an algorithm called TRITON (Texture Recovering Image Translation Network) that combines neural rendering, image translation, and two special surface consistency losses to create surface-consistent translations.
+In this paper, we discuss an algorithm called TRITON (Texture Recovering Image Translation Network) that combines neural rendering, image translation, and two special surface consistency losses to create surface-consistent translations over frames.
 We use the term surface-consistent to refer to the desirable quality of preserving the visual appearance of object surfaces as they move, or are viewed from another angles.
@@
 TRITON is applicable when we have a simulator capable of generating a realistic distribution of geometric data, but when we do not have any information about the surfaces of those objects (which we need to render realistic images).
-For example, in our experiments we use a robotic arm model provided by the manufacturer that contains no material information, and then learn to render the materials of the arm using TRITON.
-As opposed to requiring an artist to create 3d models with meaningful textures, TRITON can generate these from scratch using a set of photographs capturing the distribution of states in a simulation, without requiring any matches between domains.
+For example, in one of our experiments we use a robotic arm model provided by the manufacturer that contains no material information, and then learn to render the materials of the arm using TRITON.
+As opposed to requiring an expert/artist to create 3D models with meaningful textures, TRITON can generate these from scratch using a set of photographs capturing the distribution of states in a simulation, without requiring any matches between domains.
+That is, given a set of unpaired, unannotated real images and geometry images, TRITON learns the underlying texture of objects and surfaces appearing in the scene without any direct supervision.
 % TRITON is robust to small camera variations, and can recover crisp textures even if the geometry isn't perfect.
+
+% The three main technical contributions of this paper are our neural neural texture, and two separately sufficient surface consistency losses.
+
+We introduce the concept of \emph{neural neural texture}, which is an implicit texture representation having the form of a neural network function generating RGB values given surface coordinates.
+Unlike previous raster-based `neural textures' to create realistic images \cite{deferred_neural_rendering,surgical_video_translation}, we model surface textures as a function instead of discretized pixels.
+It is a continuous implicit pixel-less parametric texture represented by a neural network using Fourier features \cite{fourier_feature_networks} that takes in 2D UV coordinates and outputs colors.
+This is similar to how neural radiance fields (NeRF) represents a 3D scene in the form of a neural function \cite{nerf}.
+The difference is that we focus on learning textures from unpaired training images of very different scene configurations, for viewpoint as well as object motion synthesis.
+
+%One of the main contributions of this paper is our `neural neural texture'.
+%Inspired by previous works, TRITON uses raster-based neural textures to create realistic images \cite{deferred_neural_rendering,surgical_video_translation}.
+%Unlike those works however, we do not use a pixel-based neural texture.
+Instead, we use what we call a ``neural neural texture'': a continuous implicit pixelless parametric texture represented by a neural netork using fourier features \cite{fourier_feature_networks} that takes in 2d UV coordinates and outputs colors.
 
@@
 		This is an overview of what TRITON accomplishes.
-			TRITON learns the textures of 3d objects to help translate simulated images into photographs. It does this with unpaired data. Each row is a different dataset.
+		TRITON learns the textures of 3D objects to help translate simulated images into photographs. It does this with unpaired data. Each row is a different dataset.
 	}
@@
 All of these works, however, only work with static scenes.
-There are NeRF-based approaches that work on dynamic scenes \cite{dnerf,nerfies,nerualradianceflow} but none of these interactive.
+There are NeRF-based approaches that work on dynamic scenes \cite{dnerf,nerfies,nerualradianceflow} but none of these were interactive, prohibiting their usage for sim2real.
 \citet{playable_environments} is interactive, but its conditioned on learned actions and not compatible with physics simulators that would be used to train robots.
@@
 \citet{surgical_video_translation} differs from TRITON in a few very important aspects though, the biggest being that it only synthesizes new camera views, where the only difference between each scene is the placement of the camera.
-In contrast, our algorithm takes in scenes where several objects are placed in different places or deformed, so that one static  global 3d model of the environment is not sufficient to accomplish our tasks.
-In addition, TRITON uses a new type of neural texture called a ``neural neural texture'', which is represented continuously using a fourier feature network, as described in \citet{fourier_feature_networks}.
+In contrast, our algorithm takes in scenes where several objects are placed in different places or deformed, where one static global 3D model of the environment is not sufficient to accomplish our tasks.
+In addition, TRITON introduces a new type of neural texture, ``neural neural texture'', which is represented continuously using a Fourier feature network.
+%as described in \citet{fourier_feature_networks}.
 
@@
 	% TRITON stands for Texture Recovering Image Translation Network. It has two goals: to translate images, and to recover textures.
-	TRITON's goal is to turn 3d simulated images into realistic fake photographs (by training it without any matching pairs), while maintaining high surface consistency.
+	TRITON's goal is to turn 3D simulated images into realistic fake photographs (by training it without any matching pairs), while maintaining high surface consistency.
 	It does this by simultaneously learning both an image translator and a set of realistic textures.
@@
 
-	In contrast to previous works involving ``neural textures'' \cite{deferred_neural_rendering,surgical_video_translation}, TRITON can handle more than just camera movements:
+	In contrast to previous works involving neural textures \cite{deferred_neural_rendering,surgical_video_translation}, TRITON can handle more than just camera movements:
 	the positions of objects in the training data can be moved around or deformed as well between data samples.
@@
 		\caption{
-			A scene is obtained by rendering a 3d state into an image, where the first two color channels represent $u,v$ coordinates and the third channel $l$ represents object labels.
+			A scene is obtained by rendering a 3D state into an image, where the first two color channels represent $u,v$ coordinates and the third channel $l$ represents object labels.
 			% This diagram shows the purpose of a UVL image.
@@
 
-	There are two components in every dataset: A set of simulated 3d scenes, and a set of photographs.
+	There are two components in every dataset: A set of simulated 3D scenes, and a set of photographs.
 	Datasets usually have many more scenes than photographs, since scenes can be generated automatically.
@@
 
-	In this work, a scene refers to a rendered 3d simulation state - which includes the position, rotation, and deformation of every object (including the camera).
+	In this work, a scene refers to a rendered 3D simulation state - which includes the position, rotation, and deformation of every object (including the camera).
 	% Using some 3d rendering software, be it Blender or Gazebo or some other 3d creates an image from these 
-	We represent each 3d state with a simple $(r,g,b)$ image, in a simple enough format that any decent simulator should able to provide.
+	We represent each 3D state with a simple $(r,g,b)$ image, in a simple enough format that any decent simulator should able to provide.
 	% These have the same datatype and dimensions as photographs and are denoted as 
@@
 \section{Method} \label{sec:method}
-	\begin{figure}[thbp]
+	\begin{figure}[t]
 	    \vspace{-15pt}
@@
 			% \includegraphics[width=400pt]{../images/main_diagram_condensed_with_domains.pdf}
-			\includegraphics[width=0.9\textwidth]{../images/main_diagram_beautiful.pdf}
+			\includegraphics[width=\textwidth]{../images/main_diagram_beautiful.pdf}
 		\end{center}
@@
 			%
-			This figure is an overview TRITON.
+			An overview of TRITON.
 			Inputs are on the left, and outputs are on the right.
@@
 	\end{figure}
-		In this section, we describe how TRITON works to translate images from domain A (simulation) to domain B (photos) while maintaining surface consistency. 
-		TRITON introduces a learneable neural neural texture with two novel surface consistency losses to an existing image translator.
+		In this section, we describe how TRITON works to translate images from domain A (simulation) to domain B (photos) while maintaining surface consistency (Figure \ref{fig:main_diagram}). 
+		TRITON introduces a learnable neural neural texture with two novel surface consistency losses to an existing image translator.
 In the end, TRITON is able to effectively generate photorealistic images.
@@
 	\vspace{-3pt}
-		\begin{figure}[t]
-		    \vspace{-5pt}
-			\begin{center}
-				\includegraphics[width=0.8\textwidth]{../images/learnable_textures.pdf}
-			\end{center}
-			\vspace{-3pt}
-			\caption{
-				This figure details how our neural neural textures are calculated in Figure~\ref{fig:main_diagram}.
-They are fully differentiable, and represented continuously along the texture's u and v axes using Fourier feature networks.
-			}
-			\vspace{-3pt}
-			% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
-			% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
-			% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
-			\label{fig:learnable_textures}
-		\end{figure}
 
@@
 		% Using neural neural textures, we can encode features directly onto the surfaces of the 3d objects in a scene, which the image translation module uses to maintain visual consistency between states and viewpoints.
-		Instead of feeding a scene $s$ directly into the image translator $\Tab$, we first apply learnable textures $\psi$ to its surfaces as shown in Figure \ref{fig:main_diagram}.
-		Previous works called these learnable textures ``neural textures'', and were parametrized by a discrete grid of differentiable texels. 
+		Instead of feeding a scene $s$ directly into the image translator $\Tab$, we first apply learnable textures $\psi$ to its surfaces, which is learned jointly with $\Tab$. 
+		%(as illustrated in Figure \ref{fig:main_diagram}).
+		%Previous works called these learnable textures ``neural textures'', and were parametrized by a discrete grid of differentiable texels. 
 		% In contrast, we call our learnable textures ``neural nerual textures'', becuase our textures are a type of neural texture that is parametrized continuously over UV space using a neural fourier feature network.
-		In contrast, we call our learnable textures as ``neural nerual textures'', because our textures themselves are represented as a neural network function, parameterized continuously over UV space.
-		Our neural textures $\psi\toL$ are learned jointly with our image translator $T$.
+		%In contrast, we call our learnable textures as ``neural nerual textures'', because our textures themselves are represented as a neural network function, parameterized continuously over UV space.
+		%Our neural textures $\psi\toL$ are learned jointly with our image translator $T$.
 
@@
 		Given a scene $s$, we obtain projection $\pi$ by applying a texture $\psi^i \in \psi\toL$ to every pixel $(u,v,l) \in s$ individually, where texture index $i=I(l)$ is decided by the label value $l$ of that scene pixel.
+The projection $\pi$, which is an intermediate image is computed as:
 		% Each pixel in the resulting projection $rgb\in\pi$ is the result of selecting a texture index $i$ based on the rank of label value $l$, then applying $\psi^i$ to the $u,v$ values.
@@
 Subscripts mean multidimensional indexing.
+
+		\begin{figure}[t]
+		    \vspace{-5pt}
+			\begin{center}
+				\includegraphics[width=0.8\textwidth]{../images/learnable_textures.pdf}
+			\end{center}
+			\vspace{-3pt}
+			\caption{
+				Details of how our neural neural textures are calculated in Figure~\ref{fig:main_diagram}.
+They are fully differentiable, and represented continuously along the texture's u and v axes using Fourier feature networks.
+			}
+			\vspace{-3pt}
+			% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
+			% We found this method gave better results than storing each differentiable texture as a raster matrix of pixels, as well as being faster to train.
+			% During inference, you can store the results of this MLP as a raster image of arbitrarily large resolution, saving both time and VRAM.
+			\label{fig:learnable_textures}
+		\end{figure}
 
@@
 		We now discuss the implementation of our neural neural networks $\psi\toL$.
-		Each neural neural texture $\psi^i$ is a function consisting of two components: a multi-layer perceptron $M^i$ and a static set of 256 random spatial frequencies $f_{1...256} \in \real ^ {256 \times 2}$.
+		Each neural neural texture $\psi^i$ is a function consisting of two components: a multi-layer perceptron $M^i$ and a static set of 256 random spatial frequencies $f_{1...256} \in \real ^ {256 \times 2}$ (Figure \ref{fig:learnable_textures}).
 		Given a two-dimensional $(u,v)$ vector, the spatial frequencies are used to generate a high dimensional embedding of $(u,v)$ as input for $M^i$, where $M^i$ is a function $\real^{256} \to \real^{3}$ mapping that embedding to an $(r,g,b)$ color value:
@@
 		\end{equation}
-		where $g_k=f_k\cdot(u,v)$
+		where $g_k=f_k\cdot(u,v)$.
 		% , $f^i \in N_{ormal}(\mu=0,\ \sigma=10)$ is a two dimensional random gaussian vector,
-		, $f_k \in \mathcal{N}(\mu=0,\ \sigma=10)$ is a two dimensional random gaussian vector,
+		$f_k \in \mathcal{N}(\mu=0,\ \sigma=10)$ is a two dimensional random gaussian vector,
 		\mbox{and $\cdot$} is the dot product operator.
@@
 		\begin{equation}
+		\label{eq:omega}
 			\similar(x,y) = L_2(x,y)-\msssim(x,y) 
@@
 		% Up until now we have not put any constraints on this neural texture. 
-		Without $\lTR$, $\psi$ can look wildly different each time you train it.
+		$\similar$ is the image similarity from Equation \ref{eq:omega}. Without $\lTR$, $\psi$ can look wildly different each time you train it.
 		As seen in the top row of Figure \ref{fig:texture_realism_ablation}, the neural texture looks very unrealistic --- the colors are completely arbitrary.
@@
 In our setting, each dataset is composed of two sets of unpaired images: UVL scenes from a simulator and real photographs.
-Note that the images in all datasets are unpaired and UVL scenes only rely on rough 3d models of the objects in the scene without need of precisely aligning objects in the simulator to the real world.
+Note that the images in all datasets are unpaired and UVL scenes only rely on rough 3D models of the objects in the scene without need of precisely aligning objects in the simulator to the real world.
 % . They are all unpaired, and have RGB values ranging from 0 to 1.
@@
 	\begin{center}
-		\includegraphics[width=.9\textwidth]{../images/frame_inconsistency_diagram.png}
+		\includegraphics[width=\textwidth]{../images/frame_inconsistency_diagram.png}
 	\end{center}
@@
 \subsection{Sim2real Transfer for Robot Learning}
+\label{sec:robotarm_results}
 \begin{figure}[thbp]
@@
     \vspace{-10pt}
-    \includegraphics[width=.8\textwidth]{../images/sim2real_framework.pdf}
+    \includegraphics[width=\textwidth]{../images/sim2real_framework.pdf}
     \vspace{-10pt}
@@
     \vspace{-3pt}
-    \includegraphics[width=.95\textwidth]{../images/sim2real_res.pdf}
+    \includegraphics[width=\textwidth]{../images/sim2real_res.pdf}
     \vspace{-5pt}
@@
 
-% \clearpage
+\clearpage
 
@@
      	These neural textures are not stored in raster form during training.
-Instead, as illustrated in figure \ref{fig:learnable_textures}, they're paramaterized by pixel-wise fourier feature networks \cite{fourier_feature_networks} that take in UV coordinates and returns RGB colors.
+Instead, as illustrated in Figure \ref{fig:learnable_textures}, they're paramaterized by pixel-wise Fourier feature networks \cite{fourier_feature_networks} that take in UV coordinates and returns RGB colors.
 During inference, however, these textures are rasterized to save both time and video memory.
@@
 		$
-		Using $\bar{p}$ from figure \ref{fig:unprojection_consistency_loss}
+		Using $\bar{p}$ from Figure \ref{fig:unprojection_consistency_loss}
 
@@
 		Compatible datasets have two sets of images: a set of UVL scenes and a set of photographs.
-		TRITON is a sim-to-real image translation algorithm, taking in synthetic UVL scenes and aiming to create realistic fake photographs. 
+		TRITON is a sim2real image translation algorithm, taking in synthetic UVL scenes and aiming to create realistic fake photographs. 
 		Being an unsupervised algorithm, there are no correspondences between synthetic and real images.

### 2022-06-25 CORL/example.tex
Branchini\

--- 2022-06-24 CORL/example.tex
@@
 
-\usepackage[preprint]{corl_2022} % Use this for the initial submission.
+\usepackage{corl_2022} % Use this for the initial submission.
 % \usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
@@
 % \title{TRITON: Globally Consistent Sim-to-Real Transfer
-\title{Neural Neural Textures Make Sim2Real Consistent}
-% \title{Neural Texture Fields from Unpaired Images for Better? Realistic? Sim2Real}
+\title{\mbox{TRITON: Neural Neural Textures for Better Sim2Real}
 %``I Can't Believe It's Not Real!''%Definitely gonna delete this lol
 %via Neural Textures
+}
 
 \author{%
-	Ryan Burgert \quad Jinghuan Shang \quad Xiang Li \quad Michael S. Ryoo\\
+	Ryan Burgert \\
 	Department of Computer Science\\
@@
 	Stony Brook, NY 11794 \\
-	\texttt{\{rburgert,jishang, xiangli8, mryoo\}@cs.stonybrook.edu} \\
+	\texttt{rburgert@cs.stonybrook.edu} \\
 	% \And
@@
 	% \texttt{mryoo@cs.stonybrook.edu} \\
-	%\And
-%	Emma Burgert \\
-%	Ryan Burgert's Dog\\
+	\And
+	Emma Burgert \\
+	Ryan Burgert's Dog\\
 }
@@
 In contrast, our algorithm takes in scenes where several objects are placed in different places or deformed, so that one static  global 3d model of the environment is not sufficient to accomplish our tasks.
-In addition, TRITON uses a new type of neural texture called a ``neural neural texture'', which is represented continuously using a fourier feature network, as described in \citet{fourier_feature_networks}.
+In addition, TRITON uses a new type of neural texture called a ``neural neural texture'', which is represented continuously using a fourier feature network, as described in \citep{fourier_feature_networks}.
 
@@
 	\subsection{Neural Neural Texture Projection}
-	\label{sec:neural_tex}
 	\vspace{-3pt}
-		\begin{figure}[t]
+		\begin{figure}[thbp]
 		    \vspace{-5pt}
 			\begin{center}
-				\includegraphics[width=0.8\textwidth]{../images/learnable_textures.pdf}
+				\includegraphics[width=0.6\textwidth]{../images/learnable_textures.pdf}
 			\end{center}
@@
 			}
-			\vspace{-3pt}
+			\vspace{-10pt}
 			% For each texture, there is a separate Fourier feature network (Fourier features fed into a pixel-wise MLP) that will take in Fourier features as inputs, and output an RGB image using the method described in \citet{fourier_feature_networks}.
@@
 		% Given two tensors $x$ and $y$, their similarity loss is $\mu\left((x-y)^2\right) - \text{msssim}(x,y)$. 
-		We define an image similarity loss $\similar$ between two images $x,y$ that returns a score between -1 and 1, where 0 means perfect similarity:
+		We define an image similarity loss $\similar$ between two images $x,y$ that returns a score between 0 and 1, where 0 means perfect similarity:
 		\begin{equation}
@@
 \subsection{Datasets}
-\label{sec:datasetsresults}
 \vspace{-2pt}
@@
 	\begin{center}
-		\includegraphics[width=.9\textwidth]{../images/frame_inconsistency_diagram.png}
+		\includegraphics[width=.9\textwidth]{../images/frame_inconsistency.pdf}
 	\end{center}
@@
 		TRITON consistently outputs high quality results over different object arrangements. 
-		``TRITON Texture-Only'' stands for TRITON without two surface consistency losses $\lUC$ and $\lTR$.
+		``TRITON texture only'' stands for TRITON without two surface consistency losses $\lUC$ and $\lTR$.
 		% Each column of images is a different image translation algorithm.
@@
     \vspace{-10pt}
-    \includegraphics[width=.8\textwidth]{../images/sim2real_framework.pdf}
+    \includegraphics[width=.8\textwidth]{images/sim2real_framework.pdf}
     \vspace{-10pt}
@@
 where $\hat{a}_j$ and $a_j$ are replicated and target joint angles respectively, and $j$ is the joint index.
-We use an xArm robot which has seven joints.
+We use an xArm robot which has 7 joints.
 We also attached patterns and tapes on the robot to make its texture more challenging to model.
@@
     \vspace{-3pt}
-    \includegraphics[width=\textwidth]{../images/sim2real_res.pdf}
+    \includegraphics[width=.95\textwidth]{images/sim2real_res.pdf}
     \vspace{-5pt}
     \caption{Evaluation results of sim2real robot learning.
-We compare TRITON against two baselines and one TRITON variant w/o $\psi, \ell_{UC}, \ell_{TR}$ across 3 different input image resolutions.
+We compare TRITON against two baselines and one TRITON variant w/o $\ell_{UC}$ across 3 different input image resolutions.
 TRITON outperforms CycleGAN~\cite{cyclegan} and CUT~\cite{cut} consistently across (a) all resolutions and (b) unseen viewpoints.
@@
 
-\acknowledgments{We thank Srijan Das and Kanchana Ranasinghe for valuable discussions. This work was supported by the National Science Foundation (IIS-2104404 and CNS-2104416).}
 %===============================================================================
@@
 
-% \clearpage
+\clearpage
 % The acknowledgments are automatically included only in the final and preprint versions of the paper.
+\acknowledgments{}
 
@@
 
-% \clearpage
-
-\input{appendix.tex}
-
 \begin{comment}
+
 \clearpage
 
-\section*{Appendix} 
+\section{Appendix} 
 \label{sec:appendix}
@@
 
-		TRITON is very robust to geometric imperfections. However, sometimes it takes this a bit too far - it can over-fit textures onto the wrong objects and still maintain consistency.
+		TRITON is very robust to geomtric imperfections. However, sometimes it takes this a bit too far - it can overfit textures onto the wrong objects and still maintain consistency.
 		In one example, it manages to map an apple texture onto a cube.
@@
 		To help TRITON correctly match textures to objects, we introduce a small amount of supervision by adding a color loss.
-I'm going to stop writing this because I don't know if I even want to keep this in the paper...you can achieve the same result by running the algorithm multiple times, and so its not strictly necessary.
+I'm going to stop writing this because I don't know if I even want to keep this in the paper...you can achieve the same result by running the algorithm multiple times, and so its not strictly nessecary.
 
@@
 
+\appendix
+
+\section{Appendix}
+
+\subsection{Neural Neural Textures: More Details}
+
+	In Section \ref{sec:neural_tex}, we mentioned that neural neural textures learn better than raster neural textures. 
+	TRITON can be ablated to use raster textures. Let's call this version ``Raster TRITON''. 
+	Raster TRITON is extremely sensitive to the resolution of its neural texture, and can be numerically unstable if that resolution is too high.
+	In comparison, regular TRITON's neural neural textures do not have a specific resolution: they are continuously defined over the UV domain using Fourier feature networks.
+
+	\begin{figure}[H]
+		\begin{center}
+			\includegraphics[width=400pt]{../images/raster_texture_resolution_comparisons.pdf}
+		\end{center}
+		\caption{
+			The resolution of the raster neural texture seriously impacts performance in ``Raster TRITON''. Each column has a different neural texture resolution.
+			The neural texture only looks like the translation when the resolution is low.
+		}
+		\label{fig:raster_texture_resolution_comparisons}
+	\end{figure}
+
+	In this paragraph we offer possible explanations for these observations.
+	With raster-based textures, only the side of an object that currently is seen in a view is allowed to change during each update, because the gradient can not be propagated into pixels which are not seen.
+	If this means changing overall brightness of an object for example, the brightness of that object can not be changed over the entire object until every side has been seen - which will not happen in a single iteration, since the batch size is limited.
+
+	In addition to not propagating the gradient to unseen sides of objects, it also can not propagate to texels in-between the UVL values seen in a scene image.
+	When the raster neural texture is too large, aliasing effects occur: if you have a raster texture with very high resolution, the loss gradient is less likely to be passed to a given texel because the chance that a given UV value in a scene will be rounded to that pixel's coordinates is very small.
+	In practice, this makes large raster neural textures unstable and limits us to using small amounts of detail.
+	With neural neural textures, this aliasing problem is mostly mitigated, because when a certain texture receives a gradient at particular UV coordinates, the areas of the texture between those coordinates are also changed.
+
+\subsection{Unprojection Consistency Loss: More Details}
+
+	Here, we give more details about unprojection consistency loss $\lUC$.
+
+	The exact equation for $\lUC$ is as follows:
+	to formally define $\lUC$ we define unprojections $\unprojection^{1...N,1...L}$ and mean unprojections (aka recovered textures) $\bar{\unprojection}^{1...L}$ 
+	with each $\unprojection^{n,i}\in\real^{3\times128\times128}$:
+	%Jinghyan's Version (uses expectation)
+	% \begin{equation}
+	% 	\unprojection_{U,V}^{n,i}=\expectation\ph_{x,y}^n 
+	% 	\eqand \bar{\unprojection}^i_{u,v}   =   
+	% 		\frac{1}{N} \lsum_n\unprojection^{n,i}_{u,v} 
+	% 	\eqand 
+	% 	%\lUC=\frac{\lsum_{i,U,V}
+	% 	%\sqrt[]{\frac{1}{N}\lsum_n\left(\bar{\unprojection}^i_{u,v}-\unprojection^{i,n}_{U,V}\right)^2}}
+	% 	%{128\cdot128\cdot L}
+	% 	\lUC=\mathbb{E}\left[
+	% 	\sqrt[]{\frac{1}{N}\lsum_n\left(\bar{\unprojection}^i_{u,v}-\unprojection^{i,n}_{U,V}\right)^2} \right]
+	% \end{equation}
+	%
+	%
+	%Unabbreviated: Not Jinguan's version; 
+	\begin{multline}
+		\unprojection_{c,U,V}^{n,i}=\expectation\ph_{c,x,y}^n 
+		\eqand \bar{\unprojection}^i_{c,u,v}   =   
+			\frac{1}{N} \lsum_{n=1}^N\unprojection^{n,i}_{c,u,v} 
+		\eqand \\
+		\lUC=\frac{\lsum_{i=1}^L\lsum_{c=1}^3\lsum_{U=1}^{128}\lsum_{V=1}^{128}
+		\sqrt[]{\frac{1}{N}\lsum_{n=1}^N\left(\bar{\unprojection}^i_{c,u,v}-\unprojection^{i,n}_{c,U,V}\right)^2}}
+		{3\cdot128\cdot128\cdot L}
+	\end{multline}
+	where $U=\lfloor128u\rfloor$ and $V=\lfloor128v\rfloor$ and $i=I(l)$ with
+	%  $(u,v,l)=s^n_{1...3,x,y}$
+	$u=s^n_{1,x,y}$, $v=s^n_{2,x,y}$, $l=s^n_{3,x,y}$
+	for all 
+	$n \in \{1...N\}$ , 
+	$i \in \{1...L\}$ , 
+	$x \in \{1...W\}$ , 
+	$y \in \{1...H\}$ , 
+	$U \in \{1...128\}$ , 
+	$V \in \{1...128\}$.
+
+	\bigskip
+
+	The hyperparameter 128 we described in Section \ref{sec:unprojection_consistency_loss} refers to the resolution of the unprojections used to calculate $\lUC$.
+	In Figure \ref{fig:unprojection_resolution_comparison} we see that if we were to set it higher, the gradient wouldn't affect the neural texture as densely.
+
+	\begin{figure}[H]
+		\begin{center}
+			\includegraphics[width=400pt]{../images/unprojection_resolution_comparison.pdf}
+		\end{center}
+		\caption{
+			Here, we unproject a single fake photo $\ph^i$.
+The resolution of the unprojection matters for unprojection consistency loss.
+The larger it is, the more precise the alignment will be but the less likely a given UV value is to be assigned a loss greater than 0, creating numerical instability and slowing down learning.
+			When the unprojection resolution is too high, only a few areas of the neural texture will receive a gradient during backpropogation. In practice we use the resolution $128\times128$.
+		}
+		\label{fig:unprojection_resolution_comparison}
+	\end{figure}
+
+\subsection{Training Procedures}
+
+	In this section we detail the training procedures used to create results in Section \ref{sec:results} from Triton, CycleGAN, CUT,
+		TRITON w/o $\lUC,\lTR$ (aka TRITON with neither unprojection consistency loss nor texture reality loss), and
+		TRITON w/o $\psi, \lUC,\lTR$ (aka TRITON without textures, and therefore also without unprojection consistency loss or texture reality loss).
+
+	\subsubsection{TRITON}
+	\label{par:triton}
+	We train TRITON for 200,000 iterations on all datasets. This takes about 36-48 hours on an NVIDIA RTX A5000. 
+	The dimension of each input scene is defined by hyperparameter height $H$; the width is scaled to match the aspect ratio of the original input.
+	To avoid running out of video memory, we randomly crop each input to a $256\times256$ subset and run TRITON on that cropped input.
+	We use batch size 5 during training.
+
+	We found that the best way to train TRITON is to start with smaller $H$ values and progressively increase that value during training.
+	For the first 50,000 iterations we use $H=320$, then for the next 50,000 iterations $H=420$, then for the last 100,000 iterations $H=\text{(the height of the original input scene)}$.
+
+	Like in \cite{surgical_video_translation}, we use three Adam optimizers: two for the translation module's encoders and decoders, and another for the neural texture.
+	For the translation module's optimizers, we use learning rate $\num{1e-4}$, and for the neural neural texture we use learning rate $\num{1e-3}$. 
+	Every 100,000 iterations all learning rates are halved.
+
+	During evaluation, we render the neural neural texture onto a raster grid of pixels.
+Because the neural neural texture has a 2d manifold, it can be closely approximated by an RGB image.
+Using this method lets us avoid evlauating $\psi$'s fourier feature network on every frame by using a raster image as a lookup table.
+This decreases video memory usage and speeds up calulations during inference.
+
+	\subsubsection{TRITON w/o $\lUC,\lTR$}
+	\label{par:triton_without_luc}
+	This ablation is also known as ``Texture-Only'' TRITON, because it has a learnable texture $\psi$ but no consistency losses.
+	Its trained the same way that we train TRITON normally as discussed above in \ref{par:triton}, except the surface consistency losses $\lUC$ and $\lTR$ are omitted.
+	Effectively, it performs better than MUNIT-like TRITON (aka TRITON w/o $\psi, \lUC,\lTR$, discussed in \ref{par:munit_triton})
+	% It still has a learnable texture $\psi$ though, which is allowed to change however it likes.
+
+	\subsubsection{TRITON w/o $\psi, \lUC,\lTR$}
+	\label{par:munit_triton}
+	This ablation is very similar to MUNIT, as TRITON is based on MUNIT and this ablation has neither learnable texture nor consistency losses.
+	Like in subsection \ref{par:triton_without_luc}, this ablation shares the same training procedures as TRITON.
+
+	\subsubsection{CycleGAN}
+	\label{par:cyclegan}
+	We use the original implementation of CycleGAN, and stick to the reccomended 200 epochs, as it tends to overfit if you go further. 
+	For our tests, we run CycleGAN on multiple different scales of the input scenes, with input sizes $286\times286$ (CycleGAN's default), $320\times320$, $420\times420$ and $512\times512$. 
+	After translation, we stretch the image into the input's aspect ratio.
+	We also set $\lambda_{identity}=0$, meaning we disable the identity loss.
+	The reported results are the calculated using the best results among these resolutions.
+	This dramatically improves CycleGAN's performance when translating UVL scenes to photographs, as this loss was built with the assumption that some parts of the input should not be changed during translation (which is not true in our case).
+
+	\subsubsection{CUT}
+	\label{par:cut}
+	We use the original implementation of CUT, and stick to the recommended 400 epochs, as it tends to overfit if you go further. 
+	Like with CycleGAN in \ref{par:cyclegan}, we run CUT on multiple different resolutions of the input scenes, with input sizes $286\times286$ (CUT's default), $320\times320$, $420\times420$ and $512\times512$.
+	After translation, we stretch the image into the input's aspect ratio.
+	The reported results are the calculated using the best results among these resolutions.
+
+\subsection{More Results}
+
+	\subsubsection{Unprojection Comparisons}
+
+		In this section we expand on the results in Subsection \ref{sec:datasetsresults} by showing the mean unprojection (aka recovered texture) for different image translation algorithms.
+With the 14 UVL images and corresponding fake photos (or photos) as calculated in \ref{sec:datasetsresults}, we average their unprojections.
+		If a translation algorithm is consistent, these unprojections should align well and the average $bar{\omega}$ should not be blurry.
+
+		\begin{figure}[H]
+			\begin{center}
+				\includegraphics[width=400pt]{../images/unprojection_comparisons.pdf}
+			\end{center}
+			\caption{
+				In this figure, we compare the recovered textures $\bar{\omega}$ (aka mean unprojections) of the 14 labeled images between different algorithms, and compare it to a ground truth.
+In this diagram, we align all the unprojections to make them easier to compare.
+Note how TRITON is more crisp and matches the unprojected photographs better than the other algorithms, which are blurrier and have the wrong colors and letters on each side of the alphabet blocks.
+CycleGAN and CUT for example incorrectly duplicate letters between alphabet blocks.
+			}
+			\label{fig:unprojection_resolution_comparison}
+		\end{figure}
+
+\pagebreak
+	\subsubsection{Videos}
+
+		In this section we have links to animations that help demonstrate various aspects of TRITON.
+		If you are viewing this document on a computer, click a thumbnail to view the video.
+
+		% https://youtu.be/fuTSta_M6NQ
+
+		\begin{figure}[H]
+			\begin{center}
+			\href{https://youtu.be/kecK_cJgLT8}{
+					\includegraphics[width=300pt]{../images/robot_arm_animation_thumbnail.png}
+					}
+				\end{center}
+			\caption{
+				This animation shows a side-by-side comparison of different camera viewpoints of the results discussed in Section \ref{sec:robotarm_results}, as well as the inputs, ground truth video, TRITON and TRITON ablation videos.
+				Url: \href{https://youtu.be/kecK_cJgLT8}{youtu.be/kecK\_cJgLT8}
+			}
+			\label{fig:robotarm_anim}
+		\end{figure}
+
+		\begin{figure}[H]
+			\begin{center}
+			\href{https://youtu.be/0t0xiVS_8D0}{
+					\includegraphics[width=300pt]{../images/algo_comparison_thumbnail.pdf}
+					}
+				\end{center}
+			\caption{
+				This animation shows an animation of various algorithms on a dataset with 5 alphabet blocks moving around. 
+				When watching, note how the numbers on the top of the cubes in both CycleGAN and CUT change over time, while with TRITON they stay the same.
+				Url: \href{https://youtu.be/0t0xiVS_8D0}{youtu.be/0t0xiVS\_8D0}
+			}
+			\label{fig:algocomparisonvideo}
+		\end{figure}
+
+		\begin{figure}[H]
+			\begin{center}
+			\href{https://youtu.be/0t0xiVS_8D0}{
+					\includegraphics[width=300pt]{../images/ThreeDatasets.png}
+					}
+				\end{center}
+			\caption{
+				This video shows the results of TRITON applied on three of the datasets shown in Figure \ref{fig:first_diagram}.
+				The top row shows the input scenes $s$, and the bottom row shows the fake photographs $\ph$.
+				Url: \href{https://youtu.be/0t0xiVS_8D0}{youtu.be/0t0xiVS\_8D0}
+			}
+			\label{fig:algocomparisonvideo}
+		\end{figure}
+
 \end{document}
